### 2020-01-11 ForReport20200114/HandOut.Rmd
updated with template for handout

---
title: "Try Bayesian Survival Analysis using the JACC study data"
subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
author: "Chaochen Wang | Aichi Medical University"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
ctex: yes
biblio-title: Reference
bibliography: skeleton.bib
link-citations: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, include=FALSE}
library(tufte)
# tufte版本变化之后更新knitr缓存
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'), 
kable.force.latex = TRUE)
options(htmltools.dir.version = FALSE)
```

## Data preparation

Before exclusion, we have 110585 participants (46395 men and 64190 women) in the JACC data set:

<!-- 我们可以用**knitr**包中的`kable()`函数生成简单的表格。HTML输出中表格的标题也会被放在边栏中。 -->

```{r datapre, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}

library(readr)
library(tidyverse)
library(lubridate) # for dealing with date time data

MILK <- read_csv("../data/StrokeMilk.csv", 
                     progress = show_progress(), 
                     col_types = cols(.default = "c"))

MILK %>% 
  filter(tr_age > 39 & tr_age < 80) %>% 
  group_by(tr_sex) %>% 
  summarise(n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))  
# delete subjects outside of age range ------------------------------------

MILK_0 <- MILK %>%
  filter(tr_age > 39 & tr_age < 80)

MILK_0 <- MILK_0 %>% 
  mutate(Tot_Stroke = if_else(grepl("I6[0-9][0-9]|I6[0-9]",  
                                    ICD10), "I60_9", 
                        if_else(!is.na(ICD10), "other_death", 
                                      "Alive/Censor"))) %>% 
    mutate(HemoStroke = if_else(grepl("I6[0-2][0-9]|I6[0-2]",  
                                    ICD10), "I60_2", 
                              if_else(!is.na(ICD10), "other_death", 
                                      "Alive/Censor"))) %>% 
  mutate(IscheStroke = if_else(grepl("I63[0-9]|I63",  
                                    ICD10), "I63", 
                              if_else(!is.na(ICD10), "other_death", 
                                      "Alive/Censor"))) %>%
  mutate(CHD = if_else(grepl("I2[0-5][0-9]|I2[0-5]",  
                                     ICD10), "I20_5", 
                               if_else(!is.na(ICD10), "other_death", 
                                       "Alive/Censor"))) %>%
  mutate(HeartF = if_else(grepl("I50[0-9]|I50",  
                                     ICD10), "I50", 
                               if_else(!is.na(ICD10), "other_death", 
                                       "Alive/Censor"))) %>% 
  mutate(Milk_fre = as.numeric(MILK)) %>% 
  mutate(Milk_fre = as.factor(Milk_fre)) %>% 
  mutate(Mlkfre = fct_collapse(Milk_fre,
                               Never = "1",
                               Mon1_2 = "2", 
                               Wek1_2 = "3",
                               Wek3_4 = "4",
                               Daily  = "5")) %>% 
  mutate(MlkLogi = fct_collapse(Mlkfre,
                                Never = "Never", 
                                Drinker = c("Mon1_2", "Wek1_2", "Wek3_4", "Daily"))) %>% 
    mutate(Age = as.numeric(tr_age)) %>% 
  mutate(Agegrp = cut(as.numeric(tr_age), c(30, 45, 55, 65, 75, 80), right = FALSE)) %>% 
  mutate(followpy = as.numeric(actual)/365.25) %>% 
    mutate(Smoking = replace_na(SM1, "unknown")) %>% 
  mutate(Smoking = as_factor(Smoking)) %>% 
  mutate(Smoking = fct_recode(Smoking, Never = "3", Past = "2", Current = "1")) %>% 
  mutate(Smoking = factor(Smoking, levels = c("Never", "Past", "Current", "unknown"))) %>%  # Smoking
  mutate(Alc_Fre = if_else(as.numeric(DR1) >= 2, "Never or past", 
                           if_else(as.numeric(DR1F) == 1, "Daily", 
                                   if_else(as.numeric(DR1F) == 4, "< 1/week", 
                                           if_else((as.numeric(DR1F) == 2) | (as.numeric(DR1F) == 3), 
                                                   "1-4 /week", "Unknown"))))) %>% 
  mutate(Alc_Fre = fct_explicit_na(Alc_Fre, na_level = "unknown")) %>% 
  mutate(BMI = as.numeric(wt10)/(as.numeric(ht10)^2) * 100000) %>% # define BMI groups
  mutate(BMIgrp = cut(BMI, breaks = c(14, 18.5, 25, 30, 40), right = FALSE)) %>% 
  mutate(BMIgrp = as.character(BMIgrp)) %>% 
  replace_na(list(BMIgrp = "unknown")) %>% 
  mutate(BMIgrp = factor(BMIgrp, levels = c("[18.5,25)",
                                            "[14,18.5)",
                                            "[25,30)", 
                                            "[30,40)", "unknown"))) %>%
  mutate(DM_hist = if_else(as.numeric(p_DM) > 1, TRUE, FALSE)) %>% 
  replace_na(list(DM_hist = "unknown")) %>% # recode DM history status
  mutate(HT_hist = if_else(as.numeric(p_HT) > 1, TRUE, FALSE)) %>% 
  replace_na(list(HT_hist = "unknown")) %>% # recode hyt history status
  mutate(MI_hist = if_else(as.numeric(p_MI) > 1, TRUE, FALSE)) %>% 
  replace_na(list(MI_hist = "unknown")) %>% # recode MI history status
  mutate(APO_hist = if_else(as.numeric(p_APO) > 1, TRUE, FALSE)) %>% 
  replace_na(list(APO_hist = "unknown")) %>% # recode APO history status
  mutate(KID_hist = if_else(as.numeric(p_KID) > 1, TRUE, FALSE)) %>% 
  replace_na(list(KID_hist = "unknown")) %>% # recode KID history status
  mutate(LIV_hist = if_else(as.numeric(p_LIV) > 1, TRUE, FALSE)) %>% 
  replace_na(list(LIV_hist = "unknown")) %>% # recode LIV history status
  mutate(Can_hist = if_else(as.numeric(p_can1) > 1 | 
                              as.numeric(p_can2) > 1, TRUE, FALSE)) %>% 
  replace_na(list(Can_hist = "unknown")) %>% # recode Can history status
  mutate(Exercise = as.numeric(sport) != 4) %>% # define exercise habits
  mutate(Exercise = as.character(Exercise)) %>% 
  replace_na(list(Exercise = "unknown")) %>% 
  mutate(Exercise = factor(Exercise, levels = c("FALSE", "TRUE", "unknown"))) %>% 
  mutate(Exercise = fct_recode(Exercise, 
                               "> 1h/w" = "TRUE", 
                               "Almost0" = "FALSE", 
                               unknown   = "unknown")) %>% 
  mutate(Engy = log(as.numeric(ENERGY))) %>% 
  mutate(Sleep = as.numeric(SLEEP)/10) %>% 
  mutate(Slepgrp = cut(Sleep, breaks = c(0, 6.9, 7.9, 8.9, 23), right = FALSE)) %>% 
  mutate(Slepgrp = as.character(Slepgrp)) %>% 
  replace_na(list(Slepgrp = "unknown")) %>% 
  mutate(Slepgrp = factor(Slepgrp, levels = c("[0,6.9)",
                                            "[6.9,7.9)",
                                            "[7.9,8.9)", 
                                            "[8.9,23)", "unknown"))) %>% 
  mutate(Spi = as.factor(SPI)) %>% # define vegetable intake
  mutate(Spi = fct_collapse(Spi, 
                            unknown = "X", 
                            daily = "5",
                            Thre4tw = "4",
                            One2tw = "3",
                            Less1tm = c("1", "2"))) %>% 
  mutate(Spi = fct_explicit_na(Spi, na_level = "unknown")) %>% 
  mutate(Fru = as.factor(FRU)) %>% # define fruit intake
  mutate(Fru = fct_collapse(Fru, 
                            unknown = "X",
                            daily = "5",
                            Thre4tw = "4",
                            One2tw = "3",
                            Less1tm = c("1", "2"))) %>% 
  mutate(Fru = fct_explicit_na(Fru, na_level = "unknown")) %>% 
  mutate(Gretea = as.factor(GreTEA1)) %>% # define greentea intake
  mutate(Gretea = fct_collapse(Gretea, 
                               unknown = "X", 
                               Thre3tw = "2", 
                               Thre3tw = "3",
                               Thre3tw = "4",
                               Never = "5", 
                               daily = "1")) %>% 
  mutate(Gretea = fct_explicit_na(Gretea, na_level = "unknown"))  %>% 
  mutate(Cofe = as.factor(COFE)) %>% # define greentea intake
  mutate(Cofe = fct_collapse(Cofe, 
                               unknown = "X", 
                               Thre3tw = "2", 
                               Thre3tw = "3",
                               Thre3tw = "4",
                               Never = "5", 
                               daily = "1")) %>% 
  mutate(Cofe = fct_explicit_na(Cofe, na_level = "unknown"))  %>% 
  mutate(Educ = as.numeric(MILK_0$SCHOOL)) %>% 
  mutate(Educgrp = cut(Educ, breaks = c(0, 18, 70), right = FALSE)) %>% 
  mutate(Educgrp = as.character(Educgrp)) %>% 
  replace_na(list(Educgrp = "unknown")) %>% 
  mutate(Educgrp = factor(Educgrp, levels = c("[0,18)",
                                              "[18,70)",
                                              "unknown"))) %>% # Define menopause for women
  mutate(Menopause = if_else(!is.na(MENO_AGE)& tr_sex == "2", TRUE,  # define menopause
                             if_else(as.numeric(tr_age) >= 50 & tr_sex == "2", 
                                     TRUE, FALSE))) %>% 
    mutate(areano = as.numeric(areano)) %>% 
  mutate(Area = if_else(areano %in% c(11, 22, 23, 24, 41, 30,
                                      170, 178, 179, 298, 299), "Touhoku", 
                  if_else(areano %in% c(51, 61, 81, 91, 92, 93, 
                                          110, 130, 311), "Kanto", 
                    if_else(areano %in% c(151, 181), "Chubu", 
                      if_else(areano %in% c(100, 108, 109, 201, 211, 212, 213, 
                                214, 221, 241, 242, 243), "Kinki", 
                        if_else(areano %in% c(250, 261), "Chugoku", 
                          if_else(areano %in% c(271, 272, 273, 274, 300, 301, 302, 303, 304, 
                            305, 306, 307, 308, 309), "Kyushiu", "else"))))))) %>% 
  mutate(Area = factor(Area)) %>% 
    mutate(p_Oth1 = as.numeric(p_oth1c)) %>% 
  mutate(p_Oth2 = as.numeric(p_oth2c)) %>% 
  mutate(IscheHeart = if_else((p_Oth1 >=410 & p_Oth1 <=414) | 
                                (p_Oth2 >=410 & p_Oth2 <=414), TRUE, FALSE)) %>% 
  replace_na(list(IscheHeart = "unknown")) %>% # recode IscheHeart history status
  mutate(OtheHeart = if_else((p_Oth1 >=420 & p_Oth1 <=429) | 
                                (p_Oth2 >=420 & p_Oth2 <=429), TRUE, FALSE)) %>% 
  replace_na(list(OtheHeart = "unknown")) #%>% # recode Otherheart history status

MData <- MILK_0 %>%
  filter(APO_hist != "TRUE" & IscheHeart != "TRUE" & 
           OtheHeart != "TRUE" & Can_hist != "TRUE" & MI_hist != "TRUE" & !is.na(Mlkfre)) %>% 
  select(Area, Age, Agegrp, tr_sex, ICD10, T_DX, Tot_Stroke, HemoStroke, IscheStroke, CHD, HeartF, MlkLogi, 
         Mlkfre, followpy, Smoking, Alc_Fre, BMI, BMIgrp, DM_hist, HT_hist, KID_hist, 
         LIV_hist, Exercise, Engy, ENERGY, Sleep, Slepgrp, Spi, Fru, Gretea, Cofe, Educ,
         Educgrp, Menopause)

MData_men <- MData %>% 
  filter(tr_sex == "1")
MData_fem <- MData %>% 
  filter(tr_sex == "2")

# knitr::kable(
#   mtcars[1:6, 1:6], caption = 'mtcars数据的前几行。'
# )
```

## Excluding participants with conditions

1. With stroke history: n = 1496 (915 men and 581 wmen);
2. With cancer history: n = 1461 (411 men and 1050 women);
3. With myocardial infarction history: n = 2994 (1310 men and 1684 women);
4. With ischemic heart diseases history: n = 186 (91 men, 95 women);
5. With other heart diseases history (ICD9 codes: 420-429):  n = 518 (204 men and 314 women);
6. Did not answer the question about milk intake frequency: n = 9545 (3593 men and 5952 women); 
7. Finally, n = 94385 (39386 men and 54999 women) are left in the data:

```{r datapre2, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
MILK_0 %>% 
  group_by(tr_sex, APO_hist) %>% 
  summarise (n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))  %>% 
  print(n=Inf)
```

```{r datapre3, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

MILK_0 %>% 
  group_by(tr_sex, Can_hist) %>% 
  summarise (n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))  %>% 
  print(n=Inf)

```

```{r datapre4, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

MILK_0 %>% 
  group_by(tr_sex, MI_hist) %>% 
  summarise (n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))  %>% 
  print(n=Inf)

```

```{r datapre5, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

MILK_0 %>% 
  group_by(tr_sex, IscheHeart) %>% 
  summarise (n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))  %>% 
  print(n=Inf)
```

```{r datapre6, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
MILK_0 %>% 
  group_by(tr_sex, OtheHeart) %>% 
  summarise (n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))  %>% 
  print(n=Inf)
```

```{r datapre7, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
MData %>%   
  group_by(tr_sex, Tot_Stroke) %>%
  summarise(n= n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 2), "%"))
```

- N of total stroke mortality (I60-I69) confirmed: 2675 (1352 men and 1323 women)
- Subtypes of stroke and CHD, heart failure: 
    - Ischemic stroke: 957 (520 men and 437 women);
    - Hemorrhagic stroke: 952 (432 men and 520 women);
    - CHD: 1320 (749 men and 571 women);
    - Heart failure: 1097 (498 men and 599 women).

<!-- Tufte样式在Edward Tufte的书以及物理学家费曼的教科书很常见，它的一个显著特点就是边栏的使用。例如脚注和边栏注解，以及放在边栏里的小型插图。Tufte样式在LaTeX和HTML/CSS中都有实现^[参见Github库[tufte-latex](https://github.com/tufte-latex/tufte-latex)和 [tufte-css](https://github.com/edwardtufte/tufte-css)]。我们将这两种实现都纳入了[**tufte**包](https://github.com/rstudio/tufte)。若需要LaTeX/PDF输出，使用输出格式`tufte_handout`即可，类似地，`tufte_book`可以用来输出PDF书，`tufte_html`生成HTML网页。这些输出格式可以在YAML元数据中指定，或者传给`rmarkdown::render()`函数。若对**rmarkdown**包不熟悉，可参见 @R-rmarkdown。 -->

<!-- ```yaml -->
<!-- --- -->
<!-- title: "一个Tufte样式示例" -->
<!-- author: "张三" -->
<!-- ctex: yes -->
<!-- output: -->
<!--   tufte::tufte_handout: -->
<!--     latex_engine: xelatex -->
<!--   tufte::tufte_html: default -->
<!-- --- -->
<!-- ``` -->

<!-- # 章节标题 -->

<!-- Tufte样式不主张太深的章节目录，一般仅仅使用一级标题（Markdown中用一个井号`#`）和二级标题（两个井号）。 -->

\newpage

```{r baseline, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
## 数値として入っているカテゴリカル変数をまとめておきます。
factorVars <- c("Mlkfre","MlkLogi","Smoking","Alc_Fre","BMIgrp","DM_hist","HT_hist","KID_hist","LIV_hist","Exercise","Slepgrp","Spi",
                "Fru", "Gretea", "Cofe", "Educgrp")#, 
                #"Menopause")
## 変数のvectorを作っておきます
vars <- c("Age", "Smoking","Alc_Fre","BMI","BMIgrp","Exercise","Slepgrp","Spi",
                "Fru", "Gretea", "Cofe", "Educgrp", "DM_hist","HT_hist","KID_hist","LIV_hist")

library(tableone)
tableOne <- CreateTableOne(vars = vars, strata = "MlkLogi", data = MData_men, factorVars = factorVars)

table1 <- print(x = tableOne)

tableTwo <- CreateTableOne(vars = vars, strata = "Mlkfre", data = MData_men, factorVars = factorVars)
table2 <- print(x = tableTwo)
write.csv(table1,"tab/table1.csv") 
write.csv(table2,"tab/table2.csv") 
```

```{r tab1, echo=FALSE, eval=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/tab1.csv", header = T)
names(dt) <- c("Characteristic", "Never", "Drinker", "1-2 t/Mon", "1-2 t/Week", "3-4 t/Week", "Daily", "P value")

kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
  add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53)) %>%
  footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
```

\begin{table}[ht]

Table 1. Baseline characteristics of subjects in the JACC study by milk intake level in Men (n = 39,386).

\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Milk drinkers} & \multicolumn{1}{c}{} \\
\cmidrule(l{3pt}r{3pt}){4-7}
Characteristic & Never & Drinker & 1-2 t/Mon & 1-2 t/Week & 3-4 t/Week & Daily & P value\\
\midrule
\rowcolor{gray!6}  n & 8508 & 30878 & 3522 & 5928 & 5563 & 15865 & \\
Age (mean (SD)) & 56.80 (9.97) & 56.78 (10.15) & 55.18 (10.14) & 55.42 (10.10) & 55.43 (9.95) & 58.12 (10.07) & <0.001\\
\rowcolor{gray!6}  Smoking (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}Never & 1384 (16.3) & 6479 (21.0) & 652 (18.5) & 1091 (18.4) & 1141 (20.5) & 3595 (22.7) & \\
\rowcolor{gray!6}  \hspace{1em}Past & 1836 (21.6) & 7729 (25.0) & 730 (20.7) & 1298 (21.9) & 1335 (24.0) & 4366 (27.5) & \\
\hspace{1em}Current & 4996 (58.7) & 15386 (49.8) & 2020 (57.4) & 3313 (55.9) & 2845 (51.1) & 7208 (45.4) & \\
\rowcolor{gray!6}  Alc\_Fre (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}< 1/week & 355 ( 4.2) & 1469 ( 4.8) & 130 ( 3.7) & 273 ( 4.6) & 301 ( 5.4) & 765 ( 4.8) & \\
\rowcolor{gray!6}  \hspace{1em}1-4 /week & 1105 (13.0) & 5316 (17.2) & 597 (17.0) & 1056 (17.8) & 1033 (18.6) & 2630 (16.6) & \\
\hspace{1em}Daily & 4416 (51.9) & 14746 (47.8) & 1793 (50.9) & 2871 (48.4) & 2706 (48.6) & 7376 (46.5) & \\
\rowcolor{gray!6}  \hspace{1em}Never or past & 2028 (23.8) & 7060 (22.9) & 727 (20.6) & 1257 (21.2) & 1120 (20.1) & 3956 (24.9) & \\
BMI (mean (SD)) & 22.58 (3.41) & 22.71 (3.41) & 22.76 (2.75) & 22.76 (2.82) & 22.91 (5.44) & 22.61 (2.75) & <0.001\\
\rowcolor{gray!6}  BMIgrp (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}18.5-24.9 & 6099 (71.7) & 22591 (73.2) & 2562 (72.7) & 4313 (72.8) & 4042 (72.7) & 11674 (73.6) & \\
\rowcolor{gray!6}  \hspace{1em}< 18.5 & 505 ( 5.9) & 1446 ( 4.7) & 152 ( 4.3) & 266 ( 4.5) & 213 ( 3.8) & 815 ( 5.1) & \\
\hspace{1em}25-29.9 & 1404 (16.5) & 5246 (17.0) & 612 (17.4) & 1082 (18.3) & 988 (17.8) & 2564 (16.2) & \\
\rowcolor{gray!6}  \hspace{1em}> 30 & 90 ( 1.1) & 296 ( 1.0) & 38 ( 1.1) & 54 ( 0.9) & 63 ( 1.1) & 141 ( 0.9) & \\
Exercise (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}Almost0 & 5009 (58.9) & 17232 (55.8) & 2274 (64.6) & 3316 (55.9) & 2954 (53.1) & 8688 (54.8) & \\
\hspace{1em}> 1h/w & 1618 (19.0) & 8509 (27.6) & 934 (26.5) & 1482 (25.0) & 1418 (25.5) & 4675 (29.5) & \\
\rowcolor{gray!6}  Slepgrp (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}< 6.9 & 1502 (17.7) & 5274 (17.1) & 582 (16.5) & 1036 (17.5) & 948 (17.0) & 2708 (17.1) & \\
\rowcolor{gray!6}  \hspace{1em}7-7.9 & 2559 (30.1) & 9953 (32.2) & 1182 (33.6) & 1891 (31.9) & 1802 (32.4) & 5078 (32.0) & \\
\hspace{1em}8-8.9 & 3026 (35.6) & 11074 (35.9) & 1217 (34.6) & 2143 (36.2) & 1953 (35.1) & 5761 (36.3) & \\
\rowcolor{gray!6}  \hspace{1em}> 9 & 1113 (13.1) & 3102 (10.0) & 374 (10.6) & 581 ( 9.8) & 553 ( 9.9) & 1594 (10.0) & \\
Veg (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}Less1tm & 1002 (11.8) & 2556 ( 8.3) & 556 (15.8) & 508 ( 8.6) & 362 ( 6.5) & 1130 ( 7.1) & \\
\hspace{1em}One2tw & 2198 (25.8) & 7915 (25.6) & 1118 (31.7) & 1828 (30.8) & 1280 (23.0) & 3689 (23.3) & \\
\rowcolor{gray!6}  \hspace{1em}Thre4tw & 1787 (21.0) & 7791 (25.2) & 871 (24.7) & 1333 (22.5) & 1582 (28.4) & 4005 (25.2) & \\
\hspace{1em}daily & 1810 (21.3) & 7844 (25.4) & 709 (20.1) & 1209 (20.4) & 1158 (20.8) & 4768 (30.1) & \\
\rowcolor{gray!6}  Fruit (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}Less1tm & 1888 (22.2) & 4007 (13.0) & 786 (22.3) & 810 (13.7) & 618 (11.1) & 1793 (11.3) & \\
\rowcolor{gray!6}  \hspace{1em}One2tw & 1877 (22.1) & 6691 (21.7) & 999 (28.4) & 1581 (26.7) & 1099 (19.8) & 3012 (19.0) & \\
\hspace{1em}Thre4tw & 1376 (16.2) & 6120 (19.8) & 695 (19.7) & 1122 (18.9) & 1271 (22.8) & 3032 (19.1) & \\
\rowcolor{gray!6}  \hspace{1em}daily & 1260 (14.8) & 6924 (22.4) & 542 (15.4) & 968 (16.3) & 961 (17.3) & 4453 (28.1) & \\
Greentea (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}daily & 6508 (76.5) & 24444 (79.2) & 2814 (79.9) & 4641 (78.3) & 4332 (77.9) & 12657 (79.8) & \\
\hspace{1em}Thre3tw & 737 ( 8.7) & 2926 ( 9.5) & 378 (10.7) & 588 ( 9.9) & 562 (10.1) & 1398 ( 8.8) & \\
\rowcolor{gray!6}  \hspace{1em}Never & 659 ( 7.7) & 1748 ( 5.7) & 184 ( 5.2) & 327 ( 5.5) & 299 ( 5.4) & 938 ( 5.9) & \\
Coffe (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}daily & 3727 (43.8) & 15662 (50.7) & 1780 (50.5) & 2845 (48.0) & 2642 (47.5) & 8395 (52.9) & \\
\hspace{1em}Thre3tw & 2267 (26.6) & 8511 (27.6) & 998 (28.3) & 1822 (30.7) & 1774 (31.9) & 3917 (24.7) & \\
\rowcolor{gray!6}  \hspace{1em}Never & 2299 (27.0) & 6006 (19.5) & 700 (19.9) & 1123 (18.9) & 983 (17.7) & 3200 (20.2) & \\
Educgrp (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}>= 18 y.o & 2168 (25.5) & 10701 (34.7) & 1190 (33.8) & 1973 (33.3) & 1726 (31.0) & 5812 (36.6) & \\
DM\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 423 ( 5.0) & 1942 ( 6.3) & 160 ( 4.5) & 250 ( 4.2) & 304 ( 5.5) & 1228 ( 7.7) & \\
HT\_hist (\%) &  &  &  &  &  &  & 0.039\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 1568 (18.4) & 5526 (17.9) & 616 (17.5) & 1013 (17.1) & 937 (16.8) & 2960 (18.7) & \\
KID\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 257 ( 3.0) & 1038 ( 3.4) & 135 ( 3.8) & 178 ( 3.0) & 168 ( 3.0) & 557 ( 3.5) & \\
LIV\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 495 ( 5.8) & 2016 ( 6.5) & 223 ( 6.3) & 356 ( 6.0) & 300 ( 5.4) & 1137 ( 7.2) & \\
\bottomrule
\multicolumn{8}{l}{\textit{Note: }}\\
\multicolumn{8}{l}{Abbreviations: n, number; SD, standard deviation; Alc\_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration}\\
\multicolumn{8}{l}{groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV\_hist, diabetes, hypertension, kidney disease,}\\
\multicolumn{8}{l}{liver disease history.}\\
\end{tabular}
\end{table}

\newpage

```{r baselinef, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
## 数値として入っているカテゴリカル変数をまとめておきます。
factorVars <- c("Mlkfre","MlkLogi","Smoking","Alc_Fre","BMIgrp","DM_hist","HT_hist","KID_hist","LIV_hist","Exercise","Slepgrp","Spi",
                "Fru", "Gretea", "Cofe", "Educgrp", 
                "Menopause")
## 変数のvectorを作っておきます
vars <- c("Age", "Smoking","Alc_Fre","BMI","BMIgrp","Exercise","Slepgrp","Spi",
                "Fru", "Gretea", "Cofe", "Educgrp", "DM_hist","HT_hist","KID_hist","LIV_hist","Menopause")

tableOne <- CreateTableOne(vars = vars, strata = "MlkLogi", data = MData_fem, factorVars = factorVars)

table1 <- print(x = tableOne)

tableTwo <- CreateTableOne(vars = vars, strata = "Mlkfre", data = MData_fem, factorVars = factorVars)
table2 <- print(x = tableTwo)
write.csv(table1,"tab/table1f.csv") 
write.csv(table2,"tab/table2f.csv") 
```

```{r tab1f, echo=FALSE, eval=FALSE}

dt <- read.csv("tab/tab1f.csv", header = T)
names(dt) <- c("Characteristic", "Never", "Drinker", "1-2 t/Mon", "1-2 t/Week", "3-4 t/Week", "Daily", "P value")

kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
  add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
  footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
```

\begin{table}[!ht]
Table 2. Baseline characteristics of subjects in the JACC study by milk intake level in Women (n = 54,999).

\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Milk drinkers} & \multicolumn{1}{c}{} \\
\cmidrule(l{3pt}r{3pt}){4-7}
Characteristic & Never & Drinker & 1-2 t/Mon & 1-2 t/Week & 3-4 t/Week & Daily & P value\\
\midrule
\rowcolor{gray!6}  n & 10407 & 44592 & 3640 & 7590 & 8108 & 25254 & \\
Age (mean (SD)) & 58.03 (10.17) & 56.97 (9.99) & 56.52 (10.19) & 55.60 (10.08) & 55.58 (9.89) & 57.90 (9.86) & <0.001\\
\rowcolor{gray!6}  Smoking (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}Never & 8318 (79.9) & 36978 (82.9) & 2974 (81.7) & 6219 (81.9) & 6763 (83.4) & 21022 (83.2) & \\
\rowcolor{gray!6}  \hspace{1em}Past & 169 ( 1.6) & 607 ( 1.4) & 49 ( 1.3) & 113 ( 1.5) & 98 ( 1.2) & 347 ( 1.4) & \\
\hspace{1em}Current & 723 ( 6.9) & 1860 ( 4.2) & 222 ( 6.1) & 420 ( 5.5) & 346 ( 4.3) & 872 ( 3.5) & \\
\rowcolor{gray!6}  Alc\_Fre (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}< 1/week & 697 ( 6.7) & 3084 ( 6.9) & 191 ( 5.2) & 567 ( 7.5) & 673 ( 8.3) & 1653 ( 6.5) & \\
\rowcolor{gray!6}  \hspace{1em}1-4 /week & 837 ( 8.0) & 4611 (10.3) & 357 ( 9.8) & 828 (10.9) & 918 (11.3) & 2508 ( 9.9) & \\
\hspace{1em}Daily & 450 ( 4.3) & 2021 ( 4.5) & 200 ( 5.5) & 325 ( 4.3) & 338 ( 4.2) & 1158 ( 4.6) & \\
\rowcolor{gray!6}  \hspace{1em}Never or past & 7449 (71.6) & 30670 (68.8) & 2562 (70.4) & 5196 (68.5) & 5416 (66.8) & 17496 (69.3) & \\
BMI (mean (SD)) & 23.01 (3.38) & 22.91 (3.69) & 23.02 (3.80) & 23.07 (4.41) & 23.07 (3.08) & 22.80 (3.62) & <0.001\\
\rowcolor{gray!6}  BMIgrp (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}18.5-24.9 & 6589 (63.3) & 30588 (68.6) & 2438 (67.0) & 5121 (67.5) & 5496 (67.8) & 17533 (69.4) & \\
\rowcolor{gray!6}  \hspace{1em}< 18.5 & 703 ( 6.8) & 2465 ( 5.5) & 188 ( 5.2) & 380 ( 5.0) & 398 ( 4.9) & 1499 ( 5.9) & \\
\hspace{1em}25-29.9 & 2173 (20.9) & 8545 (19.2) & 756 (20.8) & 1505 (19.8) & 1678 (20.7) & 4606 (18.2) & \\
\rowcolor{gray!6}  \hspace{1em}> 30 & 280 ( 2.7) & 769 ( 1.7) & 76 ( 2.1) & 175 ( 2.3) & 158 ( 1.9) & 360 ( 1.4) & \\
Exercise (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}Almost0 & 6618 (63.6) & 27513 (61.7) & 2624 (72.1) & 4816 (63.5) & 4790 (59.1) & 15283 (60.5) & \\
\hspace{1em}> 1h/w & 1417 (13.6) & 9265 (20.8) & 624 (17.1) & 1401 (18.5) & 1522 (18.8) & 5718 (22.6) & \\
\rowcolor{gray!6}  Slepgrp (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}< 6.9 & 2805 (27.0) & 11968 (26.8) & 1019 (28.0) & 2047 (27.0) & 2103 (25.9) & 6799 (26.9) & \\
\rowcolor{gray!6}  \hspace{1em}7-7.9 & 3336 (32.1) & 16071 (36.0) & 1245 (34.2) & 2721 (35.8) & 2944 (36.3) & 9161 (36.3) & \\
\hspace{1em}8-8.9 & 2886 (27.7) & 11432 (25.6) & 914 (25.1) & 1965 (25.9) & 2056 (25.4) & 6497 (25.7) & \\
\rowcolor{gray!6}  \hspace{1em}> 9 & 887 ( 8.5) & 2543 ( 5.7) & 254 ( 7.0) & 439 ( 5.8) & 435 ( 5.4) & 1415 ( 5.6) & \\
Veg (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}Less1tm & 917 ( 8.8) & 2356 ( 5.3) & 399 (11.0) & 445 ( 5.9) & 337 ( 4.2) & 1175 ( 4.7) & \\
\hspace{1em}One2tw & 2514 (24.2) & 10127 (22.7) & 1029 (28.3) & 2195 (28.9) & 1642 (20.3) & 5261 (20.8) & \\
\rowcolor{gray!6}  \hspace{1em}Thre4tw & 2331 (22.4) & 11845 (26.6) & 1001 (27.5) & 1876 (24.7) & 2452 (30.2) & 6516 (25.8) & \\
\hspace{1em}daily & 2567 (24.7) & 13537 (30.4) & 909 (25.0) & 1866 (24.6) & 1963 (24.2) & 8799 (34.8) & \\
\rowcolor{gray!6}  Fruit (\%) &  &  &  &  &  &  & <0.001\\
\hspace{1em}Less1tm & 1397 (13.4) & 3270 ( 7.3) & 523 (14.4) & 594 ( 7.8) & 514 ( 6.3) & 1639 ( 6.5) & \\
\rowcolor{gray!6}  \hspace{1em}One2tw & 1913 (18.4) & 6761 (15.2) & 801 (22.0) & 1515 (20.0) & 1122 (13.8) & 3323 (13.2) & \\
\hspace{1em}Thre4tw & 1926 (18.5) & 9018 (20.2) & 845 (23.2) & 1591 (21.0) & 1922 (23.7) & 4660 (18.5) & \\
\rowcolor{gray!6}  \hspace{1em}daily & 2601 (25.0) & 15939 (35.7) & 967 (26.6) & 2216 (29.2) & 2369 (29.2) & 10387 (41.1) & \\
Greentea (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}daily & 7680 (73.8) & 34264 (76.8) & 2804 (77.0) & 5800 (76.4) & 6146 (75.8) & 19514 (77.3) & \\
\hspace{1em}Thre3tw & 946 ( 9.1) & 4615 (10.3) & 394 (10.8) & 848 (11.2) & 921 (11.4) & 2452 ( 9.7) & \\
\rowcolor{gray!6}  \hspace{1em}Never & 944 ( 9.1) & 2928 ( 6.6) & 230 ( 6.3) & 467 ( 6.2) & 466 ( 5.7) & 1765 ( 7.0) & \\
Coffe (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}daily & 4121 (39.6) & 21483 (48.2) & 1682 (46.2) & 3519 (46.4) & 3597 (44.4) & 12685 (50.2) & \\
\hspace{1em}Thre3tw & 2648 (25.4) & 12514 (28.1) & 1069 (29.4) & 2279 (30.0) & 2698 (33.3) & 6468 (25.6) & \\
\rowcolor{gray!6}  \hspace{1em}Never & 3387 (32.5) & 9670 (21.7) & 835 (22.9) & 1611 (21.2) & 1620 (20.0) & 5604 (22.2) & \\
Educgrp (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}>= 18 y.o & 2073 (19.9) & 14092 (31.6) & 1016 (27.9) & 2263 (29.8) & 2225 (27.4) & 8588 (34.0) & \\
DM\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 269 ( 2.6) & 1642 ( 3.7) & 115 ( 3.2) & 206 ( 2.7) & 219 ( 2.7) & 1102 ( 4.4) & \\
HT\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 2236 (21.5) & 8782 (19.7) & 745 (20.5) & 1446 (19.1) & 1533 (18.9) & 5058 (20.0) & \\
KID\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 371 ( 3.6) & 1830 ( 4.1) & 142 ( 3.9) & 280 ( 3.7) & 298 ( 3.7) & 1110 ( 4.4) & \\
LIV\_hist (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 365 ( 3.5) & 2047 ( 4.6) & 178 ( 4.9) & 295 ( 3.9) & 320 ( 3.9) & 1254 ( 5.0) & \\
Menopause (\%) &  &  &  &  &  &  & <0.001\\
\rowcolor{gray!6}  \hspace{1em}TRUE & 8213 (78.9) & 34021 (76.3) & 2684 (73.7) & 5408 (71.3) & 5791 (71.4) & 20138 (79.7) & \\
\bottomrule
\multicolumn{8}{l}{\textit{Note: }}\\
\multicolumn{8}{l}{Abbreviations: n, number; SD, standard deviation; Alc\_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration}\\
\multicolumn{8}{l}{groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV\_hist, diabetes, hypertension, kidney disease,}\\
\multicolumn{8}{l}{liver disease history.}\\
\end{tabular}
\end{table}

\newpage

## Traditional survival analysis (Cox proportional hazard model)

```{r figure1, echo=FALSE, eval=TRUE, fig.height=6.5, fig.width=7, message=FALSE, warning=FALSE, fig.cap="Kaplan-Meier survival curves for total stroke mortality by drinking frequency (P value was obtained from log-rank tests) in Men.",fig.align='center',  out.width='100%', cache=TRUE}

###################################################################################################
## survival object
###################################################################################################
library(survival)
library(ggplot2)
library(survminer)
library(cowplot)
library(ggsci)

# in Men
su_obj_men <- Surv(MData_men$followpy, MData_men$Tot_Stroke == "I60_9")
# in Women
su_obj_fem <- Surv(MData_fem$followpy, MData_fem$Tot_Stroke == "I60_9")

###################################################################################################
## Kaplan-Meier plots and log rank tests for TotStroke and Milk intake  (frequency)
###################################################################################################

surv.Drfreq <- with(MData_men, survfit(su_obj_men ~ Mlkfre))

ggsurv_Drfreq <- ggsurvplot(surv.Drfreq, censor = F, xlab = "Time (years)", conf.int = T, 
                            conf.int.style = "step",  # customize style of confidence intervals
                            surv.median.line = "none", ylab = "Survival function",
                            legend.labs = c("Never or past", "< 1/week", "1-2 /week", "3-4 /week", "Daily"), 
                            ggtheme = theme_bw(), palette = "npg",
                            pval = TRUE, data = MData_men, # pval.method = TRUE
                            risk.table = T,
                            risk.table.y.text.col = T, # colour risk table text annotations.
                            risk.table.y.text = FALSE,  pval.coord = c(0, 0.972),
                            ylim = c(0.93, 1.0), xlim = c(0, 22)) 
# show bars instead of names in text annotations)

ggsurv_Drfreq <- ggpar(
  ggsurv_Drfreq,
  font.title    = c(14, "bold", "black"),         
  # font.subtitle = c(15, "bold.italic", "purple"), 
  #  font.caption  = c(14, "plain", "orange"),        
  font.x        = c(14, "bold", "black"),          
  font.y        = c(14, "bold", "black"),      
  font.xtickslab = c(13, "bold", "black"),
  #  font.ytickslab = c(13, "bold", "black"),
  legend = "bottom", 
  font.legend  = c(13, "bold", "black"),
  legend.title = ""
)
ggsurv_Drfreq
```

<!-- # 插图 -->

<!-- ## 边栏插图 -->

<!-- 插图在Tufte的书中非常常见，我们可以使用三种插图：边栏图、全宽图、主栏图。先说边栏图：使用**knitr**代码段选项`fig.margin = TRUE`即可将图形放置在边栏中，如： -->

<!-- ```{r fig-margin, fig.margin = TRUE, fig.cap = "MPG与horsepower两个变量的散点图；颜色代表自动挡或手动挡。", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE, eval=FALSE} -->
<!-- library(ggplot2) -->
<!-- mtcars2 <- mtcars -->
<!-- mtcars2$am <- factor( -->
<!--   mtcars$am, labels = c('automatic', 'manual') -->
<!-- ) -->
<!-- ggplot(mtcars2, aes(hp, mpg, color = am)) + -->
<!--   geom_point() + geom_smooth() + -->
<!--   theme(legend.position = 'bottom') -->
<!-- ``` -->

<!-- 注意我们使用代码段选项`fig.cap`设定了图的标题。当然我们也可以设置图的长宽。 -->

<!-- ## 任意边栏内容 -->

<!-- 事实上我们可以在边栏中放置除了图之外的内容，此时我们不再使用```` ```{r} ````写代码段，而是用```` ```{marginfigure} ````。例如右边有一个微积分第一基本定理。 -->

<!-- ```{marginfigure} -->
<!-- 根据微积分第一基本定理我们知道，对$x \in [a, b]$有 -->
<!-- $$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$ -->
<!-- ``` -->

<!-- 为了文本内容的可移植性（同样的内容可以生成HTML和LaTeX文档），我们建议边栏中不要放置太复杂的内容，简单的加粗、倾斜都没有问题，但不建议在边栏中使用列表、参考文献等内容。 -->

<!-- ## 全宽插图 -->

<!-- 代码段选项`fig.fullwidth = TRUE`可以使得一幅图占用全部页宽，例如： -->

<!-- ```{r fig-fullwidth, fig.width = 10, fig.height = 2, fig.fullwidth = TRUE, fig.cap = "一幅全宽图形。", warning=FALSE, cache=TRUE, message=FALSE} -->
<!-- ggplot(diamonds, aes(carat, price)) + geom_smooth() + -->
<!--   facet_grid(~ cut) -->
<!-- ``` -->

<!-- 其它和图形有关的代码段选项仍然可以使用，一般情况下，全宽图形的`fig.width`选项会较大，而`fig.height`相对较小。上图的尺寸是$10 \times 2$英寸. -->

<!-- ## 主栏插图 -->

<!-- 默认情况下，R代码段生成的图形放置在主栏里，其标题放在边栏中，例如： -->

<!-- ```{r fig-main, fig.cap = "一幅主栏插图。", cache=TRUE} -->
<!-- ggplot(diamonds, aes(cut, price)) + geom_boxplot() -->
<!-- ``` -->

<!-- # 边栏附注 -->

<!-- Tufte样式的文档中，脚注会被自动转换为边栏附注^[这里本来是一个脚注]。脚注是带编号的，另一种边栏附注是不带编号的，这种附注需要用**tufte**包中的R函数`margin_note()`在**knitr**行内代码中生成。`r margin_note("这是一个边栏附注，它没有编号。")`与边栏插图一样，边栏附注中我们也不建议写太复杂的内容，通常只是一句简单的文字。 -->

<!-- # 参考文献 -->

<!-- HTML输出中，参考文献默认也放在边栏中。例如这里我们可以引用[@R-base]。这个功能需要在YAML元数据中设置`link-citations: yes`，而且`pandoc-citeproc`程序的版本应该至少是0.7.2。若这两个条件不满足，参考文献会被放在文档末尾。 -->

<!-- # 引文 -->

<!-- Markdown语法使用`>`来生成引文，如果需要在引文下面用行内代码以及`quote_footer()`函数加上一句引文来源，例如： -->

<!-- > "多亏了我的律师，要不然我现在还在牢里。两个人一起挖确实比一个人快很多啊。" -->
<!-- > -->
<!-- > `r tufte::quote_footer('--- Joe Martin')` -->

<!-- 如果不用这个函数的话，引文底部的话只是一个普通段落： -->

<!-- > "伟人论道，凡人论事，小人论酒。" -->
<!-- > -->
<!-- > --- Fran Lebowitz -->

<!-- # 响应式页面 -->

<!-- 这个包生成的HTML页面是响应式的：如果页宽小于760像素，边栏内容会自动隐藏。此时我们可以点击脚注的序号显示它，其它边栏附注则可以通过点击圆圈加号的符号显示。 -->

<!-- # 结语 -->

<!-- 希望诸位喜欢R Markdown的超级简洁性，同时我们感谢Tufte-CSS和Tufte-LaTeX项目的作者们，没有他们的辛勤劳动，就没有这个**tufte**包。这份文档的R Markdown源文档可以在[Github上找到](https://github.com/rstudio/tufte/raw/master/inst/rmarkdown/templates/tufte_ctex/skeleton/skeleton.Rmd)，或者直接使用RStudio菜单`File -> New File -> R Markdown -> From Template`新建一个文档，或直接从R里面打开这个Rmd文件： -->

<!-- ```{r eval=FALSE} -->
<!-- file.edit( -->
<!--   tufte:::template_resources( -->
<!--     'tufte_ctex', '..', 'skeleton', 'skeleton.Rmd' -->
<!--   ) -->
<!-- ) -->
<!-- ``` -->

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```

### 2020-01-11 ForReport20200114/HandOutEng.Rmd
updated with template for handout

--- 2020-01-11 ForReport20200114/HandOut.Rmd
@@
     latex_engine: xelatex
-ctex: yes
-biblio-title: Reference
 bibliography: skeleton.bib
@@
 
-## Data preparation
+# Data preparation
 
@@
 
+- Follow-up years: 
 <!-- Tufte样式在Edward Tufte的书以及物理学家费曼的教科书很常见，它的一个显著特点就是边栏的使用。例如脚注和边栏注解，以及放在边栏里的小型插图。Tufte样式在LaTeX和HTML/CSS中都有实现^[参见Github库[tufte-latex](https://github.com/tufte-latex/tufte-latex)和 [tufte-css](https://github.com/edwardtufte/tufte-css)]。我们将这两种实现都纳入了[**tufte**包](https://github.com/rstudio/tufte)。若需要LaTeX/PDF输出，使用输出格式`tufte_handout`即可，类似地，`tufte_book`可以用来输出PDF书，`tufte_html`生成HTML网页。这些输出格式可以在YAML元数据中指定，或者传给`rmarkdown::render()`函数。若对**rmarkdown**包不熟悉，可参见 @R-rmarkdown。 -->
@@
 ```
-
-<!-- # 插图 -->
-
-<!-- ## 边栏插图 -->
-
-<!-- 插图在Tufte的书中非常常见，我们可以使用三种插图：边栏图、全宽图、主栏图。先说边栏图：使用**knitr**代码段选项`fig.margin = TRUE`即可将图形放置在边栏中，如： -->
-
-<!-- ```{r fig-margin, fig.margin = TRUE, fig.cap = "MPG与horsepower两个变量的散点图；颜色代表自动挡或手动挡。", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE, eval=FALSE} -->
-<!-- library(ggplot2) -->
-<!-- mtcars2 <- mtcars -->
-<!-- mtcars2$am <- factor( -->
-<!--   mtcars$am, labels = c('automatic', 'manual') -->
-<!-- ) -->
-<!-- ggplot(mtcars2, aes(hp, mpg, color = am)) + -->
-<!--   geom_point() + geom_smooth() + -->
-<!--   theme(legend.position = 'bottom') -->
-<!-- ``` -->
-
-<!-- 注意我们使用代码段选项`fig.cap`设定了图的标题。当然我们也可以设置图的长宽。 -->
-
-<!-- ## 任意边栏内容 -->
-
-<!-- 事实上我们可以在边栏中放置除了图之外的内容，此时我们不再使用```` ```{r} ````写代码段，而是用```` ```{marginfigure} ````。例如右边有一个微积分第一基本定理。 -->
-
-<!-- ```{marginfigure} -->
-<!-- 根据微积分第一基本定理我们知道，对$x \in [a, b]$有 -->
-<!-- $$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$ -->
-<!-- ``` -->
-
-<!-- 为了文本内容的可移植性（同样的内容可以生成HTML和LaTeX文档），我们建议边栏中不要放置太复杂的内容，简单的加粗、倾斜都没有问题，但不建议在边栏中使用列表、参考文献等内容。 -->
-
-<!-- ## 全宽插图 -->
-
-<!-- 代码段选项`fig.fullwidth = TRUE`可以使得一幅图占用全部页宽，例如： -->
-
-<!-- ```{r fig-fullwidth, fig.width = 10, fig.height = 2, fig.fullwidth = TRUE, fig.cap = "一幅全宽图形。", warning=FALSE, cache=TRUE, message=FALSE} -->
-<!-- ggplot(diamonds, aes(carat, price)) + geom_smooth() + -->
-<!--   facet_grid(~ cut) -->
-<!-- ``` -->
-
-<!-- 其它和图形有关的代码段选项仍然可以使用，一般情况下，全宽图形的`fig.width`选项会较大，而`fig.height`相对较小。上图的尺寸是$10 \times 2$英寸. -->
-
-<!-- ## 主栏插图 -->
-
-<!-- 默认情况下，R代码段生成的图形放置在主栏里，其标题放在边栏中，例如： -->
-
-<!-- ```{r fig-main, fig.cap = "一幅主栏插图。", cache=TRUE} -->
-<!-- ggplot(diamonds, aes(cut, price)) + geom_boxplot() -->
-<!-- ``` -->
-
-<!-- # 边栏附注 -->
-
-<!-- Tufte样式的文档中，脚注会被自动转换为边栏附注^[这里本来是一个脚注]。脚注是带编号的，另一种边栏附注是不带编号的，这种附注需要用**tufte**包中的R函数`margin_note()`在**knitr**行内代码中生成。`r margin_note("这是一个边栏附注，它没有编号。")`与边栏插图一样，边栏附注中我们也不建议写太复杂的内容，通常只是一句简单的文字。 -->
-
-<!-- # 参考文献 -->
-
-<!-- HTML输出中，参考文献默认也放在边栏中。例如这里我们可以引用[@R-base]。这个功能需要在YAML元数据中设置`link-citations: yes`，而且`pandoc-citeproc`程序的版本应该至少是0.7.2。若这两个条件不满足，参考文献会被放在文档末尾。 -->
-
-<!-- # 引文 -->
-
-<!-- Markdown语法使用`>`来生成引文，如果需要在引文下面用行内代码以及`quote_footer()`函数加上一句引文来源，例如： -->
-
-<!-- > "多亏了我的律师，要不然我现在还在牢里。两个人一起挖确实比一个人快很多啊。" -->
-<!-- > -->
-<!-- > `r tufte::quote_footer('--- Joe Martin')` -->
-
-<!-- 如果不用这个函数的话，引文底部的话只是一个普通段落： -->
-
-<!-- > "伟人论道，凡人论事，小人论酒。" -->
-<!-- > -->
-<!-- > --- Fran Lebowitz -->
-
-<!-- # 响应式页面 -->
-
-<!-- 这个包生成的HTML页面是响应式的：如果页宽小于760像素，边栏内容会自动隐藏。此时我们可以点击脚注的序号显示它，其它边栏附注则可以通过点击圆圈加号的符号显示。 -->
-
-<!-- # 结语 -->
-
-<!-- 希望诸位喜欢R Markdown的超级简洁性，同时我们感谢Tufte-CSS和Tufte-LaTeX项目的作者们，没有他们的辛勤劳动，就没有这个**tufte**包。这份文档的R Markdown源文档可以在[Github上找到](https://github.com/rstudio/tufte/raw/master/inst/rmarkdown/templates/tufte_ctex/skeleton/skeleton.Rmd)，或者直接使用RStudio菜单`File -> New File -> R Markdown -> From Template`新建一个文档，或直接从R里面打开这个Rmd文件： -->
-
-<!-- ```{r eval=FALSE} -->
-<!-- file.edit( -->
-<!--   tufte:::template_resources( -->
-<!--     'tufte_ctex', '..', 'skeleton', 'skeleton.Rmd' -->
-<!--   ) -->
-<!-- ) -->
-<!-- ``` -->
-
-```{r bib, include=FALSE}
-# create a bib file for the R packages used in this document
-knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
-```

### 2020-01-11 AnalysisScript/traditionalPH.R

@@ -168,7 +168,7 @@ MILK_0 <-  MILK_0 %>%
   replace_na(list(APO_hist = "unknown")) %>% # recode APO history status
   mutate(KID_hist = if_else(as.numeric(p_KID) > 1, TRUE, FALSE)) %>% 
   replace_na(list(KID_hist = "unknown")) %>% # recode KID history status
-  mutate(LIV_hist = if_else(as.numeric(p_APO) > 1, TRUE, FALSE)) %>% 
+  mutate(LIV_hist = if_else(as.numeric(p_LIV) > 1, TRUE, FALSE)) %>% 
   replace_na(list(LIV_hist = "unknown")) %>% # recode LIV history status
   mutate(Can_hist = if_else(as.numeric(p_can1) > 1 | 
                               as.numeric(p_can2) > 1, TRUE, FALSE)) %>% 

### 2020-01-11 ForReport20200114/HandOutEng.Rmd
updated with all cox results

@@
     latex_engine: xelatex
+    keep_tex: true
   tufte::tufte_html: default
@@
 - N of total stroke mortality (I60-I69) confirmed: 2675 (1352 men and 1323 women)
+\newpage
 - Subtypes of stroke and CHD, heart failure: 
@@
 
-- Follow-up years: 
+- Follow-up years summary in total sample:
+
+```{r datapre9, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
+epiDisplay::summ(MData$followpy, graph = FALSE)
+```
+
+- Follow-up years summary by total stroke mortality events:
+
+```{r datapre8, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
+MData %>% 
+  group_by(tr_sex, Tot_Stroke) %>% 
+  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), MaxFolYear = max(followpy))
+```
+
+```{r figure1, echo=FALSE, eval=FALSE, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Kaplan-Meier survival curves for total stroke mortality by drinking frequency (P value was obtained from log-rank tests) in Men.",fig.align='center',  out.width='100%', cache=TRUE}
+
+###################################################################################################
+## survival object
+###################################################################################################
+library(survival)
+library(ggplot2)
+library(survminer)
+library(cowplot)
+library(ggsci)
+
+# in Men
+su_obj_men <- Surv(MData_men$followpy, MData_men$Tot_Stroke == "I60_9")
+# in Women
+su_obj_fem <- Surv(MData_fem$followpy, MData_fem$Tot_Stroke == "I60_9")
+
+###################################################################################################
+## Kaplan-Meier plots and log rank tests for TotStroke and Milk intake  (frequency)
+###################################################################################################
+
+surv.Drfreq <- with(MData_men, survfit(su_obj_men ~ Mlkfre))
+
+ggsurv_Drfreq <- ggsurvplot(surv.Drfreq, censor = F, xlab = "Time (years)", conf.int = T, 
+                            conf.int.style = "step",  # customize style of confidence intervals
+                            surv.median.line = "none", ylab = "Survival function",
+                            legend.labs = c("Never or past", "< 1/week", "1-2 /week", "3-4 /week", "Daily"), 
+                            ggtheme = theme_bw(), palette = "npg",
+                            pval = TRUE, data = MData_men, # pval.method = TRUE
+                            risk.table = T, tables.height = 0.2,
+                            risk.table.y.text.col = T, # colour risk table text annotations.
+                            risk.table.y.text = FALSE,  pval.coord = c(0, 0.972),
+                            ylim = c(0.93, 1.0), xlim = c(0, 22)) 
+# show bars instead of names in text annotations)
+
+ggsurv_Drfreq <- ggpar(
+  ggsurv_Drfreq,
+  font.title    = c(10, "bold", "black"),         
+  # font.subtitle = c(15, "bold.italic", "purple"), 
+  #  font.caption  = c(14, "plain", "orange"),        
+  font.x        = c(10, "bold", "black"),          
+  font.y        = c(10, "bold", "black"),      
+  font.xtickslab = c(10, "bold", "black"),
+  #  font.ytickslab = c(13, "bold", "black"),
+  legend = "bottom", 
+  font.legend  = c(10, "bold", "black"),
+  legend.title = ""
+)
+ggsurv_Drfreq
+```
+
+```{r fig2, echo=FALSE, eval=FALSE, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Kaplan-Meier survival curves for total stroke mortality by drinking frequency (P value was obtained from log-rank tests) in Women.",fig.align='center',  out.width='100%', cache=TRUE}
+surv.Drfreq <- with(MData_fem, survfit(su_obj_fem ~ Mlkfre))
+
+ggsurv_Drfreq <- ggsurvplot(surv.Drfreq, censor = F, xlab = "Time (years)", conf.int = T, 
+                            conf.int.style = "step",  # customize style of confidence intervals
+                            surv.median.line = "none", ylab = "Survival function",
+                            legend.labs = c("Never or past", "< 1/week", "1-2 /week", "3-4 /week", "Daily"), 
+                            ggtheme = theme_bw(), palette = "npg",
+                            pval = TRUE, data = MData_fem, # pval.method = TRUE
+                            risk.table = T, tables.height = 0.2,
+                            risk.table.y.text.col = T, # colour risk table text annotations.
+                            risk.table.y.text = FALSE,  pval.coord = c(0, 0.972),
+                            ylim = c(0.93, 1.0), xlim = c(0, 22)) 
+# show bars instead of names in text annotations)
+
+ggsurv_Drfreq <- ggpar(
+  ggsurv_Drfreq,
+  font.title    = c(10, "bold", "black"),         
+  # font.subtitle = c(15, "bold.italic", "purple"), 
+  #  font.caption  = c(14, "plain", "orange"),        
+  font.x        = c(10, "bold", "black"),          
+  font.y        = c(10, "bold", "black"),      
+  font.xtickslab = c(10, "bold", "black"),
+  #  font.ytickslab = c(13, "bold", "black"),
+  legend = "bottom", 
+  font.legend  = c(10, "bold", "black"),
+  legend.title = ""
+)
+ggsurv_Drfreq
+```
+
+```{r KMmen, echo=FALSE, out.width = '95%', cache=TRUE, fig.cap="Kaplan-Meier survival curves for total stroke mortality by milk drinking frequency (P value was obtained from log-rank tests) in men.",fig.align='center'}
+knitr::include_graphics("fig/KMfigMen.png")
+```
+
+```{r KMwomen, echo=FALSE, out.width = '90%', cache=TRUE, fig.cap="Kaplan-Meier survival curves for total stroke mortality by milk drinking frequency (P value was obtained from log-rank tests) in women.",fig.align='center'}
+knitr::include_graphics("fig/KMfigwomen.png")
+```
+
 <!-- Tufte样式在Edward Tufte的书以及物理学家费曼的教科书很常见，它的一个显著特点就是边栏的使用。例如脚注和边栏注解，以及放在边栏里的小型插图。Tufte样式在LaTeX和HTML/CSS中都有实现^[参见Github库[tufte-latex](https://github.com/tufte-latex/tufte-latex)和 [tufte-css](https://github.com/edwardtufte/tufte-css)]。我们将这两种实现都纳入了[**tufte**包](https://github.com/rstudio/tufte)。若需要LaTeX/PDF输出，使用输出格式`tufte_handout`即可，类似地，`tufte_book`可以用来输出PDF书，`tufte_html`生成HTML网页。这些输出格式可以在YAML元数据中指定，或者传给`rmarkdown::render()`函数。若对**rmarkdown**包不熟悉，可参见 @R-rmarkdown。 -->
@@
 
-\begin{table}[!ht]
+\begin{table}[ht]
 Table 2. Baseline characteristics of subjects in the JACC study by milk intake level in Women (n = 54,999).
@@
 
-\newpage
+```{r tab2, echo=FALSE, eval=FALSE}
+dt <- read.csv("tab/HRcox.csv", header = T)
+names(dt) <- c("", "Never",  "1-2 t/Mon", "1-2 t/Week", "3-4 t/Week", "Daily")
+dt[1,c(2)] <- c("")
+dt[4, 2] <- c("")
+dt[9, 2] <- c("") 
+dt[14, 2] <- c("") ; dt[19, 2] <- c("") ; dt[22, 2] <- c("") ; dt[27, 2] <- c("") ; dt[32, 2] <- c("")
+library(knitr)
+library(kableExtra)
+kable(dt, format = "latex", caption = "", booktabs = T, linesep = "") %>%
+ kable_styling(latex_options = c("striped","hold_position"), font_size = 9) 
+# %>%
+  # add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
+  # add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
+  # footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
 
-## Traditional survival analysis (Cox proportional hazard model)
+```
 
-```{r figure1, echo=FALSE, eval=TRUE, fig.height=6.5, fig.width=7, message=FALSE, warning=FALSE, fig.cap="Kaplan-Meier survival curves for total stroke mortality by drinking frequency (P value was obtained from log-rank tests) in Men.",fig.align='center',  out.width='100%', cache=TRUE}
+\begin{table}[!h]
+Table 3. Sex-specific hazard ratio (95\% CI) of mortality from stroke according to milk intake frequency.
 
-###################################################################################################
-## survival object
-###################################################################################################
-library(survival)
-library(ggplot2)
-library(survminer)
-library(cowplot)
-library(ggsci)
-
-# in Men
-su_obj_men <- Surv(MData_men$followpy, MData_men$Tot_Stroke == "I60_9")
-# in Women
-su_obj_fem <- Surv(MData_fem$followpy, MData_fem$Tot_Stroke == "I60_9")
-
-###################################################################################################
-## Kaplan-Meier plots and log rank tests for TotStroke and Milk intake  (frequency)
-###################################################################################################
-
-surv.Drfreq <- with(MData_men, survfit(su_obj_men ~ Mlkfre))
-
-ggsurv_Drfreq <- ggsurvplot(surv.Drfreq, censor = F, xlab = "Time (years)", conf.int = T, 
-                            conf.int.style = "step",  # customize style of confidence intervals
-                            surv.median.line = "none", ylab = "Survival function",
-                            legend.labs = c("Never or past", "< 1/week", "1-2 /week", "3-4 /week", "Daily"), 
-                            ggtheme = theme_bw(), palette = "npg",
-                            pval = TRUE, data = MData_men, # pval.method = TRUE
-                            risk.table = T,
-                            risk.table.y.text.col = T, # colour risk table text annotations.
-                            risk.table.y.text = FALSE,  pval.coord = c(0, 0.972),
-                            ylim = c(0.93, 1.0), xlim = c(0, 22)) 
-# show bars instead of names in text annotations)
-
-ggsurv_Drfreq <- ggpar(
-  ggsurv_Drfreq,
-  font.title    = c(14, "bold", "black"),         
-  # font.subtitle = c(15, "bold.italic", "purple"), 
-  #  font.caption  = c(14, "plain", "orange"),        
-  font.x        = c(14, "bold", "black"),          
-  font.y        = c(14, "bold", "black"),      
-  font.xtickslab = c(13, "bold", "black"),
-  #  font.ytickslab = c(13, "bold", "black"),
-  legend = "bottom", 
-  font.legend  = c(13, "bold", "black"),
-  legend.title = ""
-)
-ggsurv_Drfreq
-```
+\centering
+\fontsize{9}{11}\selectfont
+\begin{tabular}[t]{llllll}
+\toprule
+ & Never & 1-2 t/Mon & 1-2 t/Week & 3-4 t/Week & Daily\\
+\midrule
+\rowcolor{gray!6}  Men &  &  &  &  & \\
+N & 8508 & 3522 & 5928 & 5563 & 15865\\
+\rowcolor{gray!6}  Person year & 135704 & 56551 & 97098 & 92153 & 252364\\
+Total Stroke &  &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}n & 326 & 122 & 181 & 177 & 546\\
+\hspace{1em}Crude model & 1 & 0.89 (0.73, 1.11) & 0.77 (0.64, 0.92) & 0.79 (0.66, 0.95) & 0.90 (0.79, 1.04)\\
+\rowcolor{gray!6}  \hspace{1em}Age-adjusted & 1 & 0.99 (0.80, 1.22) & 0.84 (0.70, 1.01) & 0.86 (0.72, 1.03) & 0.76 (0.66, 0.87)\\
+\hspace{1em}Multivariable-adjusted & 1 & 1.03 (0.83, 1.27) & 0.91 (0.75, 1.09) & 0.96 (0.79, 1.16) & 0.87 (0.76, 1.01)\\
+\rowcolor{gray!6}  Hemorrhagic stroke &  &  &  &  \vphantom{1} & \\
+\hspace{1em}n & 100 & 42 & 58 & 56 & 176\\
+\rowcolor{gray!6}  \hspace{1em}Crude model & 1 & 1.00 (0.70, 1.44) & 0.81 (0.58, 1.11) & 0.82 (0.59, 1.14) & 0.94 (0.74, 1.21)\\
+\hspace{1em}Age-adjusted & 1 & 1.07 (0.75, 1.55) & 0.86 (0.62, 1.19) & 0.87 (0.63, 1.21) & 0.85 (0.66, 1.08)\\
+\rowcolor{gray!6}  \hspace{1em}Multivariable-adjusted & 1 & 1.11 (0.77, 1.60) & 0.94 (0.68, 1.31) & 1.01 (0.72, 1.40) & 0.98 (0.76, 1.27)\\
+Ischemic stroke &  &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}n & 151 & 41 & 64 & 66 & 198\\
+\hspace{1em}Crude model & 1 & 0.65 (0.46. 0.92) & 0.59 (0.44, 0.79) & 0.63 (0.48, 0.85) & 0.71 (0.57, 0.88)\\
+\rowcolor{gray!6}  \hspace{1em}Age-adjusted & 1 & 0.73 (0.52, 1.03) & 0.65 (0.49, 0.87) & 0.70 (0.53, 0.94) & 0.58 (0.47, 0.72)\\
+\hspace{1em}Multivariable-adjusted & 1 & 0.73 (0.51, 1.04) & 0.67 (0.49, 0.90) & 0.74 (0.55, 0.99) & 0.63 (0.50, 0.79)\\
+\rowcolor{gray!6}  Women &  &  &  &  & \\
+N & 10407 & 3640 & 7590 & 8108 & 25254\\
+\rowcolor{gray!6}  Person year & 173222 & 59904 & 129233 & 139919 & 418925\\
+Total Stroke &  &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}n & 300 & 84 & 182 & 172 & 585\\
+\hspace{1em}Crude model & 1 & 0.83 (0.65, 1.05) & 0.81 (0.67, 0.97) & 0.69 (0.58, 0.84) & 0.81 (0.71, 0.93)\\
+\rowcolor{gray!6}  \hspace{1em}Age-adjusted & 1 & 1.01 (0.79, 1.28) & 1.07 (0.89, 1.28) & 0.94 (0.78, 1.13) & 0.88 (0.77, 1.01)\\
+\hspace{1em}Multivariable-adjusted & 1 & 1.05 (0.82, 1.34) & 1.12 (0.93, 1.35) & 1.01 (0.83, 1.22) & 0.99 (0.86, 1.15)\\
+\rowcolor{gray!6}  Hemorrhagic stroke &  &  &  &  & \\
+\hspace{1em}n & 108 & 27 & 78 & 76 & 231\\
+\rowcolor{gray!6}  \hspace{1em}Crude model & 1 & 0.73 (0.48, 1.12) & 0.96 (0.72, 1.29) & 0.86 (0.64, 1.16) & 0.89 (0.71, 1.12)\\
+\hspace{1em}Age-adjusted & 1 & 0.83 (0.54, 1.26) & 1.16 (0.86, 1.55) & 1.04 (0.77, 1.39) & 0.92 (0.73, 1.15)\\
+\rowcolor{gray!6}  \hspace{1em}Multivariable-adjusted & 1 & 0.85 (0.56, 1.30) & 1.21 (0.90, 1.62) & 1.13 (0.84, 1.52) & 1.03 (0.81, 1.29)\\
+Ischemic stroke &  &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}n & 102 & 35 & 63 & 50 & 187\\
+\hspace{1em}Crude model & 1 & 1.01 (0.69, 1.48) & 0.82 (0.60, 1.13) & 0.59 (0.43, 0.84) & 0.76 (0.59, 0.97)\\
+\rowcolor{gray!6}  \hspace{1em}Age-adjusted & 1 & 1.29 (0.88, 1.89) & 1.15 (0.84, 1.58) & 0.86 (0.61, 1.20) & 0.86 (0.67, 1.09)\\
+\hspace{1em}Multivariable-adjusted & 1 & 1.30 (0.88, 1.92) & 1.18 (0.86, 1.63) & 0.87 (0.62, 1.23) & 0.93 (0.72, 1.19)\\
+\bottomrule
+\end{tabular}
+\end{table}

### 2020-01-11 AnalysisScript/traditionalPH.R

@@ -529,7 +529,11 @@ library("broom")
 tidy(SurvM0, exponentiate = TRUE, conf.int = TRUE) %>% 
   knitr::kable(.)
 
+epiDisplay::tabpct(MData_men$Mlkfre, MData_men$Tot_Stroke, graph = FALSE)
 
+MData_men %>% 
+  group_by(Mlkfre) %>% 
+  summarise(TotPY = sum(followpy))
 
 #' ## Model1 
 
@@ -550,6 +554,13 @@ tidy(SurvM2, exponentiate = TRUE, conf.int = TRUE) %>%
   knitr::kable(.)
 
 #' # In women 
+
+epiDisplay::tabpct(MData_fem$Mlkfre, MData_fem$Tot_Stroke, graph = FALSE)
+MData_fem %>% 
+  group_by(Mlkfre) %>% 
+  summarise(TotPY = sum(followpy))
+
+
 #' ## Model0
 
 SurvM0 <-  coxph(su_obj_fem ~ Mlkfre, 
@@ -588,6 +599,10 @@ su_obj_fem <- Surv(MData_fem$followpy, MData_fem$HemoStroke == "I60_2")
 
 
 #' # In Men
+#' 
+
+epiDisplay::tabpct(MData_men$Mlkfre, MData_men$HemoStroke)
+
 #' ## Model0
 
 SurvM0 <-  coxph(su_obj_men ~ Mlkfre, 
@@ -618,6 +633,9 @@ tidy(SurvM2, exponentiate = TRUE, conf.int = TRUE) %>%
   knitr::kable(.)
 
 #' # In women 
+
+epiDisplay::tabpct(MData_fem$Mlkfre, MData_fem$HemoStroke)
+
 #' ## Model0
 
 SurvM0 <-  coxph(su_obj_fem ~ Mlkfre, 
@@ -658,6 +676,9 @@ su_obj_fem <- Surv(MData_fem$followpy, MData_fem$IscheStroke == "I63")
 
 
 #' # In Men
+
+epiDisplay::tabpct(MData_men$Mlkfre, MData_men$IscheStroke)
+
 #' ## Model0
 
 SurvM0 <-  coxph(su_obj_men ~ Mlkfre, 
@@ -688,6 +709,9 @@ tidy(SurvM2, exponentiate = TRUE, conf.int = TRUE) %>%
   knitr::kable(.)
 
 #' # In women 
+
[…]

### 2020-01-11 AnalysisScript/jaccbayes.R
m0m1 men added

@@ -59,20 +59,20 @@ larynx.weibull.model <- function() {
   shape ~ dgamma(.001, .001)
   
   ### Generated values
-  AFT[2] <- exp(beta[2])
-  HR[2] <- exp(shape * beta[2])
+  AFT[2] <- exp(-beta[2])
+  HR[2] <- exp(-shape * beta[2])
   p.crit[2] <- step(1 - HR[2])
   
-  AFT[3] <- exp(beta[3])
-  HR[3] <- exp(shape * beta[3])
+  AFT[3] <- exp(-beta[3])
+  HR[3] <- exp(-shape * beta[3])
   p.crit[3] <- step(1 - HR[3])
   
-  AFT[4] <- exp(beta[4])
-  HR[4] <- exp(shape * beta[4])
+  AFT[4] <- exp(-beta[4])
+  HR[4] <- exp(-shape * beta[4])
   p.crit[4] <- step(1 - HR[4])
   
-  AFT[5] <- exp(beta[5])
-  HR[5] <- exp(shape * beta[5])
+  AFT[5] <- exp(-beta[5])
+  HR[5] <- exp(-shape * beta[5])
   p.crit[5] <- step(1 - HR[5])
 
   
@@ -83,15 +83,22 @@ MILKdataMEN <- c("t",  "c", "Mlkfre", "is.censored")
 larynx.params <- c("beta", "AFT", "HR", "p.crit", "shape")
 library(R2jags)
 
-JACC.weibull.fit <- jags(data = MILKdataMEN,
-                         parameters.to.save = larynx.params,
-                         n.chains = 2,
-                         n.iter = 1000,
-                         n.burnin = 100,
-                         n.thin = 1,
-                         model.file = larynx.weibull.model)
-print(JACC.weibull.fit)
-mcmcplots::traplot(JACC.weibull.fit, c("beta[5]", "HR[5]"))
+# JACC.weibull.fit <- jags(data = MILKdataMEN,
+#                          parameters.to.save = larynx.params,
+#                          n.chains = 2,
+#                          n.iter = 1000,
+#                          n.burnin = 100,
+#                          n.thin = 1,
+#                          model.file = larynx.weibull.model)
+
[…]

### 2020-01-11 AnalysisScript/tryYoshida.R

@@ -1,148 +1,0 @@
-# https://rpubs.com/kaz_yos/bayes_surv1
-
-library(tidyverse)
-library(survminer)
-## library(bayesSurv)
-# devtools::install_github('jburos/biostan', build_vignettes = FALSE, dependencies = TRUE)
-library(biostan)
-library(rstan)
-library(bayesplot)
-library(tidybayes)  
-library(survival)
-
-data(leukemia, package = "survival")
-leukemia <- as_data_frame(leukemia)
-leukemia  
-km_fit <- survfit(Surv(time, status) ~ x, data = leukemia)
-km_fit
-ggsurvplot(km_fit,
-           conf.int = TRUE,
-           break.time.by = 20,
-           risk.table = TRUE)
-stan_weibull_survival_model_file <- system.file('stan', 'weibull_survival_model.stan', package =  'biostan')
-biostan::print_stan_file(stan_weibull_survival_model_file)
-
-stan_weibull_survival_model_code <- biostan::read_stan_file(stan_weibull_survival_model_file)
-biostan::print_stan_code(stan_weibull_survival_model_code, section = "data")
-
-
-stan_weibull_survival_model_data <-
-  list(
-    ## Number of event individuals
-    Nobs = sum(leukemia$status == 1),
-    ## Number of censored individuals
-    Ncen = sum(leukemia$status == 0),
-    ## Number of covariates
-    M_bg = 1,
-    ## Times for event individuals
-    yobs = leukemia$time[leukemia$status == 1],
-    ## Times for censored individuals
-    ycen = leukemia$time[leukemia$status == 0],
-    ## Covariates for event individuals as a matrix
-    Xobs_bg = matrix(as.numeric(leukemia$x == "Maintained")[leukemia$status == 1]),
-    ## Covariates for censored individuals as a matrix
-    Xcen_bg = matrix(as.numeric(leukemia$x == "Maintained")[leukemia$status == 0])
-  )
-stan_weibull_survival_model_data
-
-
-stan_weibull_survival_model_fit <-
-  rstan::stan(file = stan_weibull_survival_model_file,
-              data = stan_weibull_survival_model_data)
-
-
-rstan::traceplot(stan_weibull_survival_model_fit, par = c("alpha","mu","beta_bg"))
-bayesplot::mcmc_acf(as.matrix(stan_weibull_survival_model_fit), pars = c("alpha","mu","beta_bg[1]"))
[…]

### 2020-01-11 weibullStanFromNet.R

@@ -1,0 +1,73 @@
+# https://www.bioconductor.org/help/course-materials/2016/BioC2016/ConcurrentWorkshops4/Buros/weibull-survival-model.html
+
+
+library(biostan)
+stan_file <- system.file('stan', 'weibull_survival_null_model.stan', package =  'biostan')
+biostan::print_stan_file(stan_file)
+if (interactive())
+  file.edit(stan_file)
+print_stan_file(stan_file, section = 'data')
+print_stan_file(stan_file, section = 'model')
+print_stan_file(stan_file, section = 'transformed parameters')
+
+
+
+sim_data <- function(alpha, mu, Nobs, Ncen) {
+  observed_data <- data.frame(os_status = rep_len('DECEASED', Nobs),
+                              os_months = rweibull(n = Nobs, alpha, exp(-(mu)/alpha)),
+                              stringsAsFactors = F
+  )
+  
+  censored_data <- data.frame(os_status = rep_len('LIVING', Ncen),
+                              os_months = runif(Ncen) * rweibull(Ncen, alpha, exp(-(mu)/alpha)),
+                              stringsAsFactors = F
+  )
+  
+  return(observed_data %>% bind_rows(censored_data))
+}
+
+test_alpha <- 0.8
+test_mu <- -3
+
+## sample sizes from TCGA blca data
+test_nobs <- 179 
+test_ncen <- 230
+
+## test these inputs for arbitrary values of alpha & mu
+simulated_data <- 
+  sim_data(alpha = test_alpha,
+           mu = test_mu,
+           Nobs = test_nobs,
+           Ncen = test_ncen
+  ) 
+head(simulated_data)
+
+
+print_stan_file(stan_file, section = 'data')
+
+
+observed_data <- simulated_data %>%
+  dplyr::filter(os_status == 'DECEASED')
+
+censored_data <- simulated_data %>%
+  dplyr::filter(os_status != 'DECEASED')
+
+stan_data <- list(
+  Nobs = nrow(observed_data),
+  Ncen = nrow(censored_data),
+  yobs = observed_data$os_months,
+  ycen = censored_data$os_months
+)
+rm(censored_data)
+rm(observed_data)
+str(stan_data)
+
+
+recover_simulated <- 
+  rstan::stan(stan_file,
+              data = stan_data,
+              chains = 4,
+              iter = 1000,
+              seed = 1328025050
+  )
+print(recover_simulated)

### 2020-01-12 ForReport20200114/HandOutEngBayes.tex
updated trace plot m0men

\documentclass[]{tufte-handout}

% ams
\usepackage{amssymb,amsmath}

\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \makeatletter
  \@ifpackageloaded{fontspec}{}{\usepackage{fontspec}}
  \makeatother
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \makeatletter
  \@ifpackageloaded{soul}{
     \renewcommand\allcapsspacing[1]{{\addfontfeature{LetterSpace=15}#1}}
     \renewcommand\smallcapsspacing[1]{{\addfontfeature{LetterSpace=10}#1}}
   }{}
  \makeatother

\fi

% graphix
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}

% booktabs
\usepackage{booktabs}

% url
\usepackage{url}

% hyperref
\usepackage{hyperref}

% units.
\usepackage{units}

\setcounter{secnumdepth}{-1}

% citations
\usepackage{natbib}
\bibliographystyle{plainnat}

% pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}

% longtable

% multiplecol
\usepackage{multicol}

% strikeout
\usepackage[normalem]{ulem}

% morefloats
\usepackage{morefloats}

% tightlist macro required by pandoc >= 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% title / author / date
\title{Try Bayesian Survival Analysis using the JACC study data (Bayesian
Survival Analysis presentations)}
\author{Chaochen Wang \textbar{} Aichi Medical University}
\date{2020-01-12}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\maketitle

\hypertarget{parametric-survival-analysis-model-in-a-bayesian-way}{%
\subsection{Parametric Survival Analysis Model (in a Bayesian
way)}\label{parametric-survival-analysis-model-in-a-bayesian-way}}

\begin{marginfigure}
Weibull Survival funciton in a proportional hazard way expression is:
\[S(t | \mathbf{x}) = \exp\{ -\lambda t ^\kappa e^{\mathbf{\beta_{PH}^T x}} \}\]
\end{marginfigure}

\begin{marginfigure}
Weibull Survival funciton in a AFT way expression is:
\[S(t | \mathbf{x}) = \exp\{ -\lambda t ^\kappa e^{\kappa\mathbf{\beta_{AFT}^T x}} \}\]
\end{marginfigure}

\begin{itemize}
\item
  We chose Weibull model to describe the survival data we have.
\item
  Weibull model is both a proportional hazard model and a accelerated
  failure time (AFT) model. The relationship between the acceleration
  factor and log hazard ratio:
\end{itemize}

\[
\exp(\beta^T_{PH}) = \exp(\kappa\beta^T_{AFT})
\]

\hypertarget{an-example-of-a-crude-weibull-model-using-the-jags-program-in-r}{%
\subsection{An example of a crude Weibull model using the JAGS program
in
R:}\label{an-example-of-a-crude-weibull-model-using-the-jags-program-in-r}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{jacc.weibull.model <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{() \{}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{39386}\NormalTok{)\{}
    \CommentTok{# sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])}
\NormalTok{    is.censored[i] }\OperatorTok{~}\StringTok{ }\KeywordTok{dinterval}\NormalTok{(t[i], c[i])}
\NormalTok{    t[i] }\OperatorTok{~}\StringTok{ }\KeywordTok{dweib}\NormalTok{(shape, lambda[i])}
\NormalTok{    lambda[i] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(}\OperatorTok{-}\NormalTok{mu[i] }\OperatorTok{*}\StringTok{ }\NormalTok{shape)}
\NormalTok{    mu[i] <-}\StringTok{ }\NormalTok{beta[}\DecValTok{1}\NormalTok{] }\OperatorTok{+}\StringTok{ }\NormalTok{beta[}\DecValTok{2}\NormalTok{]}\OperatorTok{*}\KeywordTok{equals}\NormalTok{(Mlkfre[i], }\DecValTok{2}\NormalTok{) }\OperatorTok{+}
\StringTok{      }\NormalTok{beta[}\DecValTok{3}\NormalTok{]}\OperatorTok{*}\KeywordTok{equals}\NormalTok{(Mlkfre[i], }\DecValTok{3}\NormalTok{) }\OperatorTok{+}\StringTok{ }\NormalTok{beta[}\DecValTok{4}\NormalTok{] }\OperatorTok{*}\StringTok{ }\KeywordTok{equals}\NormalTok{(Mlkfre[i], }\DecValTok{4}\NormalTok{) }\OperatorTok{+}
\StringTok{      }\NormalTok{beta[}\DecValTok{5}\NormalTok{] }\OperatorTok{*}\StringTok{ }\KeywordTok{equals}\NormalTok{(Mlkfre[i], }\DecValTok{5}\NormalTok{) }\CommentTok{# + }
      \CommentTok{# beta[6] * sAge[i]}

    \CommentTok{### calculate log-likelihoods}
    \CommentTok{# y[i] <- ifelse(is.censored[i], c[i], t[i])}
    \CommentTok{# loglik[i] <- log(ifelse(is.censored[i],}
    \CommentTok{#                  exp(-lambda[i] * (y[i] ^ shape)),}
    \CommentTok{#               shape * lambda[i] * (y[i] ^ (shape - 1)) * exp(-lambda[i] * (y[i] ^ shape))))}
\NormalTok{  \}}

  \CommentTok{## priors for betas}
  \ControlFlowTok{for}\NormalTok{(j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{)\{}
\NormalTok{    beta[j] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.001}\NormalTok{)}
\NormalTok{  \}}

  \CommentTok{### prior for shape}
\NormalTok{  shape }\OperatorTok{~}\StringTok{ }\KeywordTok{dgamma}\NormalTok{(.}\DecValTok{001}\NormalTok{, }\FloatTok{.001}\NormalTok{)}

  \CommentTok{### Generated values}
\NormalTok{  AFT[}\DecValTok{2}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(beta[}\DecValTok{2}\NormalTok{])}
\NormalTok{  HR[}\DecValTok{2}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(shape }\OperatorTok{*}\StringTok{ }\NormalTok{beta[}\DecValTok{2}\NormalTok{])}
\NormalTok{  p.crit[}\DecValTok{2}\NormalTok{] <-}\StringTok{ }\KeywordTok{step}\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{HR[}\DecValTok{2}\NormalTok{])}

\NormalTok{  AFT[}\DecValTok{3}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(beta[}\DecValTok{3}\NormalTok{])}
\NormalTok{  HR[}\DecValTok{3}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(shape }\OperatorTok{*}\StringTok{ }\NormalTok{beta[}\DecValTok{3}\NormalTok{])}
\NormalTok{  p.crit[}\DecValTok{3}\NormalTok{] <-}\StringTok{ }\KeywordTok{step}\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{HR[}\DecValTok{3}\NormalTok{])}

\NormalTok{  AFT[}\DecValTok{4}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(beta[}\DecValTok{4}\NormalTok{])}
\NormalTok{  HR[}\DecValTok{4}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(shape }\OperatorTok{*}\StringTok{ }\NormalTok{beta[}\DecValTok{4}\NormalTok{])}
\NormalTok{  p.crit[}\DecValTok{4}\NormalTok{] <-}\StringTok{ }\KeywordTok{step}\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{HR[}\DecValTok{4}\NormalTok{])}

\NormalTok{  AFT[}\DecValTok{5}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(beta[}\DecValTok{5}\NormalTok{])}
\NormalTok{  HR[}\DecValTok{5}\NormalTok{] <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(shape }\OperatorTok{*}\StringTok{ }\NormalTok{beta[}\DecValTok{5}\NormalTok{])}
\NormalTok{  p.crit[}\DecValTok{5}\NormalTok{] <-}\StringTok{ }\KeywordTok{step}\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{HR[}\DecValTok{5}\NormalTok{])}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

You can use the following codes to run the above model (careful about
the cost of time):

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(R2jags) }\CommentTok{#conect to jags sampling engine in R}
\NormalTok{jagsfit <-}\StringTok{ }\KeywordTok{jags.parallel}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ JACCdata,}
                         \DataTypeTok{parameters.to.save =} \KeywordTok{c}\NormalTok{(}\StringTok{"beta[5]"}\NormalTok{, }\StringTok{"HR[5]"}\NormalTok{, }\StringTok{"AFT[5]"}\NormalTok{),}
                         \CommentTok{#add more variables if you want to check more}
                         \DataTypeTok{n.iter =} \DecValTok{10000}\NormalTok{, }
                         \DataTypeTok{n.burnin =} \DecValTok{2500}\NormalTok{, }
                         \DataTypeTok{n.chains =} \DecValTok{3}\NormalTok{,}
                         \DataTypeTok{model.file =}\NormalTok{ jacc.weibull.model)}
\end{Highlighting}
\end{Shaded}

\hypertarget{check-model-fitting}{%
\subsection{Check model fitting:}\label{check-model-fitting}}

\includegraphics{HandOutEngBayes_files/figure-latex/unnamed-chunk-5-1}

\bibliography{skeleton.bib}

\end{document}

### 2020-01-12 AnalysisScript/ModelsJAGSwomen.R
start working on women models

@@ -1,0 +1,86 @@
+##%######################################################%##
+#                                                          #
+####                  data preparation                  ####
+#                                                          #
+##%######################################################%##
+
+# stage <- larynx.dat$stage
+Mlkfre <- as.numeric(MData_fem$Mlkfre)
+table(Mlkfre)
+table(MData_fem$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
+MlkLogi <- as.numeric(MData_fem$MlkLogi == "Drinker")
+
+# is.censored <- is.na(t)
+is.censored <- MData_fem$Tot_Stroke != "I60_9"
+
+# t <- larynx.dat$time
+t <- if_else(!is.censored, MData_fem$followpy, 0)
+t <- na_if(t, 0)
+t
+
+# age <- larynx.dat$age
+Agegrp <- as.numeric(MData_fem$Agegrp)
+table(Agegrp)
+table(MData_fem$Agegrp)  # 1 = [30,45) ; 2 = [45,55) ; 3 = [55,65) ; 4 =  [65,75) ; 5 = [75,80) 
+Age <- MData_fem$Age
+
+
+# c <- larynx.dat$cens_time
+c <- if_else(is.censored, MData_fem$followpy, 0)
+
+
+c[!is.censored] <- t[!is.censored] + 1
+# c
+# t
+# is.censored
+
+
+larynx.weibull.model <- function() {
+  for(i in 1:54999){
+    # sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])
+    # sYr[i] <- (yr[i] - mean(yr[])) / sd(yr[])
+    is.censored[i] ~ dinterval(t[i], c[i])
+    t[i] ~ dweib(shape, lambda[i])
+    lambda[i] <- exp(-mu[i] * shape)
+    mu[i] <- beta[1] + beta[2]*equals(Mlkfre[i], 2) +
+      beta[3]*equals(Mlkfre[i], 3) + beta[4] * equals(Mlkfre[i], 4) +
+      beta[5] * equals(Mlkfre[i], 5) 
+    
+    ### calculate log-likelihoods
+    # y[i] <- ifelse(is.censored[i], c[i], t[i])
+    # loglik[i] <- log(ifelse(is.censored[i],
[…]

### 2020-01-12 AnalysisScript/jaccbayes.R

@@ -319,6 +319,6 @@ MILKdataMEN <- c("t",  "c", "Mlkfre", "is.censored", "Age", "Smoking",
                  "Educgrp", "Gretea", "Fru")
 M2.params <- c("AFT", "HR", "p.crit")
 jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = M2.params, 
-                         n.iter=10000, n.burnin=(5000/2), n.chains = 3,
+                         n.iter=100, n.burnin=(50/2), n.chains = 3,
                          model.file=M2.weibull.model)
 print(jagsfit)

### 2020-01-12 ForReport20200114/HandOutEng.Rmd

@@
 ---
-title: "Try Bayesian Survival Analysis using the JACC study data"
+title: "Try Bayesian Survival Analysis using the JACC study data (traditional Cox-proportional hazard model presentations)"
 subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
@@
     keep_tex: true
+    # includes:  
+    #   in_header: preamble-latex.tex
   tufte::tufte_html: default
@@
 
-Before exclusion, we have 110585 participants (46395 men and 64190 women) in the JACC data set:
+Before exclusion, we have 110585 participants (46395 men and 64190 women) aged between 40-79 at baseline in the JACC data set:
 
@@
 
-<!-- Tufte样式在Edward Tufte的书以及物理学家费曼的教科书很常见，它的一个显著特点就是边栏的使用。例如脚注和边栏注解，以及放在边栏里的小型插图。Tufte样式在LaTeX和HTML/CSS中都有实现^[参见Github库[tufte-latex](https://github.com/tufte-latex/tufte-latex)和 [tufte-css](https://github.com/edwardtufte/tufte-css)]。我们将这两种实现都纳入了[**tufte**包](https://github.com/rstudio/tufte)。若需要LaTeX/PDF输出，使用输出格式`tufte_handout`即可，类似地，`tufte_book`可以用来输出PDF书，`tufte_html`生成HTML网页。这些输出格式可以在YAML元数据中指定，或者传给`rmarkdown::render()`函数。若对**rmarkdown**包不熟悉，可参见 @R-rmarkdown。 -->
-
-<!-- ```yaml -->
-<!-- --- -->
-<!-- title: "一个Tufte样式示例" -->
-<!-- author: "张三" -->
-<!-- ctex: yes -->
-<!-- output: -->
-<!--   tufte::tufte_handout: -->
-<!--     latex_engine: xelatex -->
-<!--   tufte::tufte_html: default -->
-<!-- --- -->
-<!-- ``` -->
-
-<!-- # 章节标题 -->
-
-<!-- Tufte样式不主张太深的章节目录，一般仅仅使用一级标题（Markdown中用一个井号`#`）和二级标题（两个井号）。 -->
-
 \newpage
@@
 
-\begin{table}[ht]
+\begin{table}[!htbp]
 
@@
 
-\begin{table}[ht]
+\begin{table}[!htbp]
 Table 2. Baseline characteristics of subjects in the JACC study by milk intake level in Women (n = 54,999).
@@
 
-\begin{table}[!h]
+\begin{table}[!htbp]
 Table 3. Sex-specific hazard ratio (95\% CI) of mortality from stroke according to milk intake frequency.

### 2020-01-12 ForReport20200114/HandOutEngBayes.Rmd

---
title: "Try Bayesian Survival Analysis using the JACC study data (Bayesian Survival Analysis presentations)"
subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
author: "Chaochen Wang | Aichi Medical University"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
    # includes:  
    #   in_header: preamble-latex.tex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

## Parametric Survival Analysis Model (in a Bayesian way)

```{marginfigure}
Weibull Survival funciton in a proportional hazard way expression is:
$$S(t | \mathbf{x}) = \exp\{ -\lambda t ^\kappa e^{\mathbf{\beta_{PH}^T x}} \}$$
```

```{marginfigure}
Weibull Survival funciton in a AFT way expression is:
$$S(t | \mathbf{x}) = \exp\{ -\lambda t ^\kappa e^{\kappa\mathbf{\beta_{AFT}^T x}} \}$$
```

- We chose Weibull model to describe the survival data we have.

- Weibull model is both a proportional hazard model and a accelerated failure time (AFT) model. The relationship between the acceleration factor and log hazard ratio:

$$
\exp(\beta^T_{PH}) = \exp(\kappa\beta^T_{AFT})
$$

## An example of a crude Weibull model using the JAGS program in R:

```{r modeljag, eval=FALSE}
jacc.weibull.model <- function() {
  for(i in 1:39386){
    # sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])
    is.censored[i] ~ dinterval(t[i], c[i])
    t[i] ~ dweib(shape, lambda[i])
    lambda[i] <- exp(-mu[i] * shape)
    mu[i] <- beta[1] + beta[2]*equals(Mlkfre[i], 2) +
      beta[3]*equals(Mlkfre[i], 3) + beta[4] * equals(Mlkfre[i], 4) +
      beta[5] * equals(Mlkfre[i], 5) # + 
      # beta[6] * sAge[i]

    ### calculate log-likelihoods
    # y[i] <- ifelse(is.censored[i], c[i], t[i])
    # loglik[i] <- log(ifelse(is.censored[i],
    #                  exp(-lambda[i] * (y[i] ^ shape)),
    #               shape * lambda[i] * (y[i] ^ (shape - 1)) * exp(-lambda[i] * (y[i] ^ shape))))
  }

  ## priors for betas
  for(j in 1:5){
    beta[j] ~ dnorm(0, 0.001)
  }

  ### prior for shape
  shape ~ dgamma(.001, .001)

  ### Generated values
  AFT[2] <- exp(beta[2])
  HR[2] <- exp(shape * beta[2])
  p.crit[2] <- step(1 - HR[2])

  AFT[3] <- exp(beta[3])
  HR[3] <- exp(shape * beta[3])
  p.crit[3] <- step(1 - HR[3])

  AFT[4] <- exp(beta[4])
  HR[4] <- exp(shape * beta[4])
  p.crit[4] <- step(1 - HR[4])

  AFT[5] <- exp(beta[5])
  HR[5] <- exp(shape * beta[5])
  p.crit[5] <- step(1 - HR[5])
}
```

You can use the following codes to run the above model (careful about the cost of time):

```{r eval=FALSE}
library(R2jags) #conect to jags sampling engine in R
jagsfit <- jags.parallel(data = JACCdata,
                         parameters.to.save = c("beta[5]", "HR[5]", "AFT[5]"),
                         #add more variables if you want to check more
                         n.iter = 10000, 
                         n.burnin = 2500, 
                         n.chains = 3,
                         model.file = jacc.weibull.model)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
load("../data/jagmodel0men.Rdata")
# Simulated <- coda::as.mcmc(jagsfit)
Simulated <- mcmcplots::as.mcmc.bugs(jagsfit$BUGSoutput)
library(ggmcmc)
ggSample <- ggs(Simulated)

```

## Check model fitting:

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.margin = FALSE}
library(tidyverse)
ggSample %>% 
  filter(Iteration >= 500 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
  ggs_traceplot()
```

### 2020-01-12 AnalysisScript/JACCBAYES.R
gave up the stan version

@@ -1,0 +1,94 @@
+# stage <- larynx.dat$stage
+Mlkfre <- MData_men$Mlkfre
+MlkLogi <- as.numeric(MData_men$MlkLogi == "Drinker")
+
+# is.censored <- is.na(t)
+is.censored <- MData_men$Tot_Stroke != "I60_9"
+
+# t <- larynx.dat$time
+t <- if_else(!is.censored, MData_men$followpy, 0)
+t <- na_if(t, 0)
+t
+
+# age <- larynx.dat$age
+Agegrp <- MData_men$Agegrp
+Age <- MData_men$Age
+
+
+# c <- larynx.dat$cens_time
+c <- if_else(is.censored, MData_men$followpy, 0)
+
+
+c[!is.censored] <- t[!is.censored] + 1
+# c
+# t
+# is.censored
+
+
+larynx.weibull.model <- function() {
+  for(i in 1:39386){
+    sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])
+    # sYr[i] <- (yr[i] - mean(yr[])) / sd(yr[])
+    is.censored[i] ~ dinterval(t[i], c[i])
+    t[i] ~ dweib(shape, lambda[i])
+    lambda[i] <- exp(-mu[i] * shape)
+    mu[i] <- beta[1] + beta[2]*equals(MlkLogi[i], 1) +
+      # beta[3]*equals(Age[i], 3) + beta[4] * equals(stage[i], 4) +
+      beta[3] *sAge[i] 
+    
+    ### calculate log-likelihoods
+    y[i] <- ifelse(is.censored[i], c[i], t[i])
+    loglik[i] <- log(ifelse(is.censored[i],
+                            exp(-lambda[i] * (y[i] ^ shape)),
+                            shape * lambda[i] * (y[i] ^ (shape - 1)) * exp(-lambda[i] * (y[i] ^ shape))))
+  }
+  
+  ## priors for betas
+  for(j in 1:3){
+    beta[j] ~ dnorm(0, 0.001)
+  }
+  
+  ### prior for shape
+  shape ~ dgamma(.001, .001)
+  
+  ### Generated values
+  AFT[2] <- exp(beta[2])
+  HR[2] <- exp(shape * beta[2])
+  p.crit[2] <- step(1 - HR[2])  
+  AFT[3] <- exp(beta[3])
+  HR[3] <- exp(shape * beta[3])
[…]

### 2020-01-12 AnalysisScript/tryYoshidaStanWeibullModel.R

@@ -36,7 +36,7 @@ stan_weibull_survival_model_data <-
     ## Covariates for event individuals as a matrix
     Xobs_bg = matrix(as.numeric(MData_men$MlkLogi == "Drinker")[MData_men$Tot_Stroke == "I60_9"]),
     ## Covariates for censored individuals as a matrix
-    Xcen_bg = matrix(as.numeric(MData_men$MlkLogi == "Never")[MData_men$Tot_Stroke != "I60_9"])
+    Xcen_bg = matrix(as.numeric(MData_men$MlkLogi == "Drinker")[MData_men$Tot_Stroke != "I60_9"])
   )
 stan_weibull_survival_model_data
 

### 2020-01-12 ForReport20200114/HandOutEngBayes.Rmd
updated figure setting

@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, fig.margin = FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE, fig.margin = FALSE, fig.height=7, fig.width=6}
 library(tidyverse)

### 2020-01-12 ForReport20200114/HandOutEngBayes.Rmd
updated handout bayes age-adjusted model done

--- 2020-01-12 ForReport20200114/HandOutEngBayes.Rmd
@@
 options(htmltools.dir.version = FALSE)
+options(scipen=999)
 ```
@@
 
+```{marginfigure}
+Acceleration factor is the factor by which time to failure/event is accelerated for $x_1 = 1$ compared with $x_1 = 0$
+```
+
 ## An example of a crude Weibull model using the JAGS program in R:
@@
 jacc.weibull.model <- function() {
-  for(i in 1:39386){
+  for(i in 1:39386){# loop through the subjects
     # sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])
@@
 
+The output of the above crude Weibull model:
+
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
 load("../data/jagmodel0men.Rdata")
+# summary(mcmcplots::convert.mcmc.list(jagsfit))
+# Simulated <- coda::as.mcmc(jagsfit)
+Simulated <- mcmcplots::as.mcmc.bugs(jagsfit$BUGSoutput)
+library(ggmcmc)
+ggSample <- ggs(Simulated)
+# jagsfit$BUGSoutput
+```
+
+```
+# Inference for Bugs model at "jacc.weibull.model", fit using jags,
+#  3 chains, each with 10000 iterations (first 2500 discarded), n.thin = 7
+#  n.sims = 3213 iterations saved. Sample size per chain = 1071 
+# 1. Empirical mean and standard deviation for each variable,
+#    plus standard error of the mean:
+#                   Mean        SD   Naive SE Time-series SE
+# AFT[2]        0.922303  0.064441 0.00113685     0.00420403
+# AFT[3]        0.834723  0.051485 0.00090830     0.00362857
+# AFT[4]        0.848329  0.052439 0.00092513     0.00401102
+# AFT[5]        0.928095  0.041834 0.00073803     0.00336613
+# HR[2]         0.890533  0.090586 0.00159811     0.00604246
+# HR[3]         0.769913  0.069116 0.00121934     0.00486858
+# HR[4]         0.788205  0.070624 0.00124594     0.00531505
+# HR[5]         0.897882  0.058477 0.00103164     0.00468654
+# p.crit[2]     0.871460  0.334743 0.00590548     0.01814848
+# p.crit[3]     0.996265  0.061008 0.00107630     0.00214585
+# p.crit[4]     0.998133  0.043180 0.00076177     0.00097572
+# p.crit[5]     0.953626  0.210327 0.00371056     0.02050164
+# 2. Quantiles for each variable:
+#                   2.5%          25%          50%         75%       97.5%
+# AFT[2]        0.807308     0.876649     0.918049     0.96495     1.05225
+# AFT[3]        0.738423     0.799925     0.832078     0.86719     0.94214
+# AFT[4]        0.749645     0.810952     0.847050     0.88448     0.95291
+# AFT[5]        0.847796     0.899999     0.927850     0.95594     1.01147
+# HR[2]         0.733186     0.825541     0.883106     0.94896     1.07725
+# HR[3]         0.644053     0.721892     0.765778     0.81289     0.91643
+# HR[4]         0.658787     0.737562     0.785538     0.83614     0.93282
+# HR[5]         0.788623     0.857453     0.896668     0.93613     1.01665
+# ...
+```
+
+## Check model fitting:
+
+```{r echo=FALSE, fig.height=4.5, fig.width=5, message=FALSE, warning=FALSE, fig.cap="Traceplot for AFT, and HR of daily milk drinkers from crude model (men)."}
+library(tidyverse)
+ggSample %>% 
+  filter(Iteration >= 120 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
+  ggs_traceplot()
+```
+```{r badtrace, echo=FALSE, out.width = '90%', cache=TRUE, fig.cap="Not overlapping traceplot indicating that model is not converged.",fig.align='center', fig.margin = TRUE}
+knitr::include_graphics("fig/badtraceplot.png")
+```
+
+<!-- ```{marginfigure} -->
+<!-- Overlapping of the posterior sampling chains is good. -->
+<!-- ``` -->
+
+```{r echo=FALSE, fig.height=4.5, fig.width=5, message=FALSE, warning=FALSE, fig.cap="Autocorrelation figures for AFT, and HR of daily milk drinkers from crude model (men)."}
+
+ggSample %>% 
+  filter(Iteration >= 120 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
+  ggs_autocorrelation()
+```
+
+```{r badauto, echo=FALSE, out.width = '90%', cache=TRUE, fig.cap="(bad example)Highly correlated posterior samples indicating that the samples are not independent.",fig.align='center', fig.margin = FALSE}
+knitr::include_graphics("fig/badautocorrelation.png")
+```
+
+<!-- We can report the above findings as:  -->
+
+```{r tab1, echo=FALSE, eval=FALSE, message=FALSE}
+library(knitr)
+library(kableExtra)
+dt <- read.csv("tab/HRAFTweib.csv", header = T)
+names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
+kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
+```
+
+\begin{table}[!htbp]
+Table 1.
+Estimated (crude) hazard ratios and acceleration factors for the association of milk intake and risk of stroke mortality using Bayesian MCMC methods in Men of the JACC study data (n = 39,386).
+
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllllllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
+\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
+Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
+\midrule
+\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
+1-2 t/Mon & 0.88 & 0.89 (0.09) & (0.73, 1.08) & 0.0016 & 87.15\% & 0.92 & 0.92 (0.06) & (0.81, 1.06) & 0.0011\\
+\rowcolor{gray!6}  1-2 t/Week & 0.77 & 0.77 (0.07) & (0.64, 0.92) & 0.0012 & 99.63\% & 0.83 & 0.83 (0.05) & (0.74, 0.94) & 0.0009\\
+3-4 t/Week & 0.79 & 0.79 (0.07) & (0.66, 0.93) & 0.0012 & 99.81\% & 0.85 & 0.85 (0.05) & (0.75, 0.95) & 0.0009\\
+\rowcolor{gray!6}  Daily & 0.89 & 0.90 (0.06) & (0.79, 1.02) & 0.0010 & 95.36\% & 0.93 & 0.93 (0.04) & (0.85, 1.01) & 0.0007\\
+\bottomrule
+\multicolumn{10}{l}{\textit{Note: }}\\
+\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{10}{l}{ Probability indicates that p for HR smaller than 1.}\\
+\end{tabular}
+\end{table}
+
+```{r echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Crude model HR posterior density plots."}
+par(mfrow = c(2,2))
+# HR2
+HR2 <- ggSample %>% 
+  filter(Parameter == "HR[2]")
+denHR5 <- density(HR2$value)
+plot(denHR5, main = "HR2 posterior density plot \n (shaded area = 0.8715).", 
+     ylab = "P(HR2)", xlab = "HR2 (1-2 t/Mon drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+# HR3
+HR2 <- ggSample %>% 
+  filter(Parameter == "HR[3]")
+denHR5 <- density(HR2$value)
+plot(denHR5, main = "HR3 posterior density plot \n (shaded area = 0.9963).", 
+     ylab = "P(HR3)", xlab = "HR3 (1-2 t/Week drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+# HR4 
+HR2 <- ggSample %>% 
+  filter(Parameter == "HR[4]")
+denHR5 <- density(HR2$value)
+plot(denHR5, main = "HR4 posterior density plot \n (shaded area = 0.9981).", 
+     ylab = "P(HR4)", xlab = "HR4 (3-4 t/Week drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+# HR5
+HR5 <- ggSample %>% 
+  filter(Parameter == "HR[5]")
+denHR5 <- density(HR5$value)
+plot(denHR5, main = "HR5 posterior density plot \n (shaded area = 0.9536)", 
+     ylab = "P(HR5)", xlab = "HR5 (daily drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+```
+
+```{r echo=FALSE, fig.height=3, fig.width=4, message=FALSE, warning=FALSE, fig.cap="HR5 posterior density plot (shaded area = 0.9536).", eval=FALSE}
+HR5 <- ggSample %>% 
+  filter(Parameter == "HR[5]")
+denHR5 <- density(HR5$value)
+plot(denHR5, main = "HR5 posterior density plot", 
+     ylab = "P(HR5)", xlab = "HR5 (daily drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+```
+
+```{r tab2, echo=FALSE, eval=FALSE, message=FALSE}
+library(knitr)
+library(kableExtra)
+dt <- read.csv("tab/HRAFTweibM1.csv", header = T)
+names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
+kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
+```
+
+\begin{table}[!htbp]
+Table 2.
+Estimated (age-adjusted) hazard ratios and acceleration factors for the association of milk intake and risk of stroke mortality using Bayesian MCMC methods in Men of the JACC study data (n = 39,386).
+
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllllllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
+\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
+Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
+\midrule
+\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
+1-2 t/Mon & 0.98 & 0.98 (0.11) & (0.78, 1.19) & 0.0018 & 57.86\% & 0.98 & 0.99 (0.06) & (0.87, 1.11) & 0.0011\\
+\rowcolor{gray!6}  1-2 t/Week & 0.84 & 0.84 (0.08) & (0.69, 0.99) & 0.0014 & 97.79\% & 0.90 & 0.90 (0.05) & (0.80, 0.99) & 0.0008\\
+3-4 t/Week & 0.86 & 0.86 (0.08) & (0.71, 1.02) & 0.0014 & 95.92\% & 0.91 & 0.91 (0.05) & (0.82, 1.01) & 0.0009\\
+\rowcolor{gray!6}  Daily & 0.75 & 0.75 (0.05) & (0.67, 0.85) & 0.0009 & 100.00\% & 0.85 & 0.85 (0.03) & (0.79, 0.91) & 0.0006\\
+\bottomrule
+\multicolumn{10}{l}{\textit{Note: }}\\
+\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{10}{l}{ Probability indicates the p for HR smaller than 1.}\\
+\end{tabular}
+\end{table}
+
+```{r echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Age-adjusted HR posterior density plots."}
+load("../data/jagmodel1Agemen.Rdata")
+# summary(mcmcplots::convert.mcmc.list(jagsfit))
 # Simulated <- coda::as.mcmc(jagsfit)
@@
 
+par(mfrow = c(2,2))
+# HR2
+HR2 <- ggSample %>% 
+  filter(Parameter == "HR[2]")
+denHR5 <- density(HR2$value)
+plot(denHR5, main = "HR2 posterior density plot \n (shaded area = 0.5786).", 
+     ylab = "P(HR2)", xlab = "HR2 (1-2 t/Mon drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+# HR3
+HR2 <- ggSample %>% 
+  filter(Parameter == "HR[3]")
+denHR5 <- density(HR2$value)
+plot(denHR5, main = "HR3 posterior density plot \n (shaded area = 0.9779).", 
+     ylab = "P(HR3)", xlab = "HR3 (1-2 t/Week drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+# HR4 
+HR2 <- ggSample %>% 
+  filter(Parameter == "HR[4]")
+denHR5 <- density(HR2$value)
+plot(denHR5, main = "HR4 posterior density plot \n (shaded area = 0.9592).", 
+     ylab = "P(HR4)", xlab = "HR4 (3-4 t/Week drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
+# HR5
+HR5 <- ggSample %>% 
+  filter(Parameter == "HR[5]")
+denHR5 <- density(HR5$value)
+plot(denHR5, main = "HR5 posterior density plot \n (shaded area = 1.0)", 
+     ylab = "P(HR5)", xlab = "HR5 (daily drinker against never)", col = "black")
+
+qn1   <- 1
+qn02   <- -0.2
+
+x3 <- min(which(denHR5$x >= qn02))  
+x4 <- max(which(denHR5$x <  qn1))
+
+with(denHR5, polygon(x=c(x[c(x3,x3:x4,x4)]), y= c(0, y[x3:x4], 0), col="gray"))
+
 ```
-
-## Check model fitting:
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, fig.margin = FALSE}
-library(tidyverse)
-ggSample %>% 
-  filter(Iteration >= 500 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
-  ggs_traceplot()
-```

### 2020-01-12 ForReport20200114/HandOutEngBayes.tex
updated handout bayes age-adjusted model done

@@
 
+\begin{marginfigure}
+Acceleration factor is the factor by which time to failure/event is
+accelerated for \(x_1 = 1\) compared with \(x_1 = 0\)
+\end{marginfigure}
+
 \hypertarget{an-example-of-a-crude-weibull-model-using-the-jags-program-in-r}{%
@@
 \NormalTok{jacc.weibull.model <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{() \{}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{39386}\NormalTok{)\{}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{39386}\NormalTok{)\{}\CommentTok{# loop through the subjects}
     \CommentTok{# sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])}
@@
 
+The output of the above crude Weibull model:
+
+\begin{verbatim}
+# Inference for Bugs model at "jacc.weibull.model", fit using jags,
+#  3 chains, each with 10000 iterations (first 2500 discarded), n.thin = 7
+#  n.sims = 3213 iterations saved. Sample size per chain = 1071 
+# 1. Empirical mean and standard deviation for each variable,
+#    plus standard error of the mean:
+#                   Mean        SD   Naive SE Time-series SE
+# AFT[2]        0.922303  0.064441 0.00113685     0.00420403
+# AFT[3]        0.834723  0.051485 0.00090830     0.00362857
+# AFT[4]        0.848329  0.052439 0.00092513     0.00401102
+# AFT[5]        0.928095  0.041834 0.00073803     0.00336613
+# HR[2]         0.890533  0.090586 0.00159811     0.00604246
+# HR[3]         0.769913  0.069116 0.00121934     0.00486858
+# HR[4]         0.788205  0.070624 0.00124594     0.00531505
+# HR[5]         0.897882  0.058477 0.00103164     0.00468654
+# p.crit[2]     0.871460  0.334743 0.00590548     0.01814848
+# p.crit[3]     0.996265  0.061008 0.00107630     0.00214585
+# p.crit[4]     0.998133  0.043180 0.00076177     0.00097572
+# p.crit[5]     0.953626  0.210327 0.00371056     0.02050164
+# 2. Quantiles for each variable:
+#                   2.5%          25%          50%         75%       97.5%
+# AFT[2]        0.807308     0.876649     0.918049     0.96495     1.05225
+# AFT[3]        0.738423     0.799925     0.832078     0.86719     0.94214
+# AFT[4]        0.749645     0.810952     0.847050     0.88448     0.95291
+# AFT[5]        0.847796     0.899999     0.927850     0.95594     1.01147
+# HR[2]         0.733186     0.825541     0.883106     0.94896     1.07725
+# HR[3]         0.644053     0.721892     0.765778     0.81289     0.91643
+# HR[4]         0.658787     0.737562     0.785538     0.83614     0.93282
+# HR[5]         0.788623     0.857453     0.896668     0.93613     1.01665
+# ...
+\end{verbatim}
+
 \hypertarget{check-model-fitting}{%
@@
 
-\includegraphics{HandOutEngBayes_files/figure-latex/unnamed-chunk-5-1}
+\begin{figure}
+\includegraphics{HandOutEngBayes_files/figure-latex/unnamed-chunk-6-1} \caption[Traceplot for AFT, and HR of daily milk drinkers from crude model (men)]{Traceplot for AFT, and HR of daily milk drinkers from crude model (men).}\label{fig:unnamed-chunk-6}
+\end{figure}
+\begin{marginfigure}
+
+{\centering \includegraphics[width=0.9\linewidth]{fig/badtraceplot}
+
+}
+
+\caption[Not overlapping traceplot indicating that model is not converged]{Not overlapping traceplot indicating that model is not converged.}\label{fig:badtrace}
+\end{marginfigure}
+
+\begin{figure}
+\includegraphics{HandOutEngBayes_files/figure-latex/unnamed-chunk-7-1} \caption[Autocorrelation figures for AFT, and HR of daily milk drinkers from crude model (men)]{Autocorrelation figures for AFT, and HR of daily milk drinkers from crude model (men).}\label{fig:unnamed-chunk-7}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{fig/badautocorrelation}
+
+}
+
+\caption[(bad example)Highly correlated posterior samples indicating that the samples are not independent]{(bad example)Highly correlated posterior samples indicating that the samples are not independent.}\label{fig:badauto}
+\end{figure}
+
+\begin{table}[!htbp]
+Table 1.
+Estimated (crude) hazard ratios and acceleration factors for the association of milk intake and risk of stroke mortality using Bayesian MCMC methods in Men of the JACC study data (n = 39,386).
+
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllllllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
+\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
+Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
+\midrule
+\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
+1-2 t/Mon & 0.88 & 0.89 (0.09) & (0.73, 1.08) & 0.0016 & 87.15\% & 0.92 & 0.92 (0.06) & (0.81, 1.06) & 0.0011\\
+\rowcolor{gray!6}  1-2 t/Week & 0.77 & 0.77 (0.07) & (0.64, 0.92) & 0.0012 & 99.63\% & 0.83 & 0.83 (0.05) & (0.74, 0.94) & 0.0009\\
+3-4 t/Week & 0.79 & 0.79 (0.07) & (0.66, 0.93) & 0.0012 & 99.81\% & 0.85 & 0.85 (0.05) & (0.75, 0.95) & 0.0009\\
+\rowcolor{gray!6}  Daily & 0.89 & 0.90 (0.06) & (0.79, 1.02) & 0.0010 & 95.36\% & 0.93 & 0.93 (0.04) & (0.85, 1.01) & 0.0007\\
+\bottomrule
+\multicolumn{10}{l}{\textit{Note: }}\\
+\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{10}{l}{ Probability indicates that p for HR smaller than 1.}\\
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\includegraphics{HandOutEngBayes_files/figure-latex/unnamed-chunk-8-1} \caption[Crude model HR posterior density plots]{Crude model HR posterior density plots.}\label{fig:unnamed-chunk-8}
+\end{figure}
+
+\begin{table}[!htbp]
+Table 2.
+Estimated (age-adjusted) hazard ratios and acceleration factors for the association of milk intake and risk of stroke mortality using Bayesian MCMC methods in Men of the JACC study data (n = 39,386).
+
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllllllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
+\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
+Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
+\midrule
+\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
+1-2 t/Mon & 0.98 & 0.98 (0.11) & (0.78, 1.19) & 0.0018 & 57.86\% & 0.98 & 0.99 (0.06) & (0.87, 1.11) & 0.0011\\
+\rowcolor{gray!6}  1-2 t/Week & 0.84 & 0.84 (0.08) & (0.69, 0.99) & 0.0014 & 97.79\% & 0.90 & 0.90 (0.05) & (0.80, 0.99) & 0.0008\\
+3-4 t/Week & 0.86 & 0.86 (0.08) & (0.71, 1.02) & 0.0014 & 95.92\% & 0.91 & 0.91 (0.05) & (0.82, 1.01) & 0.0009\\
+\rowcolor{gray!6}  Daily & 0.75 & 0.75 (0.05) & (0.67, 0.85) & 0.0009 & 100.00\% & 0.85 & 0.85 (0.03) & (0.79, 0.91) & 0.0006\\
+\bottomrule
+\multicolumn{10}{l}{\textit{Note: }}\\
+\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{10}{l}{ Probability indicates the p for HR smaller than 1.}\\
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\includegraphics{HandOutEngBayes_files/figure-latex/unnamed-chunk-10-1} \caption[Age-adjusted HR posterior density plots]{Age-adjusted HR posterior density plots.}\label{fig:unnamed-chunk-10}
+\end{figure}
 

### 2020-01-12 AnalysisScript/JACCBAYES.R
jaccbayes confirmed

@@ -1,94 +1,0 @@
-# stage <- larynx.dat$stage
-Mlkfre <- MData_men$Mlkfre
-MlkLogi <- as.numeric(MData_men$MlkLogi == "Drinker")
-
-# is.censored <- is.na(t)
-is.censored <- MData_men$Tot_Stroke != "I60_9"
-
-# t <- larynx.dat$time
-t <- if_else(!is.censored, MData_men$followpy, 0)
-t <- na_if(t, 0)
-t
-
-# age <- larynx.dat$age
-Agegrp <- MData_men$Agegrp
-Age <- MData_men$Age
-
-
-# c <- larynx.dat$cens_time
-c <- if_else(is.censored, MData_men$followpy, 0)
-
-
-c[!is.censored] <- t[!is.censored] + 1
-# c
-# t
-# is.censored
-
-
-larynx.weibull.model <- function() {
-  for(i in 1:39386){
-    sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])
-    # sYr[i] <- (yr[i] - mean(yr[])) / sd(yr[])
-    is.censored[i] ~ dinterval(t[i], c[i])
-    t[i] ~ dweib(shape, lambda[i])
-    lambda[i] <- exp(-mu[i] * shape)
-    mu[i] <- beta[1] + beta[2]*equals(MlkLogi[i], 1) +
-      # beta[3]*equals(Age[i], 3) + beta[4] * equals(stage[i], 4) +
-      beta[3] *sAge[i] 
-    
-    ### calculate log-likelihoods
-    y[i] <- ifelse(is.censored[i], c[i], t[i])
-    loglik[i] <- log(ifelse(is.censored[i],
-                            exp(-lambda[i] * (y[i] ^ shape)),
-                            shape * lambda[i] * (y[i] ^ (shape - 1)) * exp(-lambda[i] * (y[i] ^ shape))))
-  }
-  
-  ## priors for betas
-  for(j in 1:3){
-    beta[j] ~ dnorm(0, 0.001)
-  }
-  
-  ### prior for shape
-  shape ~ dgamma(.001, .001)
-  
-  ### Generated values
-  AFT[2] <- exp(beta[2])
-  HR[2] <- exp(shape * beta[2])
-  p.crit[2] <- step(1 - HR[2])  
-  AFT[3] <- exp(beta[3])
-  HR[3] <- exp(shape * beta[3])
[…]

### 2020-01-13 ForReport20200114/HandOutEngBayes.Rmd
updated things for the slides

@@
 - \usepackage{xcolor}
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```
+
 ```{r badtrace, echo=FALSE, out.width = '90%', cache=TRUE, fig.cap="Not overlapping traceplot indicating that model is not converged.",fig.align='center', fig.margin = TRUE}

### 2020-01-15 AnalysisScript/ModelsJAGSmen.R
updated with model jags men

@@ -267,29 +267,28 @@ M2.weibull.model <- function() {
       beta[10] * equals(Alc_Fre[i], 1) + beta[11] * equals(Alc_Fre[i], 2) + 
       beta[12] * equals(Alc_Fre[i], 3) + beta[13] * equals(Alc_Fre[i], 5) + 
       beta[14] * equals(BMIgrp[i], 2) + beta[15] * equals(BMIgrp[i], 3) + 
-      beta[16] * equals(BMIgrp[i], 4) + beta[17] * equals(BMIgrp[i], 5)
-    #+ beta[15] * equals(DM_hist[i], 2) +  
-    # beta[16] * equals(DM_hist[i], 3) + 
-    # beta[17] * equals(HT_hist[i], 2) + beta[18] * equals(HT_hist[i], 3) + 
-    # beta[19] * equals(KID_hist[i], 2) + beta[20] * equals(KID_hist[i], 3)  + 
-    # beta[21] * equals(LIV_hist[i], 2) + beta[22] * equals(LIV_hist[i], 3)  + 
-    # beta[23] * equals(Exercise[i], 2) + beta[24] * equals(Exercise[i], 3)  +
-    # beta[25] * equals(Slepgrp[i], 2) + beta[26] * equals(Slepgrp[i], 3) + 
-    # beta[27] * equals(Slepgrp[i], 4) + beta[28] * equals(Slepgrp[i], 5) +
-    # beta[29] * equals(Spi[i], 2) + beta[30] * equals(Spi[i], 3) + 
-    # beta[31] * equals(Spi[i], 4) + beta[32] * equals(Spi[i], 5) + 
-    # beta[33] * equals(Cofe[i], 2) + beta[34] * equals(Cofe[i], 3) + 
-    # beta[35] * equals(Cofe[i], 4) + beta[36] * equals(Educgrp[i], 2) + 
-    # beta[37] * equals(Educgrp[i], 3) +  beta[38] * equals(Gretea[i], 2) + 
-    # beta[39] * equals(Gretea[i], 3) +  beta[40] * equals(Gretea[i], 4) + 
-    # beta[41] * equals(Fru[i], 2) + beta[42] * equals(Fru[i], 3) + 
-    # beta[43] * equals(Fru[i], 4) + beta[44] * equals(Fru[i], 5) #+ 
+      beta[16] * equals(BMIgrp[i], 4) + beta[17] * equals(BMIgrp[i], 5) + 
[…]

### 2020-06-08 AnalysisScript/ModelsJAGSwomen.R
updated M2 women results

@@ -300,27 +300,27 @@ M2.weibull.model <- function() {
       beta[10] * equals(Alc_Fre[i], 1) + beta[11] * equals(Alc_Fre[i], 2) + 
       beta[12] * equals(Alc_Fre[i], 3) + beta[13] * equals(Alc_Fre[i], 5) + 
       beta[14] * equals(BMIgrp[i], 2) + beta[15] * equals(BMIgrp[i], 3) + 
-      beta[16] * equals(BMIgrp[i], 4) + beta[17] * equals(BMIgrp[i], 5) +
-      beta[18] * equals(DM_hist[i], 2) + beta[19] * equals(DM_hist[i], 3) + 
-    beta[20] * equals(HT_hist[i], 2) + beta[21] * equals(HT_hist[i], 3) +
-    beta[22] * equals(KID_hist[i], 2) + beta[23] * equals(KID_hist[i], 3)  +
-    beta[24] * equals(LIV_hist[i], 2) + beta[25] * equals(LIV_hist[i], 3)  +
-    beta[26] * equals(Exercise[i], 2) + beta[27] * equals(Exercise[i], 3)  +
-    beta[28] * equals(Slepgrp[i], 2) + beta[29] * equals(Slepgrp[i], 3) +
-    beta[30] * equals(Slepgrp[i], 4) + beta[31] * equals(Slepgrp[i], 5) +
-    beta[32] * equals(Spi[i], 2) + beta[33] * equals(Spi[i], 3) +
-    beta[34] * equals(Spi[i], 4) + beta[35] * equals(Spi[i], 5) +
-    beta[36] * equals(Cofe[i], 2) + beta[37] * equals(Cofe[i], 3) +
-    beta[38] * equals(Cofe[i], 4) + beta[39] * equals(Educgrp[i], 2) +
-    beta[40] * equals(Educgrp[i], 3) +  beta[41] * equals(Gretea[i], 2) +
-    beta[42] * equals(Gretea[i], 3) +  beta[43] * equals(Gretea[i], 4) +
-    beta[44] * equals(Fru[i], 2) + beta[45] * equals(Fru[i], 3) +
-    beta[46] * equals(Fru[i], 4) + beta[47] * equals(Fru[i], 5) #+
+      beta[16] * equals(BMIgrp[i], 4) + beta[17] * equals(BMIgrp[i], 5) #+
[…]

### 2020-06-08 Paperfolder/Paperfolder.Rmd
templates of latex and words added

---
title: Full title of the paper (Capitalized)
author:
  - name: Dominik Leutnant
    affil: 1,2,\ddagger,*
    orcid: 0000-0003-3293-2315
  - name: John Doe
    affil: 2, \dagger, \ddagger
affiliation:
  - num: 1
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment
      Correnstr. 25, 48149 Muenster, Germany
    email: leutnant@fh-muenster.de
  - num: 2
    address: |
      Your department
      Street, City, Country
    email: mail@mail.com
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

# Version

This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
However, the official template gets more frequently updated than the 'rticles'
package. Therefore, please make sure prior to paper submission, that you're 
using the most recent .cls, .tex and .bst files 
(available [here](http://www.mdpi.com/authors/latex)).

# Introduction

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016]. And now citing a book reference @gujer_systems_2008. Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.

# Materials and Methods

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

# Results

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Bulleted lists look like this:

* First bullet
* Second bullet
* Third bullet

Numbered lists can be added as follows:

1. First item
2. Second item
3. Third item

The text continues here.

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

<!-- Example of a proof: -->
<!-- \begin{proof}[Proof of Theorem 1] -->
<!-- Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to. -->
<!-- \end{proof} -->
<!-- The text continues here. -->

# Discussion

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

# Conclusion

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

<!-- # Patents -->

<!-- This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript. -->

### 2020-06-08 Paperfolder/Paperfolder.tex
templates of latex and words added

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[water,article,submit,moreauthors,pdftex]{mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{4pt}}
\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

\usepackage{longtable}

% see https://stackoverflow.com/a/47122900

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by:
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Full title of the paper (Capitalized)}

% Authors, for the paper (add full first names)
\Author{Dominik
Leutnant$^{1,2,\ddagger,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, John
Doe$^{2, \dagger, \ddagger}$}

% Authors, for metadata in PDF
\AuthorNames{Dominik Leutnant, John Doe}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Muenster University of Applied Sciences - Institute for
Infrastructure, Water, Resources, Environment Correnstr. 25, 48149
Muenster,
Germany; \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}\\
$^{2}$ \quad Your department Street, City,
Country; \href{mailto:mail@mail.com}{\nolinkurl{mail@mail.com}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
Tel.: +XX-000-00-0000.}

% Current address and/or shared authorship
\firstnote{Current address: Updated affiliation}
\secondnote{These authors contributed equally to this work.}

% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary
\simplesumm{A Simple summary goes here.}

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
keywords specific to the article, yet reasonably common within the
subject discipline.).}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypertarget{version}{%
\section{Version}\label{version}}

This Rmd-skeleton uses the mdpi Latex template published 2019/02.
However, the official template gets more frequently updated than the
`rticles' package. Therefore, please make sure prior to paper
submission, that you're using the most recent .cls, .tex and .bst files
(available \href{http://www.mdpi.com/authors/latex}{here}).

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The introduction should briefly place the study in a broad context and
highlight why it is important. It should define the purpose of the work
and its significance. The current state of the research field should be
reviewed carefully and key publications cited. Please highlight
controversial and diverging hypotheses when necessary. Finally, briefly
mention the main aim of the work and highlight the principal
conclusions. As far as possible, please keep the introduction
comprehensible to scientists outside your particular field of research.
Citing a journal paper
\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
And now citing a book reference \citet{gujer_systems_2008}. Please use
the command \citep{leutnant_stormwater_2016} for the following MDPI
journals, which use author-date citation: Administrative Sciences, Arts,
Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
Religions, Risks, Social Sciences.

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

Materials and Methods should be described with sufficient details to
allow others to replicate and build on published results. Please note
that publication of your manuscript implicates that you must make all
materials, data, computer code, and protocols associated with the
publication available to readers. Please disclose at the submission
stage any restrictions on the availability of materials or information.
New methods and protocols should be described in detail while
well-established methods can be briefly described and appropriately
cited.

Research manuscripts reporting large datasets that are deposited in a
publicly available database should specify where the data have been
deposited and provide the relevant accession numbers. If the accession
numbers have not yet been obtained at the time of submission, please
state that they will be provided during review. They must be provided
prior to publication.

Interventionary studies involving animals or humans, and other studies
require ethical approval must list the authority that provided approval
and the corresponding ethical approval code.

\hypertarget{results}{%
\section{Results}\label{results}}

This section may be divided by subheadings. It should provide a concise
and precise description of the experimental results, their
interpretation as well as the experimental conclusions that can be
drawn.

\hypertarget{subsection-heading-here}{%
\subsection{Subsection Heading Here}\label{subsection-heading-here}}

Subsection text here.

\hypertarget{subsubsection-heading-here}{%
\subsubsection{Subsubsection Heading
Here}\label{subsubsection-heading-here}}

Bulleted lists look like this:

\begin{itemize}
\tightlist
\item
  First bullet
\item
  Second bullet
\item
  Third bullet
\end{itemize}

Numbered lists can be added as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  First item
\item
  Second item
\item
  Third item
\end{enumerate}

The text continues here.

All figures and tables should be cited in the main text as Figure 1,
Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
\midrule
entry 1     & data          & data\\
entry 2     & data          & data\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

Example of a theorem:

\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:

\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}

The text continues here.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The
findings and their implications should be discussed in the broadest
context possible. Future research directions may also be highlighted.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

\hypertarget{patents}{%
\section{Patents}\label{patents}}

This section is not mandatory, but may be added if there are patents
resulting from the work reported in this manuscript.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% optional
% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
%
% % Only for the journal Methods and Protocols:
% % If you wish to submit a video article, please do so with any other supplementary material.
% % \supplementary{The following are available at www.mdpi.com/link: Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

\input{"appendix.tex"}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
%\reftitle{References}
%\begin{thebibliography}{999}
% Reference 1
%\bibitem[Author1(year)]{ref-journal}
%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
%\bibitem[Author2(year)]{ref-book}
%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
%\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\externalbibliography{yes}
\bibliography{mybibfile.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2020-06-08 usebrms.R

@@ -1,0 +1,49 @@
+load("data/JACCmilkstroke.Rdata")
+
+
+##%######################################################%##
+#                                                          #
+####          Example use kidney data in brms           ####
+#                                                          #
+##%######################################################%##
+
+
+library(brms)
+data("kidney")
+
+head(kidney)
+table(kidney$censored)
+## performing surivival analysis using the "weibull" family
+fit1 <- brm(time | cens(censored) ~ age + sex + disease, 
+            data = kidney, family = weibull, inits = "0")
+summary(fit1) 
+plot(fit1)
+
+##%######################################################%##
+#                                                          #
+####                 try use men data                   ####
+#                                                          #
+##%######################################################%##
+library(tidyverse)
+Mlkfre <- MData_men$Mlkfre
+
+# is.censored <- is.na(t)
+is.censored <- MData_men$Tot_Stroke != "I60_9"
+
+# t <- larynx.dat$time
+t <- if_else(!is.censored, MData_men$followpy, 0)
+t <- na_if(t, 0)
+
+Age <- MData_men$Age
+
+c <- if_else(is.censored, MData_men$followpy, 0)
+
+
+c[!is.censored] <- t[!is.censored] + 1
+
+MILKdataMEN_brm <- data.frame(t = t,  c = c, Mlkfre = Mlkfre, is.censored = is.censored)
+
+
+M0men20200608 <- brm(c | cens(is.censored) ~ Mlkfre, 
+                     data = MILKdataMEN_brm, 
+                     family = weibull, inits = "0")

### 2020-06-08 Paperfolder/Paperfolder.Rmd
prepare to write in rstudio with latex

@@
 ---
-title: Full title of the paper (Capitalized)
+title: Milk intake and risk of mortality risk 
 author:
-  - name: Dominik Leutnant
-    affil: 1,2,\ddagger,*
-    orcid: 0000-0003-3293-2315
+  - name: Chaochen Wang
+    affil: 1,*
+    orcid: 0000-0001-5533-1497
   - name: John Doe

### 2020-06-09 Paperfolder/Paperfolder.Rmd
updated paper started writing@

@@
     orcid: 0000-0001-5533-1497
-  - name: John Doe
-    affil: 2, \dagger, \ddagger
+  - name: Hiroshi Yatsuya
+    affil: 2 
+  - name: Yingsong Lin
+    affil: 1
+  - name: 
 affiliation:
@@
   leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
-journal: water
+journal: nutrients
 type: article

### 2020-06-09 Paperfolder/Paperfolder.tex
updated paper started writing@

@@
 %=================================================================
-\documentclass[water,article,submit,moreauthors,pdftex]{mdpi}
+\documentclass[nutrients,article,submit,moreauthors,pdftex]{mdpi}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Full title of the paper (Capitalized)}
+\Title{Milk intake and risk of mortality risk}
 
 % Authors, for the paper (add full first names)
-\Author{Dominik
-Leutnant$^{1,2,\ddagger,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, John
-Doe$^{2, \dagger, \ddagger}$}
+\Author{Chaochen
+Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
+Yatsuya$^{2}$, Yingsong Lin$^{1}$, $^{}$}
 
 % Authors, for metadata in PDF
-\AuthorNames{Dominik Leutnant, John Doe}
+\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, }
 
@@
 
-Example of a proof:
-
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-
-The text continues here.
-
 \hypertarget{discussion}{%
@@
 discussion is unusually long or complex.
-
-\hypertarget{patents}{%
-\section{Patents}\label{patents}}
-
-This section is not mandatory, but may be added if there are patents
-resulting from the work reported in this manuscript.
 

### 2020-06-12 Paperfolder/MDPI_template/Definitions/journalnames.tex
updated names of the authors

%\DeclareOption{			}{		\gdef\@journal{			}		\gdef\@journalshort{			}				\gdef\@journalfull{			}				\gdef\@doiabbr{		}	\gdef\@ISSN{		}	}
\DeclareOption{acoustics}{		\gdef\@journal{acoustics}			\gdef\@journalshort{Acoustics}					\gdef\@journalfull{Acoustics}					\gdef\@doiabbr{acoustics}	\gdef\@ISSN{2624-599X}	}
\DeclareOption{actuators}{		\gdef\@journal{actuators}			\gdef\@journalshort{Actuators}					\gdef\@journalfull{Actuators}					\gdef\@doiabbr{act}			\gdef\@ISSN{2076-0825}	}
\DeclareOption{addictions}{		\gdef\@journal{addictions}		\gdef\@journalshort{Addictions}				\gdef\@journalfull{Addictions}					\gdef\@doiabbr{}			\gdef\@ISSN{0006-0006}	}
\DeclareOption{admsci}{			\gdef\@journal{admsci}			\gdef\@journalshort{Adm. Sci.}					\gdef\@journalfull{Administrative Sciences}		\gdef\@doiabbr{admsci}		\gdef\@ISSN{2076-3387}	}
\DeclareOption{aerospace}{		\gdef\@journal{aerospace}		\gdef\@journalshort{Aerospace}				\gdef\@journalfull{Aerospace}					\gdef\@doiabbr{aerospace}	\gdef\@ISSN{2226-4310}	}
\DeclareOption{agriculture}{		\gdef\@journal{agriculture}		\gdef\@journalshort{Agriculture}				\gdef\@journalfull{Agriculture}					\gdef\@doiabbr{agriculture}	\gdef\@ISSN{2077-0472}	}
\DeclareOption{agriengineering}{	\gdef\@journal{agriengineering}	\gdef\@journalshort{AgriEngineering}			\gdef\@journalfull{AgriEngineering}				\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}}
\DeclareOption{agronomy}{		\gdef\@journal{agronomy}			\gdef\@journalshort{Agronomy}					\gdef\@journalfull{Agronomy}					\gdef\@doiabbr{agronomy}	\gdef\@ISSN{2073-4395}	}
\DeclareOption{ai}{				\gdef\@journal{ai}				\gdef\@journalshort{AI}						\gdef\@journalfull{AI}						\gdef\@doiabbr{ai}			\gdef\@ISSN{2673-2688}	}
\DeclareOption{algorithms}{		\gdef\@journal{algorithms}		\gdef\@journalshort{Algorithms}				\gdef\@journalfull{Algorithms}					\gdef\@doiabbr{a}			\gdef\@ISSN{1999-4893}	}
\DeclareOption{allergies}{			\gdef\@journal{allergies}			\gdef\@journalshort{Allergies}					\gdef\@journalfull{Allergies}					\gdef\@doiabbr{allergies}		\gdef\@ISSN{2313-5786}	}
\DeclareOption{analytica}{			\gdef\@journal{analytica}			\gdef\@journalshort{Analytica}					\gdef\@journalfull{Analytica}					\gdef\@doiabbr{analy}		\gdef\@ISSN{2673-4532}	}
\DeclareOption{animals}{			\gdef\@journal{animals}			\gdef\@journalshort{Animals}					\gdef\@journalfull{Animals}					\gdef\@doiabbr{ani}			\gdef\@ISSN{2076-2615}	}
\DeclareOption{antibiotics}{		\gdef\@journal{antibiotics}			\gdef\@journalshort{Antibiotics}					\gdef\@journalfull{Antibiotics}					\gdef\@doiabbr{antibiotics}	\gdef\@ISSN{2079-6382}	}
\DeclareOption{antibodies}{		\gdef\@journal{antibodies}		\gdef\@journalshort{Antibodies}				\gdef\@journalfull{Antibodies}					\gdef\@doiabbr{antib}		\gdef\@ISSN{2073-4468}	}
\DeclareOption{antioxidants}{		\gdef\@journal{antioxidants}		\gdef\@journalshort{Antioxidants}				\gdef\@journalfull{Antioxidants}					\gdef\@doiabbr{antiox}		\gdef\@ISSN{2076-3921}	}
\DeclareOption{applnano}{		\gdef\@journal{applnano}			\gdef\@journalshort{Appl. Nano}				\gdef\@journalfull{Applied Nano}				\gdef\@doiabbr{applnano}		\gdef\@ISSN{2673-3501}	}
\DeclareOption{applmech}{		\gdef\@journal{applmech}			\gdef\@journalshort{Appl. Mech.}				\gdef\@journalfull{Applied Mechanics}			\gdef\@doiabbr{applmech}	\gdef\@ISSN{2673-3161}	}
\DeclareOption{applsci}{			\gdef\@journal{applsci}			\gdef\@journalshort{Appl. Sci.}					\gdef\@journalfull{Applied Sciences}				\gdef\@doiabbr{app}			\gdef\@ISSN{2076-3417}}
\DeclareOption{arts}{				\gdef\@journal{arts}				\gdef\@journalshort{Arts}						\gdef\@journalfull{Arts}						\gdef\@doiabbr{arts}			\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{				\gdef\@journal{asc}				\gdef\@journalshort{Autom. Syst. Control}			\gdef\@journalfull{Automatic Systems and Control}	\gdef\@doiabbr{}			\gdef\@ISSN{		}	}
\DeclareOption{asi}{				\gdef\@journal{asi}				\gdef\@journalshort{Appl. Syst. Innov.}			\gdef\@journalfull{Applied System Innovation}		\gdef\@doiabbr{asi}			\gdef\@ISSN{2571-5577}	}
\DeclareOption{atmosphere}{		\gdef\@journal{atmosphere}		\gdef\@journalshort{Atmosphere}				\gdef\@journalfull{Atmosphere}					\gdef\@doiabbr{atmos}		\gdef\@ISSN{2073-4433}	}
\DeclareOption{atoms}{			\gdef\@journal{atoms}			\gdef\@journalshort{Atoms}					\gdef\@journalfull{Atoms}						\gdef\@doiabbr{atoms}		\gdef\@ISSN{2218-2004}	}
\DeclareOption{automation}{		\gdef\@journal{automation}		\gdef\@journalshort{Automation}				\gdef\@journalfull{Automation}					\gdef\@doiabbr{automation}	\gdef\@ISSN{2673-4052}	}
\DeclareOption{axioms}{			\gdef\@journal{axioms}			\gdef\@journalshort{Axioms}					\gdef\@journalfull{Axioms}					\gdef\@doiabbr{axioms}		\gdef\@ISSN{2075-1680}	}
\DeclareOption{batteries}{			\gdef\@journal{batteries}			\gdef\@journalshort{Batteries}					\gdef\@journalfull{Batteries}					\gdef\@doiabbr{batteries}		\gdef\@ISSN{2313-0105}	}
\DeclareOption{bdcc}{			\gdef\@journal{bdcc}				\gdef\@journalshort{Big Data Cogn. Comput.}		\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@doiabbr{bdcc}		\gdef\@ISSN{2504-2289}	}
\DeclareOption{behavsci}{ 		\gdef\@journal{behavsci} 			\gdef\@journalshort{Behav. Sci.}				\gdef\@journalfull{Behavioral Sciences}			\gdef\@doiabbr{bs}			\gdef\@ISSN{2076-328X}	}
\DeclareOption{beverages}{		\gdef\@journal{beverages}		\gdef\@journalshort{Beverages}				\gdef\@journalfull{Beverages}					\gdef\@doiabbr{beverages}	\gdef\@ISSN{2306-5710}	}
\DeclareOption{bioengineering}{	\gdef\@journal{bioengineering}		\gdef\@journalshort{Bioengineering}				\gdef\@journalfull{Bioengineering}				\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}	}
\DeclareOption{biology}{			\gdef\@journal{biology}			\gdef\@journalshort{Biology}					\gdef\@journalfull{Biology}					\gdef\@doiabbr{biology}		\gdef\@ISSN{2079-7737}	}
\DeclareOption{biomedicines}{		\gdef\@journal{biomedicines}		\gdef\@journalshort{Biomedicines}				\gdef\@journalfull{Biomedicines}				\gdef\@doiabbr{biomedicines}	\gdef\@ISSN{2227-9059}	}
\DeclareOption{biomimetics}{		\gdef\@journal{biomimetics}		\gdef\@journalshort{Biomimetics}				\gdef\@journalfull{Biomimetics}					\gdef\@doiabbr{biomimetics}	\gdef\@ISSN{2313-7673}	}
\DeclareOption{biomolecules}{		\gdef\@journal{biomolecules}		\gdef\@journalshort{Biomolecules}				\gdef\@journalfull{Biomolecules}				\gdef\@doiabbr{biom}		\gdef\@ISSN{2218-273X}	}
\DeclareOption{biosensors}{		\gdef\@journal{biosensors}		\gdef\@journalshort{Biosensors}				\gdef\@journalfull{Biosensors}					\gdef\@doiabbr{bios}		\gdef\@ISSN{2079-6374}	}
\DeclareOption{bloods}{			\gdef\@journal{bloods}			\gdef\@journalshort{Bloods}					\gdef\@journalfull{Bloods}						\gdef\@doiabbr{bloods}		\gdef\@ISSN{2673-415X}	}
\DeclareOption{brainsci}{ 			\gdef\@journal{brainsci} 			\gdef\@journalshort{Brain Sci.}					\gdef\@journalfull{Brain Sciences}				\gdef\@doiabbr{brainsci}		\gdef\@ISSN{2076-3425}	}
\DeclareOption{breath}{			\gdef\@journal{breath}			\gdef\@journalshort{Breath}					\gdef\@journalfull{Breath}						\gdef\@doiabbr{breath}		\gdef\@ISSN{		}	}
\DeclareOption{buildings}{			\gdef\@journal{buildings}			\gdef\@journalshort{Buildings}					\gdef\@journalfull{Buildings}					\gdef\@doiabbr{buildings}		\gdef\@ISSN{2075-5309}	}
\DeclareOption{cancers}{			\gdef\@journal{cancers}			\gdef\@journalshort{Cancers}					\gdef\@journalfull{Cancers}					\gdef\@doiabbr{cancers}		\gdef\@ISSN{2072-6694}	}
\DeclareOption{carbon}{ 			\gdef\@journal{carbon} 			\gdef\@journalshort{C}						\gdef\@journalfull{C}							\gdef\@doiabbr{c}			\gdef\@ISSN{2311-5629}	}
\DeclareOption{catalysts}{			\gdef\@journal{catalysts}			\gdef\@journalshort{Catalysts}					\gdef\@journalfull{Catalysts}					\gdef\@doiabbr{catal}		\gdef\@ISSN{2073-4344}	}
\DeclareOption{cells}{			\gdef\@journal{cells}				\gdef\@journalshort{Cells}						\gdef\@journalfull{Cells}						\gdef\@doiabbr{cells}		\gdef\@ISSN{2073-4409}	}
\DeclareOption{ceramics}{			\gdef\@journal{ceramics}			\gdef\@journalshort{Ceramics}					\gdef\@journalfull{Ceramics}					\gdef\@doiabbr{ceramics}		\gdef\@ISSN{2571-6131}	}
\DeclareOption{challenges}{		\gdef\@journal{challenges}		\gdef\@journalshort{Challenges}				\gdef\@journalfull{Challenges}					\gdef\@doiabbr{challe}		\gdef\@ISSN{2078-1547}	}
\DeclareOption{chemengineering}{	\gdef\@journal{chemengineering}	\gdef\@journalshort{ChemEngineering}			\gdef\@journalfull{ChemEngineering}		\gdef\@doiabbr{chemengineering}	\gdef\@ISSN{2305-7084}	}
\DeclareOption{chemistry}{		\gdef\@journal{chemistry}			\gdef\@journalshort{Chemistry}					\gdef\@journalfull{Chemistry}					\gdef\@doiabbr{chemistry}	\gdef\@ISSN{2624-8549}	}
\DeclareOption{chemosensors}{	\gdef\@journal{chemosensors}		\gdef\@journalshort{Chemosensors}				\gdef\@journalfull{Chemosensors}				\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}	}
\DeclareOption{chemproc}{		\gdef\@journal{chemproc}			\gdef\@journalshort{Chem. Proc.}				\gdef\@journalfull{Chemistry Proceedings}		\gdef\@doiabbr{chemproc}	\gdef\@ISSN{2673-4583}	}
\DeclareOption{children}{			\gdef\@journal{children}			\gdef\@journalshort{Children}					\gdef\@journalfull{Children}					\gdef\@doiabbr{children}		\gdef\@ISSN{2227-9067}	}
\DeclareOption{civileng}{			\gdef\@journal{civileng}			\gdef\@journalshort{CivilEng}					\gdef\@journalfull{CivilEng}					\gdef\@doiabbr{civileng}		\gdef\@ISSN{2673-4109}	}
\DeclareOption{cleantechnol}{		\gdef\@journal{cleantechnol}		\gdef\@journalshort{Clean Technol.}				\gdef\@journalfull{Clean Technologies}			\gdef\@doiabbr{cleantechnol}	\gdef\@ISSN{2571-8797}	}
\DeclareOption{climate}{			\gdef\@journal{climate}			\gdef\@journalshort{Climate}					\gdef\@journalfull{Climate}					\gdef\@doiabbr{cli}			\gdef\@ISSN{2225-1154}	}
\DeclareOption{clockssleep}{		\gdef\@journal{clockssleep}		\gdef\@journalshort{Clocks\&Sleep}				\gdef\@journalfull{Clocks \& Sleep}				\gdef\@doiabbr{clockssleep}	\gdef\@ISSN{2624-5175}	}
\DeclareOption{cmd}{			\gdef\@journal{cmd}				\gdef\@journalshort{Corros. Mater. Degrad.}		\gdef\@journalfull{Corrosion and Materials Degradation}	\gdef\@doiabbr{cmd}	\gdef\@ISSN{2624-5558}	}
\DeclareOption{coatings}{			\gdef\@journal{coatings}			\gdef\@journalshort{Coatings}					\gdef\@journalfull{Coatings}					\gdef\@doiabbr{coatings}		\gdef\@ISSN{2079-6412}	}
\DeclareOption{colloids}{			\gdef\@journal{colloids}			\gdef\@journalshort{Colloids Interfaces}			\gdef\@journalfull{Colloids Interfaces}			\gdef\@doiabbr{colloids}		\gdef\@ISSN{2504-5377}	}
\DeclareOption{computation}{		\gdef\@journal{computation}		\gdef\@journalshort{Computation}				\gdef\@journalfull{Computation}				\gdef\@doiabbr{computation}	\gdef\@ISSN{2079-3197}	}
\DeclareOption{computers}{		\gdef\@journal{computers}		\gdef\@journalshort{Computers}				\gdef\@journalfull{Computers}					\gdef\@doiabbr{computers}	\gdef\@ISSN{2073-431X}	}
\DeclareOption{condensedmatter}{	\gdef\@journal{condensedmatter}	\gdef\@journalshort{Condens. Matter}			\gdef\@journalfull{Condensed Matter}			\gdef\@doiabbr{condmat}		\gdef\@ISSN{2410-3896}	}
\DeclareOption{cosmetics}{		\gdef\@journal{cosmetics}			\gdef\@journalshort{Cosmetics}				\gdef\@journalfull{Cosmetics}					\gdef\@doiabbr{cosmetics}	\gdef\@ISSN{2079-9284}	}
\DeclareOption{cryptography}{		\gdef\@journal{cryptography}		\gdef\@journalshort{Cryptography}				\gdef\@journalfull{Cryptography}				\gdef\@doiabbr{cryptography}	\gdef\@ISSN{2410-387X}	}
\DeclareOption{crystals}{			\gdef\@journal{crystals}			\gdef\@journalshort{Crystals}					\gdef\@journalfull{Crystals}					\gdef\@doiabbr{cryst}		\gdef\@ISSN{2073-4352}	}
\DeclareOption{cyber}{			\gdef\@journal{cyber}			\gdef\@journalshort{Cyber}					\gdef\@journalfull{Cyber}						\gdef\@doiabbr{cyber}		\gdef\@ISSN{2624-800X}	}
\DeclareOption{dairy}{			\gdef\@journal{dairy}			\gdef\@journalshort{Dairy}					\gdef\@journalfull{Dairy}						\gdef\@doiabbr{dairy}		\gdef\@ISSN{2624-862X}	}
\DeclareOption{data}{			\gdef\@journal{data}				\gdef\@journalshort{Data}						\gdef\@journalfull{Data}						\gdef\@doiabbr{data}		\gdef\@ISSN{2306-5729}	}
\DeclareOption{dentistry}{			\gdef\@journal{dentistry}			\gdef\@journalshort{Dent. J.}					\gdef\@journalfull{Dentistry Journal}				\gdef\@doiabbr{dj}			\gdef\@ISSN{2304-6767}	}
\DeclareOption{designs}{ 			\gdef\@journal{designs} 			\gdef\@journalshort{Designs}					\gdef\@journalfull{Designs}					\gdef\@doiabbr{designs}		\gdef\@ISSN{2411-9660}	}
\DeclareOption{diagnostics}{		\gdef\@journal{diagnostics}		\gdef\@journalshort{Diagnostics}				\gdef\@journalfull{Diagnostics}					\gdef\@doiabbr{diagnostics}	\gdef\@ISSN{2075-4418}	}
\DeclareOption{diseases}{			\gdef\@journal{diseases}			\gdef\@journalshort{Diseases}					\gdef\@journalfull{Diseases}					\gdef\@doiabbr{diseases}		\gdef\@ISSN{2079-9721}	}
\DeclareOption{diversity}{			\gdef\@journal{diversity}			\gdef\@journalshort{Diversity}					\gdef\@journalfull{Diversity}					\gdef\@doiabbr{d}			\gdef\@ISSN{1424-2818}	}
\DeclareOption{drones}{			\gdef\@journal{drones}			\gdef\@journalshort{Drones}					\gdef\@journalfull{Drones}					\gdef\@doiabbr{drones}		\gdef\@ISSN{2504-446X}	}
\DeclareOption{earth}{			\gdef\@journal{earth}			\gdef\@journalshort{Earth}					\gdef\@journalfull{Earth}						\gdef\@doiabbr{earth}		\gdef\@ISSN{		}	}
\DeclareOption{ecologies}{		\gdef\@journal{ecologies}			\gdef\@journalshort{Ecologies}					\gdef\@journalfull{Ecologies}					\gdef\@doiabbr{ecologies}	\gdef\@ISSN{2673-4133}	}
\DeclareOption{econometrics}{		\gdef\@journal{econometrics}		\gdef\@journalshort{Econometrics}				\gdef\@journalfull{Econometrics}				\gdef\@doiabbr{econometrics}	\gdef\@ISSN{2225-1146}	}
\DeclareOption{economies}{		\gdef\@journal{economies}		\gdef\@journalshort{Economies}				\gdef\@journalfull{Economies}					\gdef\@doiabbr{economies}	\gdef\@ISSN{2227-7099}	}
\DeclareOption{education}{		\gdef\@journal{education}			\gdef\@journalshort{Educ. Sci.}					\gdef\@journalfull{Education Sciences}			\gdef\@doiabbr{educsci}		\gdef\@ISSN{2227-7102}	}
\DeclareOption{ejbc}{\gdef\@journal{ejbc}\gdef\@journalshort{Eur. J. Burn Care}\gdef\@journalfull{European Journal of Burn Care}										\gdef\@doiabbr{ejbc}		\gdef\@ISSN{2673-1991}	}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@journalfull{European Journal of Investigation in Health, Psychology and Education}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}}
\DeclareOption{electricity}{		\gdef\@journal{electricity}			\gdef\@journalshort{Electricity}					\gdef\@journalfull{Electricity}					\gdef\@doiabbr{el}			\gdef\@ISSN{2673-4826}	}
\DeclareOption{electrochem}{		\gdef\@journal{electrochem}		\gdef\@journalshort{Electrochem}				\gdef\@journalfull{Electrochem}				\gdef\@doiabbr{electrochem}	\gdef\@ISSN{2673-3293}	}
\DeclareOption{electronicmat}{		\gdef\@journal{electronicmat}		\gdef\@journalshort{Electron. Mater.}			\gdef\@journalfull{Electronic Materials}			\gdef\@doiabbr{electronicmat}	\gdef\@ISSN{2673-3978}	}
\DeclareOption{electronics}{		\gdef\@journal{electronics}		\gdef\@journalshort{Electronics}				\gdef\@journalfull{Electronics}					\gdef\@doiabbr{electronics}	\gdef\@ISSN{2079-9292}	}
\DeclareOption{endocrines}{		\gdef\@journal{endocrines}		\gdef\@journalshort{Endocrines}				\gdef\@journalfull{Endocrines}					\gdef\@doiabbr{endocrines}	\gdef\@ISSN{2673-396X}	}
\DeclareOption{energies}{			\gdef\@journal{energies}			\gdef\@journalshort{Energies}					\gdef\@journalfull{Energies}					\gdef\@doiabbr{en}			\gdef\@ISSN{1996-1073}	}
\DeclareOption{engproc}{			\gdef\@journal{engproc}			\gdef\@journalshort{Eng. Proc.}				\gdef\@journalfull{Engineering Proceedings}		\gdef\@doiabbr{engproc}		\gdef\@ISSN{2673-4591}	}
\DeclareOption{entropy}{			\gdef\@journal{entropy}			\gdef\@journalshort{Entropy}					\gdef\@journalfull{Entropy}					\gdef\@doiabbr{e}			\gdef\@ISSN{1099-4300}	}
\DeclareOption{environments}{		\gdef\@journal{environments}		\gdef\@journalshort{Environments}				\gdef\@journalfull{Environments}				\gdef\@doiabbr{environments}	\gdef\@ISSN{2076-3298}	}
\DeclareOption{environsciproc}{	\gdef\@journal{environsciproc}		\gdef\@journalshort{Environ. Sci. Proc.}			\gdef\@journalfull{Environmental Sciences Proceedings}	\gdef\@doiabbr{environsciproc}	\gdef\@ISSN{2673-4931}	}
\DeclareOption{epidemiologia}{		\gdef\@journal{epidemiologia}		\gdef\@journalshort{Epidemiologia}				\gdef\@journalfull{Epidemiologia}				\gdef\@doiabbr{epidemiol}	\gdef\@ISSN{2673-3986}	}
\DeclareOption{epigenomes}{		\gdef\@journal{epigenomes}		\gdef\@journalshort{Epigenomes}				\gdef\@journalfull{Epigenomes}				\gdef\@doiabbr{epigenomes}	\gdef\@ISSN{2075-4655}	}
\DeclareOption{est}{				\gdef\@journal{est}				\gdef\@journalshort{Electrochem. Sci. Technol.}	\gdef\@journalfull{Electrochemical Science and Technology}	\gdef\@doiabbr{}	\gdef\@ISSN{		}	}
\DeclareOption{fermentation}{		\gdef\@journal{fermentation}		\gdef\@journalshort{Fermentation}				\gdef\@journalfull{Fermentation}				\gdef\@doiabbr{fermentation}	\gdef\@ISSN{2311-5637}	}
\DeclareOption{fibers}{			\gdef\@journal{fibers}			\gdef\@journalshort{Fibers}					\gdef\@journalfull{Fibers}						\gdef\@doiabbr{fib}			\gdef\@ISSN{2079-6439}	}
\DeclareOption{fire}{				\gdef\@journal{fire}				\gdef\@journalshort{Fire}						\gdef\@journalfull{Fire}						\gdef\@doiabbr{fire}			\gdef\@ISSN{2571-6255}	}
\DeclareOption{fishes}{			\gdef\@journal{fishes}			\gdef\@journalshort{Fishes}					\gdef\@journalfull{Fishes}						\gdef\@doiabbr{fishes}		\gdef\@ISSN{2410-3888}	}
\DeclareOption{fluids}{			\gdef\@journal{fluids}			\gdef\@journalshort{Fluids}					\gdef\@journalfull{Fluids}						\gdef\@doiabbr{fluids}		\gdef\@ISSN{2311-5521}	}
\DeclareOption{foods}{			\gdef\@journal{foods}			\gdef\@journalshort{Foods}					\gdef\@journalfull{Foods}						\gdef\@doiabbr{foods}		\gdef\@ISSN{2304-8158}	}
\DeclareOption{forecasting}{		\gdef\@journal{forecasting}		\gdef\@journalshort{Forecasting}				\gdef\@journalfull{Forecasting}					\gdef\@doiabbr{forecast}		\gdef\@ISSN{2571-9394}	}
\DeclareOption{forests}{			\gdef\@journal{forests}			\gdef\@journalshort{Forests}					\gdef\@journalfull{Forests}					\gdef\@doiabbr{f}			\gdef\@ISSN{1999-4907}	}
\DeclareOption{fractalfract}{		\gdef\@journal{fractalfract}		\gdef\@journalshort{Fractal Fract.}				\gdef\@journalfull{Fractal and Fractional}			\gdef\@doiabbr{fractalfract}	\gdef\@ISSN{2504-3110}	}
\DeclareOption{fuels}{			\gdef\@journal{fuels}				\gdef\@journalshort{Fuels}					\gdef\@journalfull{Fuels}						\gdef\@doiabbr{fu}			\gdef\@ISSN{2673-3994}	}
\DeclareOption{futureinternet}{		\gdef\@journal{futureinternet}		\gdef\@journalshort{Future Internet}				\gdef\@journalfull{Future Internet}				\gdef\@doiabbr{fi}			\gdef\@ISSN{1999-5903}	}
\DeclareOption{futurephys}{		\gdef\@journal{futurephys}		\gdef\@journalshort{Future Phys.}				\gdef\@journalfull{Future Physics}				\gdef\@doiabbr{futurephys}	\gdef\@ISSN{2624-6503}	}
\DeclareOption{galaxies}{			\gdef\@journal{galaxies}			\gdef\@journalshort{Galaxies}					\gdef\@journalfull{Galaxies}					\gdef\@doiabbr{galaxies}		\gdef\@ISSN{2075-4434}	}
\DeclareOption{games}{			\gdef\@journal{games}			\gdef\@journalshort{Games}					\gdef\@journalfull{Games}					\gdef\@doiabbr{g}			\gdef\@ISSN{2073-4336}	}
\DeclareOption{gardens}{			\gdef\@journal{gardens}			\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}	\gdef\@doiabbr{		}	\gdef\@ISSN{		}	}
\DeclareOption{gases}{			\gdef\@journal{gases}			\gdef\@journalshort{Gases}					\gdef\@journalfull{Gases}						\gdef\@doiabbr{gases}		\gdef\@ISSN{		}	}
\DeclareOption{gastrointestdisord}{	\gdef\@journal{gastrointestdisord}	\gdef\@journalshort{Gastrointest. Disord.}			\gdef\@journalfull{Gastrointestinal Disorders}		\gdef\@doiabbr{gidisord}		\gdef\@ISSN{2624-5647}	}
\DeclareOption{gels}{			\gdef\@journal{gels}				\gdef\@journalshort{Gels}						\gdef\@journalfull{Gels}						\gdef\@doiabbr{gels}		\gdef\@ISSN{2310-2861}	}
\DeclareOption{genealogy}{		\gdef\@journal{genealogy}		\gdef\@journalshort{Genealogy}				\gdef\@journalfull{Genealogy}					\gdef\@doiabbr{genealogy}	\gdef\@ISSN{2313-5778}	}
\DeclareOption{genes}{			\gdef\@journal{genes}			\gdef\@journalshort{Genes}					\gdef\@journalfull{Genes}						\gdef\@doiabbr{genes}		\gdef\@ISSN{2073-4425}	}
\DeclareOption{geohazards}{		\gdef\@journal{geohazards}		\gdef\@journalshort{GeoHazards}				\gdef\@journalfull{GeoHazards}				\gdef\@doiabbr{geohazards}	\gdef\@ISSN{2624-795X}	}
\DeclareOption{geosciences}{		\gdef\@journal{geosciences}		\gdef\@journalshort{Geosciences}				\gdef\@journalfull{Geosciences}				\gdef\@doiabbr{geosciences}	\gdef\@ISSN{2076-3263}	}
\DeclareOption{geriatrics}{		\gdef\@journal{geriatrics}			\gdef\@journalshort{Geriatrics}					\gdef\@journalfull{Geriatrics}					\gdef\@doiabbr{geriatrics}		\gdef\@ISSN{2308-3417}	}
\DeclareOption{hazardousmatters}{	\gdef\@journal{hazardousmatters}	\gdef\@journalshort{Hazard. Matters}			\gdef\@journalfull{Hazardous Matters}			\gdef\@doiabbr{}			\gdef\@ISSN{0014-0014}	}
\DeclareOption{healthcare}{		\gdef\@journal{healthcare}		\gdef\@journalshort{Healthcare}				\gdef\@journalfull{Healthcare}					\gdef\@doiabbr{healthcare}	\gdef\@ISSN{2227-9032}	}
\DeclareOption{hearts}{			\gdef\@journal{hearts}			\gdef\@journalshort{Hearts}					\gdef\@journalfull{Hearts}						\gdef\@doiabbr{hearts}		\gdef\@ISSN{2673-3846}	}
\DeclareOption{heritage}{			\gdef\@journal{heritage}			\gdef\@journalshort{Heritage}					\gdef\@journalfull{Heritage}					\gdef\@doiabbr{heritage}		\gdef\@ISSN{2571-9408}	}
\DeclareOption{highthroughput}{	\gdef\@journal{highthroughput}		\gdef\@journalshort{High-Throughput}			\gdef\@journalfull{High-Throughput}				\gdef\@doiabbr{ht}			\gdef\@ISSN{2571-5135}	}
\DeclareOption{horticulturae}{		\gdef\@journal{horticulturae}		\gdef\@journalshort{Horticulturae}				\gdef\@journalfull{Horticulturae}				\gdef\@doiabbr{horticulturae}	\gdef\@ISSN{2311-7524}	}
\DeclareOption{humanities}{		\gdef\@journal{humanities}		\gdef\@journalshort{Humanities}				\gdef\@journalfull{Humanities}					\gdef\@doiabbr{h}			\gdef\@ISSN{2076-0787}	}
\DeclareOption{hydrogen}{		\gdef\@journal{hydrogen}			\gdef\@journalshort{Hydrogen}					\gdef\@journalfull{Hydrogen}					\gdef\@doiabbr{hydrogen}	\gdef\@ISSN{2673-4141}	}
\DeclareOption{hydrology}{		\gdef\@journal{hydrology}			\gdef\@journalshort{Hydrology}					\gdef\@journalfull{Hydrology}					\gdef\@doiabbr{hydrology}	\gdef\@ISSN{2306-5338}	}
\DeclareOption{ijd}{		\gdef\@journal{ijd}	\gdef\@journalshort{Int. J. Diabetol.}			\gdef\@journalfull{International Journal of Diabetology}								\gdef\@doiabbr{ijd}	\gdef\@ISSN{2673-4540}	}
\DeclareOption{ijerph}{	\gdef\@journal{ijerph}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}	}
\DeclareOption{ijfs}{		\gdef\@journal{ijfs}	\gdef\@journalshort{Int. J. Financial Stud.}	\gdef\@journalfull{International Journal of Financial Studies}							\gdef\@doiabbr{ijfs}	\gdef\@ISSN{2227-7072}	}
\DeclareOption{ijgi}{		\gdef\@journal{ijgi}	\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}	\gdef\@journalfull{ISPRS International Journal of Geo-Information}						\gdef\@doiabbr{ijgi}	\gdef\@ISSN{2220-9964}	}
\DeclareOption{ijms}{	\gdef\@journal{ijms}	\gdef\@journalshort{Int. J. Mol. Sci.}			\gdef\@journalfull{International Journal of Molecular Sciences}							\gdef\@doiabbr{ijms}	\gdef\@ISSN{1422-0067}	}
\DeclareOption{ijtpp}{	\gdef\@journal{ijtpp}	\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@journalfull{International Journal of Turbomachinery, Propulsion and Power}	\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}	}
\DeclareOption{informatics}{		\gdef\@journal{informatics}		\gdef\@journalshort{Informatics}				\gdef\@journalfull{Informatics}					\gdef\@doiabbr{informatics}	\gdef\@ISSN{2227-9709}	}
\DeclareOption{information}{		\gdef\@journal{information}		\gdef\@journalshort{Information}				\gdef\@journalfull{Information}					\gdef\@doiabbr{info}			\gdef\@ISSN{2078-2489}	}
\DeclareOption{infrastructures}{		\gdef\@journal{infrastructures}		\gdef\@journalshort{Infrastructures}				\gdef\@journalfull{Infrastructures}				\gdef\@doiabbr{infrastructures}	\gdef\@ISSN{2412-3811}	}
\DeclareOption{inorganics}{		\gdef\@journal{inorganics}		\gdef\@journalshort{Inorganics}				\gdef\@journalfull{Inorganics}					\gdef\@doiabbr{inorganics}	\gdef\@ISSN{2304-6740}	}
\DeclareOption{insects}{			\gdef\@journal{insects}			\gdef\@journalshort{Insects}					\gdef\@journalfull{Insects}						\gdef\@doiabbr{insects}		\gdef\@ISSN{2075-4450}	}
\DeclareOption{instruments}{		\gdef\@journal{instruments}		\gdef\@journalshort{Instruments}				\gdef\@journalfull{Instruments}					\gdef\@doiabbr{instruments}	\gdef\@ISSN{2410-390X}	}
\DeclareOption{inventions}{		\gdef\@journal{inventions}		\gdef\@journalshort{Inventions}					\gdef\@journalfull{Inventions}					\gdef\@doiabbr{inventions}	\gdef\@ISSN{2411-5134}	}
\DeclareOption{iot}{				\gdef\@journal{iot}				\gdef\@journalshort{IoT}						\gdef\@journalfull{IoT}						\gdef\@doiabbr{iot}			\gdef\@ISSN{2624-831X}	}
\DeclareOption{j}{				\gdef\@journal{j}				\gdef\@journalshort{J}						\gdef\@journalfull{J}							\gdef\@doiabbr{j}			\gdef\@ISSN{2571-8800}	}
\DeclareOption{jcdd}{	\gdef\@journal{jcdd}	\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}		\gdef\@journalfull{Journal of Cardiovascular Development and Disease}		\gdef\@doiabbr{jcdd}		\gdef\@ISSN{2308-3425}	}
\DeclareOption{jcm}{		\gdef\@journal{jcm}	\gdef\@journalshort{J. Clin. Med.}				\gdef\@journalfull{Journal of Clinical Medicine}							\gdef\@doiabbr{jcm}			\gdef\@ISSN{2077-0383}	}
\DeclareOption{jcp}{		\gdef\@journal{jcp}	\gdef\@journalshort{J. Cybersecur. Priv.}			\gdef\@journalfull{Journal of Cybersecurity and Privacy}					\gdef\@doiabbr{jcp}			\gdef\@ISSN{2624-800X}	}
\DeclareOption{jcs}{		\gdef\@journal{jcs}	\gdef\@journalshort{J. Compos. Sci.}			\gdef\@journalfull{Journal of Composites Science}						\gdef\@doiabbr{jcs}			\gdef\@ISSN{2504-477X}	}
\DeclareOption{jdb}{		\gdef\@journal{jdb}	\gdef\@journalshort{J. Dev. Biol.}				\gdef\@journalfull{Journal of Developmental Biology}					\gdef\@doiabbr{jdb}			\gdef\@ISSN{2221-3759}	}
\DeclareOption{jfb}{		\gdef\@journal{jfb}	\gdef\@journalshort{J. Funct. Biomater.}  		 	\gdef\@journalfull{Journal of Functional Biomaterials}   					\gdef\@doiabbr{jfb}			\gdef\@ISSN{2079-4983}	}
\DeclareOption{jfmk}{	\gdef\@journal{jfmk}	\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}   	\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}   		\gdef\@doiabbr{jfmk}		\gdef\@ISSN{2411-5142}	}
\DeclareOption{jimaging}{		\gdef\@journal{jimaging}		\gdef\@journalshort{J. Imaging}	\gdef\@journalfull{Journal of Imaging}								\gdef\@doiabbr{jimaging}		\gdef\@ISSN{2313-433X}	}
\DeclareOption{jintelligence}{	\gdef\@journal{jintelligence}	\gdef\@journalshort{J. Intell.}		\gdef\@journalfull{Journal of Intelligence}								\gdef\@doiabbr{jintelligence}	\gdef\@ISSN{2079-3200}	}
\DeclareOption{jlpea}{	\gdef\@journal{jlpea}	\gdef\@journalshort{J. Low Power Electron. Appl.}	\gdef\@journalfull{Journal of Low Power Electronics and Applications}		\gdef\@doiabbr{jlpea}		\gdef\@ISSN{2079-9268}	}
\DeclareOption{jmmp}{	\gdef\@journal{jmmp}\gdef\@journalshort{J. Manuf. Mater. Process.}	\gdef\@journalfull{Journal of Manufacturing and Materials Processing}		\gdef\@doiabbr{jmmp}		\gdef\@ISSN{2504-4494}	}
\DeclareOption{jmse}{	\gdef\@journal{jmse}	\gdef\@journalshort{J. Mar. Sci. Eng.}			\gdef\@journalfull{Journal of Marine Science and Engineering}				\gdef\@doiabbr{jmse}		\gdef\@ISSN{2077-1312}	}
\DeclareOption{jne}{		\gdef\@journal{jne}	\gdef\@journalshort{J. Nucl. Eng.}				\gdef\@journalfull{Journal of Nuclear Engineering}						\gdef\@doiabbr{jne}			\gdef\@ISSN{2673-4362}	}
\DeclareOption{jnt}{		\gdef\@journal{jnt}	\gdef\@journalshort{J. Nanotheranostics}			\gdef\@journalfull{Journal of Nanotheranostics}							\gdef\@doiabbr{jnt}			\gdef\@ISSN{2624-845X}	}
\DeclareOption{jof}{		\gdef\@journal{jof}	\gdef\@journalshort{J. Fungi}					\gdef\@journalfull{Journal of Fungi}									\gdef\@doiabbr{jof}			\gdef\@ISSN{2309-608X}	}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@journalfull{Journal of Open Innovation: Technology, Market, and Complexity}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{journalmedia}{		\gdef\@journal{journalmedia}		\gdef\@journalshort{Journal. Media}				\gdef\@journalfull{Journalism and Media}			\gdef\@doiabbr{		}	\gdef\@ISSN{		}	}
\DeclareOption{jpm}{		\gdef\@journal{jpm}	\gdef\@journalshort{J. Pers. Med.}				\gdef\@journalfull{Journal of Personalized Medicine}						\gdef\@doiabbr{jpm}			\gdef\@ISSN{2075-4426}	}
\DeclareOption{jrfm}{		\gdef\@journal{jrfm}	\gdef\@journalshort{J. Risk Financial Manag.}		\gdef\@journalfull{Journal of Risk and Financial Management}				\gdef\@doiabbr{jrfm}			\gdef\@ISSN{1911-8074}	}
\DeclareOption{jsan}{	\gdef\@journal{jsan}	\gdef\@journalshort{J. Sens. Actuator Netw.}		\gdef\@journalfull{Journal of Sensor and Actuator Networks}				\gdef\@doiabbr{jsan}		\gdef\@ISSN{2224-2708}	}
\DeclareOption{land}{			\gdef\@journal{land}				\gdef\@journalshort{Land}						\gdef\@journalfull{Land}						\gdef\@doiabbr{land}		\gdef\@ISSN{2073-445X}	}
\DeclareOption{languages}{		\gdef\@journal{languages}		\gdef\@journalshort{Languages}				\gdef\@journalfull{Languages}					\gdef\@doiabbr{languages}	\gdef\@ISSN{2226-471X}	}
\DeclareOption{laws}{			\gdef\@journal{laws}				\gdef\@journalshort{Laws}					\gdef\@journalfull{Laws}						\gdef\@doiabbr{laws}		\gdef\@ISSN{2075-471X}	}
\DeclareOption{life}{				\gdef\@journal{life}				\gdef\@journalshort{Life}						\gdef\@journalfull{Life}						\gdef\@doiabbr{life}			\gdef\@ISSN{2075-1729}	}
\DeclareOption{literature}{			\gdef\@journal{literature}			\gdef\@journalshort{Literature}					\gdef\@journalfull{Literature}					\gdef\@doiabbr{}			\gdef\@ISSN{2410-9789}	}
\DeclareOption{livers}{			\gdef\@journal{livers}			\gdef\@journalshort{Livers}					\gdef\@journalfull{Livers}						\gdef\@doiabbr{livers}		\gdef\@ISSN{2673-4389}	}
\DeclareOption{logistics}{			\gdef\@journal{logistics}			\gdef\@journalshort{Logistics}					\gdef\@journalfull{Logistics}					\gdef\@doiabbr{logistics}		\gdef\@ISSN{2305-6290}	}
\DeclareOption{lubricants}{		\gdef\@journal{lubricants}			\gdef\@journalshort{Lubricants}				\gdef\@journalfull{Lubricants}					\gdef\@doiabbr{lubricants}	\gdef\@ISSN{2075-4442}	}
\DeclareOption{machines}{		\gdef\@journal{machines}			\gdef\@journalshort{Machines}					\gdef\@journalfull{Machines}					\gdef\@doiabbr{machines}	\gdef\@ISSN{2075-1702}	}
\DeclareOption{magnetochemistry}{	\gdef\@journal{magnetochemistry}	\gdef\@journalshort{Magnetochemistry}			\gdef\@journalfull{Magnetochemistry}		\gdef\@doiabbr{magnetochemistry}	\gdef\@ISSN{2312-7481}	}
\DeclareOption{make}{			\gdef\@journal{make}			\gdef\@journalshort{Mach. Learn. Knowl. Extr.}	\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@doiabbr{make}	\gdef\@ISSN{2504-4990}	}
\DeclareOption{marinedrugs}{		\gdef\@journal{marinedrugs}		\gdef\@journalshort{Mar. Drugs}				\gdef\@journalfull{Marine Drugs}				\gdef\@doiabbr{md}			\gdef\@ISSN{1660-3397}	}
\DeclareOption{materials}{		\gdef\@journal{materials}			\gdef\@journalshort{Materials}					\gdef\@journalfull{Materials}					\gdef\@doiabbr{ma}			\gdef\@ISSN{1996-1944}	}
\DeclareOption{materproc}{		\gdef\@journal{materproc}		\gdef\@journalshort{Mater. Proc.}				\gdef\@journalfull{Materials Proceedings}			\gdef\@doiabbr{materproc}	\gdef\@ISSN{2673-4605}	}
\DeclareOption{mathematics}{		\gdef\@journal{mathematics}		\gdef\@journalshort{Mathematics}				\gdef\@journalfull{Mathematics}				\gdef\@doiabbr{math}		\gdef\@ISSN{2227-7390}	}
\DeclareOption{mca}{			\gdef\@journal{mca}				\gdef\@journalshort{Math. Comput. Appl.}	\gdef\@journalfull{Mathematical and Computational Applications}	\gdef\@doiabbr{mca}	\gdef\@ISSN{2297-8747}	}
\DeclareOption{medicina}{			\gdef\@journal{medicina}			\gdef\@journalshort{Medicina}					\gdef\@journalfull{Medicina}					\gdef\@doiabbr{medicina}		\gdef\@ISSN{1010-660X}	}
\DeclareOption{medicines}{		\gdef\@journal{medicines}		\gdef\@journalshort{Medicines}					\gdef\@journalfull{Medicines}					\gdef\@doiabbr{medicines}	\gdef\@ISSN{2305-6320}	}
\DeclareOption{medsci}{			\gdef\@journal{medsci}			\gdef\@journalshort{Med. Sci.}					\gdef\@journalfull{Medical Sciences}				\gdef\@doiabbr{medsci}		\gdef\@ISSN{2076-3271}	}
\DeclareOption{membranes}{		\gdef\@journal{membranes}		\gdef\@journalshort{Membranes}				\gdef\@journalfull{Membranes}					\gdef\@doiabbr{membranes}	\gdef\@ISSN{2077-0375}	}
\DeclareOption{metabolites}{		\gdef\@journal{metabolites}		\gdef\@journalshort{Metabolites}				\gdef\@journalfull{Metabolites}					\gdef\@doiabbr{metabo}		\gdef\@ISSN{2218-1989}	}
\DeclareOption{metals}{			\gdef\@journal{metals}			\gdef\@journalshort{Metals}					\gdef\@journalfull{Metals}						\gdef\@doiabbr{met}			\gdef\@ISSN{2075-4701}	}
\DeclareOption{microarrays}{		\gdef\@journal{microarrays}		\gdef\@journalshort{Microarrays}				\gdef\@journalfull{Microarrays}					\gdef\@doiabbr{}			\gdef\@ISSN{2076-3905}	}
\DeclareOption{micromachines}{	\gdef\@journal{micromachines}		\gdef\@journalshort{Micromachines}				\gdef\@journalfull{Micromachines}				\gdef\@doiabbr{mi}			\gdef\@ISSN{2072-666X}	}
\DeclareOption{microorganisms}{	\gdef\@journal{microorganisms}	\gdef\@journalshort{Microorganisms}			\gdef\@journalfull{Microorganisms}			\gdef\@doiabbr{microorganisms}	\gdef\@ISSN{2076-2607}	}
\DeclareOption{minerals}{			\gdef\@journal{minerals}			\gdef\@journalshort{Minerals}					\gdef\@journalfull{Minerals}					\gdef\@doiabbr{min}			\gdef\@ISSN{2075-163X}	}
\DeclareOption{modelling}{		\gdef\@journal{modelling}			\gdef\@journalshort{Modelling}					\gdef\@journalfull{Modelling}					\gdef\@doiabbr{}			\gdef\@ISSN{0012-0012}	}
\DeclareOption{molbank}{			\gdef\@journal{molbank}			\gdef\@journalshort{Molbank}					\gdef\@journalfull{Molbank}					\gdef\@doiabbr{M}			\gdef\@ISSN{1422-8599}	}
\DeclareOption{molecules}{		\gdef\@journal{molecules}		\gdef\@journalshort{Molecules}					\gdef\@journalfull{Molecules}					\gdef\@doiabbr{molecules}	\gdef\@ISSN{1420-3049}	}
\DeclareOption{mps}{			\gdef\@journal{mps}				\gdef\@journalshort{Methods Protoc.}			\gdef\@journalfull{Methods and Protocols}		\gdef\@doiabbr{mps}		\gdef\@ISSN{2409-9279}	}
\DeclareOption{mti}{				\gdef\@journal{mti}				\gdef\@journalshort{Multimodal Technol. Interact.}	\gdef\@journalfull{Multimodal Technologies and Interaction}	\gdef\@doiabbr{mti}	\gdef\@ISSN{2414-4088}	}
\DeclareOption{nanomaterials}{		\gdef\@journal{nanomaterials}		\gdef\@journalshort{Nanomaterials}				\gdef\@journalfull{Nanomaterials}				\gdef\@doiabbr{nano}		\gdef\@ISSN{2079-4991}	}
\DeclareOption{ncrna}{			\gdef\@journal{ncrna}			\gdef\@journalshort{Non-coding RNA}			\gdef\@journalfull{Non-coding RNA}				\gdef\@doiabbr{ncrna}		\gdef\@ISSN{2311-553X}	}
\DeclareOption{ijns}{				\gdef\@journal{ijns}				\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@doiabbr{ijns}		\gdef\@ISSN{2409-515X}	}
\DeclareOption{neurosci}{			\gdef\@journal{neurosci}			\gdef\@journalshort{NeuroSci}					\gdef\@journalfull{NeuroSci}					\gdef\@doiabbr{neurosci}		\gdef\@ISSN{		}	}
\DeclareOption{neuroglia}{		\gdef\@journal{neuroglia}			\gdef\@journalshort{Neuroglia}					\gdef\@journalfull{Neuroglia}					\gdef\@doiabbr{neuroglia}		\gdef\@ISSN{2571-6980}	}
\DeclareOption{nitrogen}{			\gdef\@journal{nitrogen}			\gdef\@journalshort{Nitrogen}					\gdef\@journalfull{Nitrogen}					\gdef\@doiabbr{nitrogen}		\gdef\@ISSN{2504-3129}	}
\DeclareOption{notspecified}{		\gdef\@journal{notspecified}		\gdef\@journalshort{Journal Not Specified}		\gdef\@journalfull{Journal Not Specified}			\gdef\@doiabbr{}			\gdef\@ISSN{		}	}
\DeclareOption{nutrients}{			\gdef\@journal{nutrients}			\gdef\@journalshort{Nutrients}					\gdef\@journalfull{Nutrients}					\gdef\@doiabbr{nu}			\gdef\@ISSN{2072-6643}	}
\DeclareOption{obesities}{			\gdef\@journal{obesities}			\gdef\@journalshort{Obesities}					\gdef\@journalfull{Obesities}					\gdef\@doiabbr{obesities}		\gdef\@ISSN{2673-4168}	}
\DeclareOption{oceans}{			\gdef\@journal{oceans}			\gdef\@journalshort{Oceans}					\gdef\@journalfull{Oceans}					\gdef\@doiabbr{oceans}		\gdef\@ISSN{2673-1924}	}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@journalfull{Journal of Otorhinolaryngology, Hearing and Balance Medicine}\gdef\@doiabbr{ohbm}	\gdef\@ISSN{2504-463X}	}
\DeclareOption{optics}{			\gdef\@journal{optics}			\gdef\@journalshort{Optics}					\gdef\@journalfull{Optics}						\gdef\@doiabbr{opt}			\gdef\@ISSN{2673-3269}	}
\DeclareOption{organics}{			\gdef\@journal{organics}			\gdef\@journalshort{Organics}					\gdef\@journalfull{Organics}					\gdef\@doiabbr{org}			\gdef\@ISSN{2673-401X}	}
\DeclareOption{osteology}{		\gdef\@journal{osteology}			\gdef\@journalshort{Osteology}					\gdef\@journalfull{Osteology}					\gdef\@doiabbr{osteology}	\gdef\@ISSN{2673-4036}	}
\DeclareOption{particles}{			\gdef\@journal{particles}			\gdef\@journalshort{Particles}					\gdef\@journalfull{Particles}					\gdef\@doiabbr{particles}		\gdef\@ISSN{2571-712X}	}
\DeclareOption{pathogens}{		\gdef\@journal{pathogens}		\gdef\@journalshort{Pathogens}				\gdef\@journalfull{Pathogens}					\gdef\@doiabbr{pathogens}	\gdef\@ISSN{2076-0817}	}
\DeclareOption{pharmaceuticals}{	\gdef\@journal{pharmaceuticals}	\gdef\@journalshort{Pharmaceuticals}			\gdef\@journalfull{Pharmaceuticals}				\gdef\@doiabbr{ph}			\gdef\@ISSN{1424-8247}	}
\DeclareOption{pharmaceutics}{	\gdef\@journal{pharmaceutics}		\gdef\@journalshort{Pharmaceutics}				\gdef\@journalfull{Pharmaceutics}				\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}	}
\DeclareOption{pharmacy}{		\gdef\@journal{pharmacy}			\gdef\@journalshort{Pharmacy}					\gdef\@journalfull{Pharmacy}					\gdef\@doiabbr{pharmacy}	\gdef\@ISSN{2226-4787}	}
\DeclareOption{philosophies}{		\gdef\@journal{philosophies}		\gdef\@journalshort{Philosophies}				\gdef\@journalfull{Philosophies}				\gdef\@doiabbr{philosophies}	\gdef\@ISSN{2409-9287}	}
\DeclareOption{photonics}{		\gdef\@journal{photonics}			\gdef\@journalshort{Photonics}					\gdef\@journalfull{Photonics}					\gdef\@doiabbr{photonics}	\gdef\@ISSN{2304-6732}	}
\DeclareOption{physics}{			\gdef\@journal{physics}			\gdef\@journalshort{Physics}					\gdef\@journalfull{Physics}					\gdef\@doiabbr{physics}		\gdef\@ISSN{2624-8174}	}
\DeclareOption{plants}{			\gdef\@journal{plants}			\gdef\@journalshort{Plants}					\gdef\@journalfull{Plants}						\gdef\@doiabbr{plants}		\gdef\@ISSN{2223-7747}	}
\DeclareOption{plasma}{			\gdef\@journal{plasma}			\gdef\@journalshort{Plasma}					\gdef\@journalfull{Plasma}					\gdef\@doiabbr{plasma}		\gdef\@ISSN{2571-6182}	}
\DeclareOption{pollutants}{		\gdef\@journal{pollutants}			\gdef\@journalshort{Pollutants}					\gdef\@journalfull{Pollutants}					\gdef\@doiabbr{pollutants}	\gdef\@ISSN{		}	}
\DeclareOption{polymers}{		\gdef\@journal{polymers}			\gdef\@journalshort{Polymers}					\gdef\@journalfull{Polymers}					\gdef\@doiabbr{polym}		\gdef\@ISSN{2073-4360}	}
\DeclareOption{polysaccharides}{	\gdef\@journal{polysaccharides}	\gdef\@journalshort{Polysaccharides}			\gdef\@journalfull{Polysaccharides}				\gdef\@doiabbr{}			\gdef\@ISSN{		}	}
\DeclareOption{preprints}{ 		\gdef\@journal{preprints} 			\gdef\@journalshort{Preprints}					\gdef\@journalfull{Preprints}					\gdef\@doiabbr{}			\gdef\@ISSN{		}	}
\DeclareOption{proceedings}{		\gdef\@journal{proceedings}		\gdef\@journalshort{Proceedings}				\gdef\@journalfull{Proceedings}				\gdef\@doiabbr{proceedings}	\gdef\@ISSN{2504-3900}	}
\DeclareOption{processes}{		\gdef\@journal{processes}		\gdef\@journalshort{Processes}				\gdef\@journalfull{Processes}					\gdef\@doiabbr{pr}			\gdef\@ISSN{2227-9717}	}
\DeclareOption{prosthesis}{		\gdef\@journal{prosthesis}		\gdef\@journalshort{Prosthesis}				\gdef\@journalfull{Prosthesis}					\gdef\@doiabbr{prosthesis}	\gdef\@ISSN{2673-1592}	}
\DeclareOption{proteomes}{		\gdef\@journal{proteomes}		\gdef\@journalshort{Proteomes}				\gdef\@journalfull{Proteomes}					\gdef\@doiabbr{proteomes}	\gdef\@ISSN{2227-7382}	}
\DeclareOption{psych}{			\gdef\@journal{psych}			\gdef\@journalshort{Psych}					\gdef\@journalfull{Psych}						\gdef\@doiabbr{psych}		\gdef\@ISSN{2624-8611}	}
\DeclareOption{psychiatryint}{		\gdef\@journal{psychiatryint}		\gdef\@journalshort{Psychiatry Int.}				\gdef\@journalfull{Psychiatry International}		\gdef\@doiabbr{psychiatryint}	\gdef\@ISSN{		}	}
\DeclareOption{publications}{		\gdef\@journal{publications}		\gdef\@journalshort{Publications}				\gdef\@journalfull{Publications}					\gdef\@doiabbr{publications}	\gdef\@ISSN{2304-6775}	}
\DeclareOption{quantumrep}{		\gdef\@journal{quantumrep}		\gdef\@journalshort{Quantum Rep.}				\gdef\@journalfull{Quantum Reports}			\gdef\@doiabbr{quantum}		\gdef\@ISSN{2624-960X}	}
\DeclareOption{quaternary}{		\gdef\@journal{quaternary}		\gdef\@journalshort{Quaternary}				\gdef\@journalfull{Quaternary}					\gdef\@doiabbr{quat}		\gdef\@ISSN{2571-550X}	}
\DeclareOption{qubs}{			\gdef\@journal{qubs}			\gdef\@journalshort{Quantum Beam Sci.}			\gdef\@journalfull{Quantum Beam Science}		\gdef\@doiabbr{qubs}		\gdef\@ISSN{2412-382X}	}
\DeclareOption{reactions}{		\gdef\@journal{reactions}			\gdef\@journalshort{Reactions}					\gdef\@journalfull{Reactions}					\gdef\@doiabbr{reactions}		\gdef\@ISSN{2624-781X}	}
\DeclareOption{recycling}{			\gdef\@journal{recycling}			\gdef\@journalshort{Recycling}					\gdef\@journalfull{Recycling}					\gdef\@doiabbr{recycling}		\gdef\@ISSN{2313-4321}	}
\DeclareOption{religions}{			\gdef\@journal{religions}			\gdef\@journalshort{Religions}					\gdef\@journalfull{Religions}					\gdef\@doiabbr{rel}			\gdef\@ISSN{2077-1444}	}
\DeclareOption{remotesensing}{	\gdef\@journal{remotesensing}		\gdef\@journalshort{Remote Sens.}				\gdef\@journalfull{Remote Sensing}				\gdef\@doiabbr{rs}			\gdef\@ISSN{2072-4292}	}
\DeclareOption{reports}{			\gdef\@journal{reports}			\gdef\@journalshort{Reports}					\gdef\@journalfull{Reports}					\gdef\@doiabbr{reports}		\gdef\@ISSN{2571-841X}	}
\DeclareOption{reprodmed}{		\gdef\@journal{reprodmed}		\gdef\@journalshort{Reprod. Med.}				\gdef\@journalfull{Reproductive Medicine}			\gdef\@doiabbr{reprodmed}	\gdef\@ISSN{2673-3897}	}
\DeclareOption{resources}{		\gdef\@journal{resources}			\gdef\@journalshort{Resources}				\gdef\@journalfull{Resources}					\gdef\@doiabbr{resources}	\gdef\@ISSN{2079-9276}	}
\DeclareOption{risks}{			\gdef\@journal{risks}				\gdef\@journalshort{Risks}					\gdef\@journalfull{Risks}						\gdef\@doiabbr{risks}		\gdef\@ISSN{2227-9091}	}
\DeclareOption{robotics}{			\gdef\@journal{robotics}			\gdef\@journalshort{Robotics}					\gdef\@journalfull{Robotics}					\gdef\@doiabbr{robotics}		\gdef\@ISSN{2218-6581}	}
\DeclareOption{safety}{			\gdef\@journal{safety}			\gdef\@journalshort{Safety}					\gdef\@journalfull{Safety}						\gdef\@doiabbr{safety}		\gdef\@ISSN{2313-576X}	}
\DeclareOption{sci}{				\gdef\@journal{sci}				\gdef\@journalshort{Sci}						\gdef\@journalfull{Sci}						\gdef\@doiabbr{sci}			\gdef\@ISSN{2413-4155}	}
\DeclareOption{scipharm}{		\gdef\@journal{scipharm}			\gdef\@journalshort{Sci. Pharm.}				\gdef\@journalfull{Scientia Pharmaceutica}		\gdef\@doiabbr{scipharm}		\gdef\@ISSN{2218-0532}	}
\DeclareOption{sensors}{			\gdef\@journal{sensors}			\gdef\@journalshort{Sensors}					\gdef\@journalfull{Sensors}					\gdef\@doiabbr{s}			\gdef\@ISSN{1424-8220}	}
\DeclareOption{separations}{		\gdef\@journal{separations}		\gdef\@journalshort{Separations}				\gdef\@journalfull{Separations}					\gdef\@doiabbr{separations}	\gdef\@ISSN{2297-8739}	}
\DeclareOption{sexes}{			\gdef\@journal{sexes}			\gdef\@journalshort{Sexes}					\gdef\@journalfull{Sexes}						\gdef\@doiabbr{}			\gdef\@ISSN{2411-5118}	}
\DeclareOption{signals}{			\gdef\@journal{signals}			\gdef\@journalshort{Signals}					\gdef\@journalfull{Signals}					\gdef\@doiabbr{signals}		\gdef\@ISSN{2624-6120}	}
\DeclareOption{sinusitis}{			\gdef\@journal{sinusitis}			\gdef\@journalshort{Sinusitis}					\gdef\@journalfull{Sinusitis}					\gdef\@doiabbr{sinusitis}		\gdef\@ISSN{2309-107X}	}
\DeclareOption{skins}{			\gdef\@journal{skins}			\gdef\@journalshort{Skins}					\gdef\@journalfull{Skins}						\gdef\@doiabbr{skins}		\gdef\@ISSN{		}	}
\DeclareOption{smartcities}{		\gdef\@journal{smartcities}		\gdef\@journalshort{Smart Cities}				\gdef\@journalfull{Smart Cities}					\gdef\@doiabbr{smartcities}	\gdef\@ISSN{2624-6511}	}
\DeclareOption{sna}{				\gdef\@journal{sna}				\gdef\@journalshort{Sinusitis Asthma}			\gdef\@journalfull{Sinusitis and Asthma}			\gdef\@doiabbr{sna}			\gdef\@ISSN{2624-7003}	}
\DeclareOption{societies}{			\gdef\@journal{societies}			\gdef\@journalshort{Societies}					\gdef\@journalfull{Societies}					\gdef\@doiabbr{soc}			\gdef\@ISSN{2075-4698}	}
\DeclareOption{socsci}{			\gdef\@journal{socsci}			\gdef\@journalshort{Soc. Sci.}					\gdef\@journalfull{Social Sciences}				\gdef\@doiabbr{socsci}		\gdef\@ISSN{2076-0760}	}
\DeclareOption{solids}{			\gdef\@journal{solids}			\gdef\@journalshort{Solids}					\gdef\@journalfull{Solids}						\gdef\@doiabbr{solids}		\gdef\@ISSN{		}	}
\DeclareOption{soilsystems}{		\gdef\@journal{soilsystems}		\gdef\@journalshort{Soil Syst.}					\gdef\@journalfull{Soil Systems}				\gdef\@doiabbr{soilsystems}	\gdef\@ISSN{2571-8789}	}
\DeclareOption{sports}{			\gdef\@journal{sports}			\gdef\@journalshort{Sports}					\gdef\@journalfull{Sports}						\gdef\@doiabbr{sports}		\gdef\@ISSN{2075-4663}	}
\DeclareOption{standards}{		\gdef\@journal{standards}			\gdef\@journalshort{Standards}					\gdef\@journalfull{Standards}					\gdef\@doiabbr{}			\gdef\@ISSN{2305-6703}	}
\DeclareOption{stats}{			\gdef\@journal{stats}				\gdef\@journalshort{Stats}					\gdef\@journalfull{Stats}						\gdef\@doiabbr{stats}		\gdef\@ISSN{2571-905X}	}
\DeclareOption{surfaces}{			\gdef\@journal{surfaces}			\gdef\@journalshort{Surfaces}					\gdef\@journalfull{Surfaces}					\gdef\@doiabbr{surfaces}		\gdef\@ISSN{2571-9637}	}
\DeclareOption{surgeries}{		\gdef\@journal{surgeries}			\gdef\@journalshort{Surgeries}					\gdef\@journalfull{Surgeries}					\gdef\@doiabbr{}			\gdef\@ISSN{2017-2017}	}
\DeclareOption{suschem}{			\gdef\@journal{suschem}			\gdef\@journalshort{Sus. Chem.}				\gdef\@journalfull{Sustainable Chemistry}			\gdef\@doiabbr{suschem}		\gdef\@ISSN{2673-4079}	}
\DeclareOption{sustainability}{		\gdef\@journal{sustainability}		\gdef\@journalshort{Sustainability}				\gdef\@journalfull{Sustainability}				\gdef\@doiabbr{su}			\gdef\@ISSN{2071-1050}	}
\DeclareOption{world}{			\gdef\@journal{world}			\gdef\@journalshort{World}					\gdef\@journalfull{World}						\gdef\@doiabbr{world}		\gdef\@ISSN{2673-4060}	}
\DeclareOption{symmetry}{		\gdef\@journal{symmetry}			\gdef\@journalshort{Symmetry}					\gdef\@journalfull{Symmetry}					\gdef\@doiabbr{sym}		\gdef\@ISSN{2073-8994}	}
\DeclareOption{systems}{			\gdef\@journal{systems}			\gdef\@journalshort{Systems}					\gdef\@journalfull{Systems}					\gdef\@doiabbr{systems}		\gdef\@ISSN{2079-8954}	}
\DeclareOption{technologies}{		\gdef\@journal{technologies}		\gdef\@journalshort{Technologies}				\gdef\@journalfull{Technologies}				\gdef\@doiabbr{technologies}	\gdef\@ISSN{2227-7080}	}
\DeclareOption{telecom}{			\gdef\@journal{telecom}			\gdef\@journalshort{Telecom}					\gdef\@journalfull{Telecom}					\gdef\@doiabbr{telecom}		\gdef\@ISSN{2673-4001}	}
\DeclareOption{test}{				\gdef\@journal{test}				\gdef\@journalshort{Test}						\gdef\@journalfull{Test}						\gdef\@doiabbr{}			\gdef\@ISSN{		}	}
\DeclareOption{tourismhosp}{		\gdef\@journal{tourismhosp}		\gdef\@journalshort{Tour. Hosp.}				\gdef\@journalfull{Tourism and Hospitality}		\gdef\@doiabbr{tourhosp}		\gdef\@ISSN{		}	}
\DeclareOption{toxics}{			\gdef\@journal{toxics}			\gdef\@journalshort{Toxics}					\gdef\@journalfull{Toxics}						\gdef\@doiabbr{toxics}		\gdef\@ISSN{2305-6304}	}
\DeclareOption{toxins}{			\gdef\@journal{toxins}			\gdef\@journalshort{Toxins}					\gdef\@journalfull{Toxins}						\gdef\@doiabbr{toxins}		\gdef\@ISSN{2072-6651}	}
\DeclareOption{transplantology}{	\gdef\@journal{transplantology}		\gdef\@journalshort{Transplantology}			\gdef\@journalfull{Transplantology}				\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}	}
\DeclareOption{tropicalmed}{		\gdef\@journal{tropicalmed}		\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@journalfull{Tropical Medicine and Infectious Disease}	\gdef\@doiabbr{tropicalmed}	\gdef\@ISSN{2414-6366}	}
\DeclareOption{universe}{			\gdef\@journal{universe}			\gdef\@journalshort{Universe}					\gdef\@journalfull{Universe}					\gdef\@doiabbr{universe}		\gdef\@ISSN{2218-1997}	}
\DeclareOption{urbansci}{			\gdef\@journal{urbansci}			\gdef\@journalshort{Urban Sci.}				\gdef\@journalfull{Urban Science}				\gdef\@doiabbr{urbansci}		\gdef\@ISSN{2413-8851}	}
\DeclareOption{uro}{				\gdef\@journal{uro}				\gdef\@journalshort{Uro J. Urol.}				\gdef\@journalfull{Uro---Journal of Urology}		\gdef\@doiabbr{uro}			\gdef\@ISSN{2673-4397}	}
\DeclareOption{vaccines}{			\gdef\@journal{vaccines}			\gdef\@journalshort{Vaccines}					\gdef\@journalfull{Vaccines}					\gdef\@doiabbr{vaccines}		\gdef\@ISSN{2076-393X}	}
\DeclareOption{vehicles}{			\gdef\@journal{vehicles}			\gdef\@journalshort{Vehicles}					\gdef\@journalfull{Vehicles}					\gdef\@doiabbr{vehicles}		\gdef\@ISSN{2624-8921}	}
\DeclareOption{vetsci}{			\gdef\@journal{vetsci}			\gdef\@journalshort{Vet. Sci.}					\gdef\@journalfull{Veterinary Sciences}			\gdef\@doiabbr{vetsci}		\gdef\@ISSN{2306-7381}	}
\DeclareOption{vibration}{			\gdef\@journal{vibration}			\gdef\@journalshort{Vibration}					\gdef\@journalfull{Vibration}					\gdef\@doiabbr{vibration}		\gdef\@ISSN{2571-631X}	}
\DeclareOption{viruses}{			\gdef\@journal{viruses}			\gdef\@journalshort{Viruses}					\gdef\@journalfull{Viruses}					\gdef\@doiabbr{v}			\gdef\@ISSN{1999-4915}	}
\DeclareOption{vision}{			\gdef\@journal{vision}			\gdef\@journalshort{Vision}					\gdef\@journalfull{Vision}						\gdef\@doiabbr{vision}		\gdef\@ISSN{2411-5150}	}
\DeclareOption{water}{			\gdef\@journal{water}			\gdef\@journalshort{Water}					\gdef\@journalfull{Water}						\gdef\@doiabbr{w}			\gdef\@ISSN{2073-4441}	}
\DeclareOption{wem}{			\gdef\@journal{wem}				\gdef\@journalshort{Wildl. Ecol. Manag.}			\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@doiabbr{}			\gdef\@ISSN{1234-4321}	}
\DeclareOption{wevj}{			\gdef\@journal{wevj}				\gdef\@journalshort{World Electric Vehicle Journal}	\gdef\@journalfull{World Electric Vehicle Journal}	\gdef\@doiabbr{wevj}		\gdef\@ISSN{2032-6653}	}
\DeclareOption{women}{			\gdef\@journal{women}			\gdef\@journalshort{Women}					\gdef\@journalfull{Women}					\gdef\@doiabbr{women}		\gdef\@ISSN{2673-4184}	}

### 2020-06-12 Paperfolder/MDPI_template/template.tex
updated names of the authors

--- 2020-06-09 Paperfolder/Paperfolder.tex
@@
 %=================================================================
-\documentclass[nutrients,article,submit,moreauthors,pdftex]{mdpi}
+\documentclass[journal,article,submit,moreauthors,pdftex]{Definitions/mdpi}
 
@@
 For preprints.org, the editorial staff will make this change immediately prior to posting.
-
-%% Some pieces required from the pandoc template
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{4pt}}
-\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
-\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}
-
-\usepackage{longtable}
-
-% see https://stackoverflow.com/a/47122900
 
@@
 % Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj
+% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, applmech, applnano, applsci, arts, asc, asi, atmosphere, atoms, automation, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, bloods, brainsci, breath, buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cyber, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, earth, econometrics, ecologies, economies, education, ejbc, ejihpe, electricity, electrochem, electronicmat, electronics, endocrines, energies, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, fuels, futureinternet, futurephys, galaxies, games, gardens, gases, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, hearts, heritage, highthroughput, horticulturae, humanities, hydrogen, hydrology, ijerph, ijfs, ijgi, ijms, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jce, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jne, jnt, jof, joitmc, journalmedia, jpm, jrfm, jsan, land, languages, laws, life, literature, livers, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, ijns, neurosci, neuroglia, nitrogen, notspecified, nutrients, obesities, oceans, ohbm, osteology, optics, organics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, pollutants, polymers, polysaccharides, preprints , proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reprodmed, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, surfaces, surgeries, suschem, sustainability, world, symmetry, systems, technologies, telecom, test, tourismhosp, toxics, toxins, transplantology, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj, women
 
@@
 \articlenumber{5}
-\pubyear{2019}
-\copyrightyear{2019}
+\pubyear{2020}
+\copyrightyear{2020}
 %\externaleditor{Academic Editor: name}
 \history{Received: date; Accepted: date; Published: date}
-\updates{yes} % If there is an update available, un-comment this line
+%\updates{yes} % If there is an update available, un-comment this line
 
@@
 % Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx,epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
 
 %=================================================================
-%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
 %% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
@@
 % Full title of the paper (Capitalized)
-\Title{Milk intake and risk of mortality risk}
+\Title{Title}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+
+% Author homepage: enter homapage URL or remove command
+\newcommand{\homepageauthorA}{https://www.mdpi.com/} % Add \homepageA{} behind the author's name
+%\newcommand{\homepageauthorB}{https://www.mdpi.com/} % Add \homepageB{} behind the author's name
 
 % Authors, for the paper (add full first names)
-\Author{Chaochen
-Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
-Yatsuya$^{2}$, Yingsong Lin$^{1}$, $^{}$}
+\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}\homepageA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
 
 % Authors, for metadata in PDF
-\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, }
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
 
@@
 \address{%
-$^{1}$ \quad Muenster University of Applied Sciences - Institute for
-Infrastructure, Water, Resources, Environment Correnstr. 25, 48149
-Muenster,
-Germany; \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}\\
-$^{2}$ \quad Your department Street, City,
-Country; \href{mailto:mail@mail.com}{\nolinkurl{mail@mail.com}}\\
-}
+$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
+$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+
 % Contact information of the corresponding author
-\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
-Tel.: +XX-000-00-0000.}
+\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
 
 % Current address and/or shared authorship
-\firstnote{Current address: Updated affiliation}
+\firstnote{Current address: Affiliation 3} 
 \secondnote{These authors contributed equally to this work.}
-
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
 
-% Simple summary
-\simplesumm{A Simple summary goes here.}
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
 
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum. For research
-articles, abstracts should give a pertinent overview of the work. We
-strongly encourage authors to use the following style of structured
-abstracts, but without headings: 1) Background: Place the question
-addressed in a broad context and highlight the purpose of the study; 2)
-Methods: Describe briefly the main methods or treatments applied; 3)
-Results: Summarize the article's main findings; and 4) Conclusion:
-Indicate the main conclusions or interpretations. The abstract should be
-an objective representation of the article, it must not contain results
-which are not presented and substantiated in the main text and should
-not exaggerate the main conclusions.}
+\abstract{A single paragraph of about 200 words maximum.
+For research articles, abstracts should give a pertinent overview of the work.
+We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: Place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: Describe briefly the main methods or treatments applied; (3) Results: Summarize the article's main findings; and (4) Conclusion: Indicate the main conclusions or interpretations.
+The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
-keywords specific to the article, yet reasonably common within the
-subject discipline.).}
+\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
@@
 
-\hypertarget{version}{%
-\section{Version}\label{version}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{section}{-1} %% Remove this when starting to work on the template.
+\section{How to Use this Template}
+The template details the sections that can be used in a manuscript.
+Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
+Please check the instructions for authors page of the journal to verify the correct order and names.
+For any questions, please contact the editorial office of the journal or support@mdpi.com.
+For LaTeX related questions please contact latex@mdpi.com.
+%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
 
-This Rmd-skeleton uses the mdpi Latex template published 2019/02.
-However, the official template gets more frequently updated than the
-`rticles' package. Therefore, please make sure prior to paper
-submission, that you're using the most recent .cls, .tex and .bst files
-(available \href{http://www.mdpi.com/authors/latex}{here}).
+\section{Introduction}
+The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the principal conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+Citing a journal paper \cite{ref-journal}.
+And now citing a book reference \cite{ref-book}.
+Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
 
-The introduction should briefly place the study in a broad context and
-highlight why it is important. It should define the purpose of the work
-and its significance. The current state of the research field should be
-reviewed carefully and key publications cited. Please highlight
-controversial and diverging hypotheses when necessary. Finally, briefly
-mention the main aim of the work and highlight the principal
-conclusions. As far as possible, please keep the introduction
-comprehensible to scientists outside your particular field of research.
-Citing a journal paper
-\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
-And now citing a book reference \citet{gujer_systems_2008}. Please use
-the command \citep{leutnant_stormwater_2016} for the following MDPI
-journals, which use author-date citation: Administrative Sciences, Arts,
-Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
-Religions, Risks, Social Sciences.
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\begin{quote}
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\end{quote}
 
-\hypertarget{materials-and-methods}{%
-\section{Materials and Methods}\label{materials-and-methods}}
-
-Materials and Methods should be described with sufficient details to
-allow others to replicate and build on published results. Please note
-that publication of your manuscript implicates that you must make all
-materials, data, computer code, and protocols associated with the
-publication available to readers. Please disclose at the submission
-stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while
-well-established methods can be briefly described and appropriately
-cited.
-
-Research manuscripts reporting large datasets that are deposited in a
-publicly available database should specify where the data have been
-deposited and provide the relevant accession numbers. If the accession
-numbers have not yet been obtained at the time of submission, please
-state that they will be provided during review. They must be provided
-prior to publication.
-
-Interventionary studies involving animals or humans, and other studies
-require ethical approval must list the authority that provided approval
-and the corresponding ethical approval code.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-This section may be divided by subheadings. It should provide a concise
-and precise description of the experimental results, their
-interpretation as well as the experimental conclusions that can be
-drawn.
-
-\hypertarget{subsection-heading-here}{%
-\subsection{Subsection Heading Here}\label{subsection-heading-here}}
-
-Subsection text here.
-
-\hypertarget{subsubsection-heading-here}{%
-\subsubsection{Subsubsection Heading
-Here}\label{subsubsection-heading-here}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Subsection}
+\unskip
+\subsubsection{Subsubsection}
 
 Bulleted lists look like this:
-
-\begin{itemize}
-\tightlist
-\item
-  First bullet
-\item
-  Second bullet
-\item
-  Third bullet
+\begin{itemize}[leftmargin=*,labelsep=5.8mm]
+\item	First bullet
+\item	Second bullet
+\item	Third bullet
 \end{itemize}
@@
 Numbered lists can be added as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  First item
-\item
-  Second item
-\item
-  Third item
+\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
+\item	First item 
+\item	Second item
+\item	Third item
 \end{enumerate}
@@
 
-All figures and tables should be cited in the main text as Figure 1,
-Table 1, etc.
+\subsection{Figures, Tables and Schemes}
+
+All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
 
@@
 \centering
-\includegraphics[width=3 cm]{logo-mdpi}
+\includegraphics[width=2 cm]{Definitions/logo-mdpi}
 \caption{This is a figure, Schemes follow the same formatting.
@@
 
+Text
+
+Text
+
 \begin{table}[H]
@@
 \centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
+%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
 \begin{tabular}{ccc}
@@
 
+Text
+
+Text
+
+%\begin{listing}[H]
+%\caption{Title of the listing}
+%\rule{\textwidth}{1pt}
+%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
+%\rule{\textwidth}{1pt}
+%\end{listing}
+
+\subsection{Formatting of Mathematical Components}
+
 This is an example of an equation:
@@
 \begin{equation}
-\mathbb{S}
+a + b = c
 \end{equation}
+%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+This ensures correct linenumbering.
+The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
 
-Example of a theorem:
-
+Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%% Example of a theorem:
 \begin{Theorem}
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+%% Example of a proof:
+\begin{proof}[Proof of Theorem 1]
+Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
+\end{proof}
+The text continues here.
 
-Authors should discuss the results and how they can be interpreted in
-perspective of previous studies and of the working hypotheses. The
-findings and their implications should be discussed in the broadest
-context possible. Future research directions may also be highlighted.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
 
-This section is not mandatory, but can be added to the manuscript if the
-discussion is unusually long or complex.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Materials and Methods}
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %% optional
-% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
-%
-% % Only for the journal Methods and Protocols:
-% % If you wish to submit a video article, please do so with any other supplementary material.
-% % \supplementary{The following are available at www.mdpi.com/link: Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
+Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
+Please disclose at the submission stage any restrictions on the availability of materials or information.
+New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
 
+Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
+If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
+They must be provided prior to publication.
+
+Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
+
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Patents}
+This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{6pt}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{All sources of funding of the study should be
-disclosed. Please clearly indicate grants that you have received in
-support of your research work. Clearly state if you received funds for
-covering the costs to publish in open access.}
+%% optional
+%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short
-paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X. and Y.Y. conceive and
-designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
-analyzed the data; W.W. contributed reagents/materials/analysis tools;
-Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
-contributed substantially to the work reported.}
+\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
+The following statements should be used ``Conceptualization, X.X.
+and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
+and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
+All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
+Authorship must be limited to those who have contributed substantially to the work reported.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{Declare conflicts of interest or state `The authors
-declare no conflict of interest.' Authors must identify and declare any
-personal circumstances or interest that may be perceived as
-inappropriately influencing the representation or interpretation of
-reported research results. Any role of the funding sponsors in the
-design of the study; in the collection, analyses or interpretation of
-data in the writing of the manuscript, or in the decision to publish the
-results must be declared in this section. If there is no role, please
-state `The founding sponsors had no role in the design of the study; in
-the collection, analyses, or interpretation of data; in the writing of
-the manuscript, an in the decision to publish the results'.}
+\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
+Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
+This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
+Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
+If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results''.}
 
@@
 \begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute \\
-DOAJ & Directory of open access journals \\
-TLA & Three letter acronym \\
-LD & linear dichroism \\
+MDPI & Multidisciplinary Digital Publishing Institute\\
+DOAJ & Directory of open access journals\\
+TLA & Three letter acronym\\
+LD & linear dichroism
 \end{tabular}}
 
-\input{"appendix.tex"}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendix
+\section{}
+\unskip
+\subsection{}
+The appendix is an optional section that can contain details and data supplemental to the main text.
+For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
+Mathematical proofs of results not central to the paper can be added as an appendix.
+
+\section{}
+All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
 % Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
@@
 %=====================================
-% References, variant A: internal bibliography
+% References, variant A: external bibliography
 %=====================================
-%\reftitle{References}
-%\begin{thebibliography}{999}
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+
+%=====================================
+% References, variant B: internal bibliography
+%=====================================
+\begin{thebibliography}{999}
 % Reference 1
-%\bibitem[Author1(year)]{ref-journal}
-%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
+\bibitem[Author1(year)]{ref-journal}
+Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
 % Reference 2
-%\bibitem[Author2(year)]{ref-book}
-%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-%\end{thebibliography}
+\bibitem[Author2(year)]{ref-book}
+Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
+\end{thebibliography}
 
@@
 
-%=====================================
-% References, variant B: external bibliography
-%=====================================
-\reftitle{References}
-\externalbibliography{yes}
-\bibliography{mybibfile.bib}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% optional
-\sampleavailability{Samples of the compounds \ldots\ldots{} are
-available from the authors.}
+\sampleavailability{Samples of the compounds ...... are available from the authors.}
 

### 2020-06-12 Paperfolder/Paperfolder.Rmd
updated names of the authors

--- 2020-06-08 Paperfolder/Paperfolder.Rmd
@@
     orcid: 0000-0001-5533-1497
-  - name: John Doe
-    affil: 2, \dagger, \ddagger
+  - name: Hiroshi Yatsuya
+    affil: 2 
+    orcid: 0000-0002-6220-9251
+  - name: Yingsong Lin
+    affil: 1
+    orcid: 0000-0003-0214-3649
+  - name: Shogo Kikuchi
+    affil: 1
+    orcid: 0000-0001-9499-9668
+  - name: Tae Sasakabe 
+    affil: 1 
+    orcid: 0000-0002-7417-5693
+  - name: Sayo Kawai
+    affil: 1
+    orcid: 0000-0002-5156-4880
+  - name: Hiroyasu Iso
+    affil: 3
+    orcid: 0000-0002-9241-7289 
+  - name: Akiko Tamakoshi
+    affil: 4
+    orcid: 0000-0002-9761-3879 
 affiliation:
@@
     address: |
-      Muenster University of Applied Sciences - 
-      Institute for Infrastructure, Water, Resources, Environment
-      Correnstr. 25, 48149 Muenster, Germany
-    email: leutnant@fh-muenster.de
+      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
+#    email: chaochen@wangcc.me
   - num: 2
     address: |
-      Your department
-      Street, City, Country
-    email: mail@mail.com
+      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
+  - num: 3
+    address: |
+      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
+  - num: 4
+    address: |
+      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
+#    email: yatsuya@gmail.com
 # firstnote to eighthnote
-firstnote: |
-  Current address: Updated affiliation
-secondnote: |
-  These authors contributed equally to this work.
+# firstnote: |
+#   Current address: Updated affiliation
+# secondnote: |
+#   These authors contributed equally to this work.
 correspondence: |
-  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
-journal: water
+  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
+journal: nutrients
 type: article
@@
 bibliography: mybibfile.bib
-appendix: appendix.tex
-simplesummary: |
-  A Simple summary goes here.
+# appendix: appendix.tex
+# simplesummary: |
+#  A Simple summary goes here.
 abstract: |
@@
 authorcontributions: |
-  For research articles with several authors, a short paragraph specifying their 
-  individual contributions must be provided. The following statements should be 
-  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
+  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
   experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
-  limited to those who have contributed substantially to the work reported.
+  reagents/materials/analysis tools; Y.Y. wrote the paper.''
 conflictsofinterest: |
-  Declare conflicts of interest or state 'The authors declare no conflict of 
-  interest.' Authors must identify and declare any personal circumstances or
-  interest that may be perceived as inappropriately influencing the
-  representation or interpretation of reported research results. Any role of the
-  funding sponsors in the design of the study; in the collection, analyses or 
-  interpretation of data in the writing of the manuscript, or in the decision to 
-  publish the results must be declared in this section. If there is no role, 
-  please state 'The founding sponsors had no role in the design of the study; 
-  in the collection, analyses, or interpretation of data; in the writing of the 
-  manuscript, an in the decision to publish the results'.
-sampleavailability: |
-  Samples of the compounds ...... are available from the authors.
+  The authors declare no conflict of interest.
+The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
+# sampleavailability: |
+#   Samples of the compounds ...... are available from the authors.
 abbreviations:
@@
 
-# Version
+<!-- # Version -->
 
-This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
-However, the official template gets more frequently updated than the 'rticles'
-package. Therefore, please make sure prior to paper submission, that you're 
-using the most recent .cls, .tex and .bst files 
-(available [here](http://www.mdpi.com/authors/latex)).
+<!-- This Rmd-skeleton uses the mdpi Latex template published 2019/02.  -->
+<!-- However, the official template gets more frequently updated than the 'rticles' -->
+<!-- package. Therefore, please make sure prior to paper submission, that you're  -->
+<!-- using the most recent .cls, .tex and .bst files  -->
+<!-- (available [here](http://www.mdpi.com/authors/latex)). -->
 

### 2020-06-12 Paperfolder/Paperfolder.tex
updated names of the authors

@@
 Wang$^{1,*}$\href{https://orcid.org/0000-0001-5533-1497}{\orcidicon}, Hiroshi
-Yatsuya$^{2}$, Yingsong Lin$^{1}$, $^{}$}
+Yatsuya$^{2}$\href{https://orcid.org/0000-0002-6220-9251}{\orcidicon}, Yingsong
+Lin$^{1}$\href{https://orcid.org/0000-0003-0214-3649}{\orcidicon}, Shogo
+Kikuchi$^{1}$\href{https://orcid.org/0000-0001-9499-9668}{\orcidicon}, Tae
+Sasakabe$^{1}$\href{https://orcid.org/0000-0002-7417-5693}{\orcidicon}, Sayo
+Kawai$^{1}$\href{https://orcid.org/0000-0002-5156-4880}{\orcidicon}, Hiroyasu
+Iso$^{3}$\href{https://orcid.org/0000-0002-9241-7289}{\orcidicon}, Akiko
+Tamakoshi$^{4}$\href{https://orcid.org/0000-0002-9761-3879}{\orcidicon}}
 
 % Authors, for metadata in PDF
-\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, }
+\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Shogo
+Kikuchi, Tae Sasakabe, Sayo Kawai, Hiroyasu Iso, Akiko Tamakoshi}
 
@@
 \address{%
-$^{1}$ \quad Muenster University of Applied Sciences - Institute for
-Infrastructure, Water, Resources, Environment Correnstr. 25, 48149
-Muenster,
-Germany; \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}\\
-$^{2}$ \quad Your department Street, City,
-Country; \href{mailto:mail@mail.com}{\nolinkurl{mail@mail.com}}\\
+$^{1}$ \quad Department of Public Health, Aichi Medical University
+School of Medicine, Nagakute, Japan; \\
+$^{2}$ \quad Departmet of Public Health, Fujita Health University School
+of Medicine, Toyoake, Japan; \\
+$^{3}$ \quad Public Health, Department of Social Medicine, Osaka
+University Graduate School of Medicine, Osaka, Japan; \\
+$^{4}$ \quad Department of Public Health, Faculty of Medicine, Hokkaido
+University, Sapporo, Japan; \\
 }
 % Contact information of the corresponding author
-\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
-Tel.: +XX-000-00-0000.}
+\corres{Correspondence: Email.:
+\href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}; Tel.:
++81-561-62-3311. Department of Public Health, Aichi Medical University
+School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan
+(C.W.)}
 
 % Current address and/or shared authorship
-\firstnote{Current address: Updated affiliation}
-\secondnote{These authors contributed equally to this work.}
 
@@
 % Simple summary
-\simplesumm{A Simple summary goes here.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\hypertarget{version}{%
-\section{Version}\label{version}}
-
-This Rmd-skeleton uses the mdpi Latex template published 2019/02.
-However, the official template gets more frequently updated than the
-`rticles' package. Therefore, please make sure prior to paper
-submission, that you're using the most recent .cls, .tex and .bst files
-(available \href{http://www.mdpi.com/authors/latex}{here}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short
-paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X. and Y.Y. conceive and
-designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
-analyzed the data; W.W. contributed reagents/materials/analysis tools;
-Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
-contributed substantially to the work reported.}
+\authorcontributions{``X.X. and Y.Y. conceive and designed the
+experiments; X.X. performed the experiments; X.X. and Y.Y. analyzed the
+data; W.W. contributed reagents/materials/analysis tools; Y.Y. wrote the
+paper.'\,'}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{Declare conflicts of interest or state `The authors
-declare no conflict of interest.' Authors must identify and declare any
-personal circumstances or interest that may be perceived as
-inappropriately influencing the representation or interpretation of
-reported research results. Any role of the funding sponsors in the
-design of the study; in the collection, analyses or interpretation of
-data in the writing of the manuscript, or in the decision to publish the
-results must be declared in this section. If there is no role, please
-state `The founding sponsors had no role in the design of the study; in
-the collection, analyses, or interpretation of data; in the writing of
-the manuscript, an in the decision to publish the results'.}
+\conflictsofinterest{The authors declare no conflict of interest. The
+founding sponsors had no role in the design of the study; in the
+collection, analyses, or interpretation of data; in the writing of the
+manuscript, an in the decision to publish the results.}
 
@@
 \end{tabular}}
-
-\input{"appendix.tex"}
 
@@
 %% optional
-\sampleavailability{Samples of the compounds \ldots\ldots{} are
-available from the authors.}
 

### 2020-06-12 Paperfolder/Paperfolder.Rmd
update template confirmed

@@
     orcid: 0000-0003-0214-3649
-  - name: Shogo Kikuchi
-    affil: 1
-    orcid: 0000-0001-9499-9668
   - name: Tae Sasakabe 
@@
     orcid: 0000-0002-5156-4880
+  - name: Shogo Kikuchi
+    affil: 1
+    orcid: 0000-0001-9499-9668
   - name: Hiroyasu Iso
@@
 abbreviations:
-  - short: MDPI
-    long: Multidisciplinary Digital Publishing Institute
+  - short: JACC
+    long: Japan Collaborative Cohort 
   - short: DOAJ
@@
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
+<!-- The introduction should briefly place the study in a broad context and highlight why it is important.
 It should define the purpose of the work and its significance.
@@
 Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
+-->
 
@@
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+<!-- Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
 Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
@@
 New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+-->
 
-Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
+<!-- Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
 If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
 They must be provided prior to publication.
+-->
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+<!-- Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code. -->
 
@@
 
-This section may be divided by subheadings.
+<!-- This section may be divided by subheadings.
 It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+-->
 
@@
 
-Subsection text here.
+<!-- Subsection text here. -->
 
@@
 
-Bulleted lists look like this:
+<!-- Bulleted lists look like this: -->
 
-* First bullet
-* Second bullet
-* Third bullet
+<!-- * First bullet -->
+<!-- * Second bullet -->
+<!-- * Third bullet -->
 
-Numbered lists can be added as follows:
+<!-- Numbered lists can be added as follows: -->
 
-1. First item
-2. Second item
-3. Third item
+<!-- 1. First item -->
+<!-- 2. Second item -->
+<!-- 3. Third item -->
 
-The text continues here.
+<!-- The text continues here. -->
 
-All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
+<!-- All figures and tables should be cited in the main text as Figure 1, Table 1, etc. -->
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=3 cm]{logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
+<!-- \begin{figure}[H] -->
+<!-- \centering -->
+<!-- \includegraphics[width=3 cm]{logo-mdpi} -->
+<!-- \caption{This is a figure, Schemes follow the same formatting.
 If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
@@
 Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
+A caption on a single line should be centered.} -->
+<!-- \end{figure} -->
 
@@
 
-This is an example of an equation:
+<!-- This is an example of an equation: -->
 
-\begin{equation}
-\mathbb{S}
-\end{equation}
+<!-- \begin{equation} -->
+<!-- \mathbb{S} -->
+<!-- \end{equation} -->
 <!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
@@
 <!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
-Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+<!-- Example of a theorem: -->
+<!-- \begin{Theorem} -->
+<!-- Example text of a theorem. -->
+<!-- \end{Theorem} -->
 
-The text continues here. Proofs must be formatted as follows:
+<!-- The text continues here. Proofs must be formatted as follows: -->
 
@@
 
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
+<!-- Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
 The findings and their implications should be discussed in the broadest context possible.
 Future research directions may also be highlighted.
+-->
 
@@
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+<!-- This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex. -->
 

### 2020-06-12 Paperfolder/Paperfolder.tex
update template confirmed

@@
 Yatsuya$^{2}$\href{https://orcid.org/0000-0002-6220-9251}{\orcidicon}, Yingsong
-Lin$^{1}$\href{https://orcid.org/0000-0003-0214-3649}{\orcidicon}, Shogo
-Kikuchi$^{1}$\href{https://orcid.org/0000-0001-9499-9668}{\orcidicon}, Tae
+Lin$^{1}$\href{https://orcid.org/0000-0003-0214-3649}{\orcidicon}, Tae
 Sasakabe$^{1}$\href{https://orcid.org/0000-0002-7417-5693}{\orcidicon}, Sayo
-Kawai$^{1}$\href{https://orcid.org/0000-0002-5156-4880}{\orcidicon}, Hiroyasu
+Kawai$^{1}$\href{https://orcid.org/0000-0002-5156-4880}{\orcidicon}, Shogo
+Kikuchi$^{1}$\href{https://orcid.org/0000-0001-9499-9668}{\orcidicon}, Hiroyasu
 Iso$^{3}$\href{https://orcid.org/0000-0002-9241-7289}{\orcidicon}, Akiko
@@
 % Authors, for metadata in PDF
-\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Shogo
-Kikuchi, Tae Sasakabe, Sayo Kawai, Hiroyasu Iso, Akiko Tamakoshi}
+\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Tae
+Sasakabe, Sayo Kawai, Shogo Kikuchi, Hiroyasu Iso, Akiko Tamakoshi}
 
@@
 
-The introduction should briefly place the study in a broad context and
-highlight why it is important. It should define the purpose of the work
-and its significance. The current state of the research field should be
-reviewed carefully and key publications cited. Please highlight
-controversial and diverging hypotheses when necessary. Finally, briefly
-mention the main aim of the work and highlight the principal
-conclusions. As far as possible, please keep the introduction
-comprehensible to scientists outside your particular field of research.
-Citing a journal paper
-\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
-And now citing a book reference \citet{gujer_systems_2008}. Please use
-the command \citep{leutnant_stormwater_2016} for the following MDPI
-journals, which use author-date citation: Administrative Sciences, Arts,
-Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
-Religions, Risks, Social Sciences.
-
 \hypertarget{materials-and-methods}{%
 \section{Materials and Methods}\label{materials-and-methods}}
-
-Materials and Methods should be described with sufficient details to
-allow others to replicate and build on published results. Please note
-that publication of your manuscript implicates that you must make all
-materials, data, computer code, and protocols associated with the
-publication available to readers. Please disclose at the submission
-stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while
-well-established methods can be briefly described and appropriately
-cited.
-
-Research manuscripts reporting large datasets that are deposited in a
-publicly available database should specify where the data have been
-deposited and provide the relevant accession numbers. If the accession
-numbers have not yet been obtained at the time of submission, please
-state that they will be provided during review. They must be provided
-prior to publication.
-
-Interventionary studies involving animals or humans, and other studies
-require ethical approval must list the authority that provided approval
-and the corresponding ethical approval code.
 
@@
 
-This section may be divided by subheadings. It should provide a concise
-and precise description of the experimental results, their
-interpretation as well as the experimental conclusions that can be
-drawn.
-
 \hypertarget{subsection-heading-here}{%
 \subsection{Subsection Heading Here}\label{subsection-heading-here}}
-
-Subsection text here.
 
@@
 Here}\label{subsubsection-heading-here}}
-
-Bulleted lists look like this:
-
-\begin{itemize}
-\tightlist
-\item
-  First bullet
-\item
-  Second bullet
-\item
-  Third bullet
-\end{itemize}
-
-Numbered lists can be added as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  First item
-\item
-  Second item
-\item
-  Third item
-\end{enumerate}
-
-The text continues here.
-
-All figures and tables should be cited in the main text as Figure 1,
-Table 1, etc.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=3 cm]{logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
 
@@
 \end{table}
-
-This is an example of an equation:
-
-\begin{equation}
-\mathbb{S}
-\end{equation}
-
-Example of a theorem:
-
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
 
@@
 \begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute \\
+JACC & Japan Collaborative Cohort \\
 DOAJ & Directory of open access journals \\

### 2020-06-12 Paperfolder/Paperfolder.Rmd
updated change the bib file

@@
 status: submit
-bibliography: mybibfile.bib
+bibliography: milk.bib
 # appendix: appendix.tex

### 2020-06-15 Paperfolder/Paperfolder.Rmd
updated with new tables

@@
 
+```{r tab1, echo=FALSE, eval=FALSE, message=FALSE}
+library(knitr)
+library(kableExtra)
+dt <- read.csv("tab/HRAFTweib.csv", header = T)
+names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
+kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
+```
+
 \begin{table}[H]

### 2020-06-15 Paperfolder/Paperfolder.tex
updated with new tables

@@
 
-Authors should discuss the results and how they can be interpreted in
-perspective of previous studies and of the working hypotheses. The
-findings and their implications should be discussed in the broadest
-context possible. Future research directions may also be highlighted.
-
 \hypertarget{conclusion}{%
 \section{Conclusion}\label{conclusion}}
-
-This section is not mandatory, but can be added to the manuscript if the
-discussion is unusually long or complex.
 
@@
 \externalbibliography{yes}
-\bibliography{mybibfile.bib}
+\bibliography{milk.bib}
 

### 2020-06-15 Paperfolder/Paperfolder.Rmd
updated table 1 done

--- 2020-06-12 Paperfolder/Paperfolder.Rmd
@@
 
+```{r tab1, echo=FALSE, eval=TRUE, message=FALSE}
+library(knitr)
+library(kableExtra)
+dt <- read.csv("tab/HRAFTweib.csv", header = T)
+names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
+kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
+```
+
 \begin{table}[H]

### 2020-06-15 Paperfolder/Paperfolder.tex
updated table 1 done

@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
 \begin{document}
@@
 Here}\label{subsubsection-heading-here}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:tab1}}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllllllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
+\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
+Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
+\midrule
+\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & \vphantom{2} -\\
+1-2 t/Mon & 0.88 & 0.89 (0.09) & (0.73, 1.08) & 0.0022 & 86.50\% & 0.93 & 0.93 (0.06) & (0.81, 1.06) & 0.0016\\
+\rowcolor{gray!6}  1-2 t/Week & 0.77 & 0.77 (0.07) & (0.63, 0.91) & 0.0019 & 99.90\% & 0.83 & 0.83 (0.05) & (0.73, 0.94) & 0.0014\\
+3-4 t/Week & 0.79 & 0.79 (0.07) & (0.66, 0.94) & 0.0022 & 99.70\% & 0.85 & 0.85 (0.05) & (0.74, 0.96) & 0.0016\\
+\rowcolor{gray!6}  Daily & 0.90 & 0.90 (0.06) & (0.79, 1.03) & 0.0018 & 93.47\% & 0.93 & 0.93 (0.04) & (0.85, 1.02) & 0.0013\\
+Never & - & - & - & - & - & - & - & - & \vphantom{1} -\\
+\rowcolor{gray!6}  1-2 t/Mon & 0.98 & 0.98 (0.11) & (0.79, 1.19) & 0.0027 & 58.70\% & 0.99 & 0.99 (0.06) & (0.87, 1.11) & 0.0016\\
+1-2 t/Week & 0.84 & 0.84 (0.08) & (0.70, 1.00) & 0.0022 & 97.31\% & 0.90 & 0.90 (0.05) & (0.81, 1.00) & 0.0014\\
+\rowcolor{gray!6}  3-4 t/Week & 0.85 & 0.86 (0.08) & (0.71, 1.02) & 0.0021 & 96.05\% & 0.91 & 0.91 (0.05) & (0.82, 1.01) & 0.0013\\
+Daily & 0.75 & 0.76 (0.05) & (0.66, 0.87) & 0.0016 & 100.00\% & 0.85 & 0.85 (0.04) & (0.78, 0.92) & 0.0011\\
+\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
+1-2 t/Mon & 1.00 & 1.01 (0.12) & (0.81, 1.24) & 0.0041 & 50.61\% & 1.00 & 1.00 (0.07) & (0.88, 1.14) & 0.0029\\
+\rowcolor{gray!6}  1-2 t/Week & 0.86 & 0.87 (0.09) & (0.72, 1.05) & 0.0036 & 93.73\% & 0.92 & 0.92 (0.06) & (0.82, 1.03) & 0.0024\\
+3-4 t/Week & 0.89 & 0.90 (0.09) & (0.74, 1.08) & 0.0038 & 89.62\% & 0.93 & 0.94 (0.06) & (0.84, 1.05) & 0.0026\\
+\rowcolor{gray!6}  Daily & 0.80 & 0.80 (0.07) & (0.69, 0.93) & 0.0031 & 99.04\% & 0.88 & 0.88 (0.05) & (0.81, 0.96) & 0.0020\\
+\bottomrule
+\multicolumn{10}{l}{\textit{Note: }}\\
+\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{10}{l}{ Probability indicates that the p for HR smaller than 1.}\\
+\end{tabular}
+\end{table}
 

### 2020-06-15 Paperfolder/presentation.R

@@ -1,0 +1,5 @@
+load("data/JACCmilkstroke.Rdata")
+
+summary(coda::as.mcmc(M0men_20200520))
+summary(coda::as.mcmc(M1_agemen_20200520))
+summary(coda::as.mcmc(M2men_20200521))

### 2020-06-18 AnalysisScript/ModelsJAGSmen.R
model for hemo stroke event added

@@ -423,7 +423,7 @@ save.image(file = "data/JACCmilkstroke.Rdata")
 # DIC info (using the rule, pD = var(deviance)/2)
 # pD = 3031.2 and DIC = 17868.1
 # DIC is an estimate of expected predictive error (lower deviance is better).
-=======
+# =======
 # jaccbayes
 
 
@@ -752,4 +752,3 @@ M2menfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = M2.params,
                          n.iter=10000, n.burnin=(5000/2), n.chains = 3,
                          model.file=M2.weibull.model)
 print(M2menfit)
->>>>>>> da69867550273960aa54ce724fa178551b867532

### 2020-06-18 AnalysisScript/ModelsJAGSmenHemoStroke.R

@@ -1,0 +1,83 @@
+# HemoStroke == "I60_2"
+
+library(tidyverse)
+
+#######################Model 0 crude#######################
+#                                                          #
+#                      Model 0 crude                       #
+#                                                          #
+#**********************************************************#
+
+
+# Define exposure
+Mlkfre <- as.numeric(MData_men$Mlkfre)
+table(Mlkfre)
+table(MData_men$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
+
+# define events 
+is.censored <- MData_men$HemoStroke == "I60_2"
+
+# define followup time for events
+t <- if_else(!is.censored, MData_men$followpy, 0)
+t <- na_if(t, 0)
+t
+
+
+# define followup time for censored 
+c <- if_else(is.censored, MData_men$followpy, 0)
+
+c[!is.censored] <- t[!is.censored] + 1
+
+
+
+
+jacc.weibull.model0 <- function() {
+  for(i in 1:39386){
+    is.censored[i] ~ dinterval(t[i], c[i])
+    t[i] ~ dweib(shape, lambda[i])
+    lambda[i] <- exp(-mu[i] * shape)
+    mu[i] <- beta[1] + beta[2]*equals(Mlkfre[i], 2) +
+      beta[3]*equals(Mlkfre[i], 3) + beta[4] * equals(Mlkfre[i], 4) +
+      beta[5] * equals(Mlkfre[i], 5) 
+  }
+  
+  ## priors for betas
+  for(j in 1:5){
+    beta[j] ~ dnorm(0, 0.001)
+  }
+  
+  ### prior for shape
+  shape ~ dgamma(.001, .001)
+  
+  ### Generated values
+  AFT[2] <- exp(-beta[2])
+  HR[2] <- exp(-shape * beta[2])
+  p.crit[2] <- step(1 - HR[2])
+  
+  AFT[3] <- exp(-beta[3])
+  HR[3] <- exp(-shape * beta[3])
+  p.crit[3] <- step(1 - HR[3])
+  
+  AFT[4] <- exp(-beta[4])
+  HR[4] <- exp(-shape * beta[4])
+  p.crit[4] <- step(1 - HR[4])
+  
+  AFT[5] <- exp(-beta[5])
+  HR[5] <- exp(-shape * beta[5])
+  p.crit[5] <- step(1 - HR[5])
+}
+
[…]

### 2020-06-22 AnalysisScript/ModelsJAGSmenHemoStroke.R
updated codes for another outcome

@@ -74,7 +74,7 @@ library(R2jags)
 
 start.time <- Sys.time()
 jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = larynx.params, 
-                         n.iter=100000, n.burnin=(5000/2), n.chains = 3, n.thin = 100,
+                         n.iter=100000, n.burnin=(5000/2), n.chains = 3, #n.thin = 100,
                          model.file=jacc.weibull.model0)
 end.time <- Sys.time()
 end.time - start.time 

### 2020-06-22 AnalysisScript/ModelsJAGSmenHemoStroke.R
upddated another script Rdata to save

@@ -80,4 +80,5 @@ end.time <- Sys.time()
 end.time - start.time 
 M0menHemoStroke_20200618 <- jagsfit
 print(M0menHemoStroke_20200618)
+save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 save.image(file = "data/JACCmilkstroke.Rdata")

### 2020-06-22 Paperfolder/Paperfolder.Rmd
updated exposure and outcome

@@
 ---
-title: Milk intake and risk of mortality risk 
+title: Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
 author:
@@
     long: Japan Collaborative Cohort 
-  - short: DOAJ
-    long: Directory of open access journals
-  - short: TLA
-    long: Three letter acronym
-  - short: LD 
-    long: linear dichroism
+  - short: FFQ
+    long: Food Frequency Questionnaire
 output: rticles::mdpi_article
@@
 # Materials and Methods
+
+## The database
+
+We used data from the Japan Collaborative Cohort (JACC) study, which was sponsored by the Ministry of Education, Sports, Science, and Technology of Japan.
+Sampling methods and details about the JACC study have been described extensively in the literature [@Ohno2001; @Tamakoshi2005; @Tamakoshi2013].
+Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer.
+In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) were successfully retained for the current analysis.
+We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women).
+Finally, 94385 (39386 men and 54999 women) are left in the database.
+The study design and informed consent procedure were approved by the Ethics Review Committee of Nagoya University School of Medicine.
+
+## Exposure and the outcome of interest
+
+Frequency of milk intake during the preceding year of the baseline was assessed by FFQ from "never", "1-2 times/month", "1-2 times/week", "3-4 times/week", and "Almost daily".
 

### 2020-06-22 Paperfolder/Paperfolder.tex
updated exposure and outcome

@@
 % Full title of the paper (Capitalized)
-\Title{Milk intake and risk of mortality risk}
+\Title{Milk intake and risk of mortality risk in the Japan Collaborative
+Cohort Study - a Bayesian survival analysis}
 
@@
 
+\hypertarget{the-database}{%
+\subsection{The database}\label{the-database}}
+
+We used data from the Japan Collaborative Cohort (JACC) study, which was
+sponsored by the Ministry of Education, Sports, Science, and Technology
+of Japan. Sampling methods and details about the JACC study have been
+described extensively in the literature
+\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
+study completed self-administered questionnaires about their lifestyles,
+food intake (food frequency questionnaire, FFQ), and medical histories
+of cardiovascular disease or cancer. In the final follow-up of the JACC
+study, data from a total of 110585 individuals (46395 men and 64190
+women) were successfully retained for the current analysis. We further
+excluded samples if they meet one of the following criteria: 1) with any
+disease history of stroke, cancer, myocardial infarction, ischemic heart
+disease, or other types heart disease (n = 6655, 2931 men and 3724
+women); 2) did not answer the question regarding their milk consumption
+in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally,
+94385 (39386 men and 54999 women) are left in the database. The study
+design and informed consent procedure were approved by the Ethics Review
+Committee of Nagoya University School of Medicine.
+
+\hypertarget{exposure-and-the-outcome-of-interest}{%
+\subsection{Exposure and the outcome of
+interest}\label{exposure-and-the-outcome-of-interest}}
+
+Frequency of milk intake during the preceding year of the baseline was
+assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
+``3-4 times/week'', and ``Almost daily''.
+
 \hypertarget{results}{%
@@
 JACC & Japan Collaborative Cohort \\
-DOAJ & Directory of open access journals \\
-TLA & Three letter acronym \\
-LD & linear dichroism \\
+FFQ & Food Frequency Questionnaire \\
 \end{tabular}}

### 2020-06-22 Paperfolder/Paperfolder.Rmd
updated expo and endpoint

@@
 Frequency of milk intake during the preceding year of the baseline was assessed by FFQ from "never", "1-2 times/month", "1-2 times/week", "3-4 times/week", and "Almost daily".
+The exact amount of milk consumption was difficult to assess here.
+However, good reproducibility and validity were confirmed previously (Spearman rank correlation coefficient between milk intake frequency and weighed dietary record for 12 days was 0.65) [@Date2005].
+
+The causes and date of death were obtained from death certificates and were systematically reviewed.
+The follow-up period was defined as from the time of the baseline survey was completed, which was between 1988-1990, until the end of 2009 (administrative censor), or the date when move-out of study area, or the date of death from stroke recorded, whichever occurred first.
+Other causes of death were treated as censored and assumed not informative.
+The causes of death were coded by the 10th Revision of the International Statistical Classification of Diseases and Related Health Problems (ICD-10), therefore stroke was defined as I60-I69.
+We further classified these deaths into hemorrhagic stroke (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke in their death certificate were available.
+
+## Statistical approach
 

### 2020-06-22 Paperfolder/Paperfolder.tex
updated expo and endpoint

@@
 assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
-``3-4 times/week'', and ``Almost daily''.
+``3-4 times/week'', and ``Almost daily''. The exact amount of milk
+consumption was difficult to assess here. However, good reproducibility
+and validity were confirmed previously (Spearman rank correlation
+coefficient between milk intake frequency and weighed dietary record for
+12 days was 0.65) \citep{Date2005}.
+
+The causes and date of death were obtained from death certificates and
+were systematically reviewed. The follow-up period was defined as from
+the time of the baseline survey was completed, which was between
+1988-1990, until the end of 2009 (administrative censor), or the date
+when move-out of study area, or the date of death from stroke recorded,
+whichever occurred first. Other causes of death were treated as censored
+and assumed not informative. The causes of death were coded by the 10th
+Revision of the International Statistical Classification of Diseases and
+Related Health Problems (ICD-10), therefore stroke was defined as
+I60-I69. We further classified these deaths into hemorrhagic stroke
+(I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke
+in their death certificate were available.
+
+\hypertarget{statistical-approach}{%
+\subsection{Statistical approach}\label{statistical-approach}}
 

### 2020-06-23 AnalysisScript/ModelsJAGSmen.R
update MCSE values

@@ -101,6 +101,61 @@ M0men_20200520 <- jagsfit
 print(M0men_20200520)
 save.image(file = "data/JACCmilkstroke.Rdata")
 
+# 
+# Iterations = 1:97389
+# Thinning interval = 97 
+# Number of chains = 3 
+# Sample size per chain = 1005 
+# 
+# 1. Empirical mean and standard deviation for each variable,
+# plus standard error of the mean:
+#   
+#                Mean       SD  Naive SE Time-series SE
+# AFT[2]    9.276e-01  0.06579 0.0011982      0.0015899
+# AFT[3]    8.345e-01  0.05350 0.0009744      0.0014405
+# AFT[4]    8.491e-01  0.05445 0.0009917      0.0015845
+# AFT[5]    9.312e-01  0.04423 0.0008056      0.0012693
+# HR[2]     8.981e-01  0.09250 0.0016846      0.0022461
+# HR[3]     7.701e-01  0.07135 0.0012995      0.0019555
+# HR[4]     7.898e-01  0.07320 0.0013331      0.0021559
+# HR[5]     9.024e-01  0.06216 0.0011320      0.0017923
+# beta[1]   5.050e+00  0.06238 0.0011361      0.0034163
+# beta[2]   7.768e-02  0.07096 0.0012923      0.0017130
+# beta[3]   1.830e-01  0.06429 0.0011708      0.0016984
+# beta[4]   1.656e-01  0.06412 0.0011678      0.0018635
+# beta[5]   7.237e-02  0.04749 0.0008649      0.0013610
+# deviance  1.649e+04 72.89115 1.3274896      1.5329732
+# p.crit[2] 8.650e-01  0.34177 0.0062243      0.0068845
+# p.crit[3] 9.990e-01  0.03153 0.0005743      0.0005743
+# p.crit[4] 9.970e-01  0.05456 0.0009937      0.0011170
+# p.crit[5] 9.347e-01  0.24717 0.0045014      0.0058620
+# shape     1.453e+00  0.03510 0.0006393      0.0017323
+# 
+# 2. Quantiles for each variable:
+#   
+#                2.5%       25%       50%       75%     97.5%
+# AFT[2]     8.055e-01 8.817e-01 9.264e-01 9.706e-01 1.060e+00
[…]

### 2020-06-23 AnalysisScript/ModelsJAGSmenHemoStroke.R

@@ -81,4 +81,4 @@ end.time - start.time
 M0menHemoStroke_20200618 <- jagsfit
 print(M0menHemoStroke_20200618)
 save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
-save.image(file = "data/JACCmilkstroke.Rdata")
+# save.image(file = "data/JACCmilkstroke.Rdata")

### 2020-06-23 AnalysisScript/ModelsJAGSwomen.R

@@ -94,6 +94,59 @@ end.time - start.time #Time difference of 1.316827  days
 M0fem_20200526 <- jagsfit
 # print(JACC.weibull.fit)
 print(M0fem_20200526)
+
+# Iterations = 1:97389
+# Thinning interval = 97 
+# Number of chains = 3 
+# Sample size per chain = 1005 
+# 
+# 1. Empirical mean and standard deviation for each variable,
+# plus standard error of the mean:
+#   
+#                 Mean       SD  Naive SE Time-series SE
+# AFT[2]    8.836e-01  0.07026 0.0012796      0.0020350
+# AFT[3]    8.745e-01  0.05170 0.0009415      0.0015690
+# AFT[4]    7.992e-01  0.04946 0.0009008      0.0014763
+# AFT[5]    8.768e-01  0.04086 0.0007441      0.0015660
+# HR[2]     8.254e-01  0.10270 0.0018703      0.0029814
+# HR[3]     8.112e-01  0.07506 0.0013669      0.0021884
+# HR[4]     7.043e-01  0.06838 0.0012454      0.0020613
+# HR[5]     8.141e-01  0.05905 0.0010754      0.0022800
+# beta[1]   5.107e+00  0.07359 0.0013402      0.0046900
+# beta[2]   1.269e-01  0.07931 0.0014445      0.0021620
+# beta[3]   1.359e-01  0.05899 0.0010743      0.0017292
+# beta[4]   2.260e-01  0.06168 0.0011233      0.0018344
+# beta[5]   1.326e-01  0.04631 0.0008433      0.0017702
+# deviance  1.708e+04 72.78972 1.3256425      1.4757391
+# p.crit[2] 9.456e-01  0.22683 0.0041311      0.0055478
+# p.crit[3] 9.867e-01  0.11443 0.0020841      0.0025451
+# p.crit[4] 9.993e-01  0.02575 0.0004690      0.0006849
+# p.crit[5] 9.957e-01  0.06553 0.0011935      0.0027200
+# shape     1.572e+00  0.04129 0.0007521      0.0026140
+# 
+# 2. Quantiles for each variable:
+#   
+#   2.5%       25%       50%       75%     97.5%
+# AFT[2]     7.539e-01 8.364e-01 8.813e-01 9.286e-01 1.029e+00
[…]

### 2020-06-23 Paperfolder/Paperfolder.Rmd
Updated method 40%

@@
     long: Food Frequency Questionnaire
+  - short: MCMC
+    long: Markov Chain Monte Carlo
+  - short: JAGS
+    long: Just Another Gibbs Samplers
 output: rticles::mdpi_article
@@
 The causes of death were coded by the 10th Revision of the International Statistical Classification of Diseases and Related Health Problems (ICD-10), therefore stroke was defined as I60-I69.
-We further classified these deaths into hemorrhagic stroke (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke in their death certificate were available.
+We further classified these deaths into hemorrhagic stroke (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke in their death certificates were available.
 
 ## Statistical approach
+
+We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
+Overall difference across the milk intake groups were tested by either analysis of variance for continuous variables or $\chi^2$ test for categorical variables.
+
+Full parametric proportional hazard models under Bayesian framework with Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS) program [@Plummer2003] version 4.3.0 in R version 4.0.1 [@RCT2020].
+JAGS program is similar to the OpenBUGS [@Lunn2009] project that uses a Gibbs sampling engine for Markov Chain Monte Carlo (MCMC) simulation.
+In the current analysis, we specified non-informative prior distributions ($\beta_n \sim N(0, 1000)$, and $\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)$) for each of the parameters in our models.
+The Brooks-Gelman-Rubin diagnostic [@Brooks1998] was used to refine the approximate point of convergence, the point when the ratio of the chains is stable around 1 and the within and between chain variability start to reach stability was visually checked.
+The auto-correlation tool further identified if convergence has been achieved or if a high degree of auto-correlation exists in the sample.
+Then, the number of iterations discarded as ‘burn-in’ was chosen.
+All models had a posterior sample size of 100000 from three separated chains with a "burn-in" of 2500 iterations.
+Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated HR were presented for each category of milk intake frequency taking the "never" category as the reference.
+Posterior probability that the estimated hazard ratio (HR) favors the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.
 

### 2020-06-23 Paperfolder/Paperfolder.tex
Updated method 40%

@@
 (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke
-in their death certificate were available.
+in their death certificates were available.
 
@@
 \subsection{Statistical approach}\label{statistical-approach}}
+
+We calculated sex-specific means (standard deviation, sd) and proportion
+of selected baseline characteristics according to the frequency of milk
+intake. Overall difference across the milk intake groups were tested by
+either analysis of variance for continuous variables or \(\chi^2\) test
+for categorical variables.
+
+Full parametric proportional hazard models under Bayesian framework with
+Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS)
+program \citep{Plummer2003} version 4.3.0 in R version 4.0.1
+\citep{RCT2020}. JAGS program is similar to the OpenBUGS
+\citep{Lunn2009} project that uses a Gibbs sampling engine for Markov
+Chain Monte Carlo (MCMC) simulation. In the current analysis, we
+specified non-informative prior distributions
+(\(\beta_n \sim N(0, 1000)\), and
+\(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)) for each of the
+parameters in our models. The Brooks-Gelman-Rubin diagnostic
+\citep{Brooks1998} was used to refine the approximate point of
+convergence, the point when the ratio of the chains is stable around 1
+and the within and between chain variability start to reach stability
+was visually checked. The auto-correlation tool further identified if
+convergence has been achieved or if a high degree of auto-correlation
+exists in the sample. Then, the number of iterations discarded as
+`burn-in' was chosen. All models had a posterior sample size of 100000
+from three separated chains with a ``burn-in'' of 2500 iterations.
+Posterior means (sd) and 95\% Credible Intervals (CrI) of the estimated
+HR were presented for each category of milk intake frequency taking the
+``never'' category as the reference. Posterior probability that the
+estimated hazard ratio (HR) favors the milk intake for frequency that
+higher or equal to ``1-2 times/month'' is smaller compared with those
+who chose ``never'' to their milk intake frequency were calculated as
+\(P(\text{HR} < 1)\).
 
@@
 FFQ & Food Frequency Questionnaire \\
+MCMC & Markov Chain Monte Carlo \\
+JAGS & Just Another Gibbs Samplers \\
 \end{tabular}}

### 2020-06-23 Paperfolder/presentation.R

@@ -1,4 +1,6 @@
 load("data/JACCmilkstroke.Rdata")
+M0men_20200520
+
 
 summary(coda::as.mcmc(M0men_20200520))
 summary(coda::as.mcmc(M1_agemen_20200520))

### 2020-06-24 Paperfolder/Paperfolder.Rmd
updated method done, table 1done

@@
 JAGS program is similar to the OpenBUGS [@Lunn2009] project that uses a Gibbs sampling engine for Markov Chain Monte Carlo (MCMC) simulation.
-In the current analysis, we specified non-informative prior distributions ($\beta_n \sim N(0, 1000)$, and $\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)$) for each of the parameters in our models.
+In the current analysis, we specified non-informative prior distributions for each of the parameters in our models ($\beta_n \sim N(0, 1000)$, and $\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)$).
 The Brooks-Gelman-Rubin diagnostic [@Brooks1998] was used to refine the approximate point of convergence, the point when the ratio of the chains is stable around 1 and the within and between chain variability start to reach stability was visually checked.
@@
 Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated HR were presented for each category of milk intake frequency taking the "never" category as the reference.
-Posterior probability that the estimated hazard ratio (HR) favors the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.
+Posterior probability that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.
+
+The parametric forms of the models fitted in the Bayesian survival analyses include three models: 1) the crude model, 2) the age-centered adjusted model, 3) and a model further adjusted for potential confounders which includes: age (centered, continuous), smoking habit (never, current, former), alcohol intake (never or past, $<$ 4 times/week, Daily), body mass index ($<$ 18.5, $\geq$ 18.5 and $<$ 25, $\geq$ 25 and $<$ 30, $\geq$ 30 kg/m$^2$), history of hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more than 1 hour/week, yes/no), sleep duration ($<$ 7, $\geq$ 7 and $<$ 8, $\geq$ 8 and $<$ 9, $\geq$ 9, hours), coffee intake (never, $<$ 3-4 times/week, almost daily), education level (attended school till age 18, yes/no)
 
@@
 # Results
+
+```{r tab1f, echo=FALSE, eval=FALSE}
+library(knitr)
+library(kableExtra)
+
+dt <- read.csv("tab/tab1.csv", header = T)
+names(dt) <- c("", "Never", "Drinker", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Daily", "P value")
+
+kable(dt, format = "latex", caption = "Sex-specific baseline characteristics according to the frequency of milk intake.", booktabs = T,linesep = "") %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
+  # add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
+  pack_rows("Men (n = 39386)", 1, 16) %>%
+  pack_rows("Women (n = 545999)", 17, 32) #%>% 
+  # footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
+```
+
+\begin{table}[H]
+\caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake.}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lccccccc}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} & \multicolumn{1}{c}{} \\
+\cmidrule(l{3pt}r{3pt}){4-7}
+ & \textbf{Never} & \textbf{Drinker} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
+ &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  & \textbf{\textit{P} value}\\
+\midrule
+\rowcolor{gray!6}  \addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Men (n = 39386)}}\\
+\hspace{1em}number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865 & \\
+\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1) & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4 & <0.001\\
+\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8) & <0.001\\
+\hspace{1em}Exercise (> 1h/week), \% & 19 & 27.6 & 26.5 & 25 & 25.5 & 29.5 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3 & <0.001\\
+\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1 & <0.001\\
+\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48 & 47.5 & 52.9 & <0.001\\
+\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31 & 36.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.5 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7 & <0.001\\
+\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7 & 0.039\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5 & <0.001\\
+\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2 & <0.001\\
+\rowcolor{gray!6}  \addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Women (n = 545999)}}\\
+\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254 & \\
+\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9) & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5 & <0.001\\
+\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m2 (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6) & <0.001\\
+\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7 & <0.001\\
+\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25 & 24.6 & 24.2 & 34.8 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
+\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2 & <0.001\\
+\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4 & <0.001\\
+\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4 & <0.001\\
+\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0 & <0.001\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-entry 1		& data			& data\\
-entry 2		& data			& data\\
-\bottomrule
-\end{tabular}
-\end{table}
+<!-- \begin{table}[H] -->
+<!-- \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.} -->
+<!-- \centering -->
+<!-- %% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used. -->
+<!-- \begin{tabular}{ccc} -->
+<!-- \toprule -->
+<!-- \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\ -->
+<!-- \midrule -->
+<!-- entry 1		& data			& data\\ -->
+<!-- entry 2		& data			& data\\ -->
+<!-- \bottomrule -->
+<!-- \end{tabular} -->
+<!-- \end{table} -->
 

### 2020-06-24 Paperfolder/Paperfolder.tex
updated method done, table 1done

@@
 Chain Monte Carlo (MCMC) simulation. In the current analysis, we
-specified non-informative prior distributions
-(\(\beta_n \sim N(0, 1000)\), and
-\(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)) for each of the
-parameters in our models. The Brooks-Gelman-Rubin diagnostic
-\citep{Brooks1998} was used to refine the approximate point of
-convergence, the point when the ratio of the chains is stable around 1
-and the within and between chain variability start to reach stability
-was visually checked. The auto-correlation tool further identified if
-convergence has been achieved or if a high degree of auto-correlation
-exists in the sample. Then, the number of iterations discarded as
-`burn-in' was chosen. All models had a posterior sample size of 100000
-from three separated chains with a ``burn-in'' of 2500 iterations.
-Posterior means (sd) and 95\% Credible Intervals (CrI) of the estimated
-HR were presented for each category of milk intake frequency taking the
-``never'' category as the reference. Posterior probability that the
-estimated hazard ratio (HR) favors the milk intake for frequency that
-higher or equal to ``1-2 times/month'' is smaller compared with those
-who chose ``never'' to their milk intake frequency were calculated as
-\(P(\text{HR} < 1)\).
+specified non-informative prior distributions for each of the parameters
+in our models (\(\beta_n \sim N(0, 1000)\), and
+\(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)). The
+Brooks-Gelman-Rubin diagnostic \citep{Brooks1998} was used to refine the
+approximate point of convergence, the point when the ratio of the chains
+is stable around 1 and the within and between chain variability start to
+reach stability was visually checked. The auto-correlation tool further
+identified if convergence has been achieved or if a high degree of
+auto-correlation exists in the sample. Then, the number of iterations
+discarded as `burn-in' was chosen. All models had a posterior sample
+size of 100000 from three separated chains with a ``burn-in'' of 2500
+iterations. Posterior means (sd) and 95\% Credible Intervals (CrI) of
+the estimated HR were presented for each category of milk intake
+frequency taking the ``never'' category as the reference. Posterior
+probability that the estimated hazard of dying from stroke for the milk
+intake for frequency that higher or equal to ``1-2 times/month'' is
+smaller compared with those who chose ``never'' to their milk intake
+frequency were calculated as \(P(\text{HR} < 1)\).
+
+The parametric forms of the models fitted in the Bayesian survival
+analyses include three models: 1) the crude model, 2) the age-centered
+adjusted model, 3) and a model further adjusted for potential
+confounders which includes: age (centered, continuous), smoking habit
+(never, current, former), alcohol intake (never or past, \(<\) 4
+times/week, Daily), body mass index (\(<\) 18.5, \(\geq\) 18.5 and \(<\)
+25, \(\geq\) 25 and \(<\) 30, \(\geq\) 30 kg/m\(^2\)), history of
+hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more
+than 1 hour/week, yes/no), sleep duration (\(<\) 7, \(\geq\) 7 and \(<\)
+8, \(\geq\) 8 and \(<\) 9, \(\geq\) 9, hours), coffee intake (never,
+\(<\) 3-4 times/week, almost daily), education level (attended school
+till age 18, yes/no)
 
@@
 \section{Results}\label{results}}
+
+\begin{table}[H]
+\caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake.}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lccccccc}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} & \multicolumn{1}{c}{} \\
+\cmidrule(l{3pt}r{3pt}){4-7}
+ & \textbf{Never} & \textbf{Drinker} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
+ &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  & \textbf{\textit{P} value}\\
+\midrule
+\rowcolor{gray!6}  \addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Men (n = 39386)}}\\
+\hspace{1em}number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865 & \\
+\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1) & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4 & <0.001\\
+\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8) & <0.001\\
+\hspace{1em}Exercise (> 1h/week), \% & 19 & 27.6 & 26.5 & 25 & 25.5 & 29.5 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3 & <0.001\\
+\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1 & <0.001\\
+\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48 & 47.5 & 52.9 & <0.001\\
+\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31 & 36.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.5 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7 & <0.001\\
+\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7 & 0.039\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5 & <0.001\\
+\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2 & <0.001\\
+\rowcolor{gray!6}  \addlinespace[0.3em]
+\multicolumn{8}{l}{\textbf{Women (n = 545999)}}\\
+\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254 & \\
+\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9) & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5 & <0.001\\
+\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m2 (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6) & <0.001\\
+\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7 & <0.001\\
+\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25 & 24.6 & 24.2 & 34.8 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
+\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2 & <0.001\\
+\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4 & <0.001\\
+\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4 & <0.001\\
+\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0 & <0.001\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \multicolumn{10}{l}{ Probability indicates that the p for HR smaller than 1.}\\
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
-\midrule
-entry 1     & data          & data\\
-entry 2     & data          & data\\
-\bottomrule
 \end{tabular}

### 2020-06-25 Paperfolder/Paperfolder.Rmd
updated table 2 40% men

@@
 
+The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women).
+Among these stroke mortality, 957 were cerebral infarction (520 men and 437 women), and 952 were hemorrhagic stroke (432 men and 520 women).
+
+As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at the baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
+Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.
+
+Table
+
 ```{r tab1f, echo=FALSE, eval=FALSE}
@@
 dt <- read.csv("tab/tab1.csv", header = T)
-names(dt) <- c("", "Never", "Drinker", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Daily", "P value")
+names(dt) <- c("", "Never", "Drinker", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily", "P value")
 
@@
 \rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 19 & 27.6 & 26.5 & 25 & 25.5 & 29.5 & <0.001\\
+\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5 & <0.001\\
 \rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3 & <0.001\\
@@
 \hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48 & 47.5 & 52.9 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31 & 36.6 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9 & <0.001\\
+\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6 & <0.001\\
 \rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.5 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7 & <0.001\\
@@
 \rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25 & 24.6 & 24.2 & 34.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
+\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8 & <0.001\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
 \hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3 & <0.001\\
 \rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34 & <0.001\\
+\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0 & <0.001\\
 \rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4 & <0.001\\
-\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20 & <0.001\\
+\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0 & <0.001\\
 \rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4 & <0.001\\
@@
 
-## Subsection Heading Here
+<!-- ## Subsection Heading Here -->
 
@@
 
-### Subsubsection Heading Here
+<!-- ### Subsubsection Heading Here -->
 
@@
 
-```{r tab1, echo=FALSE, eval=TRUE, message=FALSE}
+```{r tab2, echo=FALSE, eval=TRUE, message=FALSE}
 library(knitr)
@@
 dt <- read.csv("tab/HRAFTweib.csv", header = T)
-names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
-kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
+# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
+names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
+
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.", booktabs = T, linesep = "") %>%
+    # collapse_rows(columns = 1, valign = "top") %>% 
+  pack_rows("Model 0", 4, 7) %>%
+  pack_rows("Model 1", 8, 11) %>%
+  pack_rows("Model 2", 12, 15) %>%
 kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
-  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
+  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))
+
 ```

### 2020-06-25 Paperfolder/Paperfolder.tex
updated table 2 40% men

@@
 
+The total follow-up was 1555073 person-years (median = 19.3 years),
+during which 2675 death from stroke was confirmed (1352 men and 1323
+women). Among these stroke mortality, 957 were cerebral infarction (520
+men and 437 women), and 952 were hemorrhagic stroke (432 men and 520
+women).
+
+As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
+chose ``never'' as their milk intake frequency at the baseline, milk
+drinkers were less likely to be a current smoker or a daily alcohol
+consumer in both men and women. Furthermore, people consumed milk more
+than 1-2 times/month were more likely to be a daily consumers of
+vegetable, fruit as well as coffee, and more likely to join exercise
+more than 1 hour/week among either sex.
+
+Table
+
 \begin{table}[H]
@@
 
-\hypertarget{subsection-heading-here}{%
-\subsection{Subsection Heading Here}\label{subsection-heading-here}}
-
-\hypertarget{subsubsection-heading-here}{%
-\subsubsection{Subsubsection Heading
-Here}\label{subsubsection-heading-here}}
-
 \begin{table}[!h]
 
-\caption{\label{tab:tab1}}
+\caption{\label{tab:tab2}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.}
 \centering
 \fontsize{8}{10}\selectfont
-\begin{tabular}[t]{llllllllll}
+\begin{tabular}[t]{llllll}
 \toprule
-\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
-\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
-Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
+  & Never & 1-2 times/Month & 1-2 times/Week & 3-4 times/Week & Almost Daily\\
 \midrule
-\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & \vphantom{2} -\\
-1-2 t/Mon & 0.88 & 0.89 (0.09) & (0.73, 1.08) & 0.0022 & 86.50\% & 0.93 & 0.93 (0.06) & (0.81, 1.06) & 0.0016\\
-\rowcolor{gray!6}  1-2 t/Week & 0.77 & 0.77 (0.07) & (0.63, 0.91) & 0.0019 & 99.90\% & 0.83 & 0.83 (0.05) & (0.73, 0.94) & 0.0014\\
-3-4 t/Week & 0.79 & 0.79 (0.07) & (0.66, 0.94) & 0.0022 & 99.70\% & 0.85 & 0.85 (0.05) & (0.74, 0.96) & 0.0016\\
-\rowcolor{gray!6}  Daily & 0.90 & 0.90 (0.06) & (0.79, 1.03) & 0.0018 & 93.47\% & 0.93 & 0.93 (0.04) & (0.85, 1.02) & 0.0013\\
-Never & - & - & - & - & - & - & - & - & \vphantom{1} -\\
-\rowcolor{gray!6}  1-2 t/Mon & 0.98 & 0.98 (0.11) & (0.79, 1.19) & 0.0027 & 58.70\% & 0.99 & 0.99 (0.06) & (0.87, 1.11) & 0.0016\\
-1-2 t/Week & 0.84 & 0.84 (0.08) & (0.70, 1.00) & 0.0022 & 97.31\% & 0.90 & 0.90 (0.05) & (0.81, 1.00) & 0.0014\\
-\rowcolor{gray!6}  3-4 t/Week & 0.85 & 0.86 (0.08) & (0.71, 1.02) & 0.0021 & 96.05\% & 0.91 & 0.91 (0.05) & (0.82, 1.01) & 0.0013\\
-Daily & 0.75 & 0.76 (0.05) & (0.66, 0.87) & 0.0016 & 100.00\% & 0.85 & 0.85 (0.04) & (0.78, 0.92) & 0.0011\\
-\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
-1-2 t/Mon & 1.00 & 1.01 (0.12) & (0.81, 1.24) & 0.0041 & 50.61\% & 1.00 & 1.00 (0.07) & (0.88, 1.14) & 0.0029\\
-\rowcolor{gray!6}  1-2 t/Week & 0.86 & 0.87 (0.09) & (0.72, 1.05) & 0.0036 & 93.73\% & 0.92 & 0.92 (0.06) & (0.82, 1.03) & 0.0024\\
-3-4 t/Week & 0.89 & 0.90 (0.09) & (0.74, 1.08) & 0.0038 & 89.62\% & 0.93 & 0.94 (0.06) & (0.84, 1.05) & 0.0026\\
-\rowcolor{gray!6}  Daily & 0.80 & 0.80 (0.07) & (0.69, 0.93) & 0.0031 & 99.04\% & 0.88 & 0.88 (0.05) & (0.81, 0.96) & 0.0020\\
+\rowcolor{gray!6}  Person-year & 135704 & 56551 & 97098 & 92153 & 252364\\
+N & 8508 & 3522 & 5928 & 5563 & 15865\\
+\rowcolor{gray!6}  Total Stroke & 326 & 122 & 181 & 177 & 546\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}MeanHR (SD) & - & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
+\hspace{1em}MCSE & - & 0.0022 & 0.0019 & 0.0022 & 0.0018\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.47\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\hspace{1em}MeanHR (SD) & - & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
+\hspace{1em}MCSE & - & 0.0027 & 0.0022 & 0.0021 & 0.0016\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.31\% & 96.05\% & 100.00\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}MeanHR (SD) & - & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
+\hspace{1em}MCSE & - & 0.0041 & 0.0036 & 0.0038 & 0.0031\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.61\% & 93.73\% & 89.62\% & 99.04\%\\
 \bottomrule
-\multicolumn{10}{l}{\textit{Note: }}\\
-\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
-\multicolumn{10}{l}{ Probability indicates that the p for HR smaller than 1.}\\
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{6}{l}{Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
 \end{tabular}

### 2020-06-28 AnalysisScript/ModelsJAGSmenHemoStroke.R
updated hemo M0

@@ -82,3 +82,31 @@ M0menHemoStroke_20200618 <- jagsfit
 print(M0menHemoStroke_20200618)
 save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # save.image(file = "data/JACCmilkstroke.Rdata")
+
+
+
+
+# Inference for Bugs model at "M2.weibull.model", fit using jags,
+# 3 chains, each with 1e+05 iterations (first 250 discarded), n.thin = 99
+# n.sims = 3021 iterations saved
+# mu.vect sd.vect      2.5%       25%       50%       75%     97.5%  Rhat n.eff
+# AFT[2]        1.006   0.124     0.847     0.942     0.995     1.053     1.203 1.009  1100
+# AFT[3]        1.114   0.142     0.977     1.053     1.098     1.148     1.295 1.016   710
+# AFT[4]        1.022   0.119     0.886     0.969     1.010     1.056     1.186 1.014  2900
+# AFT[5]        0.972   0.097     0.877     0.934     0.963     0.994     1.104 1.015  1700
+# HR[2]         1.010   0.168     0.752     0.903     0.992     1.092     1.357 1.004   660
+# HR[3]         1.194   0.170     0.960     1.093     1.175     1.268     1.517 1.007   380
+# HR[4]         1.033   0.150     0.813     0.947     1.018     1.097     1.314 1.004  1400
+# HR[5]         0.950   0.117     0.798     0.889     0.938     0.990     1.175 1.006   610
+# p.crit[2]     0.528   0.499     0.000     0.000     1.000     1.000     1.000 1.003   690
+# p.crit[3]     0.064   0.245     0.000     0.000     0.000     0.000     1.000 1.007  1100
+# p.crit[4]     0.444   0.497     0.000     0.000     0.000     1.000     1.000 1.003   920
+# p.crit[5]     0.781   0.414     0.000     1.000     1.000     1.000     1.000 1.002  1000
+# deviance  11949.549 126.233 11809.943 11893.025 11934.989 11981.600 12112.061 1.005  1800
+# 
+# For each parameter, n.eff is a crude measure of effective sample size,
+# and Rhat is the potential scale reduction factor (at convergence, Rhat=1).
+# 
+# DIC info (using the rule, pD = var(deviance)/2)
+# pD = 7964.3 and DIC = 19913.8
+# DIC is an estimate of expected predictive error (lower deviance is better).

### 2020-06-28 AnalysisScript/Stan_brms.R

@@ -1,0 +1,76 @@
+############################################################
+#                                                          #
+#              Example from the brms package               #
+#                                                          #
+############################################################
+
+library(brms)
+data("kidney")
+fit1 <- brm(time | cens(censored) ~ age + sex + disease, 
+            data = kidney, family = weibull, inits = "0")
+summary(fit1) 
+plot(fit1)
+
+# ## adding random intercepts over patients
+# fit2 <- brm(time | cens(censored) ~ age + sex + disease + (1|patient), 
+#             data = kidney, family = weibull(), inits = "0",
+#             prior = set_prior("cauchy(0,2)", class = "sd"))
+# summary(fit2) 
+# plot(fit2)         
+
+############################################################
+#                                                          #
+#              do the crude model using brms               #
+#                                                          #
+############################################################
+
+load("data/JACCmilkstroke.Rdata")
+
+# define exposure
+Mlkfre <- MData_men$Mlkfre 
+table(Mlkfre)
+
+# define event
+is.censored <- as.integer(MData_men$Tot_Stroke == "I60_9")
+
+# define time of followup
+t <- MData_men$followpy
+
+CrudeData <- data.frame(t, is.censored, Mlkfre)
+# fit a crude weibull model
+M0 <- brm(t | cens(is.censored) ~ Mlkfre, 
+            data = CrudeData, family = weibull, inits = "0",
+          cores = parallel::detectCores()-1)
+summary(M0) 
+plot(M0)
+
+stancode(M0)
+M0data <- standata(M0)
+
+library(rstan)
+M0_0 <- stan(file = "AnalysisScript/M0StanMen.stan", 
+             data = M0data, 
+             seed = 1234, 
+             pars = c("HR", "AFT", "b", "shape"), 
+             options(mc.cores = 8), 
+             chains = 4, 
+             iter = 10000)
+
+
+############################################################
+#                                                          #
+#               Fit the age adjusted model                 #
+#                                                          #
+############################################################
+
+
+Age <- MData_men$Age
+
+AgeData <- data.frame(t, is.censored, Mlkfre, Age)
+
+
+M1 <- brm(t | cens(is.censored) ~ Mlkfre + Age, 
+          data = AgeData, family = weibull, inits = "0",
+          cores = parallel::detectCores()-1)
+summary(M1) 
+plot(M1)

### 2020-06-29 Paperfolder/Paperfolder.Rmd
updated tables structures

@@
 \begin{table}[H]
-\caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake.}
+\caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake (JACC study, 1988-2009).}
 \centering
@@
 
-kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.", booktabs = T, linesep = "") %>%
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "") %>%
     # collapse_rows(columns = 1, valign = "top") %>% 
@@
   pack_rows("Model 2", 12, 15) %>%
+    pack_rows("Model 0", 17, 20) %>%
+  pack_rows("Model 1", 21, 24) %>%
+  pack_rows("Model 2", 25, 28) %>%
+  pack_rows("Model 0", 30, 33) %>%
+  pack_rows("Model 1", 34, 37) %>%
+  pack_rows("Model 2", 38, 41) %>%
 kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
   # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
+```
 
+```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
+dt <- read.csv("tab/HRAFTweibF.csv", header = T)
+# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
+names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
+
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "") %>%
+    # collapse_rows(columns = 1, valign = "top") %>% 
+  pack_rows("Model 0", 4, 7) %>%
+  pack_rows("Model 1", 8, 11) %>%
+  pack_rows("Model 2", 12, 15) %>%
+  pack_rows("Model 0", 17, 20) %>%
+  pack_rows("Model 1", 21, 24) %>%
+  pack_rows("Model 2", 25, 28) %>%
+  pack_rows("Model 0", 30, 33) %>%
+  pack_rows("Model 1", 34, 37) %>%
+  pack_rows("Model 2", 38, 41) %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
 ```

### 2020-06-29 Paperfolder/Paperfolder.tex
updated tables structures

@@
 
-\caption{\label{tab:tab2}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.}
+\caption{\label{tab:tab2}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).}
 \centering
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}MeanHR (SD) & - & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
+\hspace{1em}MeanHR (SD) & 1 & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
@@
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & - & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
+\hspace{1em}MeanHR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
@@
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}MeanHR (SD) & - & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
+\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
@@
 \rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.61\% & 93.73\% & 89.62\% & 99.04\%\\
+Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.01 (0.08) &  &  & \\
+\hspace{1em}95\% CrI &  & (0.75, 1.04) &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{5} & \\
+\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{5} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{4} & \\
+\hspace{1em}95\% CrI &  &  &  &  \vphantom{4} & \\
+\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{4} & \\
+\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{4} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{3} & \\
+\hspace{1em}95\% CrI &  &  &  &  \vphantom{3} & \\
+\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{3} & \\
+\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{3} & \\
+\rowcolor{gray!6}  Cerebral infarction & 151 & 41 & 64 & 66 & 198\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{2} & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  \vphantom{2} & \\
+\hspace{1em}MCSE &  &  &  &  \vphantom{2} & \\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{2} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  \vphantom{1} & \\
+\hspace{1em}MCSE &  &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{1} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}MeanHR (SD) & 1 &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  & \\
+\hspace{1em}MCSE &  &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  & \\
 \bottomrule
@@
 \multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
-\multicolumn{6}{l}{Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
+\multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
+\multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
+\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
+\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:tab3}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllll}
+\toprule
+  & Never & 1-2 times/Month & 1-2 times/Week & 3-4 times/Week & Almost Daily\\
+\midrule
+\rowcolor{gray!6}  Person-year & 173222 & 59904 & 129233 & 139919 & 418925\\
+N & 10407 & 3640 & 7590 & 8108 & 25254\\
+\rowcolor{gray!6}  Total Stroke & 300 & 84 & 182 & 172 & 585\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}MeanHR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.05) & (0.68, 0.97) & (0.58, 0.85) & (0.71, 0.93)\\
+\hspace{1em}MCSE & - & 0.0029 & 0.0022 & 0.0021 & 0.0023\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\hspace{1em}MeanHR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
+\hspace{1em}MCSE & - & 0.0038 & 0.0045 & 0.0042 & 0.0034\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.3\% & 6.3\% & 42.0\% & 86.8\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.36) & (0.96, 1.52) & (0.81, 1.31) & (0.80, 1.17)\\
+\hspace{1em}MCSE & - & 0.0083 & 0.0096 & 0.0079 & 0.0075\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
+Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{5} & \\
+\hspace{1em}95\% CrI & - &  &  &  \vphantom{5} & \\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{5} & \\
+\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{5} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{4} & \\
+\hspace{1em}95\% CrI & - &  &  &  \vphantom{4} & \\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{4} & \\
+\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{4} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{3} & \\
+\hspace{1em}95\% CrI & - &  &  &  \vphantom{3} & \\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{3} & \\
+\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{3} & \\
+\rowcolor{gray!6}  Cerebral infarction & 102 & 35 & 63 & 50 & 187\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{2} & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
+\hspace{1em}MCSE & - &  &  &  \vphantom{2} & \\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{2} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
+\hspace{1em}MCSE & - &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{1} & \\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}MeanHR (SD) & 1 &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
+\hspace{1em}MCSE & - &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  & \\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
+\multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
+\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
+\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
 \end{tabular}

### 2020-06-29 Paperfolder/Paperfolder.Rmd
updated tables done

--- 2020-06-25 Paperfolder/Paperfolder.Rmd
@@
   pack_rows("Model 2", 12, 15) %>%
+    row_spec(15,  hline_after = TRUE) %>%
+    pack_rows("Model 0", 17, 20) %>%
+  pack_rows("Model 1", 21, 24) %>%
+  pack_rows("Model 2", 25, 28) %>%
+      row_spec(28,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 30, 33) %>%
+  pack_rows("Model 1", 34, 37) %>%
+  pack_rows("Model 2", 38, 41) %>%
 kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
   # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
+```
 
+```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
+dt <- read.csv("tab/HRAFTweibF.csv", header = T)
+# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
+names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
+
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "") %>%
+    # collapse_rows(columns = 1, valign = "top") %>% 
+  pack_rows("Model 0", 4, 7) %>%
+  pack_rows("Model 1", 8, 11) %>%
+  pack_rows("Model 2", 12, 15) %>%
+  row_spec(15,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 17, 20) %>%
+  pack_rows("Model 1", 21, 24) %>%
+  pack_rows("Model 2", 25, 28) %>%
+  row_spec(28,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 30, 33) %>%
+  pack_rows("Model 1", 34, 37) %>%
+  pack_rows("Model 2", 38, 41) %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
 ```

### 2020-06-30 AnalysisScript/ModelsJAGSmenHemoStroke.R
updated H0hemomen updated correctly

@@ -15,7 +15,7 @@ table(Mlkfre)
 table(MData_men$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
 
 # define events 
-is.censored <- MData_men$HemoStroke == "I60_2"
+is.censored <- MData_men$HemoStroke != "I60_2"
 
 # define followup time for events
 t <- if_else(!is.censored, MData_men$followpy, 0)
@@ -31,7 +31,7 @@ c[!is.censored] <- t[!is.censored] + 1
 
 
 
-jacc.weibull.model0 <- function() {
+jacchemo.weibull.model0 <- function() {
   for(i in 1:39386){
     is.censored[i] ~ dinterval(t[i], c[i])
     t[i] ~ dweib(shape, lambda[i])
@@ -73,23 +73,74 @@ library(R2jags)
 
 
 start.time <- Sys.time()
-jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = larynx.params, 
-                         n.iter=100000, n.burnin=(5000/2), n.chains = 3, #n.thin = 100,
-                         model.file=jacc.weibull.model0)
+jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = m0.params, 
+                         n.iter=100000, n.burnin=(5000/2), n.chains = 4, #n.thin = 100,
+                         model.file=jacchemo.weibull.model0)
 end.time <- Sys.time()
-end.time - start.time 
-M0menHemoStroke_20200618 <- jagsfit
-print(M0menHemoStroke_20200618)
+end.time - start.time #Time difference of 9.715389 hours
+M0menHemoStroke_20200629 <- jagsfit
+print(M0menHemoStroke_20200629)
+summary(mcmcplots::as.mcmc.rjags(M0menHemoStroke_20200629))
 save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # save.image(file = "data/JACCmilkstroke.Rdata")
 
 
-
+# Iterations = 1:97389
+# Thinning interval = 97 
+# Number of chains = 4 
+# Sample size per chain = 1005 
+# 
+# 1. Empirical mean and standard deviation for each variable,
+# plus standard error of the mean:
+#   
+#                 Mean       SD Naive SE Time-series SE
+# AFT[2]       1.02769  0.16489 0.002601       0.005675
+# AFT[3]       0.85116  0.12375 0.001952       0.004883
[…]

### 2020-06-30 AnalysisScript/ModelsJAGSmenHemoStroke.R
updated table 2 men 50%

@@ -137,30 +137,7 @@ save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # p.crit[5]    0.0000    0.00000    1.00000 1.000e+00    1.0000
 # shape        1.0653    1.15227    1.18998 1.229e+00    1.3038
 
-# Inference for Bugs model at "M2.weibull.model", fit using jags,
-# 3 chains, each with 1e+05 iterations (first 250 discarded), n.thin = 99
-# n.sims = 3021 iterations saved
-#             mu.vect sd.vect      2.5%       25%       50%       75%     97.5%  Rhat n.eff
-# AFT[2]        1.006   0.124     0.847     0.942     0.995     1.053     1.203 1.009  1100
-# AFT[3]        1.114   0.142     0.977     1.053     1.098     1.148     1.295 1.016   710
-# AFT[4]        1.022   0.119     0.886     0.969     1.010     1.056     1.186 1.014  2900
-# AFT[5]        0.972   0.097     0.877     0.934     0.963     0.994     1.104 1.015  1700
-# HR[2]         1.010   0.168     0.752     0.903     0.992     1.092     1.357 1.004   660
-# HR[3]         1.194   0.170     0.960     1.093     1.175     1.268     1.517 1.007   380
-# HR[4]         1.033   0.150     0.813     0.947     1.018     1.097     1.314 1.004  1400
-# HR[5]         0.950   0.117     0.798     0.889     0.938     0.990     1.175 1.006   610
-# p.crit[2]     0.528   0.499     0.000     0.000     1.000     1.000     1.000 1.003   690
-# p.crit[3]     0.064   0.245     0.000     0.000     0.000     0.000     1.000 1.007  1100
-# p.crit[4]     0.444   0.497     0.000     0.000     0.000     1.000     1.000 1.003   920
-# p.crit[5]     0.781   0.414     0.000     1.000     1.000     1.000     1.000 1.002  1000
-# deviance  11949.549 126.233 11809.943 11893.025 11934.989 11981.600 12112.061 1.005  1800
-# 
-# For each parameter, n.eff is a crude measure of effective sample size,
-# and Rhat is the potential scale reduction factor (at convergence, Rhat=1).
-# 
-# DIC info (using the rule, pD = var(deviance)/2)
-# pD = 7964.3 and DIC = 19913.8
-# DIC is an estimate of expected predictive error (lower deviance is better).
+
 
 
 

### 2020-07-01 AnalysisScript/ModelsJAGSmenHemoStroke.R
updated age hemo model men

@@ -84,6 +84,36 @@ summary(mcmcplots::as.mcmc.rjags(M0menHemoStroke_20200629))
 save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # save.image(file = "data/JACCmilkstroke.Rdata")
 
+# Inference for Bugs model at "jacchemo.weibull.model0", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       1.028   0.165    0.735    0.914    1.012    1.129    1.378 1.004   790
+# AFT[3]       0.851   0.124    0.632    0.764    0.843    0.929    1.116 1.010   260
+# AFT[4]       0.865   0.126    0.645    0.778    0.856    0.942    1.140 1.004   710
+# AFT[5]       0.975   0.110    0.784    0.899    0.963    1.042    1.223 1.008   330
+# HR[2]        1.034   0.196    0.697    0.899    1.015    1.154    1.460 1.004   770
+# HR[3]        0.827   0.143    0.579    0.726    0.815    0.915    1.135 1.009   290
+# HR[4]        0.843   0.146    0.597    0.741    0.830    0.931    1.168 1.004   790
+# HR[5]        0.970   0.129    0.748    0.882    0.956    1.050    1.259 1.008   340
+# beta[1]      6.545   0.229    6.165    6.392    6.531    6.661    7.030 1.021   360
+# beta[2]     -0.015   0.159   -0.320   -0.121   -0.012    0.090    0.308 1.004   790
+# beta[3]      0.172   0.145   -0.110    0.074    0.171    0.269    0.459 1.010   260
+# beta[4]      0.155   0.144   -0.131    0.060    0.155    0.250    0.439 1.004   710
+# beta[5]      0.032   0.111   -0.201   -0.041    0.037    0.106    0.244 1.008   330
+# p.crit[2]    0.472   0.499    0.000    0.000    0.000    1.000    1.000 1.002  1300
+# p.crit[3]    0.884   0.320    0.000    1.000    1.000    1.000    1.000 1.006   900
+# p.crit[4]    0.863   0.344    0.000    1.000    1.000    1.000    1.000 1.004  1200
[…]

### 2020-07-01 AnalysisScript/ModelsJAGSmenHemoStroke.R
script M2 hemo men added

@@ -226,7 +226,7 @@ jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = age.params,
                          n.iter=100000, n.burnin=(5000/2), n.chains = 4,
                          model.file=Agehemo.weibull.model)
 end.time <- Sys.time()
-end.time - start.time
+end.time - start.time #Time difference of 13.87173 hours
 
 M1menHemoStroke_20200630 <- jagsfit
 print(M1menHemoStroke_20200630)
@@ -290,3 +290,156 @@ save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # p.crit[3]    0.0000    1.0000    1.0000    1.0000    1.000
 # p.crit[4]    0.0000    1.0000    1.0000    1.0000    1.000
 # p.crit[5]    0.0000    1.0000    1.0000    1.0000    1.000
+
+
+
+#######################Model 2 Mult-ad######################
+#                                                          #
+#                      Model 2 Mult-ad                     #
+#                                                          #
+#**********************************************************#
+
+
+
+Smoking <- as.numeric(MData_men$Smoking)
+table(Smoking)
+table(MData_men$Smoking) #1 = Never ; 2 = Past ; 3 = Current ; 4 = unknown 
+
+Alc_Fre <- as.numeric(MData_men$Alc_Fre)
+table(Alc_Fre)
+table(MData_men$Alc_Fre) #1 = < 1/week ; 2 = 1-4 /week ; 3 = Daily ; 4 = Never or past; 5 = unknown
+
+BMI <- as.numeric(MData_men$BMI)
+BMIgrp <- as.numeric(MData_men$BMIgrp)
+table(BMIgrp)
+table(MData_men$BMIgrp) #1 = [18.5,25) ; 2 = [14,18.5) ; 3 = [25,30) ; 4 = [30,40); 5 = unknown
+
+DM_hist <- as.numeric(as.factor(MData_men$DM_hist))
+table(DM_hist)
+table(MData_men$DM_hist) #1 =  FALSE ; 2 = TRUE ; 3 = unknown
+
[…]

### 2020-07-02 AnalysisScript/ModelsJAGSmenCerebralInfar.R
updated M1-M3 ischemic Men models script

@@ -1,0 +1,309 @@
+# HemoStroke == "I63"
+
+library(tidyverse)
+load("data/JACCmilkstrokewithHemo.Rdata")
+#######################Model 0 crude#######################
+#                                                          #
+#                      Model 0 crude                       #
+#                                                          #
+#**********************************************************#
+
+
+# Define exposure
+Mlkfre <- as.numeric(MData_men$Mlkfre)
+table(Mlkfre)
+table(MData_men$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
+
+# define events 
+is.censored <- MData_men$HemoStroke != "I63"
+
+# define followup time for events
+t <- if_else(!is.censored, MData_men$followpy, 0)
+t <- na_if(t, 0)
+t
+
+
+# define followup time for censored 
+c <- if_else(is.censored, MData_men$followpy, 0)
+
+c[!is.censored] <- t[!is.censored] + 1
+
+
+
+
+jaccIschemic.weibull.model0 <- function() {
+  for(i in 1:39386){
+    is.censored[i] ~ dinterval(t[i], c[i])
+    t[i] ~ dweib(shape, lambda[i])
+    lambda[i] <- exp(-mu[i] * shape)
+    mu[i] <- beta[1] + beta[2]*equals(Mlkfre[i], 2) +
+      beta[3]*equals(Mlkfre[i], 3) + beta[4] * equals(Mlkfre[i], 4) +
+      beta[5] * equals(Mlkfre[i], 5) 
+  }
+  
+  ## priors for betas
+  for(j in 1:5){
+    beta[j] ~ dnorm(0, 0.001)
+  }
+  
+  ### prior for shape
+  shape ~ dgamma(.001, .001)
+  
+  ### Generated values
+  AFT[2] <- exp(-beta[2])
+  HR[2] <- exp(-shape * beta[2])
+  p.crit[2] <- step(1 - HR[2])
+  
+  AFT[3] <- exp(-beta[3])
+  HR[3] <- exp(-shape * beta[3])
+  p.crit[3] <- step(1 - HR[3])
+  
+  AFT[4] <- exp(-beta[4])
+  HR[4] <- exp(-shape * beta[4])
[…]

### 2020-07-03 AnalysisScript/ModelsJAGSmenCerebralInfar.R
updated ischemic stroke men scripts

@@ -15,7 +15,7 @@ table(Mlkfre)
 table(MData_men$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
 
 # define events 
-is.censored <- MData_men$HemoStroke != "I63"
+is.censored <- MData_men$IscheStroke != "I63"
 
 # define followup time for events
 t <- if_else(!is.censored, MData_men$followpy, 0)
@@ -223,7 +223,7 @@ table(MData_men$Gretea) #1 =  daily   ; 2 = Thre3tw  ; 3 = Never ; 4 = unknown
 
 
 
-M2hemo.weibull.model <- function() {
+M2Isch.weibull.model <- function() {
   for(i in 1:39386){
     sAge[i] <- (Age[i] - mean(Age[])) / sd(Age[])
     # sBMI[i] <- (BMI[i] - mean(BMI[])) / sd(BMI[])
@@ -295,7 +295,7 @@ M2.params <- c("AFT", "HR", "p.crit")
 start.time <- Sys.time()
 jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = M2.params, 
                          n.iter=100000, n.burnin=(3000/2), n.chains = 4,
-                         model.file=M2hemo.weibull.model)
+                         model.file=M2Isch.weibull.model)
 end.time <- Sys.time()
 end.time - start.time 
 

### 2020-07-03 AnalysisScript/ModelsJAGSmenHemoStroke.R
updated hemo full model stroke in men

@@ -443,3 +443,70 @@ M1menHemoStroke_20200701 <- jagsfit
 print(M1menHemoStroke_20200701)
 summary(mcmcplots::as.mcmc.rjags(M1menHemoStroke_20200701))
 save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
+
+
+# Iterations = 1:98393
+# Thinning interval = 98 
+# Number of chains = 4 
+# Sample size per chain = 1005 
+# 
+# 1. Empirical mean and standard deviation for each variable,
+# plus standard error of the mean:
+#   
+#   Mean      SD Naive SE Time-series SE
+# AFT[2]       1.1111  0.1985 0.003130       0.010852
+# AFT[3]       0.9333  0.1467 0.002314       0.007357
+# AFT[4]       0.9628  0.1592 0.002511       0.008552
+# AFT[5]       0.9596  0.1311 0.002067       0.007722
+# HR[2]        1.1373  0.2244 0.003539       0.009477
+# HR[3]        0.9169  0.1654 0.002609       0.007575
+# HR[4]        0.9527  0.1823 0.002875       0.009809
+# HR[5]        0.9477  0.1428 0.002252       0.008262
+# deviance  6060.8100 59.9484 0.945507       5.225167
+# p.crit[2]    0.2881  0.4529 0.007143       0.012517
+# p.crit[3]    0.7241  0.4470 0.007050       0.016330
+# p.crit[4]    0.6435  0.4790 0.007555       0.020082
+# p.crit[5]    0.6930  0.4613 0.007276       0.020135
+# 
+# 2. Quantiles for each variable:
+#   
+#   2.5%       25%       50%      75%    97.5%
+# AFT[2]       0.7950    0.9848    1.0928    1.214    1.575
+# AFT[3]       0.6957    0.8419    0.9210    1.011    1.249
+# AFT[4]       0.7085    0.8605    0.9498    1.043    1.340
+# AFT[5]       0.7592    0.8841    0.9489    1.021    1.247
+# HR[2]        0.7524    0.9815    1.1202    1.272    1.613
+# HR[3]        0.6294    0.8049    0.9014    1.013    1.287
+# HR[4]        0.6531    0.8248    0.9374    1.053    1.372
+# HR[5]        0.7104    0.8540    0.9362    1.027    1.276
+# deviance  5971.2341 6025.2626 6053.7141 6085.181 6206.865
+# p.crit[2]    0.0000    0.0000    0.0000    1.000    1.000
[…]

### 2020-07-04 AnalysisScript/ModelsJAGSmenCerebralInfar.R
updated model 0 ischem men

@@ -84,8 +84,88 @@ summary(mcmcplots::as.mcmc.rjags(M0menIscheStroke_20200702))
 
 save(M0menIscheStroke_20200702, file = "IscheStrokeMen.RData")
 
+# Inference for Bugs model at "jaccIschemic.weibull.model0", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       0.755   0.091    0.593    0.693    0.749    0.813    0.944 1.004   750
+# AFT[3]       0.706   0.072    0.575    0.654    0.703    0.752    0.855 1.002  4000
+# AFT[4]       0.744   0.075    0.609    0.692    0.741    0.790    0.896 1.002  2000
+# AFT[5]       0.798   0.064    0.684    0.755    0.795    0.835    0.925 1.009   440
+# HR[2]        0.657   0.121    0.450    0.575    0.646    0.731    0.919 1.004   710
+# HR[3]        0.593   0.093    0.434    0.527    0.587    0.651    0.797 1.002  4000
+# HR[4]        0.641   0.098    0.472    0.573    0.636    0.702    0.848 1.003  1900
+# HR[5]        0.712   0.085    0.563    0.652    0.707    0.761    0.893 1.006   590
+# beta[1]      5.491   0.223    5.262    5.381    5.463    5.552    5.892 1.075   590
+# beta[2]      0.288   0.120    0.058    0.207    0.289    0.366    0.523 1.004   750
+# beta[3]      0.354   0.102    0.157    0.285    0.352    0.424    0.554 1.002  4000
+# beta[4]      0.301   0.100    0.109    0.235    0.300    0.368    0.497 1.002  2000
+# beta[5]      0.229   0.079    0.078    0.180    0.230    0.281    0.379 1.009   440
+# p.crit[2]    0.991   0.097    1.000    1.000    1.000    1.000    1.000 1.031  1600
+# p.crit[3]    0.999   0.027    1.000    1.000    1.000    1.000    1.000 1.292  1300
+# p.crit[4]    0.997   0.059    1.000    1.000    1.000    1.000    1.000 1.161   690
+# p.crit[5]    0.995   0.070    1.000    1.000    1.000    1.000    1.000 1.160   490
[…]

### 2020-07-04 AnalysisScript/ModelsJAGSmenHemoStroke.R

@@ -438,7 +438,7 @@ jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = M2.params,
                          n.iter=100000, n.burnin=(3000/2), n.chains = 4,
                          model.file=M2hemo.weibull.model)
 end.time <- Sys.time()
-end.time - start.time 
+end.time - start.time  #Time difference of 2.548741 days
 M1menHemoStroke_20200701 <- jagsfit
 print(M1menHemoStroke_20200701)
 summary(mcmcplots::as.mcmc.rjags(M1menHemoStroke_20200701))

### 2020-07-04 AnalysisScript/ModelsJAGSfemHemoStroke.R
updated jagsfemhemostroker.R

@@ -1,0 +1,310 @@
+# HemoStroke == "I60_2"
+
+library(tidyverse)
+load("data/JACCmilkstrokewithHemo.Rdata")
+#######################Model 0 crude#######################
+#                                                          #
+#                      Model 0 crude                       #
+#                                                          #
+#**********************************************************#
+
+
+# Define exposure
+Mlkfre <- as.numeric(MData_fem$Mlkfre)
+table(Mlkfre)
+table(MData_fem$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
+
+# define events 
+is.censored <- MData_fem$HemoStroke != "I60_2"
+
+# define followup time for events
+t <- if_else(!is.censored, MData_fem$followpy, 0)
+t <- na_if(t, 0)
+t
+
+
+# define followup time for censored 
+c <- if_else(is.censored, MData_fem$followpy, 0)
+
+c[!is.censored] <- t[!is.censored] + 1
+
+
+
+
+jacchemo.weibull.model0 <- function() {
+  for(i in 1:54999){
+    is.censored[i] ~ dinterval(t[i], c[i])
+    t[i] ~ dweib(shape, lambda[i])
+    lambda[i] <- exp(-mu[i] * shape)
+    mu[i] <- beta[1] + beta[2]*equals(Mlkfre[i], 2) +
+      beta[3]*equals(Mlkfre[i], 3) + beta[4] * equals(Mlkfre[i], 4) +
+      beta[5] * equals(Mlkfre[i], 5) 
+  }
+  
+  ## priors for betas
+  for(j in 1:5){
+    beta[j] ~ dnorm(0, 0.001)
+  }
+  
+  ### prior for shape
+  shape ~ dgamma(.001, .001)
+  
+  ### Generated values
+  AFT[2] <- exp(-beta[2])
+  HR[2] <- exp(-shape * beta[2])
+  p.crit[2] <- step(1 - HR[2])
+  
+  AFT[3] <- exp(-beta[3])
+  HR[3] <- exp(-shape * beta[3])
+  p.crit[3] <- step(1 - HR[3])
+  
+  AFT[4] <- exp(-beta[4])
[…]

### 2020-07-05 AnalysisScript/ModelsJAGSfemHemoStroke.R
updated M0M1 ische stroke men & M0 hemo women

@@ -77,7 +77,7 @@ jagsfit <- jags.parallel(data=MILKdataFEM,  parameters.to.save = m0.params,
                          n.iter=100000, n.burnin=(5000/2), n.chains = 4, #n.thin = 100,
                          model.file=jacchemo.weibull.model0)
 end.time <- Sys.time()
-end.time - start.time #Time difference of 9.715389 hours
+end.time - start.time #Time difference of 22.07081 hours
 M0FEMHemoStroke_20200704 <- jagsfit
 print(M0FEMHemoStroke_20200704)
 summary(mcmcplots::as.mcmc.rjags(M0FEMHemoStroke_20200704))
@@ -85,7 +85,89 @@ summary(mcmcplots::as.mcmc.rjags(M0FEMHemoStroke_20200704))
 # save.image(file = "data/JACCmilkstroke.Rdata")
 save(M0FEMHemoStroke_20200704, file = "HemoStrokeFEM.RData")
 
-
+# Inference for Bugs model at "jacchemo.weibull.model0", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       0.780   0.131    0.549    0.687    0.771    0.865    1.061 1.004   780
+# AFT[3]       0.983   0.124    0.763    0.897    0.975    1.058    1.249 1.001  4000
+# AFT[4]       0.898   0.110    0.701    0.822    0.892    0.966    1.131 1.002  3500
+# AFT[5]       0.918   0.091    0.759    0.855    0.912    0.970    1.117 1.004  1900
+# HR[2]        0.732   0.157    0.469    0.618    0.718    0.832    1.076 1.002  2000
+# HR[3]        0.979   0.154    0.709    0.868    0.967    1.075    1.312 1.001  4000
+# HR[4]        0.873   0.135    0.635    0.778    0.865    0.958    1.163 1.001  3200
+# HR[5]        0.897   0.112    0.707    0.818    0.889    0.962    1.146 1.003  2200
+# beta[1]      6.436   0.264    6.054    6.282    6.405    6.545    7.012 1.058    69
+# beta[2]      0.263   0.168   -0.059    0.145    0.261    0.376    0.601 1.004   780
[…]

### 2020-07-05 AnalysisScript/ModelsJAGSmenCerebralInfar.R

@@ -222,7 +222,8 @@ jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = age.params,
                          n.iter=100000, n.burnin=(5000/2), n.chains = 4,
                          model.file=AgeIsche.weibull.model)
 end.time <- Sys.time()
-end.time - start.time #
+end.time - start.time # Time difference of 16.76311 hours
+
 
 M1menIscheStroke_20200702 <- jagsfit
 print(M1menIscheStroke_20200702)
@@ -230,7 +231,70 @@ summary(mcmcplots::as.mcmc.rjags(M1menIscheStroke_20200702))
 save(M0menIscheStroke_20200702, M1menIscheStroke_20200702, file = "IscheStrokeMen.RData")
 
 
+# Inference for Bugs model at "AgeIsche.weibull.model", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       0.835   0.085    0.678    0.778    0.832    0.889    1.010 1.004   640
+# AFT[3]       0.792   0.066    0.671    0.746    0.790    0.836    0.930 1.009   300
+# AFT[4]       0.821   0.069    0.694    0.773    0.819    0.863    0.964 1.005   630
+# AFT[5]       0.740   0.046    0.655    0.710    0.738    0.768    0.835 1.006   440
+# HR[2]        0.723   0.134    0.492    0.629    0.713    0.806    1.018 1.004   770
+# HR[3]        0.655   0.102    0.479    0.582    0.649    0.721    0.879 1.010   280
+# HR[4]        0.698   0.109    0.512    0.622    0.690    0.764    0.938 1.005   540
+# HR[5]        0.576   0.067    0.459    0.531    0.570    0.615    0.723 1.006   490
+# p.crit[2]    0.969   0.174    0.000    1.000    1.000    1.000    1.000 1.030   540
+# p.crit[3]    0.998   0.047    1.000    1.000    1.000    1.000    1.000 1.022  4000
+# p.crit[4]    0.990   0.100    1.000    1.000    1.000    1.000    1.000 1.023  2100
+# p.crit[5]    1.000   0.000    1.000    1.000    1.000    1.000    1.000 1.000     1
[…]

### 2020-07-06 AnalysisScript/ModelsJAGSfemHemoStroke.R
updated results men hemo finished@

@@ -88,7 +88,7 @@ save(M0FEMHemoStroke_20200704, file = "HemoStrokeFEM.RData")
 # Inference for Bugs model at "jacchemo.weibull.model0", fit using jags,
 # 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
 # n.sims = 4020 iterations saved
-# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
 # AFT[2]       0.780   0.131    0.549    0.687    0.771    0.865    1.061 1.004   780
 # AFT[3]       0.983   0.124    0.763    0.897    0.975    1.058    1.249 1.001  4000
 # AFT[4]       0.898   0.110    0.701    0.822    0.892    0.966    1.131 1.002  3500
@@ -125,7 +125,7 @@ save(M0FEMHemoStroke_20200704, file = "HemoStrokeFEM.RData")
 # 1. Empirical mean and standard deviation for each variable,
 # plus standard error of the mean:
 #   
-#   Mean       SD Naive SE Time-series SE
+#               Mean       SD Naive SE Time-series SE
 # AFT[2]    7.799e-01  0.13116 0.002069       0.004767
 # AFT[3]    9.828e-01  0.12436 0.001961       0.005866
 # AFT[4]    8.978e-01  0.10953 0.001727       0.004883

### 2020-07-06 AnalysisScript/ModelsJAGSmenCerebralInfar.R

@@ -87,7 +87,7 @@ save(M0menIscheStroke_20200702, file = "IscheStrokeMen.RData")
 # Inference for Bugs model at "jaccIschemic.weibull.model0", fit using jags,
 # 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
 # n.sims = 4020 iterations saved
-# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
 # AFT[2]       0.755   0.091    0.593    0.693    0.749    0.813    0.944 1.004   750
 # AFT[3]       0.706   0.072    0.575    0.654    0.703    0.752    0.855 1.002  4000
 # AFT[4]       0.744   0.075    0.609    0.692    0.741    0.790    0.896 1.002  2000
@@ -123,7 +123,7 @@ save(M0menIscheStroke_20200702, file = "IscheStrokeMen.RData")
 # 1. Empirical mean and standard deviation for each variable,
 # plus standard error of the mean:
 #   
-#   Mean       SD  Naive SE Time-series SE
+#                Mean       SD  Naive SE Time-series SE
 # AFT[2]       0.7549  0.09116 0.0014377      0.0030111
 # AFT[3]       0.7058  0.07248 0.0011431      0.0026088
 # AFT[4]       0.7436  0.07506 0.0011839      0.0026173
@@ -146,7 +146,7 @@ save(M0menIscheStroke_20200702, file = "IscheStrokeMen.RData")
 # 
 # 2. Quantiles for each variable:
 #   
-#   2.5%       25%       50%       75%     97.5%
+#                2.5%       25%       50%       75%     97.5%
 # AFT[2]    5.927e-01    0.6934    0.7492    0.8130    0.9437
 # AFT[3]    5.748e-01    0.6545    0.7031    0.7523    0.8548
 # AFT[4]    6.086e-01    0.6918    0.7407    0.7904    0.8965
@@ -234,7 +234,7 @@ save(M0menIscheStroke_20200702, M1menIscheStroke_20200702, file = "IscheStrokeMe
 # Inference for Bugs model at "AgeIsche.weibull.model", fit using jags,
 # 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
 # n.sims = 4020 iterations saved
[…]

### 2020-07-06 AnalysisScript/ModelsJAGSmenHemoStroke.R

@@ -489,7 +489,7 @@ save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # Inference for Bugs model at "M2hemo.weibull.model", fit using jags,
 # 4 chains, each with 1e+05 iterations (first 1500 discarded), n.thin = 98
 # n.sims = 4020 iterations saved
-# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
 # AFT[2]       1.111   0.198    0.795    0.985    1.093    1.214    1.575 1.002  1600
 # AFT[3]       0.933   0.147    0.696    0.842    0.921    1.011    1.249 1.005   590
 # AFT[4]       0.963   0.159    0.709    0.861    0.950    1.043    1.340 1.003   940

### 2020-07-06 AnalysisScript/ModelsJAGSfemHemoStroke.R
updated M1 hemo fem age adjusted

@@ -224,7 +224,7 @@ jagsfit <- jags.parallel(data=MILKdataFEM,  parameters.to.save = age.params,
                          n.iter=100000, n.burnin=(5000/2), n.chains = 4,
                          model.file=Agehemo.weibull.model)
 end.time <- Sys.time()
-end.time - start.time #Time difference of 13.87173 hours
+end.time - start.time #Time difference of 1.255446 days
 
 M1FEMHemoStroke_20200704 <- jagsfit
 print(M1FEMHemoStroke_20200704)
@@ -234,6 +234,70 @@ save(M0FEMHemoStroke_20200704,
      M1FEMHemoStroke_20200704, 
      file = "HemoStrokeFEM.RData")
 
+# Inference for Bugs model at "Agehemo.weibull.model", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       0.879   0.138    0.634    0.781    0.870    0.964    1.172 1.001  3600
+# AFT[3]       1.120   0.132    0.897    1.032    1.108    1.199    1.411 1.005   740
+# AFT[4]       1.043   0.128    0.822    0.953    1.035    1.122    1.319 1.001  2500
+# AFT[5]       0.949   0.091    0.800    0.885    0.941    1.001    1.141 1.003  2100
+# HR[2]        0.842   0.182    0.538    0.710    0.825    0.952    1.243 1.001  3200
+# HR[3]        1.171   0.184    0.858    1.045    1.153    1.282    1.575 1.003  1100
+# HR[4]        1.063   0.177    0.764    0.935    1.049    1.172    1.446 1.001  4000
+# HR[5]        0.931   0.121    0.732    0.844    0.920    1.002    1.199 1.002  1900
+# p.crit[2]    0.816   0.387    0.000    1.000    1.000    1.000    1.000 1.001  3400
+# p.crit[3]    0.169   0.375    0.000    0.000    0.000    0.000    1.000 1.002  1400
+# p.crit[4]    0.389   0.487    0.000    0.000    0.000    1.000    1.000 1.001  4000
+# p.crit[5]    0.746   0.435    0.000    0.000    1.000    1.000    1.000 1.002  2500
+# deviance  7423.580  46.934 7334.193 7391.375 7423.324 7454.439 7517.134 1.007   440
+# 
[…]

### 2020-07-07 AnalysisScript/ModelsJAGSmenCerebralInfar.R
cerbral infar men done

@@ -441,7 +441,8 @@ jagsfit <- jags.parallel(data=MILKdataMEN,  parameters.to.save = M2.params,
                          n.iter=100000, n.burnin=(3000/2), n.chains = 4,
                          model.file=M2Isch.weibull.model)
 end.time <- Sys.time()
-end.time - start.time 
+end.time - start.time #Time difference of 2.743878 days
+
 
 M2menIscheStroke_20200702 <- jagsfit
 print(M2menIscheStroke_20200702)
@@ -450,4 +451,67 @@ save(M0menIscheStroke_20200702,
      M1menIscheStroke_20200702, 
      M2menIscheStroke_20200702, file = "IscheStrokeMen.RData")
 
+# Inference for Bugs model at "M2Isch.weibull.model", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 1500 discarded), n.thin = 98
+# n.sims = 4020 iterations saved
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       0.837   0.093    0.672    0.777    0.834    0.893    1.024 1.005   530
+# AFT[3]       0.798   0.077    0.666    0.751    0.796    0.843    0.949 1.009   540
+# AFT[4]       0.834   0.080    0.695    0.783    0.831    0.880    0.998 1.005   520
+# AFT[5]       0.754   0.056    0.664    0.722    0.753    0.785    0.854 1.008   410
+# HR[2]        0.731   0.140    0.496    0.631    0.719    0.817    1.040 1.004   680
+# HR[3]        0.671   0.111    0.484    0.594    0.660    0.734    0.912 1.005   730
+# HR[4]        0.725   0.120    0.523    0.640    0.714    0.794    0.996 1.004   800
+# HR[5]        0.606   0.079    0.482    0.555    0.597    0.646    0.787 1.009   430
+# p.crit[2]    0.961   0.194    0.000    1.000    1.000    1.000    1.000 1.013   990
+# p.crit[3]    0.991   0.097    1.000    1.000    1.000    1.000    1.000 1.074   660
+# p.crit[4]    0.975   0.155    1.000    1.000    1.000    1.000    1.000 1.015  1300
+# p.crit[5]    0.998   0.045    1.000    1.000    1.000    1.000    1.000 1.295   500
[…]

### 2020-07-07 AnalysisScript/ModelsJAGSmenCerebralInfar.R
updated typo in men cerebra

@@ -1,4 +1,4 @@
-# HemoStroke == "I63"
+# IschemStroke == "I63"
 
 library(tidyverse)
 load("data/JACCmilkstrokewithHemo.Rdata")

### 2020-07-07 AnalysisScript/ModelsJAGSfemCerebralInfar.R
cerebra infarction women models script added

@@ -1,0 +1,308 @@
+# IschemStroke == "I63"
+
+library(tidyverse)
+load("data/JACCmilkstrokewithHemo.Rdata")
+#######################Model 0 crude#######################
+#                                                          #
+#                      Model 0 crude                       #
+#                                                          #
+#**********************************************************#
+
+
+# Define exposure
+Mlkfre <- as.numeric(MData_fem$Mlkfre)
+table(Mlkfre)
+table(MData_fem$Mlkfre) #1 = Never ; 2 = Mon1_2 ; 3 = Wek1_2 ; 4 = Wek3_4 ; 5 = Daily
+
+# define events 
+is.censored <- MData_fem$IscheStroke != "I63"
+
+# define followup time for events
+t <- if_else(!is.censored, MData_fem$followpy, 0)
+t <- na_if(t, 0)
+t
+
+
+# define followup time for censored 
+c <- if_else(is.censored, MData_fem$followpy, 0)
+
+c[!is.censored] <- t[!is.censored] + 1
+
+
+
+
+jaccIschemic.weibull.model0 <- function() {
+  for(i in 1:54999){
+    is.censored[i] ~ dinterval(t[i], c[i])
+    t[i] ~ dweib(shape, lambda[i])
+    lambda[i] <- exp(-mu[i] * shape)
+    mu[i] <- beta[1] + beta[2]*equals(Mlkfre[i], 2) +
+      beta[3]*equals(Mlkfre[i], 3) + beta[4] * equals(Mlkfre[i], 4) +
+      beta[5] * equals(Mlkfre[i], 5) 
+  }
+  
+  ## priors for betas
+  for(j in 1:5){
+    beta[j] ~ dnorm(0, 0.001)
+  }
+  
+  ### prior for shape
+  shape ~ dgamma(.001, .001)
+  
+  ### Generated values
+  AFT[2] <- exp(-beta[2])
+  HR[2] <- exp(-shape * beta[2])
+  p.crit[2] <- step(1 - HR[2])
+  
+  AFT[3] <- exp(-beta[3])
+  HR[3] <- exp(-shape * beta[3])
+  p.crit[3] <- step(1 - HR[3])
+  
+  AFT[4] <- exp(-beta[4])
[…]

### 2020-07-07 Paperfolder/Paperfolder.Rmd
updated tables and results finished

--- 2020-06-25 Paperfolder/Paperfolder.Rmd
@@
     long: Just Another Gibbs Samplers
+  - short: HR
+    long: hazard ratio
+  - short: sd
+    long: standard deviation
+  - short: CrI
+    long: credible interval
 output: rticles::mdpi_article
@@
 The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women).
-Among these stroke mortality, 957 were cerebral infarction (520 men and 437 women), and 952 were hemorrhagic stroke (432 men and 520 women).
-
-As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at the baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
-Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.
-
-Table
+Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
 
@@
 
-<!-- This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
--->
+As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
+Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.
 
-<!-- ## Subsection Heading Here -->
+Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women).
+Compared to those who never had milk, both men and women had lower hazard of dying from total stroke in crude models.
+Chances that the posterior HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women.
+However, lower hazard was observed to remain after age or multivariable adjustment only in men.
+Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
+Daily female milk consumers had posterior HRs that was distributed with mean (sd) of 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be lower than 1.
 
-<!-- Subsection text here. -->
+Posterior distributions of HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
+In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 26%-37% lower hazard of dying from cerebral infarction compared with men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
+We were more than 95.7% sure that these posterior HRs could be lower than 1.
+No associations were observed between milk intake and hazard of cerebral infarction among women.
 
-<!-- ### Subsubsection Heading Here -->
+# Discussion
 
-<!-- Bulleted lists look like this: -->
+In the JACC study cohort, we observed that
 
-<!-- * First bullet -->
-<!-- * Second bullet -->
-<!-- * Third bullet -->
-
-<!-- Numbered lists can be added as follows: -->
-
-<!-- 1. First item -->
-<!-- 2. Second item -->
-<!-- 3. Third item -->
-
-<!-- The text continues here. -->
-
-<!-- All figures and tables should be cited in the main text as Figure 1, Table 1, etc. -->
-
-<!-- \begin{figure}[H] -->
-<!-- \centering -->
-<!-- \includegraphics[width=3 cm]{logo-mdpi} -->
-<!-- \caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.} -->
-<!-- \end{figure} -->
+# Conclusion
 
@@
 
-kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.", booktabs = T, linesep = "") %>%
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
     # collapse_rows(columns = 1, valign = "top") %>% 
@@
   pack_rows("Model 2", 12, 15) %>%
+    row_spec(15,  hline_after = TRUE) %>%
+    pack_rows("Model 0", 17, 20) %>%
+  pack_rows("Model 1", 21, 24) %>%
+  pack_rows("Model 2", 25, 28) %>%
+      row_spec(28,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 30, 33) %>%
+  pack_rows("Model 1", 34, 37) %>%
+  pack_rows("Model 2", 38, 41) %>%
 kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
   # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))
-
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
 ```
 
-<!-- \begin{table}[H] -->
-<!-- \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.} -->
-<!-- \centering -->
-<!-- %% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used. -->
-<!-- \begin{tabular}{ccc} -->
-<!-- \toprule -->
-<!-- \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\ -->
-<!-- \midrule -->
-<!-- entry 1		& data			& data\\ -->
-<!-- entry 2		& data			& data\\ -->
-<!-- \bottomrule -->
-<!-- \end{tabular} -->
-<!-- \end{table} -->
+```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
+dt <- read.csv("tab/HRAFTweibF.csv", header = T)
+# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
+names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
 
-<!-- This is an example of an equation: -->
-
-<!-- \begin{equation} -->
-<!-- \mathbb{S} -->
-<!-- \end{equation} -->
-<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
--->
-
-<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
-<!-- Example of a theorem: -->
-<!-- \begin{Theorem} -->
-<!-- Example text of a theorem. -->
-<!-- \end{Theorem} -->
-
-<!-- The text continues here. Proofs must be formatted as follows: -->
-
-<!-- Example of a proof: -->
-<!-- \begin{proof}[Proof of Theorem 1] -->
-<!-- Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to. -->
-<!-- \end{proof} -->
-<!-- The text continues here. -->
-
-# Discussion
-
-<!-- Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
--->
-
-# Conclusion
-
-<!-- This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex. -->
-
-<!-- # Patents -->
-
-<!-- This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript. -->
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
+    # collapse_rows(columns = 1, valign = "top") %>% 
+  pack_rows("Model 0", 4, 7) %>%
+  pack_rows("Model 1", 8, 11) %>%
+  pack_rows("Model 2", 12, 15) %>%
+  row_spec(15,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 17, 20) %>%
+  pack_rows("Model 1", 21, 24) %>%
+  pack_rows("Model 2", 25, 28) %>%
+  row_spec(28,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 30, 33) %>%
+  pack_rows("Model 1", 34, 37) %>%
+  pack_rows("Model 2", 38, 41) %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
+```

### 2020-07-07 Paperfolder/Paperfolder.tex
updated tables done
updated table 2 men 50%
updted table 2
updated table 2 80% and table 3 50%
updated tables and results finished

@@
 during which 2675 death from stroke was confirmed (1352 men and 1323
-women). Among these stroke mortality, 957 were cerebral infarction (520
-men and 437 women), and 952 were hemorrhagic stroke (432 men and 520
+women). Among these stroke mortality, 952 were hemorrhagic stroke (432
+men and 520 women), and 957 were cerebral infarction (520 men and 437
 women).
-
-As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
-chose ``never'' as their milk intake frequency at the baseline, milk
-drinkers were less likely to be a current smoker or a daily alcohol
-consumer in both men and women. Furthermore, people consumed milk more
-than 1-2 times/month were more likely to be a daily consumers of
-vegetable, fruit as well as coffee, and more likely to join exercise
-more than 1 hour/week among either sex.
-
-Table
 
@@
 
+As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
+chose ``never'' as their milk intake frequency at baseline, milk
+drinkers were less likely to be a current smoker or a daily alcohol
+consumer in both men and women. Furthermore, people consumed milk more
+than 1-2 times/month were more likely to be a daily consumers of
+vegetable, fruit as well as coffee, and more likely to join exercise
+more than 1 hour/week among either sex.
+
+Detailed results from the Bayesian survival models (crude, age-adjusted
+and multivariable adjusted) according to the frequency of milk intake
+separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
+\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
+milk, both men and women had lower hazard of dying from total stroke in
+crude models. Chances that the posterior HRs were estimated to be lower
+than 1 for those who had at least 1-2 times/month was higher than 86.5\%
+in men and more than 94.6\% in women. However, lower hazard was observed
+to remain after age or multivariable adjustment only in men.
+Specifically, the mean (sd; 95\% CrI) of posterior
+multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd
+= 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller
+than the null value (=1). Daily female milk consumers had posterior HRs
+that was distributed with mean (sd) of 0.95 (sd = 0.12; 95\% CrI: 0.80,
+1.17) which had 78.0\% of chance that their HRs could be lower than 1.
+
+Posterior distributions of HRs for mortality from hemorrhagic stroke
+were found to contain the null value for either men or women among all
+fitted models. In contrast, men who had milk intake frequency higher
+than 1-2 times/week were found to be associated with averagely 26\%-37\%
+lower hazard of dying from cerebral infarction compared with men who
+never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were
+more than 95.7\% sure that these posterior HRs could be lower than 1. No
+associations were observed between milk intake and hazard of cerebral
+infarction among women.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+In the JACC study cohort, we observed that
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
 \begin{table}[!h]
@@
 \fontsize{8}{10}\selectfont
-\begin{tabular}[t]{llllll}
+\begin{tabular}[t]{lccccc}
 \toprule
@@
 \hspace{1em}MCSE & - & 0.0022 & 0.0019 & 0.0022 & 0.0018\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.47\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\
 \addlinespace[0.3em]
@@
 \hspace{1em}MCSE & - & 0.0027 & 0.0022 & 0.0021 & 0.0016\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.31\% & 96.05\% & 100.00\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\
 \addlinespace[0.3em]
@@
 \hspace{1em}MCSE & - & 0.0041 & 0.0036 & 0.0038 & 0.0031\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.61\% & 93.73\% & 89.62\% & 99.04\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\
+\hline
 Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.01 (0.08) &  &  & \\
-\hspace{1em}95\% CrI &  & (0.75, 1.04) &  &  & \\
-\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{5} & \\
-\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{5} & \\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
+\hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0066 & 0.0057 & 0.0057 & 0.0062\\
+\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{4} & \\
-\hspace{1em}95\% CrI &  &  &  &  \vphantom{4} & \\
-\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{4} & \\
-\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{4} & \\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
+\hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0091 & 0.0067 & 0.0073 & 0.0076\\
+\hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{3} & \\
-\hspace{1em}95\% CrI &  &  &  &  \vphantom{3} & \\
-\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{3} & \\
-\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{3} & \\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
+\hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0093 & 0.0075 & 0.0098 & 0.0082\\
+\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\
+\hline
 \rowcolor{gray!6}  Cerebral infarction & 151 & 41 & 64 & 66 & 198\\
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{2} & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  \vphantom{2} & \\
-\hspace{1em}MCSE &  &  &  &  \vphantom{2} & \\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{2} & \\
+\hspace{1em}MeanHR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
+\hspace{1em}MCSE & - & 0.0042 & 0.0037 & 0.0036 & 0.0038\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{1} & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  \vphantom{1} & \\
-\hspace{1em}MCSE &  &  &  &  \vphantom{1} & \\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{1} & \\
+\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
+\hspace{1em}MCSE & - & 0.0045 & 0.0035 & 0.0041 & 0.0029\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}MeanHR (SD) & 1 &  &  &  & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  & \\
-\hspace{1em}MCSE &  &  &  &  & \\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  & \\
+\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
+\hspace{1em}MCSE & - & 0.0049 & 0.0047 & 0.0061 & 0.0052\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\
 \bottomrule
@@
 \rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
+\hline
 Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{5} & \\
-\hspace{1em}95\% CrI & - &  &  &  \vphantom{5} & \\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{5} & \\
-\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{5} & \\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
+\hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0058 & 0.0071 & 0.0061 & 0.0065\\
+\hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{4} & \\
-\hspace{1em}95\% CrI & - &  &  &  \vphantom{4} & \\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{4} & \\
-\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{4} & \\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
+\hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0065 & 0.0089 & 0.0084 & 0.0069\\
+\hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{3} & \\
-\hspace{1em}95\% CrI & - &  &  &  \vphantom{3} & \\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{3} & \\
-\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{3} & \\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
+\hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
+\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0051 & 0.0067 & 0.0039 & 0.0047\\
+\hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\
+\hline
 \rowcolor{gray!6}  Cerebral infarction & 102 & 35 & 63 & 50 & 187\\
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{2} & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
-\hspace{1em}MCSE & - &  &  &  \vphantom{2} & \\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{2} & \\
+\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.13) & 0.82 (0.14) & 0.59 (0.14) & 0.76 (0.16)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
+\hspace{1em}MCSE & - & 0.0087 & 0.0079 & 0.0064 & 0.0071\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{1} & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
-\hspace{1em}MCSE & - &  &  &  \vphantom{1} & \\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{1} & \\
+\hspace{1em}MeanHR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
+\hspace{1em}MCSE & - & 0.0071 & 0.0072 & 0.0095 & 0.0054\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}MeanHR (SD) & 1 &  &  &  & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
-\hspace{1em}MCSE & - &  &  &  & \\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  & \\
+\hspace{1em}MeanHR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
+\hspace{1em}MCSE & - & 0.0055 & 0.0057 & 0.0067 & 0.0047\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\
 \bottomrule
@@
 \end{table}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
 
@@
 JAGS & Just Another Gibbs Samplers \\
+HR & hazard ratio \\
+sd & standard deviation \\
+CrI & credible interval \\
 \end{tabular}}

### 2020-07-08 Paperfolder/Paperfolder.Rmd
Updated intro started

@@
 ---
-title: Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
+title: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
 author:
@@
 
-<!-- # Version -->
-
-<!-- This Rmd-skeleton uses the mdpi Latex template published 2019/02.  -->
-<!-- However, the official template gets more frequently updated than the 'rticles' -->
-<!-- package. Therefore, please make sure prior to paper submission, that you're  -->
-<!-- using the most recent .cls, .tex and .bst files  -->
-<!-- (available [here](http://www.mdpi.com/authors/latex)). -->
-
 # Introduction
 
-<!-- The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016].
-And now citing a book reference @gujer_systems_2008.
-Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
--->
+Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
+More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all.
+For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since it should be formally defined as the probability of the occurrence of an event at a given time point.
+Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably.
+However, it would still possibly be mixed up with "risk" that only contain pure "probability" without a point or a period of time in cross-sectional settings.
+For better understanding and interpretation of the data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.
 

### 2020-07-08 Paperfolder/Paperfolder.tex
Updated intro started

@@
 % Full title of the paper (Capitalized)
-\Title{Milk intake and risk of mortality risk in the Japan Collaborative
+\Title{Milk intake and stroke mortality in the Japan Collaborative
 Cohort Study - a Bayesian survival analysis}
@@
 \section{Introduction}\label{introduction}}
+
+Dairy food, especially milk has been recommended to reduce stroke risk
+by nearly 7\% for each 200 g increment of daily consumption
+\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
+would be possible if we were able to compute the exact probability for
+people who had milk intake may had lower hazard of dying from stroke
+compared with those who never drank milk at all. For general
+public/media reporting, concept of hazard in epidemiological studies
+could still sometimes be challenging to be understood or misinterpreted
+since it should be formally defined as the probability of the occurrence
+of an event at a given time point. Usually, authors of epidemiological
+papers would tend to use ``risk'' instead of ``hazard'' or
+interchangeably. However, it would still possibly be mixed up with
+``risk'' that only contain pure ``probability'' without a point or a
+period of time in cross-sectional settings. For better understanding and
+interpretation of the data that researchers endeavored to collect,
+statistical literature have provided plenty of choices that could help
+us better communicate with each other.
 

### 2020-07-08 AnalysisScript/ModelsJAGSfemCerebralInfar.R
model 0 cerebra infar women added@

@@ -84,6 +84,88 @@ summary(mcmcplots::as.mcmc.rjags(M0femIscheStroke_20200707))
 
 save(M0femIscheStroke_20200707, file = "IscheStrokefem.RData")
 
+# Inference for Bugs model at "jaccIschemic.weibull.model0", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+#             mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       1.013   0.125    0.789    0.927    1.007    1.090    1.267 1.001  3700
+# AFT[3]       0.902   0.089    0.746    0.842    0.896    0.957    1.099 1.007   480
+# AFT[4]       0.745   0.078    0.600    0.690    0.742    0.794    0.906 1.007   420
+# AFT[5]       0.863   0.064    0.746    0.817    0.862    0.904    0.998 1.006   540
+# HR[2]        1.028   0.207    0.671    0.881    1.013    1.156    1.468 1.001  4000
+# HR[3]        0.845   0.138    0.613    0.749    0.830    0.929    1.159 1.006   580
+# HR[4]        0.614   0.108    0.428    0.538    0.604    0.679    0.850 1.006   500
+# HR[5]        0.783   0.097    0.615    0.713    0.779    0.843    0.996 1.005   760
+# beta[1]      5.639   0.211    5.361    5.523    5.609    5.712    6.085 1.075   160
+# beta[2]     -0.005   0.122   -0.236   -0.086   -0.007    0.075    0.237 1.001  3700
+# beta[3]      0.108   0.097   -0.094    0.044    0.110    0.172    0.293 1.007   480
+# beta[4]      0.300   0.105    0.098    0.230    0.298    0.371    0.511 1.007   420
+# beta[5]      0.150   0.074    0.002    0.101    0.149    0.202    0.292 1.006   540
+# p.crit[2]    0.471   0.499    0.000    0.000    0.000    1.000    1.000 1.001  3500
+# p.crit[3]    0.864   0.343    0.000    1.000    1.000    1.000    1.000 1.008   570
+# p.crit[4]    0.997   0.052    1.000    1.000    1.000    1.000    1.000 1.137  1100
[…]

### 2020-07-08 AnalysisScript/ModelsJAGSmenHemoStroke.R

@@ -470,7 +470,7 @@ save.image(file = "data/JACCmilkstrokewithHemo.Rdata")
 # 
 # 2. Quantiles for each variable:
 #   
-#   2.5%       25%       50%      75%    97.5%
+#               2.5%       25%       50%      75%    97.5%
 # AFT[2]       0.7950    0.9848    1.0928    1.214    1.575
 # AFT[3]       0.6957    0.8419    0.9210    1.011    1.249
 # AFT[4]       0.7085    0.8605    0.9498    1.043    1.340

### 2020-07-08 Paperfolder/Paperfolder.Rmd
updated introduction done

@@
 keywords: |
-  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
-  to the article, yet reasonably common within the subject discipline.).
+  milk intake; mortality; stroke; Bayesian survival anlysis; time-to-event data; JACC study 
 acknowledgement: |
@@
     long: Just Another Gibbs Samplers
+  - short: AFT
+    long: accelerated failure time 
   - short: HR
     long: hazard ratio
+  - short: AF
+    long: acceleration factor
   - short: sd
@@
     long: credible interval
+header-includes:
+   - \usepackage{graphicx}
 output: rticles::mdpi_article
@@
 More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all.
-For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since it should be formally defined as the probability of the occurrence of an event at a given time point.
+For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling].
 Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably.
-However, it would still possibly be mixed up with "risk" that only contain pure "probability" without a point or a period of time in cross-sectional settings.
-For better understanding and interpretation of the data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.
+However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings.
+For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.
+Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard.
+Accelerated failure time models are among these convenient tools that would avoid frequently unmet assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
+
+Our aim was to overcome these potential pitfalls, avoid misunderstanding, and provide a more straightforward answer to the main research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk.
+If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process.
+A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a stroke event from happening after controlling for the other potential confounders.
 
@@
 Full parametric proportional hazard models under Bayesian framework with Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS) program [@Plummer2003] version 4.3.0 in R version 4.0.1 [@RCT2020].
-JAGS program is similar to the OpenBUGS [@Lunn2009] project that uses a Gibbs sampling engine for Markov Chain Monte Carlo (MCMC) simulation.
+JAGS program is similar to the OpenBUGS [@Lunn2009] project that uses a Gibbs sampling engine for MCMC simulation.
 In the current analysis, we specified non-informative prior distributions for each of the parameters in our models ($\beta_n \sim N(0, 1000)$, and $\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)$).
@@
 Then, the number of iterations discarded as ‘burn-in’ was chosen.
-All models had a posterior sample size of 100000 from three separated chains with a "burn-in" of 2500 iterations.
-Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated HR were presented for each category of milk intake frequency taking the "never" category as the reference.
-Posterior probability that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.
+All models had a posterior sample size of 100000 from four separated chains with a "burn-in" of 2500 iterations.
+Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated hazard ratios (HRs) as well as acceleration factors (AFs) were presented for each category of milk intake frequency taking the "never" category as the reference.
+Posterior probabilities that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.
 
-The parametric forms of the models fitted in the Bayesian survival analyses include three models: 1) the crude model, 2) the age-centered adjusted model, 3) and a model further adjusted for potential confounders which includes: age (centered, continuous), smoking habit (never, current, former), alcohol intake (never or past, $<$ 4 times/week, Daily), body mass index ($<$ 18.5, $\geq$ 18.5 and $<$ 25, $\geq$ 25 and $<$ 30, $\geq$ 30 kg/m$^2$), history of hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more than 1 hour/week, yes/no), sleep duration ($<$ 7, $\geq$ 7 and $<$ 8, $\geq$ 8 and $<$ 9, $\geq$ 9, hours), coffee intake (never, $<$ 3-4 times/week, almost daily), education level (attended school till age 18, yes/no)
-
-<!-- Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
--->
-
-<!-- Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
--->
-
-<!-- Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code. -->
-
-# Results
-
-The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women).
-Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
+The parametric forms of the models fitted in the Bayesian survival analyses included three models: 1) the crude model, 2) the age-centered adjusted model, 3) and a model further adjusted for potential confounders which includes: age (centered, continuous), smoking habit (never, current, former), alcohol intake (never or past, $<$ 4 times/week, Daily), body mass index ($<$ 18.5, $\geq$ 18.5 and $<$ 25, $\geq$ 25 and $<$ 30, $\geq$ 30 kg/m$^2$), history of hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more than 1 hour/week, yes/no), sleep duration ($<$ 7, $\geq$ 7 and $<$ 8, $\geq$ 8 and $<$ 9, $\geq$ 9, hours), coffee intake (never, $<$ 3-4 times/week, almost daily), education level (attended school till age 18, yes/no)
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake (JACC study, 1988-2009).}
@@
 \fontsize{8}{10}\selectfont
+\resizebox{\textwidth}{!}{%
 \begin{tabular}[t]{lccccccc}
@@
 \bottomrule
-\end{tabular}
+\end{tabular}}
 \end{table}
+
+# Results
+
+The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women).
+Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
 
@@
 
-```{r tab2, echo=FALSE, eval=TRUE, message=FALSE}
+```{r tab2, echo=FALSE, eval=FALSE, message=FALSE}
 library(knitr)
@@
 
-kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
+kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
+  row_spec(0, bold = T) %>% 
     # collapse_rows(columns = 1, valign = "top") %>% 
+    pack_rows("Model 0", 4, 8) %>%
+  pack_rows("Model 1", 9, 13) %>%
+  pack_rows("Model 2", 14, 18) %>%
+  row_spec(18,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 20, 24) %>%
+  pack_rows("Model 1", 25, 29) %>%
+  pack_rows("Model 2", 30, 34) %>%
+  row_spec(34,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 36, 40) %>%
+  pack_rows("Model 1", 41, 45) %>%
+  pack_rows("Model 2", 46, 50) %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
+  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
+```
+
+\begin{table}[!h]
+
+\caption{\label{tab:tab2}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke types according to the frequency of milk intake in men (JACC study, 1988-2009).}
+\centering
+\fontsize{6}{8}\selectfont
+\resizebox*{\textwidth}{\dimexpr\textheight-\lineskip\relax}{%
+\begin{tabular}[t]{lccccc}
+\toprule
+\textbf{ } & \textbf{Never} & \textbf{1-2 times/Month} & \textbf{1-2 times/Week} & \textbf{3-4 times/Week} & \textbf{Almost Daily}\\
+\midrule
+\rowcolor{gray!6}  Person-year & 135704 & 56551 & 97098 & 92153 & 252364\\
+N & 8508 & 3522 & 5928 & 5563 & 15865\\
+\rowcolor{gray!6}  Total Stroke & 326 & 122 & 181 & 177 & 546\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.07) & 0.83 (0.05) & 0.85 (0.05) & 0.93 (0.04)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.06) & (0.73, 0.94) & (0.74, 0.96) & (0.85, 1.02)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
+\hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.50\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.06) & 0.90 (0.05) & 0.91 (0.05) & 0.85 (0.04)\\
+\hspace{1em}95\% CrI & - & (0.87, 1.11) & (0.81, 1.00) & (0.82, 1.01) & (0.78, 0.92)\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
+\hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.30\% & 96.10\% & 100.00\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 & 1.00 (0.07) & 0.92 (0.06) & 0.94 (0.06) & 0.88 (0.05)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.14) & (0.82, 1.03) & (0.84, 1.05) & (0.81, 0.96)\\
+\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
+\hspace{1em}Pr(HR < 1) & - & 50.60\% & 93.70\% & 89.60\% & 99.00\%\\
+\hline
+\rowcolor{gray!6}  Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 1.03 (0.17) & 0.85 (0.12) & 0.87 (0.13) & 0.98 (0.11)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.74, 1.38) & (0.63, 1.12) & (0.65, 1.14) & (0.78, 1.22)\\
+\hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
+\hspace{1em}Pr(HR < 1) & - & 47.20\% & 88.40\% & 86.30\% & 63.10\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 1.08 (0.17) & 0.91 (0.13) & 0.92 (0.13) & 0.90 (0.10)\\
+\hspace{1em}95\% CrI & - & (0.80, 1.45) & (0.70, 1.20) & (0.71, 1.19) & (0.74, 1.11)\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
+\hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.60\% & 79.70\% & 76.60\% & 87.60\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 & 1.11 (0.18) & 0.93 (0.15) & 0.96 (0.16) & 0.96 (0.13)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.58) & (0.70, 1.25) & (0.71, 1.34) & (0.76, 1.25)\\
+\hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
+\hspace{1em}Pr(HR < 1) & - & 28.80\% & 72.40\% & 64.40\% & 69.30\%\\
+\hline
+\rowcolor{gray!6}  Cerebral infarction & 151 & 41 & 64 & 66 & 198\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.76 (0.09) & 0.71 (0.07) & 0.74 (0.08) & 0.79 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.59, 0.94) & (0.58, 0.86) & (0.61, 0.89) & (0.68, 0.93)\\
+\hspace{1em}MeanHR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
+\hspace{1em}Pr(HR < 1) & - & 99.10\% & 99.90\% & 99.70\% & 99.50\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.83 (0.08) & 0.79 (0.07) & 0.82 (0.07) & 0.74 (0.05)\\
+\hspace{1em}95\% CrI & - & (0.68, 1.01) & (0.67, 0.93) & (0.69, 0.96) & (0.66, 0.84)\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
+\hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.90\% & 99.80\% & 98.90\% & 100.00\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.84 (0.09) & 0.80 (0.08) & 0.83 (0.08) & 0.75 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.67, 1.02) & (0.67, 0.95) & (0.69, 0.99) & (0.66, 0.85)\\
+\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
+\hspace{1em}Pr(HR < 1) & - & 96.10\% & 99.10\% & 97.50\% & 99.80\%\\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
+\multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
+\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
+\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
+\end{tabular}}
+\end{table}
+
+```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
+library(knitr)
+library(kableExtra)
+dt <- read.csv("tab/HRAFTweibF.csv", header = T)
+# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
+names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
+
+kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
+    # collapse_rows(columns = 1, valign = "top") %>% 
+    row_spec(0, bold = T) %>% 
   pack_rows("Model 0", 4, 7) %>%
@@
   pack_rows("Model 2", 38, 41) %>%
-kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
   # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
@@
 ```
-
-```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
-dt <- read.csv("tab/HRAFTweibF.csv", header = T)
-# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
-names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
-
-kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
-    # collapse_rows(columns = 1, valign = "top") %>% 
-  pack_rows("Model 0", 4, 7) %>%
-  pack_rows("Model 1", 8, 11) %>%
-  pack_rows("Model 2", 12, 15) %>%
-  row_spec(15,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 17, 20) %>%
-  pack_rows("Model 1", 21, 24) %>%
-  pack_rows("Model 2", 25, 28) %>%
-  row_spec(28,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 30, 33) %>%
-  pack_rows("Model 1", 34, 37) %>%
-  pack_rows("Model 2", 38, 41) %>%
-kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
-  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
-```

### 2020-07-08 Paperfolder/Paperfolder.tex
updated introduction done

@@
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
-keywords specific to the article, yet reasonably common within the
-subject discipline.).}
+\keyword{milk intake; mortality; stroke; Bayesian survival anlysis;
+time-to-event data; JACC study}
 
@@
 
+\usepackage{graphicx}
 \usepackage{booktabs}
@@
 could still sometimes be challenging to be understood or misinterpreted
-since it should be formally defined as the probability of the occurrence
-of an event at a given time point. Usually, authors of epidemiological
-papers would tend to use ``risk'' instead of ``hazard'' or
-interchangeably. However, it would still possibly be mixed up with
-``risk'' that only contain pure ``probability'' without a point or a
-period of time in cross-sectional settings. For better understanding and
-interpretation of the data that researchers endeavored to collect,
+since hazard is formally defined as the probability of the occurrence of
+an event at a given time point \citep{collett2015modelling}. Usually,
+authors of epidemiological papers would tend to use ``risk'' instead of
+``hazard'' or interchangeably. However, it would still possibly be mixed
+up with ``risk'' that only contain pure meaning of ``probability of an
+event'' without redefining a point or a period of time in
+cross-sectional settings. For better understanding and interpretation of
+the findings from data that researchers endeavored to collect,
 statistical literature have provided plenty of choices that could help
-us better communicate with each other.
+us better communicate with each other. Another approach of comparing the
+time-to-event survival probabilities between different groups would be
+to model the time before observing an event rather than the hazard which
+always required the assumption of a proportional hazard. Accelerated
+failure time models are among these convenient tools that would avoid
+frequently unmet assumption of proportional hazard and directly show how
+faster/slower that one individual in an exposure group might have an
+event compared to others among different exposure groups
+\citep{Wei1992}.
+
+Our aim was to overcome these potential pitfalls, avoid
+misunderstanding, and provide a more straightforward answer to the main
+research question that whether someone answered he/she drank milk at the
+baseline of study had lower hazard of dying from stroke compared with
+his/her counterparts who said they never consumed milk. If the answer to
+the primary objective was yes, then the probabilities that individuals
+with different frequencies of milk intake may had lower hazard compared
+with those who never drank milk were calculated through a Markov Chain
+Monte Carlo (MCMC) simulation process. A Bayesian survival analysis
+method was applied on an existing database and through which, we also
+provided estimates about whether drinking milk could delay or slow down
+the speed towards a stroke event from happening after controlling for
+the other potential confounders.
 
@@
 \citep{RCT2020}. JAGS program is similar to the OpenBUGS
-\citep{Lunn2009} project that uses a Gibbs sampling engine for Markov
-Chain Monte Carlo (MCMC) simulation. In the current analysis, we
-specified non-informative prior distributions for each of the parameters
-in our models (\(\beta_n \sim N(0, 1000)\), and
+\citep{Lunn2009} project that uses a Gibbs sampling engine for MCMC
+simulation. In the current analysis, we specified non-informative prior
+distributions for each of the parameters in our models
+(\(\beta_n \sim N(0, 1000)\), and
 \(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)). The
@@
 discarded as `burn-in' was chosen. All models had a posterior sample
-size of 100000 from three separated chains with a ``burn-in'' of 2500
+size of 100000 from four separated chains with a ``burn-in'' of 2500
 iterations. Posterior means (sd) and 95\% Credible Intervals (CrI) of
-the estimated HR were presented for each category of milk intake
-frequency taking the ``never'' category as the reference. Posterior
-probability that the estimated hazard of dying from stroke for the milk
-intake for frequency that higher or equal to ``1-2 times/month'' is
-smaller compared with those who chose ``never'' to their milk intake
-frequency were calculated as \(P(\text{HR} < 1)\).
+the estimated hazard ratios (HRs) as well as acceleration factors (AFs)
+were presented for each category of milk intake frequency taking the
+``never'' category as the reference. Posterior probabilities that the
+estimated hazard of dying from stroke for the milk intake for frequency
+that higher or equal to ``1-2 times/month'' is smaller compared with
+those who chose ``never'' to their milk intake frequency were calculated
+as \(P(\text{HR} < 1)\).
 
 The parametric forms of the models fitted in the Bayesian survival
-analyses include three models: 1) the crude model, 2) the age-centered
+analyses included three models: 1) the crude model, 2) the age-centered
 adjusted model, 3) and a model further adjusted for potential
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-The total follow-up was 1555073 person-years (median = 19.3 years),
-during which 2675 death from stroke was confirmed (1352 men and 1323
-women). Among these stroke mortality, 952 were hemorrhagic stroke (432
-men and 520 women), and 957 were cerebral infarction (520 men and 437
-women).
-
-\begin{table}[H]
+\begin{table}[h]
 \caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake (JACC study, 1988-2009).}
@@
 \bottomrule
-\end{tabular}
+\end{tabular}}
 \end{table}
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+The total follow-up was 1555073 person-years (median = 19.3 years),
+during which 2675 death from stroke was confirmed (1352 men and 1323
+women). Among these stroke mortality, 952 were hemorrhagic stroke (432
+men and 520 women), and 957 were cerebral infarction (520 men and 437
+women).
 
@@
 
-\caption{\label{tab:tab2}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).}
+\caption{\label{tab:tab2}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke types according to the frequency of milk intake in men (JACC study, 1988-2009).}
 \centering
-\fontsize{8}{10}\selectfont
+\fontsize{6}{8}\selectfont
+\resizebox*{\textwidth}{\dimexpr\textheight-\lineskip\relax}{%
 \begin{tabular}[t]{lccccc}
 \toprule
-  & Never & 1-2 times/Month & 1-2 times/Week & 3-4 times/Week & Almost Daily\\
+\textbf{ } & \textbf{Never} & \textbf{1-2 times/Month} & \textbf{1-2 times/Week} & \textbf{3-4 times/Week} & \textbf{Almost Daily}\\
 \midrule
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}MeanHR (SD) & 1 & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
+\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.07) & 0.83 (0.05) & 0.85 (0.05) & 0.93 (0.04)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.06) & (0.73, 0.94) & (0.74, 0.96) & (0.85, 1.02)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
-\hspace{1em}MCSE & - & 0.0022 & 0.0019 & 0.0022 & 0.0018\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\
+\hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.50\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
-\hspace{1em}MCSE & - & 0.0027 & 0.0022 & 0.0021 & 0.0016\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.06) & 0.90 (0.05) & 0.91 (0.05) & 0.85 (0.04)\\
+\hspace{1em}95\% CrI & - & (0.87, 1.11) & (0.81, 1.00) & (0.82, 1.01) & (0.78, 0.92)\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
+\hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.30\% & 96.10\% & 100.00\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 & 1.00 (0.07) & 0.92 (0.06) & 0.94 (0.06) & 0.88 (0.05)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.14) & (0.82, 1.03) & (0.84, 1.05) & (0.81, 0.96)\\
 \hspace{1em}MeanHR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
-\hspace{1em}MCSE & - & 0.0041 & 0.0036 & 0.0038 & 0.0031\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\
+\hspace{1em}Pr(HR < 1) & - & 50.60\% & 93.70\% & 89.60\% & 99.00\%\\
 \hline
-Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
+\rowcolor{gray!6}  Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
-\hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0066 & 0.0057 & 0.0057 & 0.0062\\
-\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\
+\hspace{1em}Mean AF (SD) & 1 & 1.03 (0.17) & 0.85 (0.12) & 0.87 (0.13) & 0.98 (0.11)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.74, 1.38) & (0.63, 1.12) & (0.65, 1.14) & (0.78, 1.22)\\
+\hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
+\hspace{1em}Pr(HR < 1) & - & 47.20\% & 88.40\% & 86.30\% & 63.10\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 1.08 (0.17) & 0.91 (0.13) & 0.92 (0.13) & 0.90 (0.10)\\
+\hspace{1em}95\% CrI & - & (0.80, 1.45) & (0.70, 1.20) & (0.71, 1.19) & (0.74, 1.11)\\
 \rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
 \hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0091 & 0.0067 & 0.0073 & 0.0076\\
-\hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.60\% & 79.70\% & 76.60\% & 87.60\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
-\hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0093 & 0.0075 & 0.0098 & 0.0082\\
-\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\
+\hspace{1em}Mean AF (SD) & 1 & 1.11 (0.18) & 0.93 (0.15) & 0.96 (0.16) & 0.96 (0.13)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.58) & (0.70, 1.25) & (0.71, 1.34) & (0.76, 1.25)\\
+\hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
+\hspace{1em}Pr(HR < 1) & - & 28.80\% & 72.40\% & 64.40\% & 69.30\%\\
 \hline
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.76 (0.09) & 0.71 (0.07) & 0.74 (0.08) & 0.79 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.59, 0.94) & (0.58, 0.86) & (0.61, 0.89) & (0.68, 0.93)\\
 \hspace{1em}MeanHR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
-\hspace{1em}MCSE & - & 0.0042 & 0.0037 & 0.0036 & 0.0038\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\
+\hspace{1em}Pr(HR < 1) & - & 99.10\% & 99.90\% & 99.70\% & 99.50\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
-\hspace{1em}MCSE & - & 0.0045 & 0.0035 & 0.0041 & 0.0029\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.83 (0.08) & 0.79 (0.07) & 0.82 (0.07) & 0.74 (0.05)\\
+\hspace{1em}95\% CrI & - & (0.68, 1.01) & (0.67, 0.93) & (0.69, 0.96) & (0.66, 0.84)\\
+\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
+\hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.90\% & 99.80\% & 98.90\% & 100.00\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.84 (0.09) & 0.80 (0.08) & 0.83 (0.08) & 0.75 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.67, 1.02) & (0.67, 0.95) & (0.69, 0.99) & (0.66, 0.85)\\
 \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
-\hspace{1em}MCSE & - & 0.0049 & 0.0047 & 0.0061 & 0.0052\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\
+\hspace{1em}Pr(HR < 1) & - & 96.10\% & 99.10\% & 97.50\% & 99.80\%\\
 \bottomrule
@@
 \multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 \centering
-\fontsize{8}{10}\selectfont
+\fontsize{7}{9}\selectfont
 \begin{tabular}[t]{lccccc}
 \toprule
-  & Never & 1-2 times/Month & 1-2 times/Week & 3-4 times/Week & Almost Daily\\
+\textbf{ } & \textbf{Never} & \textbf{1-2 times/Month} & \textbf{1-2 times/Week} & \textbf{3-4 times/Week} & \textbf{Almost Daily}\\
 \midrule
@@
 JAGS & Just Another Gibbs Samplers \\
+AFT & accelerated failure time \\
 HR & hazard ratio \\
+AF & acceleration factor \\
 sd & standard deviation \\

### 2020-07-09 Paperfolder/Paperfolder.Rmd
table 2 100% tab3 60% added AF

@@
 For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.
-Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard.
-Accelerated failure time models are among these convenient tools that would avoid frequently unmet assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
+Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met.
+Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
 
@@
 
+<!-- - summary of the finding -->
+
 In the JACC study cohort, we observed that
+
+-
 
@@
 \fontsize{6}{8}\selectfont
-\resizebox*{\textwidth}{\dimexpr\textheight-\lineskip\relax}{%
+\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
 \begin{tabular}[t]{lccccc}
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
-\hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.50\%\\
+\hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\
 \addlinespace[0.3em]
@@
 \hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.30\% & 96.10\% & 100.00\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\
 \addlinespace[0.3em]
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
-\hspace{1em}Pr(HR < 1) & - & 50.60\% & 93.70\% & 89.60\% & 99.00\%\\
+\hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\
 \hline
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
-\hspace{1em}Pr(HR < 1) & - & 47.20\% & 88.40\% & 86.30\% & 63.10\%\\
+\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\
 \addlinespace[0.3em]
@@
 \hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.60\% & 79.70\% & 76.60\% & 87.60\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\
 \addlinespace[0.3em]
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
-\hspace{1em}Pr(HR < 1) & - & 28.80\% & 72.40\% & 64.40\% & 69.30\%\\
+\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\
 \hline
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
-\hspace{1em}Pr(HR < 1) & - & 99.10\% & 99.90\% & 99.70\% & 99.50\%\\
+\hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\
 \addlinespace[0.3em]
@@
 \hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.90\% & 99.80\% & 98.90\% & 100.00\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\
 \addlinespace[0.3em]
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
-\hspace{1em}Pr(HR < 1) & - & 96.10\% & 99.10\% & 97.50\% & 99.80\%\\
+\hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\
 \bottomrule
@@
 
-```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
+```{r tab3, echo=FALSE, eval=FALSE, message=FALSE}
 library(knitr)
@@
 
-kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
+kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
     # collapse_rows(columns = 1, valign = "top") %>% 
   row_spec(0, bold = T) %>% 
-  pack_rows("Model 0", 4, 7) %>%
-  pack_rows("Model 1", 8, 11) %>%
-  pack_rows("Model 2", 12, 15) %>%
-    row_spec(15,  hline_after = TRUE) %>%
-    pack_rows("Model 0", 17, 20) %>%
-  pack_rows("Model 1", 21, 24) %>%
-  pack_rows("Model 2", 25, 28) %>%
-      row_spec(28,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 30, 33) %>%
-  pack_rows("Model 1", 34, 37) %>%
-  pack_rows("Model 2", 38, 41) %>%
+    # collapse_rows(columns = 1, valign = "top") %>% 
+    pack_rows("Model 0", 4, 8) %>%
+  pack_rows("Model 1", 9, 13) %>%
+  pack_rows("Model 2", 14, 18) %>%
+  row_spec(18,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 20, 24) %>%
+  pack_rows("Model 1", 25, 29) %>%
+  pack_rows("Model 2", 30, 34) %>%
+  row_spec(34,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 36, 40) %>%
+  pack_rows("Model 1", 41, 45) %>%
+  pack_rows("Model 2", 46, 50) %>%
 kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
@@
 ```
+
+\begin{table}[!h]
+
+\caption{\label{tab:tab3}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}
+\centering
+\fontsize{7}{9}\selectfont
+\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
+\begin{tabular}[t]{lccccc}
+\toprule
+\textbf{ } & \textbf{Never} & \textbf{1-2 times/Month} & \textbf{1-2 times/Week} & \textbf{3-4 times/Week} & \textbf{Almost Daily}\\
+\midrule
+\rowcolor{gray!6}  Person-year & 173222 & 59904 & 129233 & 139919 & 418925\\
+N & 10407 & 3640 & 7590 & 8108 & 25254\\
+\rowcolor{gray!6}  Total Stroke & 300 & 84 & 182 & 172 & 585\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.88 (0.07) & 0.87 (0.05) & 0.79 (0.05) & 0.88 (0.04)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.03) & (0.78, 0.98) & (0.71, 0.90) & (0.80, 0.96)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.05) & (0.68, 0.97) & (0.58, 0.85) & (0.71, 0.93)\\
+\hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.09) & 1.11 (0.08) & 1.02 (0.08) & 0.95 (0.06)\\
+\hspace{1em}95\% CrI & - & (0.85, 1.17) & (0.97, 1.26) & (0.89, 1.16) & (0.86, 1.06)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
+\hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.3\% & 6.3\% & 42.0\% & 86.8\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.12) & 1.11 (0.14) & 1.02 (0.12) & 0.97 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.85, 1.20) & (0.97, 1.30) & (0.89, 1.19) & (0.88, 1.10)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.36) & (0.96, 1.52) & (0.81, 1.31) & (0.80, 1.17)\\
+\hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
+\hline
+\rowcolor{gray!6}  Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 0.78 (0.13) & 0.98 (0.12) & 0.90 (0.11) & 0.92 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.06) & (0.76, 1.25) & (0.70, 1.13) & (0.76, 1.12)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
+\hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.88 (0.13) & 1.12 (0.13) & 1.04 (0.13) & 0.95 (0.09)\\
+\hspace{1em}95\% CrI & - & (0.63, 1.17) & (0.90, 1.41) & (0.82, 1.32) & (0.80, 1.14)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
+\hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{2} & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
+\hspace{1em}Mean HR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
+\hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\
+\hline
+\rowcolor{gray!6}  Cerebral infarction & 102 & 35 & 63 & 50 & 187\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 0}}\\
+\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.13) & 0.90 (0.09) & 0.75 (0.08) & 0.86 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.27) & (0.75, 1.10) & (0.60, 0.91) & (0.75, 0.99)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.20) & 0.85 (0.14) & 0.61 (0.11) & 0.78 (0.10)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
+\hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 1}}\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{1} & \\
+\hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
+\hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{Model 2}}\\
+\hspace{1em}Mean AF (SD) & 1 &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
+\hspace{1em}Mean HR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
+\hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
+\multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
+\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
+\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
+\end{tabular}}
+\end{table}

### 2020-07-09 Paperfolder/Paperfolder.tex
table 2 100% tab3 60% added AF

@@
 \usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 
@@
 to model the time before observing an event rather than the hazard which
-always required the assumption of a proportional hazard. Accelerated
-failure time models are among these convenient tools that would avoid
-frequently unmet assumption of proportional hazard and directly show how
-faster/slower that one individual in an exposure group might have an
-event compared to others among different exposure groups
+always required the assumption of a proportional hazard to be met.
+Accelerated failure time models are among these convenient tools that
+would avoid worrying about the assumption of proportional hazard and
+directly show how faster/slower that one individual in an exposure group
+might have an event compared to others among different exposure groups
 \citep{Wei1992}.
@@
 
-\caption{\label{tab:tab3}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}
+\caption{\label{tab:tab3}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}
 \centering
 \fontsize{7}{9}\selectfont
+\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
 \begin{tabular}[t]{lccccc}
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}MeanHR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
+\hspace{1em}Mean AF (SD) & 1 & 0.88 (0.07) & 0.87 (0.05) & 0.79 (0.05) & 0.88 (0.04)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.03) & (0.78, 0.98) & (0.71, 0.90) & (0.80, 0.96)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.05) & (0.68, 0.97) & (0.58, 0.85) & (0.71, 0.93)\\
-\hspace{1em}MCSE & - & 0.0029 & 0.0022 & 0.0021 & 0.0023\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
+\hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
-\hspace{1em}MCSE & - & 0.0038 & 0.0045 & 0.0042 & 0.0034\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.09) & 1.11 (0.08) & 1.02 (0.08) & 0.95 (0.06)\\
+\hspace{1em}95\% CrI & - & (0.85, 1.17) & (0.97, 1.26) & (0.89, 1.16) & (0.86, 1.06)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
+\hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
 \rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.3\% & 6.3\% & 42.0\% & 86.8\%\\
@@
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
+\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.12) & 1.11 (0.14) & 1.02 (0.12) & 0.97 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.85, 1.20) & (0.97, 1.30) & (0.89, 1.19) & (0.88, 1.10)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.36) & (0.96, 1.52) & (0.81, 1.31) & (0.80, 1.17)\\
-\hspace{1em}MCSE & - & 0.0083 & 0.0096 & 0.0079 & 0.0075\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
+\hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
 \hline
-Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
+\rowcolor{gray!6}  Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
-\hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0058 & 0.0071 & 0.0061 & 0.0065\\
+\hspace{1em}Mean AF (SD) & 1 & 0.78 (0.13) & 0.98 (0.12) & 0.90 (0.11) & 0.92 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.06) & (0.76, 1.25) & (0.70, 1.13) & (0.76, 1.12)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
 \hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\
@@
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.88 (0.13) & 1.12 (0.13) & 1.04 (0.13) & 0.95 (0.09)\\
+\hspace{1em}95\% CrI & - & (0.63, 1.17) & (0.90, 1.41) & (0.82, 1.32) & (0.80, 1.14)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
 \hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0065 & 0.0089 & 0.0084 & 0.0069\\
-\hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
-\hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
-\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0051 & 0.0067 & 0.0039 & 0.0047\\
+\hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{2} & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
+\hspace{1em}Mean HR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
 \hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\
@@
 \multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.13) & 0.82 (0.14) & 0.59 (0.14) & 0.76 (0.16)\\
+\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.13) & 0.90 (0.09) & 0.75 (0.08) & 0.86 (0.06)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.27) & (0.75, 1.10) & (0.60, 0.91) & (0.75, 0.99)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.20) & 0.85 (0.14) & 0.61 (0.11) & 0.78 (0.10)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
-\hspace{1em}MCSE & - & 0.0087 & 0.0079 & 0.0064 & 0.0071\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
+\hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\hspace{1em}MeanHR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
-\hspace{1em}MCSE & - & 0.0071 & 0.0072 & 0.0095 & 0.0054\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{1} & \\
+\hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
+\hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
 \rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\
@@
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}MeanHR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
+\hspace{1em}Mean AF (SD) & 1 &  &  &  & \\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
+\hspace{1em}Mean HR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
-\hspace{1em}MCSE & - & 0.0055 & 0.0057 & 0.0067 & 0.0047\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\
+\hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\
 \bottomrule

### 2020-07-09 Paperfolder/Paperfolder.Rmd
updated AF description in results section

@@
 As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
-Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.
+Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sex.
 
 Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women).
-Compared to those who never had milk, both men and women had lower hazard of dying from total stroke in crude models.
-Chances that the posterior HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women.
-However, lower hazard was observed to remain after age or multivariable adjustment only in men.
-Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
-Daily female milk consumers had posterior HRs that was distributed with mean (sd) of 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be lower than 1.
+Compared to those who never had milk, both men and women had lower hazard and slower speed of dying from total stroke in crude models.
+Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95% CrI: 0.80, 0.96) compared with non-consumers.
+Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women.
+However, lower hazard and speed was observed to remain after age or multivariable adjustment only in daily male milk consumers.
+Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
+Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be smaller than 1.
 
-Posterior distributions of HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
-In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 26%-37% lower hazard of dying from cerebral infarction compared with men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
-We were more than 95.7% sure that these posterior HRs could be lower than 1.
-No associations were observed between milk intake and hazard of cerebral infarction among women.
+Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
+In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared against men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
+We were more than 97.5% sure that these posterior HRs were distributed below the null value.
+No apparent associations were observed between milk intake and hazard of cerebral infarction among women.
 

### 2020-07-09 Paperfolder/Paperfolder.tex
updated AF description in results section

@@
 vegetable, fruit as well as coffee, and more likely to join exercise
-more than 1 hour/week among either sex.
+more than 1 hour/week among both sex.
 
@@
 \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
-milk, both men and women had lower hazard of dying from total stroke in
-crude models. Chances that the posterior HRs were estimated to be lower
-than 1 for those who had at least 1-2 times/month was higher than 86.5\%
-in men and more than 94.6\% in women. However, lower hazard was observed
-to remain after age or multivariable adjustment only in men.
-Specifically, the mean (sd; 95\% CrI) of posterior
-multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd
-= 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller
-than the null value (=1). Daily female milk consumers had posterior HRs
-that was distributed with mean (sd) of 0.95 (sd = 0.12; 95\% CrI: 0.80,
-1.17) which had 78.0\% of chance that their HRs could be lower than 1.
+milk, both men and women had lower hazard and slower speed of dying from
+total stroke in crude models. Velocities that milk consumers dying from
+stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
+0.05; 95\% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95\% CrI: 0.80, 0.96)
+compared with non-consumers. Chances that the posterior crude HRs were
+estimated to be lower than 1 for those who had at least 1-2 times/month
+was higher than 86.5\% in men and more than 94.6\% in women. However,
+lower hazard and speed was observed to remain after age or multivariable
+adjustment only in daily male milk consumers. Specifically, the mean
+(sd; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
+male consumers of milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and
+0.80 (sd = 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
+be smaller than the null value (=1). Daily female milk consumers had
+posterior AFs and HRs that was distributed with means of 0.97 (sd =
+0.09; 95\% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17)
+which had 78.0\% of chance that their HRs could be smaller than 1.
 
-Posterior distributions of HRs for mortality from hemorrhagic stroke
-were found to contain the null value for either men or women among all
-fitted models. In contrast, men who had milk intake frequency higher
-than 1-2 times/week were found to be associated with averagely 26\%-37\%
-lower hazard of dying from cerebral infarction compared with men who
-never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were
-more than 95.7\% sure that these posterior HRs could be lower than 1. No
+Posterior distributions of AFs and HRs for mortality from hemorrhagic
+stroke were found to contain the null value for either men or women
+among all fitted models. In contrast, men who had milk intake frequency
+higher than 1-2 times/week were found to be associated with averagely
+17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
+cerebral infarction compared against men who never drank milk (Model 2
+in \textbf{Table \ref{tab:tab2}}). We were more than 97.5\% sure that
+these posterior HRs were distributed below the null value. No apparent
 associations were observed between milk intake and hazard of cerebral
@@
 In the JACC study cohort, we observed that
+
+\begin{itemize}
+\tightlist
+\item
+\end{itemize}
 

### 2020-07-09 Paperfolder/Paperfolder.Rmd
updated discussion started

@@
 If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process.
-A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a stroke event from happening after controlling for the other potential confounders.
+A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a mortality from stroke event from happening after controlling for the other potential confounders.
 
@@
 
-In the JACC study cohort, we observed that
+In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
+Our evidence also suggested that stroke events were found to be delayed from happening among Japanese male daily milk consumers compared with non-consumers.
 
--
+<!-- - comparison with previous meta-analysis -->
+These findings are in line with our previous report [@wang_milk_2015] with further additional and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event.
+A recent meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
+<!-- - potential biological reasons -->
+
+<!-- - strength and limitation of current study -->
 

### 2020-07-09 Paperfolder/Paperfolder.tex
updated discussion started

@@
 provided estimates about whether drinking milk could delay or slow down
-the speed towards a stroke event from happening after controlling for
-the other potential confounders.
+the speed towards a mortality from stroke event from happening after
+controlling for the other potential confounders.
 
@@
 
-In the JACC study cohort, we observed that
+In the JACC study cohort, our analysis showed that men in Japan who
+consumed milk almost daily had lower hazard of dying from stroke
+especially from cerebral infarction. Our evidence also suggested that
+stroke events were found to be delayed from happening among Japanese
+male daily milk consumers compared with non-consumers.
 
-\begin{itemize}
-\tightlist
-\item
-\end{itemize}
+These findings are in line with our previous report
+\citep{wang_milk_2015} with further additional and more forthright
+evidence about whether and how certain we could hold about daily
+consumption of milk is contributing to a postponed stroke (mostly
+cerebral infarction) mortality event. A recent meta-analysis of 18
+prospective cohort studies had shown a similar negative association
+\citep{DeGoede2016} between milk consumption and risk of stroke.
 

### 2020-07-09 Paperfolder/Paperfolder.Rmd
Updated discu 30%

@@
 In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
-Our evidence also suggested that stroke events were found to be delayed from happening among Japanese male daily milk consumers compared with non-consumers.
+Our evidence also suggested that stroke mortality events were delayed from happening among Japanese male daily milk consumers compared with non-consumers.
 
 <!-- - comparison with previous meta-analysis -->
-These findings are in line with our previous report [@wang_milk_2015] with further additional and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event.
-A recent meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
+These findings are in line with our previous report [@wang_milk_2015], we further updated with more comprehensive and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event.
+A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
+The same meta-analysis however also found a slightly higher risk of stroke per 200 g/day whole milk intake from five cohort studies that were conducted on European or American population [@goldbohm2011dairy; @Iso1999].
 <!-- - potential biological reasons -->

### 2020-07-09 Paperfolder/Paperfolder.tex
Updated discu 30%

@@
 especially from cerebral infarction. Our evidence also suggested that
-stroke events were found to be delayed from happening among Japanese
-male daily milk consumers compared with non-consumers.
+stroke mortality events were delayed from happening among Japanese male
+daily milk consumers compared with non-consumers.
 
 These findings are in line with our previous report
-\citep{wang_milk_2015} with further additional and more forthright
-evidence about whether and how certain we could hold about daily
-consumption of milk is contributing to a postponed stroke (mostly
-cerebral infarction) mortality event. A recent meta-analysis of 18
-prospective cohort studies had shown a similar negative association
-\citep{DeGoede2016} between milk consumption and risk of stroke.
+\citep{wang_milk_2015}, we further updated with more comprehensive and
+more forthright evidence about whether and how certain we could hold
+about daily consumption of milk is contributing to a postponed stroke
+(mostly cerebral infarction) mortality event. A recent dose-response
+meta-analysis of 18 prospective cohort studies had also shown a similar
+negative association \citep{DeGoede2016} between milk consumption and
+risk of stroke. The same meta-analysis however also found a slightly
+higher risk of stroke per 200 g/day whole milk intake from five cohort
+studies that were conducted on European or American population
+\citep{goldbohm2011dairy, Iso1999}.
 

### 2020-07-10 AnalysisScript/ModelsJAGSfemHemoStroke.R
updated hemo M2 in women

@@ -444,7 +444,8 @@ jagsfit <- jags.parallel(data=MILKdataFEM,  parameters.to.save = M2.params,
                          n.iter=100000, n.burnin=(3000/2), n.chains = 4,
                          model.file=M2hemo.weibull.model)
 end.time <- Sys.time()
-end.time - start.time 
+end.time - start.time #Time difference of 3.507339 days
+
 M2FEMHemoStroke_20200704 <- jagsfit
 print(M2FEMHemoStroke_20200704)
 summary(mcmcplots::as.mcmc.rjags(M2FEMHemoStroke_20200704))
@@ -453,4 +454,70 @@ summary(mcmcplots::as.mcmc.rjags(M2FEMHemoStroke_20200704))
 save(M0FEMHemoStroke_20200704, 
      M1FEMHemoStroke_20200704,
      M2FEMHemoStroke_20200704, file = "IscheStrokeMen.RData")
+
+# Inference for Bugs model at "M2hemo.weibull.model", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 1500 discarded), n.thin = 98
+# n.sims = 4020 iterations saved
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       0.931   0.236    0.642    0.807    0.902    1.010    1.335 1.030   360
+# AFT[3]       1.226   0.385    0.926    1.073    1.160    1.264    1.983 1.061   710
+# AFT[4]       1.138   0.330    0.868    1.001    1.081    1.180    1.826 1.072   530
+# AFT[5]       1.035   0.248    0.831    0.935    0.993    1.059    1.547 1.080   390
+# HR[2]        0.899   0.223    0.553    0.747    0.871    1.013    1.396 1.008   560
+# HR[3]        1.264   0.260    0.902    1.101    1.223    1.370    1.903 1.009  1100
+# HR[4]        1.150   0.234    0.827    1.001    1.112    1.251    1.741 1.016   560
+# HR[5]        1.021   0.186    0.779    0.913    0.991    1.080    1.509 1.021   560
+# p.crit[2]    0.732   0.443    0.000    0.000    1.000    1.000    1.000 1.003  1200
+# p.crit[3]    0.095   0.294    0.000    0.000    0.000    0.000    1.000 1.005  1100
[…]

### 2020-07-10 AnalysisScript/ModelsJAGSfemCerebralInfar.R
updated M1 ischem fem

@@ -222,8 +222,7 @@ jagsfit <- jags.parallel(data=MILKdatafem,  parameters.to.save = age.params,
                          n.iter=100000, n.burnin=(5000/2), n.chains = 4,
                          model.file=AgeIsche.weibull.model)
 end.time <- Sys.time()
-end.time - start.time # 
-
+end.time - start.time # Time difference of 1.136057 days
 
 M1femIscheStroke_20200707 <- jagsfit
 print(M1femIscheStroke_20200707)
@@ -231,7 +230,70 @@ summary(mcmcplots::as.mcmc.rjags(M1femIscheStroke_20200707))
 save(M0femIscheStroke_20200707, 
      M1femIscheStroke_20200707, file = "IscheStrokefem.RData")
 
-
+# Inference for Bugs model at "AgeIsche.weibull.model", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 2500 discarded), n.thin = 97
+# n.sims = 4020 iterations saved
+           # mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       1.214   0.321    0.945    1.074    1.151    1.241    2.077 1.099    97
+# AFT[3]       1.155   0.302    0.930    1.034    1.092    1.171    1.945 1.119    78
+# AFT[4]       0.982   0.185    0.792    0.890    0.949    1.017    1.482 1.100    84
+# AFT[5]       0.968   0.143    0.835    0.898    0.939    0.987    1.425 1.091    85
+# HR[2]        1.373   0.326    0.894    1.154    1.322    1.524    2.176 1.015   300
+# HR[3]        1.247   0.277    0.866    1.069    1.193    1.360    1.954 1.028   130
+# HR[4]        0.938   0.217    0.632    0.794    0.902    1.034    1.519 1.028   130
+# HR[5]        0.915   0.172    0.694    0.807    0.882    0.975    1.401 1.036   120
+# p.crit[2]    0.085   0.279    0.000    0.000    0.000    0.000    1.000 1.001  4000
+# p.crit[3]    0.142   0.349    0.000    0.000    0.000    0.000    1.000 1.003  1500
+# p.crit[4]    0.701   0.458    0.000    0.000    1.000    1.000    1.000 1.011   270
+# p.crit[5]    0.794   0.404    0.000    1.000    1.000    1.000    1.000 1.015   240
[…]

### 2020-07-12 AnalysisScript/ModelsJAGSfemCerebralInfar.R
updated M2ischem fem

@@ -440,7 +440,7 @@ jagsfit <- jags.parallel(data=MILKdatafem,  parameters.to.save = M2.params,
                          n.iter=100000, n.burnin=(3000/2), n.chains = 4,
                          model.file=M2Isch.weibull.model)
 end.time <- Sys.time()
-end.time - start.time #
+end.time - start.time # Time difference of 2.856959 days
 
 
 M2femIscheStroke_20200707 <- jagsfit
@@ -450,3 +450,68 @@ save(M0femIscheStroke_20200707,
      M1femIscheStroke_20200707, 
      M2femIscheStroke_20200707, file = "IscheStrokefem.RData")
 
+# Inference for Bugs model at "M2Isch.weibull.model", fit using jags,
+# 4 chains, each with 1e+05 iterations (first 1500 discarded), n.thin = 98
+# n.sims = 4020 iterations saved
+# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+# AFT[2]       1.191   0.191    0.944    1.085    1.163    1.253    1.616 1.069   100
+# AFT[3]       1.115   0.149    0.921    1.030    1.095    1.165    1.497 1.070    92
+# AFT[4]       0.955   0.118    0.780    0.887    0.943    1.007    1.208 1.025   300
+# AFT[5]       0.970   0.092    0.831    0.916    0.963    1.011    1.182 1.030   180
+# HR[2]        1.376   0.288    0.893    1.175    1.347    1.545    2.021 1.009   310
+# HR[3]        1.214   0.217    0.851    1.060    1.197    1.342    1.703 1.012   220
+# HR[4]        0.912   0.182    0.615    0.789    0.890    1.012    1.335 1.010   310
+# HR[5]        0.938   0.141    0.699    0.840    0.928    1.021    1.252 1.012   230
+# p.crit[2]    0.073   0.260    0.000    0.000    0.000    0.000    1.000 1.004  2000
+# p.crit[3]    0.156   0.363    0.000    0.000    0.000    0.000    1.000 1.003  1200
+# p.crit[4]    0.728   0.445    0.000    0.000    1.000    1.000    1.000 1.007   390
+# p.crit[5]    0.700   0.458    0.000    0.000    1.000    1.000    1.000 1.007   420
+# deviance  5582.978  84.023 5485.273 5538.494 5568.945 5603.275 5835.761 1.121    85
[…]

### 2020-07-14 AnalysisScript/ModelsJAGSfemCerebralInfar.R
updated tables fixed

@@ -453,7 +453,7 @@ save(M0femIscheStroke_20200707,
 # Inference for Bugs model at "M2Isch.weibull.model", fit using jags,
 # 4 chains, each with 1e+05 iterations (first 1500 discarded), n.thin = 98
 # n.sims = 4020 iterations saved
-# mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
+#            mu.vect sd.vect     2.5%      25%      50%      75%    97.5%  Rhat n.eff
 # AFT[2]       1.191   0.191    0.944    1.085    1.163    1.253    1.616 1.069   100
 # AFT[3]       1.115   0.149    0.921    1.030    1.095    1.165    1.497 1.070    92
 # AFT[4]       0.955   0.118    0.780    0.887    0.943    1.007    1.208 1.025   300
@@ -484,7 +484,7 @@ save(M0femIscheStroke_20200707,
 # 1. Empirical mean and standard deviation for each variable,
 # plus standard error of the mean:
 #   
-#   Mean       SD Naive SE Time-series SE
+#                Mean       SD Naive SE Time-series SE
 # AFT[2]    1.191e+00  0.19055 0.003005       0.018679
 # AFT[3]    1.115e+00  0.14923 0.002354       0.018897
 # AFT[4]    9.549e-01  0.11846 0.001868       0.010140
@@ -501,7 +501,7 @@ save(M0femIscheStroke_20200707,
 # 
 # 2. Quantiles for each variable:
 #   
-#   2.5%       25%       50%      75%    97.5%
+#                2.5%       25%       50%      75%    97.5%
 # AFT[2]       0.9437    1.0847    1.1633    1.253    1.616
 # AFT[3]       0.9212    1.0301    1.0946    1.165    1.497
 # AFT[4]       0.7797    0.8875    0.9429    1.007    1.208

### 2020-07-14 Paperfolder/Paperfolder.Rmd
updated tables fixed
Updated tables and results done

@@
 
-Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women).
-Compared to those who never had milk, both men and women had lower hazard and slower speed of dying from total stroke in crude models.
-Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95% CrI: 0.80, 0.96) compared with non-consumers.
-Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women.
-However, lower hazard and speed was observed to remain after age or multivariable adjustment only in daily male milk consumers.
+Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women).
+Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models.
+Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers.
+Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women.
+However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers.
 Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
-Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be smaller than 1.
+Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
 
 Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
-In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared against men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
-We were more than 97.5% sure that these posterior HRs were distributed below the null value.
-No apparent associations were observed between milk intake and hazard of cerebral infarction among women.
+In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared to men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
+Probability that the posterior HRs distributed below the null value was greater or equal to 97.5%.
+No evidence was found about the associations between milk intake and hazard of cerebral infarction mortality among women.
 
@@
 In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
-Our evidence also suggested that stroke mortality events were delayed from happening among Japanese male daily milk consumers compared with non-consumers.
+Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
 
 <!-- - comparison with previous meta-analysis -->
-These findings are in line with our previous report [@wang_milk_2015], we further updated with more comprehensive and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event.
+These findings are in line with our previous report [@wang_milk_2015].
+Moreover, we further updated with more comprehensive and more straightforward evidence about whether and how certain the evidence had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
 A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
@@
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{2} & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
-\hspace{1em}Mean HR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
-\hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\
+\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.24) & 1.23 (0.38) & 1.14 (0.33) & 1.04 (0.25)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.33) & (0.93, 1.98) & (0.87, 1.83) & (0.83, 1.55)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.22) & 1.26 (0.26) & 1.15 (0.23) & 1.02 (0.19)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.39) & (0.90, 1.90) & (0.83, 1.74) & (0.78, 1.51)\\
+\hspace{1em}Pr(HR < 1) & - & 73.2\% & 9.5\% & 24.8\% & 53.3\%\\
 \hline
@@
 \multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{1} & \\
-\hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
-\hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\
+\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 1.21 (0.32) & 1.16 (0.30) & 0.98 (0.19) & 0.97 (0.14)\\
+\hspace{1em}95\% CrI & - & (0.95, 2.08) & (0.93, 1.95) & (0.79, 1.48) & (0.84, 1.43)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.37 (0.33) & 1.25 (0.28) & 0.94 (0.22) & 0.92 (0.17)\\
+\hspace{1em}95\% CrI & - & (0.89, 2.18) & (0.87, 1.95) & (0.63, 1.52) & (0.69, 1.40)\\
+\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 8.5\% & 14.2\% & 70.1\% & 79.4\%\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 &  &  &  & \\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
-\hspace{1em}Mean HR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
-\hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\
+\hspace{1em}Mean AF (SD) & 1 & 1.19 (0.19) & 1.12 (0.15) & 0.96 (0.12) & 0.97 (0.09)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.94, 1.62) & (0.92, 1.49) & (0.78, 1.21) & (0.83, 1.18)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.38 (0.29) & 1.21 (0.22) & 0.91 (0.18) & 0.94 (0.14)\\
+\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.89, 2.02) & (0.85, 1.70) & (0.62, 1.34) & (0.69, 1.25)\\
+\hspace{1em}Pr(HR < 1) & - & 7.3\% & 15.6\% & 72.8\% & 70.0\%\\
 \bottomrule

### 2020-07-14 Paperfolder/Paperfolder.tex
updated tables fixed
Updated tables and results done

@@
 Detailed results from the Bayesian survival models (crude, age-adjusted
-and multivariable adjusted) according to the frequency of milk intake
+and multivariable-adjusted) according to the frequency of milk intake
 separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
 \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
-milk, both men and women had lower hazard and slower speed of dying from
+milk, both men and women had slower speed and lower hazard of dying from
 total stroke in crude models. Velocities that milk consumers dying from
 stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
-0.05; 95\% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95\% CrI: 0.80, 0.96)
+0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
 compared with non-consumers. Chances that the posterior crude HRs were
 estimated to be lower than 1 for those who had at least 1-2 times/month
-was higher than 86.5\% in men and more than 94.6\% in women. However,
-lower hazard and speed was observed to remain after age or multivariable
-adjustment only in daily male milk consumers. Specifically, the mean
-(sd; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
-male consumers of milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and
-0.80 (sd = 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
-be smaller than the null value (=1). Daily female milk consumers had
-posterior AFs and HRs that was distributed with means of 0.97 (sd =
-0.09; 95\% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17)
-which had 78.0\% of chance that their HRs could be smaller than 1.
+was higher than 86.5\% in men and greater than 94.6\% in women. However,
+lower hazard and delayed time-to-event was observed to remain after age
+or multivariable adjustment only among daily male milk consumers.
+Specifically, the mean (sd; 95\% CrI) of posterior
+multivariable-adjusted AF and HR for daily male consumers of milk were
+0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
+0.69, 0.93) with a probability of 99.0\% to be smaller than the null
+value (=1). Daily female milk consumers had posterior AFs and HRs that
+was distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10) and
+0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of chance
+that their HRs could be smaller than 1.
 
@@
 17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
-cerebral infarction compared against men who never drank milk (Model 2
-in \textbf{Table \ref{tab:tab2}}). We were more than 97.5\% sure that
-these posterior HRs were distributed below the null value. No apparent
-associations were observed between milk intake and hazard of cerebral
-infarction among women.
+cerebral infarction compared to men who never drank milk (Model 2 in
+\textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs
+distributed below the null value was greater or equal to 97.5\%. No
+evidence was found about the associations between milk intake and hazard
+of cerebral infarction mortality among women.
 
@@
 especially from cerebral infarction. Our evidence also suggested that
-stroke mortality events were delayed from happening among Japanese male
-daily milk consumers compared with non-consumers.
+stroke mortality events were delayed among Japanese male daily milk
+consumers compared with non-consumers.
 
 These findings are in line with our previous report
-\citep{wang_milk_2015}, we further updated with more comprehensive and
-more forthright evidence about whether and how certain we could hold
-about daily consumption of milk is contributing to a postponed stroke
-(mostly cerebral infarction) mortality event. A recent dose-response
-meta-analysis of 18 prospective cohort studies had also shown a similar
-negative association \citep{DeGoede2016} between milk consumption and
-risk of stroke. The same meta-analysis however also found a slightly
-higher risk of stroke per 200 g/day whole milk intake from five cohort
-studies that were conducted on European or American population
-\citep{goldbohm2011dairy, Iso1999}.
+\citep{wang_milk_2015}. Moreover, we further updated with more
+comprehensive and more straightforward evidence about whether and how
+certain the evidence had shown about daily consumption of milk is
+contributing to a postponed stroke (mostly cerebral infarction)
+mortality event among Japanese male daily milk drinker. A recent
+dose-response meta-analysis of 18 prospective cohort studies had also
+shown a similar negative association \citep{DeGoede2016} between milk
+consumption and risk of stroke. The same meta-analysis however also
+found a slightly higher risk of stroke per 200 g/day whole milk intake
+from five cohort studies that were conducted on European or American
+population \citep{goldbohm2011dairy, Iso1999}.
 

### 2020-07-14 Paperfolder/Paperfolder.Rmd
Updated almost everything except abstract

@@
 type: article
-status: submit
+status: To be submitted
 bibliography: milk.bib
@@
 abstract: |
-  A single paragraph of about 200 words maximum. For research articles, 
-  abstracts should give a pertinent overview of the work. We strongly encourage
-  authors to use the following style of structured abstracts, but without 
-  headings: 1) Background: Place the question addressed in a broad context and
-  highlight the purpose of the study; 2) Methods: Describe briefly the main
-  methods or treatments applied; 3) Results: Summarize the article's main 
-  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
-  The abstract should be an objective representation of the article, it must not 
-  contain results which are not presented and substantiated in the main text and 
-  should not exaggerate the main conclusions.
+  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used 
 keywords: |
@@
 acknowledgement: |
-  All sources of funding of the study should be disclosed. Please clearly 
-  indicate grants that you have received in support of your research work. 
-  Clearly state if you received funds for covering the costs to publish in open 
-  access.
+  The authors would like to express their sincere appreciate to Kunio Aoki and Yoshiyuki Ohno, Professors Emeritus at Nagoya University School of Medicine and former chairpersons of the JACC Study.
+The whole member of JACC Study Group can be found at https://publichealth.med.hokudai.ac.jp/jacc/index.html.
+The JACC Study has been supported by Grants-in-Aid for Scientific Research from the Ministry of Education, Culture, Sports, Science and Technology of Japan (MEXT, Monbu Kagaku-sho), Tokyo (grant numbers 61010076, 62010074, 63010074, 1010068, 2151065, 3151064, 4151063, 5151069, 6279102, 11181101, 17015022, 18014011, 20014026, 20390156, 26293138, and 16H06277), and Grants-in-Aid from the Ministry of Health, Labour and Welfare, Health and Labour Sciences Research Grants, Japan [H20-Junkankitou (Seishuu)-Ippan-013, H23-Junkankitou (Seishuu)- Ippan-005, H26-Junkankitou (Seisaku)-Ippan-001, and H29-Junkankitou (Seishuu)-Ippan-003].
 authorcontributions: |
-  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
-  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper.''
+  ``C.W.
+and H.Y.
+conceive and designed the study; C.W.
+analyzed the data; C.W.
+wrote the first draft of the paper.
+A.T.
+provided the database.
+All of the authors approved and finalized the manuscript for publication.''
 conflictsofinterest: |
@@
 
-<!-- - comparison with previous meta-analysis -->
-These findings are in line with our previous report [@wang_milk_2015].
-Moreover, we further updated with more comprehensive and more straightforward evidence about whether and how certain the evidence had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
+<!-- - comparison with previous meta-analyses -->
+These findings are in line with our previous report [@wang_milk_2015] as well as other studies conducted in East Asian populations [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@sauvaget2003intake;@Talaei_2016].
+Moreover, we have further updated with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
 A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
-The same meta-analysis however also found a slightly higher risk of stroke per 200 g/day whole milk intake from five cohort studies that were conducted on European or American population [@goldbohm2011dairy; @Iso1999].
+The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined.
+Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association].
 <!-- - potential biological reasons -->
 
+Possible reasons for a protective effect of milk consumption against stroke could be interpreted as such an association may be mediated by its content in calcium, magnesium, potassium, and other bioactive compounds, as recommended by @Iacoviello2018.
+Apart from the inorganic minerals in milk that would be helpful with health effects, recent studies on animal models also indicated key evidence that stroke-associated morbidity was delayed in stroke-prone rats who were fed with milk-protein enriched diets [@Chiba2012;@singh2016diets].
+More precisely, @Singh2020 found that whey protein and its components lactalbumin and lactoferrin improved energy balance and glycemic control against the onset of neurological deficits associated with stroke.
+Bioactive peptides from milk proteins were also responsible for limitation of thrombosis [@tokajuk2019whey] through their angiotensin convertase enzyme inhibitory potential, which might partly explain why the effect was found mainly for mortality from cerebral infarction in the current study.
+
 <!-- - strength and limitation of current study -->
+Some limitations here are worth mentioning.
+First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible.
+Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
+Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated.
+Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation.
+Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.
 
-# Conclusion
+In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk.
+Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.
 
@@
 \hspace{1em}95\% CrI & - & (0.87, 1.11) & (0.81, 1.00) & (0.82, 1.01) & (0.78, 0.92)\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
 \hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.14) & (0.82, 1.03) & (0.84, 1.05) & (0.81, 0.96)\\
-\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.74, 1.38) & (0.63, 1.12) & (0.65, 1.14) & (0.78, 1.22)\\
-\hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
@@
 \hspace{1em}95\% CrI & - & (0.80, 1.45) & (0.70, 1.20) & (0.71, 1.19) & (0.74, 1.11)\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
 \hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.58) & (0.70, 1.25) & (0.71, 1.34) & (0.76, 1.25)\\
-\hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
+\hspace{1em}Mean HR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.59, 0.94) & (0.58, 0.86) & (0.61, 0.89) & (0.68, 0.93)\\
-\hspace{1em}MeanHR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
@@
 \hspace{1em}95\% CrI & - & (0.68, 1.01) & (0.67, 0.93) & (0.69, 0.96) & (0.66, 0.84)\\
-\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
+\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
 \hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
@@
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.67, 1.02) & (0.67, 0.95) & (0.69, 0.99) & (0.66, 0.85)\\
-\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
+\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
 \rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\

### 2020-07-14 Paperfolder/Paperfolder.tex
Updated almost everything except abstract

@@
 %=================================================================
-\documentclass[nutrients,article,submit,moreauthors,pdftex]{mdpi}
+\documentclass[nutrients,article,To be
+submitted,moreauthors,pdftex]{mdpi}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{A single paragraph of about 200 words maximum. For research
-articles, abstracts should give a pertinent overview of the work. We
-strongly encourage authors to use the following style of structured
-abstracts, but without headings: 1) Background: Place the question
-addressed in a broad context and highlight the purpose of the study; 2)
-Methods: Describe briefly the main methods or treatments applied; 3)
-Results: Summarize the article's main findings; and 4) Conclusion:
-Indicate the main conclusions or interpretations. The abstract should be
-an objective representation of the article, it must not contain results
-which are not presented and substantiated in the main text and should
-not exaggerate the main conclusions.}
+\abstract{To further examine the relationship between milk intake and
+stroke mortality among the Japanese population. We used}
 
@@
 These findings are in line with our previous report
-\citep{wang_milk_2015}. Moreover, we further updated with more
-comprehensive and more straightforward evidence about whether and how
-certain the evidence had shown about daily consumption of milk is
-contributing to a postponed stroke (mostly cerebral infarction)
-mortality event among Japanese male daily milk drinker. A recent
-dose-response meta-analysis of 18 prospective cohort studies had also
-shown a similar negative association \citep{DeGoede2016} between milk
-consumption and risk of stroke. The same meta-analysis however also
-found a slightly higher risk of stroke per 200 g/day whole milk intake
-from five cohort studies that were conducted on European or American
-population \citep{goldbohm2011dairy, Iso1999}.
+\citep{wang_milk_2015} as well as other studies conducted in East Asian
+populations
+\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
+Moreover, we have further updated with more comprehensive and
+straightforward evidence about whether and how certain the data had
+shown about daily consumption of milk is contributing to a postponed
+stroke (mostly cerebral infarction) mortality event among Japanese men.
+A recent dose-response meta-analysis of 18 prospective cohort studies
+had also shown a similar negative association \citep{DeGoede2016}
+between milk consumption and risk of stroke. The same meta-analysis also
+reported a greater reduction of risk of stroke (18\%) for East Asian
+population in contrast with the 7\% less risk in the pooled overall
+finding for all populations combined. Benefits of increased milk intake
+might be particularly noticeable in East Asian countries where strokes
+are relatively more common, and milk consumption is much lower than
+those studies conducted among European or American populations
+\citep{dehghan2018association}.
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+Possible reasons for a protective effect of milk consumption against
+stroke could be interpreted as such an association may be mediated by
+its content in calcium, magnesium, potassium, and other bioactive
+compounds, as recommended by \citet{Iacoviello2018}. Apart from the
+inorganic minerals in milk that would be helpful with health effects,
+recent studies on animal models also indicated key evidence that
+stroke-associated morbidity was delayed in stroke-prone rats who were
+fed with milk-protein enriched diets \citep{Chiba2012, singh2016diets}.
+More precisely, \citet{Singh2020} found that whey protein and its
+components lactalbumin and lactoferrin improved energy balance and
+glycemic control against the onset of neurological deficits associated
+with stroke. Bioactive peptides from milk proteins were also responsible
+for limitation of thrombosis \citep{tokajuk2019whey} through their
+angiotensin convertase enzyme inhibitory potential, which might partly
+explain why the effect was found mainly for mortality from cerebral
+infarction in the current study.
+
+Some limitations here are worth mentioning. First, although our object
+was not to answer which type of milk is protective, but if such
+information were somehow available in the JACC study database, more
+detailed comparison or stratification would have been possible. Second,
+despite reasonable validity of FFQ in the JACC study cohort was assessed
+and confirmed, measurement errors are inevitable. Therefore, we did not
+try to compute the amount of consumption by multiplying an average
+volume per occasion with the frequency of intake since the random error
+might be exaggerated and the observed associations may have attenuated.
+Strengths of our analyses included that we have transformed the research
+questions to more transparent ones that is easier for interpretation.
+Direct probabilities that daily milk intake is associated with lower
+hazard or delayed stroke mortality event were provided here after
+thorough computer simulation.
+
+In conclusion, the JACC study database has provided evidence that
+Japanese men who consumed milk daily had lower hazard of dying from
+stroke especially cerebral infarction compared with their counterparts
+who never consumed milk. Time before an event of stroke mortality
+occurred were slowed down and delayed among those who drank milk
+regularly.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{All sources of funding of the study should be
-disclosed. Please clearly indicate grants that you have received in
-support of your research work. Clearly state if you received funds for
-covering the costs to publish in open access.}
+\acknowledgments{The authors would like to express their sincere
+appreciate to Kunio Aoki and Yoshiyuki Ohno, Professors Emeritus at
+Nagoya University School of Medicine and former chairpersons of the JACC
+Study. The whole member of JACC Study Group can be found at
+\url{https://publichealth.med.hokudai.ac.jp/jacc/index.html}. The JACC
+Study has been supported by Grants-in-Aid for Scientific Research from
+the Ministry of Education, Culture, Sports, Science and Technology of
+Japan (MEXT, Monbu Kagaku-sho), Tokyo (grant numbers 61010076, 62010074,
+63010074, 1010068, 2151065, 3151064, 4151063, 5151069, 6279102,
+11181101, 17015022, 18014011, 20014026, 20390156, 26293138, and
+16H06277), and Grants-in-Aid from the Ministry of Health, Labour and
+Welfare, Health and Labour Sciences Research Grants, Japan
+{[}H20-Junkankitou (Seishuu)-Ippan-013, H23-Junkankitou (Seishuu)-
+Ippan-005, H26-Junkankitou (Seisaku)-Ippan-001, and H29-Junkankitou
+(Seishuu)-Ippan-003{]}.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{``X.X. and Y.Y. conceive and designed the
-experiments; X.X. performed the experiments; X.X. and Y.Y. analyzed the
-data; W.W. contributed reagents/materials/analysis tools; Y.Y. wrote the
-paper.'\,'}
+\authorcontributions{``C.W. and H.Y. conceive and designed the study;
+C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T.
+provided the database. All of the authors approved and finalized the
+manuscript for publication.'\,'}
 

### 2020-07-14 Paperfolder/Paperfolder.Rmd
updated almost abstract done

@@
 abstract: |
-  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used 
+  To further examine the relationship between milk intake and stroke mortality among the Japanese population.
+We used data from the Japan Collaborative Cohort Study to estimate the posterior acceleration factors as well as the hazard ratios comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline.
+These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process.
+100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed.
+Posterior probabilites that daily male consumers of milk
 keywords: |

### 2020-07-14 Paperfolder/Paperfolder.tex
updated almost abstract done

@@
 \abstract{To further examine the relationship between milk intake and
-stroke mortality among the Japanese population. We used}
+stroke mortality among the Japanese population. We used data from the
+Japan Collaborative Cohort Study to estimate the posterior acceleration
+factors as well as the hazard ratios comparing individuals with
+different milk intake frequencies against those who never consumed milk
+at the study baseline. These estimations were computed through a series
+of Bayesian survival models that employed a Markov Chain Monte Carlo
+simulation process. 100000 posterior samples for each individual were
+generated separately through four independent chains after model
+convergency were confirmed. Posterior probabilites that daily male
+consumers of milk}
 

### 2020-07-14 Paperfolder/Paperfolder.Rmd
about to send to Yatsuya

--- 2020-07-14 Paperfolder/Paperfolder.Rmd
@@
 abstract: |
-  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used 
+  The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population.
+We used data from the Japan Collaborative Cohort Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline.
+These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process.
+100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed.
+Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively.
+Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.
 keywords: |
@@
 Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met.
-Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
+Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly showing how faster/slower one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
 

### 2020-07-14 Paperfolder/Paperfolder.tex
about to send to Yatsuya

--- 2020-07-14 Paperfolder/Paperfolder.tex
@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{To further examine the relationship between milk intake and
-stroke mortality among the Japanese population. We used}
+\abstract{The aim was to further examine the relationship between milk
+intake and stroke mortality among the Japanese population. We used data
+from the Japan Collaborative Cohort Study to estimate the posterior
+acceleration factors (AF) as well as the hazard ratios (HR) comparing
+individuals with different milk intake frequencies against those who
+never consumed milk at the study baseline. These estimations were
+computed through a series of Bayesian survival models that employed a
+Markov Chain Monte Carlo simulation process. 100000 posterior samples
+for each individual were generated separately through four independent
+chains after model convergency were confirmed. Posterior probabilites
+that daily milk consumers had lower hazard or delayed mortality from
+strokes compared to non-consumers was 99.0\% and 78.0\% for men and
+women, respectively. Accordingly, the estimated posterior means of AF
+and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
+0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
+0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women.}
 
@@
 would avoid worrying about the assumption of proportional hazard and
-directly show how faster/slower that one individual in an exposure group
+directly showing how faster/slower one individual in an exposure group
 might have an event compared to others among different exposure groups

### 2020-07-14 paprfolder_docx/strokeJACC.Rmd
updated docx version

--- 2020-07-14 Paperfolder/Paperfolder.Rmd
@@
 ---
-title: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
-author:
-  - name: Chaochen Wang
-    affil: 1,*
-    orcid: 0000-0001-5533-1497
-  - name: Hiroshi Yatsuya
-    affil: 2 
-    orcid: 0000-0002-6220-9251
-  - name: Yingsong Lin
-    affil: 1
-    orcid: 0000-0003-0214-3649
-  - name: Tae Sasakabe 
-    affil: 1 
-    orcid: 0000-0002-7417-5693
-  - name: Sayo Kawai
-    affil: 1
-    orcid: 0000-0002-5156-4880
-  - name: Shogo Kikuchi
-    affil: 1
-    orcid: 0000-0001-9499-9668
-  - name: Hiroyasu Iso
-    affil: 3
-    orcid: 0000-0002-9241-7289 
-  - name: Akiko Tamakoshi
-    affil: 4
-    orcid: 0000-0002-9761-3879 
-affiliation:
-  - num: 1
-    address: |
-      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
-#    email: chaochen@wangcc.me
-  - num: 2
-    address: |
-      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
-  - num: 3
-    address: |
-      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
-  - num: 4
-    address: |
-      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
-#    email: yatsuya@gmail.com
-# firstnote to eighthnote
-# firstnote: |
-#   Current address: Updated affiliation
-# secondnote: |
-#   These authors contributed equally to this work.
-correspondence: |
-  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
-journal: nutrients
-type: article
-status: To be submitted
-bibliography: milk.bib
-# appendix: appendix.tex
-# simplesummary: |
-#  A Simple summary goes here.
-abstract: |
+title: "Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis"
+output: word_document
+bibliography: ../Paperfolder/milk.bib 
+---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
+Abstract:
+
   The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population.
@@
 Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.
-keywords: |
+
+keywords: 
   milk intake; mortality; stroke; Bayesian survival anlysis; time-to-event data; JACC study
-acknowledgement: |
-  The authors would like to express their sincere appreciate to Kunio Aoki and Yoshiyuki Ohno, Professors Emeritus at Nagoya University School of Medicine and former chairpersons of the JACC Study.
-The whole member of JACC Study Group can be found at https://publichealth.med.hokudai.ac.jp/jacc/index.html.
-The JACC Study has been supported by Grants-in-Aid for Scientific Research from the Ministry of Education, Culture, Sports, Science and Technology of Japan (MEXT, Monbu Kagaku-sho), Tokyo (grant numbers 61010076, 62010074, 63010074, 1010068, 2151065, 3151064, 4151063, 5151069, 6279102, 11181101, 17015022, 18014011, 20014026, 20390156, 26293138, and 16H06277), and Grants-in-Aid from the Ministry of Health, Labour and Welfare, Health and Labour Sciences Research Grants, Japan [H20-Junkankitou (Seishuu)-Ippan-013, H23-Junkankitou (Seishuu)- Ippan-005, H26-Junkankitou (Seisaku)-Ippan-001, and H29-Junkankitou (Seishuu)-Ippan-003].
-authorcontributions: |
-  ``C.W.
-and H.Y.
-conceive and designed the study; C.W.
-analyzed the data; C.W.
-wrote the first draft of the paper.
-A.T.
-provided the database.
-All of the authors approved and finalized the manuscript for publication.''
-conflictsofinterest: |
-  The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
-# sampleavailability: |
-#   Samples of the compounds ...... are available from the authors.
-abbreviations:
-  - short: JACC
-    long: Japan Collaborative Cohort 
-  - short: FFQ
-    long: Food Frequency Questionnaire
-  - short: MCMC
-    long: Markov Chain Monte Carlo
-  - short: JAGS
-    long: Just Another Gibbs Samplers
-  - short: AFT
-    long: accelerated failure time 
-  - short: HR
-    long: hazard ratio
-  - short: AF
-    long: acceleration factor
-  - short: sd
-    long: standard deviation
-  - short: CrI
-    long: credible interval
-header-includes:
-   - \usepackage{graphicx}
-output: rticles::mdpi_article
----
 
@@
 
-```{r tab1f, echo=FALSE, eval=FALSE}
-library(knitr)
-library(kableExtra)
-
-dt <- read.csv("tab/tab1.csv", header = T)
-names(dt) <- c("", "Never", "Drinker", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily", "P value")
-
-kable(dt, format = "latex", caption = "Sex-specific baseline characteristics according to the frequency of milk intake.", booktabs = T,linesep = "") %>%
-kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
-  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
-  # add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
-  pack_rows("Men (n = 39386)", 1, 16) %>%
-  pack_rows("Women (n = 545999)", 17, 32) #%>% 
-  # footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
-```
-
-\begin{table}[h]
-\caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake (JACC study, 1988-2009).}
-\centering
-\fontsize{8}{10}\selectfont
-\resizebox{\textwidth}{!}{%
-\begin{tabular}[t]{lccccccc}
-\toprule
-\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} & \multicolumn{1}{c}{} \\
-\cmidrule(l{3pt}r{3pt}){4-7}
- & \textbf{Never} & \textbf{Drinker} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
- &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  & \textbf{\textit{P} value}\\
-\midrule
-\rowcolor{gray!6}  \addlinespace[0.3em]
-\multicolumn{8}{l}{\textbf{Men (n = 39386)}}\\
-\hspace{1em}number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865 & \\
-\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1) & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4 & <0.001\\
-\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1 & <0.001\\
-\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.5 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7 & <0.001\\
-\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7 & 0.039\\
-\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5 & <0.001\\
-\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2 & <0.001\\
-\rowcolor{gray!6}  \addlinespace[0.3em]
-\multicolumn{8}{l}{\textbf{Women (n = 545999)}}\\
-\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254 & \\
-\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9) & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5 & <0.001\\
-\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}BMI, kg/m2 (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
-\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4 & <0.001\\
-\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4 & <0.001\\
-\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0 & <0.001\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
 # Results
@@
 
-As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
+As listed in **Table 1**, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
 Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sex.
 
-Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women).
+Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in **Table 2** (men) and **Table 3** (women).
 Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models.
@@
 Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.
-
-```{r tab2, echo=FALSE, eval=FALSE, message=FALSE}
-library(knitr)
-library(kableExtra)
-dt <- read.csv("tab/HRAFTweib.csv", header = T)
-# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
-names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
-
-kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
-  row_spec(0, bold = T) %>% 
-    # collapse_rows(columns = 1, valign = "top") %>% 
-    pack_rows("Model 0", 4, 8) %>%
-  pack_rows("Model 1", 9, 13) %>%
-  pack_rows("Model 2", 14, 18) %>%
-  row_spec(18,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 20, 24) %>%
-  pack_rows("Model 1", 25, 29) %>%
-  pack_rows("Model 2", 30, 34) %>%
-  row_spec(34,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 36, 40) %>%
-  pack_rows("Model 1", 41, 45) %>%
-  pack_rows("Model 2", 46, 50) %>%
-kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
-  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
-```
-
-\begin{table}[!h]
-
-\caption{\label{tab:tab2}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke types according to the frequency of milk intake in men (JACC study, 1988-2009).}
-\centering
-\fontsize{6}{8}\selectfont
-\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
-\begin{tabular}[t]{lccccc}
-\toprule
-\textbf{ } & \textbf{Never} & \textbf{1-2 times/Month} & \textbf{1-2 times/Week} & \textbf{3-4 times/Week} & \textbf{Almost Daily}\\
-\midrule
-\rowcolor{gray!6}  Person-year & 135704 & 56551 & 97098 & 92153 & 252364\\
-N & 8508 & 3522 & 5928 & 5563 & 15865\\
-\rowcolor{gray!6}  Total Stroke & 326 & 122 & 181 & 177 & 546\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.07) & 0.83 (0.05) & 0.85 (0.05) & 0.93 (0.04)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.06) & (0.73, 0.94) & (0.74, 0.96) & (0.85, 1.02)\\
-\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
-\hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.06) & 0.90 (0.05) & 0.91 (0.05) & 0.85 (0.04)\\
-\hspace{1em}95\% CrI & - & (0.87, 1.11) & (0.81, 1.00) & (0.82, 1.01) & (0.78, 0.92)\\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
-\hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 & 1.00 (0.07) & 0.92 (0.06) & 0.94 (0.06) & 0.88 (0.05)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.14) & (0.82, 1.03) & (0.84, 1.05) & (0.81, 0.96)\\
-\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
-\hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\
-\hline
-\rowcolor{gray!6}  Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}Mean AF (SD) & 1 & 1.03 (0.17) & 0.85 (0.12) & 0.87 (0.13) & 0.98 (0.11)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.74, 1.38) & (0.63, 1.12) & (0.65, 1.14) & (0.78, 1.22)\\
-\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
-\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 1.08 (0.17) & 0.91 (0.13) & 0.92 (0.13) & 0.90 (0.10)\\
-\hspace{1em}95\% CrI & - & (0.80, 1.45) & (0.70, 1.20) & (0.71, 1.19) & (0.74, 1.11)\\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
-\hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 & 1.11 (0.18) & 0.93 (0.15) & 0.96 (0.16) & 0.96 (0.13)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.58) & (0.70, 1.25) & (0.71, 1.34) & (0.76, 1.25)\\
-\hspace{1em}Mean HR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
-\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\
-\hline
-\rowcolor{gray!6}  Cerebral infarction & 151 & 41 & 64 & 66 & 198\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}Mean AF (SD) & 1 & 0.76 (0.09) & 0.71 (0.07) & 0.74 (0.08) & 0.79 (0.06)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.59, 0.94) & (0.58, 0.86) & (0.61, 0.89) & (0.68, 0.93)\\
-\hspace{1em}Mean HR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
-\hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.83 (0.08) & 0.79 (0.07) & 0.82 (0.07) & 0.74 (0.05)\\
-\hspace{1em}95\% CrI & - & (0.68, 1.01) & (0.67, 0.93) & (0.69, 0.96) & (0.66, 0.84)\\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
-\hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 & 0.84 (0.09) & 0.80 (0.08) & 0.83 (0.08) & 0.75 (0.06)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.67, 1.02) & (0.67, 0.95) & (0.69, 0.99) & (0.66, 0.85)\\
-\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
-\hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\
-\bottomrule
-\multicolumn{6}{l}{\textit{Note: }}\\
-\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
-\multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
-\multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
-\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
-\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
-\end{tabular}}
-\end{table}
-
-```{r tab3, echo=FALSE, eval=FALSE, message=FALSE}
-library(knitr)
-library(kableExtra)
-dt <- read.csv("tab/HRAFTweibF.csv", header = T)
-# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
-names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
-
-kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
-    # collapse_rows(columns = 1, valign = "top") %>% 
-  row_spec(0, bold = T) %>% 
-    # collapse_rows(columns = 1, valign = "top") %>% 
-    pack_rows("Model 0", 4, 8) %>%
-  pack_rows("Model 1", 9, 13) %>%
-  pack_rows("Model 2", 14, 18) %>%
-  row_spec(18,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 20, 24) %>%
-  pack_rows("Model 1", 25, 29) %>%
-  pack_rows("Model 2", 30, 34) %>%
-  row_spec(34,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 36, 40) %>%
-  pack_rows("Model 1", 41, 45) %>%
-  pack_rows("Model 2", 46, 50) %>%
-kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
-  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
-```
-
-\begin{table}[!h]
-
-\caption{\label{tab:tab3}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}
-\centering
-\fontsize{7}{9}\selectfont
-\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
-\begin{tabular}[t]{lccccc}
-\toprule
-\textbf{ } & \textbf{Never} & \textbf{1-2 times/Month} & \textbf{1-2 times/Week} & \textbf{3-4 times/Week} & \textbf{Almost Daily}\\
-\midrule
-\rowcolor{gray!6}  Person-year & 173222 & 59904 & 129233 & 139919 & 418925\\
-N & 10407 & 3640 & 7590 & 8108 & 25254\\
-\rowcolor{gray!6}  Total Stroke & 300 & 84 & 182 & 172 & 585\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}Mean AF (SD) & 1 & 0.88 (0.07) & 0.87 (0.05) & 0.79 (0.05) & 0.88 (0.04)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.03) & (0.78, 0.98) & (0.71, 0.90) & (0.80, 0.96)\\
-\hspace{1em}Mean HR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.05) & (0.68, 0.97) & (0.58, 0.85) & (0.71, 0.93)\\
-\hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.09) & 1.11 (0.08) & 1.02 (0.08) & 0.95 (0.06)\\
-\hspace{1em}95\% CrI & - & (0.85, 1.17) & (0.97, 1.26) & (0.89, 1.16) & (0.86, 1.06)\\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
-\hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.3\% & 6.3\% & 42.0\% & 86.8\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.12) & 1.11 (0.14) & 1.02 (0.12) & 0.97 (0.09)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.85, 1.20) & (0.97, 1.30) & (0.89, 1.19) & (0.88, 1.10)\\
-\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.36) & (0.96, 1.52) & (0.81, 1.31) & (0.80, 1.17)\\
-\hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
-\hline
-\rowcolor{gray!6}  Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}Mean AF (SD) & 1 & 0.78 (0.13) & 0.98 (0.12) & 0.90 (0.11) & 0.92 (0.09)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.06) & (0.76, 1.25) & (0.70, 1.13) & (0.76, 1.12)\\
-\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
-\hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.88 (0.13) & 1.12 (0.13) & 1.04 (0.13) & 0.95 (0.09)\\
-\hspace{1em}95\% CrI & - & (0.63, 1.17) & (0.90, 1.41) & (0.82, 1.32) & (0.80, 1.14)\\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
-\hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.24) & 1.23 (0.38) & 1.14 (0.33) & 1.04 (0.25)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.33) & (0.93, 1.98) & (0.87, 1.83) & (0.83, 1.55)\\
-\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.22) & 1.26 (0.26) & 1.15 (0.23) & 1.02 (0.19)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.39) & (0.90, 1.90) & (0.83, 1.74) & (0.78, 1.51)\\
-\hspace{1em}Pr(HR < 1) & - & 73.2\% & 9.5\% & 24.8\% & 53.3\%\\
-\hline
-\rowcolor{gray!6}  Cerebral infarction & 102 & 35 & 63 & 50 & 187\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 0}}\\
-\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.13) & 0.90 (0.09) & 0.75 (0.08) & 0.86 (0.06)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.27) & (0.75, 1.10) & (0.60, 0.91) & (0.75, 0.99)\\
-\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.20) & 0.85 (0.14) & 0.61 (0.11) & 0.78 (0.10)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
-\hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 1}}\\
-\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 1.21 (0.32) & 1.16 (0.30) & 0.98 (0.19) & 0.97 (0.14)\\
-\hspace{1em}95\% CrI & - & (0.95, 2.08) & (0.93, 1.95) & (0.79, 1.48) & (0.84, 1.43)\\
-\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.37 (0.33) & 1.25 (0.28) & 0.94 (0.22) & 0.92 (0.17)\\
-\hspace{1em}95\% CrI & - & (0.89, 2.18) & (0.87, 1.95) & (0.63, 1.52) & (0.69, 1.40)\\
-\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 8.5\% & 14.2\% & 70.1\% & 79.4\%\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Model 2}}\\
-\hspace{1em}Mean AF (SD) & 1 & 1.19 (0.19) & 1.12 (0.15) & 0.96 (0.12) & 0.97 (0.09)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.94, 1.62) & (0.92, 1.49) & (0.78, 1.21) & (0.83, 1.18)\\
-\hspace{1em}Mean HR (SD) & 1 & 1.38 (0.29) & 1.21 (0.22) & 0.91 (0.18) & 0.94 (0.14)\\
-\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.89, 2.02) & (0.85, 1.70) & (0.62, 1.34) & (0.69, 1.25)\\
-\hspace{1em}Pr(HR < 1) & - & 7.3\% & 15.6\% & 72.8\% & 70.0\%\\
-\bottomrule
-\multicolumn{6}{l}{\textit{Note: }}\\
-\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
-\multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
-\multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
-\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
-\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
-\end{tabular}}
-\end{table}

### 2020-07-14 Paperfolder/Paperfolder.Rmd
updated ready to share with Yatsuya

@@
 and H.Y.
-conceive and designed the study; C.W.
+conceived and designed the study; C.W.
 analyzed the data; C.W.
@@
   pack_rows("Men (n = 39386)", 1, 16) %>%
-  pack_rows("Women (n = 545999)", 17, 32) #%>% 
+  pack_rows("Women (n = 54999)", 17, 32) #%>% 
   # footnote(c("Abbreviations: n, number; SD, standard deviation; Alc_Fre, alcohol intake; BMI, Body Mass Index; Slepgrp, sleep duration", "groups; Veg, vegetable intake; Coffe, coffee intake; DM/HT/KID/LIV_hist, diabetes, hypertension, kidney disease,", "liver disease history."))
@@
 \cmidrule(l{3pt}r{3pt}){4-7}
- & \textbf{Never} & \textbf{Drinker} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
+ & \textbf{Never} & \textbf{Drinkers} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
  &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  & \textbf{\textit{P} value}\\
@@
 
-In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
+In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
 Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
 
-<!-- - comparison with previous meta-analyses -->
-These findings are in line with our previous report [@wang_milk_2015] as well as other studies conducted in East Asian populations [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@sauvaget2003intake;@Talaei_2016].
-Moreover, we have further updated with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
-A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
-The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined.
-Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association].
-<!-- - potential biological reasons -->
-
-Possible reasons for a protective effect of milk consumption against stroke could be interpreted as such an association may be mediated by its content in calcium, magnesium, potassium, and other bioactive compounds, as recommended by @Iacoviello2018.
-Apart from the inorganic minerals in milk that would be helpful with health effects, recent studies on animal models also indicated key evidence that stroke-associated morbidity was delayed in stroke-prone rats who were fed with milk-protein enriched diets [@Chiba2012;@singh2016diets].
-More precisely, @Singh2020 found that whey protein and its components lactalbumin and lactoferrin improved energy balance and glycemic control against the onset of neurological deficits associated with stroke.
-Bioactive peptides from milk proteins were also responsible for limitation of thrombosis [@tokajuk2019whey] through their angiotensin convertase enzyme inhibitory potential, which might partly explain why the effect was found mainly for mortality from cerebral infarction in the current study.
-
-<!-- - strength and limitation of current study -->
-Some limitations here are worth mentioning.
-First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible.
-Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
-Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated.
-Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation.
-Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.
-
-In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk.
-Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.
-
-```{r tab2, echo=FALSE, eval=FALSE, message=FALSE}
-library(knitr)
-library(kableExtra)
-dt <- read.csv("tab/HRAFTweib.csv", header = T)
-# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
-names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
-
-kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
-  row_spec(0, bold = T) %>% 
-    # collapse_rows(columns = 1, valign = "top") %>% 
-    pack_rows("Model 0", 4, 8) %>%
-  pack_rows("Model 1", 9, 13) %>%
-  pack_rows("Model 2", 14, 18) %>%
-  row_spec(18,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 20, 24) %>%
-  pack_rows("Model 1", 25, 29) %>%
-  pack_rows("Model 2", 30, 34) %>%
-  row_spec(34,  hline_after = TRUE) %>%
-  pack_rows("Model 0", 36, 40) %>%
-  pack_rows("Model 1", 41, 45) %>%
-  pack_rows("Model 2", 46, 50) %>%
-kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
-  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
-  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
-```
-
-\begin{table}[!h]
+\begin{table}[H]
 
@@
 
-\begin{table}[!h]
+\begin{table}[H]
 
@@
 \end{table}
+
+<!-- - comparison with previous meta-analyses -->
+These findings are in line with our previous report [@wang_milk_2015] as well as other studies conducted in East Asian populations [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@sauvaget2003intake;@Talaei_2016].
+Moreover, we have further updated with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
+A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
+The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined.
+Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association].
+<!-- - potential biological reasons -->
+
+Possible reasons for a protective effect of milk consumption against stroke could be interpreted as such an association may be mediated by its content in calcium, magnesium, potassium, and other bioactive compounds, as recommended by @Iacoviello2018.
+Apart from the inorganic minerals in milk that would be helpful with health effects, recent studies on animal models also indicated key evidence that stroke-associated morbidity was delayed in stroke-prone rats who were fed with milk-protein enriched diets [@Chiba2012;@singh2016diets].
+More precisely, @Singh2020 found that whey protein and its components lactalbumin and lactoferrin improved energy balance and glycemic control against the onset of neurological deficits associated with stroke.
+Bioactive peptides from milk proteins were also responsible for limitation of thrombosis [@tokajuk2019whey] through their angiotensin convertase enzyme inhibitory potential, which might partly explain why the effect was found mainly for mortality from cerebral infarction in the current study.
+
+<!-- - strength and limitation of current study -->
+Some limitations here are worth mentioning.
+First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible.
+Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
+Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated.
+Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation.
+Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.
+
+In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk.
+Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.
+
+```{r tab2, echo=FALSE, eval=FALSE, message=FALSE}
+library(knitr)
+library(kableExtra)
+dt <- read.csv("tab/HRAFTweib.csv", header = T)
+# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
+names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")
+
+kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
+  row_spec(0, bold = T) %>% 
+    # collapse_rows(columns = 1, valign = "top") %>% 
+    pack_rows("Model 0", 4, 8) %>%
+  pack_rows("Model 1", 9, 13) %>%
+  pack_rows("Model 2", 14, 18) %>%
+  row_spec(18,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 20, 24) %>%
+  pack_rows("Model 1", 25, 29) %>%
+  pack_rows("Model 2", 30, 34) %>%
+  row_spec(34,  hline_after = TRUE) %>%
+  pack_rows("Model 0", 36, 40) %>%
+  pack_rows("Model 1", 41, 45) %>%
+  pack_rows("Model 2", 46, 50) %>%
+kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
+  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
+  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level."))
+```

### 2020-07-14 paprfolder_docx/strokeJACC.Rmd
updated ready to share with Yatsuya

@@
 
-In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
+In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
 Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
@@
 In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk.
-Time before an event of stroke mortality occurred were slowed down and delayed among those who drank milk regularly.
+Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.

### 2020-07-15 Paperfolder/Paperfolder_v0_0_0.tex
updated commented by hy

--- 2020-07-14 Paperfolder/Paperfolder.tex
@@
 
-In the JACC study cohort, our analysis showed that men in Japan who
+In the JACC study cohort, our analyses showed that men in Japan who
 consumed milk almost daily had lower hazard of dying from stroke
@@
 
-These findings are in line with our previous report
-\citep{wang_milk_2015} as well as other studies conducted in East Asian
-populations
-\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
-Moreover, we have further updated with more comprehensive and
-straightforward evidence about whether and how certain the data had
-shown about daily consumption of milk is contributing to a postponed
-stroke (mostly cerebral infarction) mortality event among Japanese men.
-A recent dose-response meta-analysis of 18 prospective cohort studies
-had also shown a similar negative association \citep{DeGoede2016}
-between milk consumption and risk of stroke. The same meta-analysis also
-reported a greater reduction of risk of stroke (18\%) for East Asian
-population in contrast with the 7\% less risk in the pooled overall
-finding for all populations combined. Benefits of increased milk intake
-might be particularly noticeable in East Asian countries where strokes
-are relatively more common, and milk consumption is much lower than
-those studies conducted among European or American populations
-\citep{dehghan2018association}.
-
-Possible reasons for a protective effect of milk consumption against
-stroke could be interpreted as such an association may be mediated by
-its content in calcium, magnesium, potassium, and other bioactive
-compounds, as recommended by \citet{Iacoviello2018}. Apart from the
-inorganic minerals in milk that would be helpful with health effects,
-recent studies on animal models also indicated key evidence that
-stroke-associated morbidity was delayed in stroke-prone rats who were
-fed with milk-protein enriched diets \citep{Chiba2012, singh2016diets}.
-More precisely, \citet{Singh2020} found that whey protein and its
-components lactalbumin and lactoferrin improved energy balance and
-glycemic control against the onset of neurological deficits associated
-with stroke. Bioactive peptides from milk proteins were also responsible
-for limitation of thrombosis \citep{tokajuk2019whey} through their
-angiotensin convertase enzyme inhibitory potential, which might partly
-explain why the effect was found mainly for mortality from cerebral
-infarction in the current study.
-
-Some limitations here are worth mentioning. First, although our object
-was not to answer which type of milk is protective, but if such
-information were somehow available in the JACC study database, more
-detailed comparison or stratification would have been possible. Second,
-despite reasonable validity of FFQ in the JACC study cohort was assessed
-and confirmed, measurement errors are inevitable. Therefore, we did not
-try to compute the amount of consumption by multiplying an average
-volume per occasion with the frequency of intake since the random error
-might be exaggerated and the observed associations may have attenuated.
-Strengths of our analyses included that we have transformed the research
-questions to more transparent ones that is easier for interpretation.
-Direct probabilities that daily milk intake is associated with lower
-hazard or delayed stroke mortality event were provided here after
-thorough computer simulation.
-
-In conclusion, the JACC study database has provided evidence that
-Japanese men who consumed milk daily had lower hazard of dying from
-stroke especially cerebral infarction compared with their counterparts
-who never consumed milk. Time before an event of stroke mortality
-occurred were slowed down and delayed among those who drank milk
-regularly.
-
-\begin{table}[!h]
+\begin{table}[H]
 
@@
 \end{table}
+
+These findings are in line with our previous report
+\citep{wang_milk_2015} as well as other studies conducted in East Asian
+populations
+\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
+Moreover, we have further updated with more comprehensive and
+straightforward evidence about whether and how certain the data had
+shown about daily consumption of milk is contributing to a postponed
+stroke (mostly cerebral infarction) mortality event among Japanese men.
+A recent dose-response meta-analysis of 18 prospective cohort studies
+had also shown a similar negative association \citep{DeGoede2016}
+between milk consumption and risk of stroke. The same meta-analysis also
+reported a greater reduction of risk of stroke (18\%) for East Asian
+population in contrast with the 7\% less risk in the pooled overall
+finding for all populations combined. Benefits of increased milk intake
+might be particularly noticeable in East Asian countries where strokes
+are relatively more common, and milk consumption is much lower than
+those studies conducted among European or American populations
+\citep{dehghan2018association}.
+
+Possible reasons for a protective effect of milk consumption against
+stroke could be interpreted as such an association may be mediated by
+its content in calcium, magnesium, potassium, and other bioactive
+compounds, as recommended by \citet{Iacoviello2018}. Apart from the
+inorganic minerals in milk that would be helpful with health effects,
+recent studies on animal models also indicated key evidence that
+stroke-associated morbidity was delayed in stroke-prone rats who were
+fed with milk-protein enriched diets \citep{Chiba2012, singh2016diets}.
+More precisely, \citet{Singh2020} found that whey protein and its
+components lactalbumin and lactoferrin improved energy balance and
+glycemic control against the onset of neurological deficits associated
+with stroke. Bioactive peptides from milk proteins were also responsible
+for limitation of thrombosis \citep{tokajuk2019whey} through their
+angiotensin convertase enzyme inhibitory potential, which might partly
+explain why the effect was found mainly for mortality from cerebral
+infarction in the current study.
+
+Some limitations here are worth mentioning. First, although our object
+was not to answer which type of milk is protective, but if such
+information were somehow available in the JACC study database, more
+detailed comparison or stratification would have been possible. Second,
+despite reasonable validity of FFQ in the JACC study cohort was assessed
+and confirmed, measurement errors are inevitable. Therefore, we did not
+try to compute the amount of consumption by multiplying an average
+volume per occasion with the frequency of intake since the random error
+might be exaggerated and the observed associations may have attenuated.
+Strengths of our analyses included that we have transformed the research
+questions to more transparent ones that is easier for interpretation.
+Direct probabilities that daily milk intake is associated with lower
+hazard or delayed stroke mortality event were provided here after
+thorough computer simulation.
+
+In conclusion, the JACC study database has provided evidence that
+Japanese men who consumed milk daily had lower hazard of dying from
+stroke especially cerebral infarction compared with their counterparts
+who never consumed milk. Time before an event of stroke mortality
+occurred were slowed down and delayed among men who drank milk
+regularly.
 

### 2020-07-15 Paperfolder/Paperfolder.Rmd
updated table1

@@
 
-kable(dt, format = "latex", caption = "Sex-specific baseline characteristics according to the frequency of milk intake.", booktabs = T,linesep = "") %>%
+kable(dt[,-8], format = "latex", caption = "Sex-specific baseline characteristics according to the frequency of milk intake.", booktabs = T,linesep = "", align = "lcccccc") %>%
 kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
-  add_header_above(c(" ", "", "", "Milk drinkers" = 4, "")) %>%
+  add_header_above(c(" ", "", "", "Milk drinkers" = 4)) %>%
   # add_indent(c(4:6, 8:11, 14:17, 19, 20, 22:25, 27:30, 32:35, 37:39, 41:43, 45, 47, 49, 51, 53, 55)) %>%
+   row_spec(0, bold = T) %>% 
   pack_rows("Men (n = 39386)", 1, 16) %>%
@@
 \begin{table}[h]
+
 \caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake  (JACC study, 1988-2009).}
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}[t]{lccccccc}
+\begin{tabular}[t]{lcccccc}
 \toprule
-\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} & \multicolumn{1}{c}{} \\
+\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} \\
 \cmidrule(l{3pt}r{3pt}){4-7}
- & \textbf{Never} & \textbf{Drinkers} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
- &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  & \textbf{\textit{P} value}\\
+ & \textbf{Never} & \textbf{Drinkers} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost}  \\
+ &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  \\
 \midrule
 \rowcolor{gray!6}  \addlinespace[0.3em]
-\multicolumn{8}{l}{\textbf{Men (n = 39386)}}\\
-\hspace{1em}number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865 & \\
-\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1) & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4 & <0.001\\
-\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1 & <0.001\\
-\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.5 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7 & <0.001\\
-\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7 & 0.039\\
-\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5 & <0.001\\
-\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2 & <0.001\\
+\multicolumn{7}{l}{\textbf{Men (n = 39386)}}\\
+\hspace{1em}Number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865\\
+\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1)\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4\\
+\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8)\\
+\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3\\
+\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1\\
+\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9\\
+\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.0 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7\\
+\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5\\
+\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2\\
 \rowcolor{gray!6}  \addlinespace[0.3em]
-\multicolumn{8}{l}{\textbf{Women (n = 545999)}}\\
-\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254 & \\
-\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9) & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5 & <0.001\\
-\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}BMI, kg/m2 (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
-\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4 & <0.001\\
-\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4 & <0.001\\
-\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0 & <0.001\\
+\multicolumn{7}{l}{\textbf{Women (n = 54999)}}\\
+\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254\\
+\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9)\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5\\
+\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6)\\
+\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7\\
+\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1\\
+\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2\\
+\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4\\
+\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4\\
+\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0\\
 \bottomrule

### 2020-07-15 Paperfolder/Paperfolder.tex
updated table1

@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}[t]{lccccccc}
+\begin{tabular}[t]{lcccccc}
 \toprule
-\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} & \multicolumn{1}{c}{} \\
+\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk drinkers}} \\
 \cmidrule(l{3pt}r{3pt}){4-7}
- & \textbf{Never} & \textbf{Drinker} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost} & \\
- &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  & \textbf{\textit{P} value}\\
+ & \textbf{Never} & \textbf{Drinkers} & \textbf{1-2 times/} & \textbf{1-2 times/} & \textbf{3-4 times/} & \textbf{Almost}  \\
+ &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}  \\
 \midrule
 \rowcolor{gray!6}  \addlinespace[0.3em]
-\multicolumn{8}{l}{\textbf{Men (n = 39386)}}\\
-\hspace{1em}number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865 & \\
-\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1) & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4 & <0.001\\
-\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1 & <0.001\\
-\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.5 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7 & <0.001\\
-\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7 & 0.039\\
-\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5 & <0.001\\
-\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2 & <0.001\\
+\multicolumn{7}{l}{\textbf{Men (n = 39386)}}\\
+\hspace{1em}Number of subjects & 8508 & 30878 & 3522 & 5928 & 5563 & 15865\\
+\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1)\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4\\
+\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8)\\
+\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3\\
+\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1\\
+\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9\\
+\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.0 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7\\
+\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5\\
+\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2\\
 \rowcolor{gray!6}  \addlinespace[0.3em]
-\multicolumn{8}{l}{\textbf{Women (n = 545999)}}\\
-\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254 & \\
-\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9) & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5 & <0.001\\
-\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}BMI, kg/m2 (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6) & <0.001\\
-\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7 & <0.001\\
-\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\
-\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2 & <0.001\\
-\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4 & <0.001\\
-\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0 & <0.001\\
-\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4 & <0.001\\
-\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0 & <0.001\\
+\multicolumn{7}{l}{\textbf{Women (n = 54999)}}\\
+\hspace{1em}number of subjects & 10407 & 44592 & 3640 & 7590 & 8108 & 25254\\
+\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9)\\
+\rowcolor{gray!6}  \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5\\
+\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6\\
+\rowcolor{gray!6}  \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6)\\
+\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6\\
+\rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7\\
+\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8\\
+\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1\\
+\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3\\
+\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2\\
+\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0\\
+\rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4\\
+\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0\\
+\rowcolor{gray!6}  \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4\\
+\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0\\
 \bottomrule
@@
 
+These findings are in line with our previous report
+\citep{wang_milk_2015} as well as other studies conducted in East Asian
+populations
+\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
+Moreover, we have further updated with more comprehensive and
+straightforward evidence about whether and how certain the data had
+shown about daily consumption of milk is contributing to a postponed
+stroke (mostly cerebral infarction) mortality event among Japanese men.
+A recent dose-response meta-analysis of 18 prospective cohort studies
+had also shown a similar negative association \citep{DeGoede2016}
+between milk consumption and risk of stroke. The same meta-analysis also
+reported a greater reduction of risk of stroke (18\%) for East Asian
+population in contrast with the 7\% less risk in the pooled overall
+finding for all populations combined. Benefits of increased milk intake
+might be particularly noticeable in East Asian countries where strokes
+are relatively more common, and milk consumption is much lower than
+those studies conducted among European or American populations
+\citep{dehghan2018association}.
+
+Possible reasons for a protective effect of milk consumption against
+stroke could be interpreted as such an association may be mediated by
+its content in calcium, magnesium, potassium, and other bioactive
+compounds, as recommended by \citet{Iacoviello2018}. Apart from the
+inorganic minerals in milk that would be helpful with health effects,
+recent studies on animal models also indicated key evidence that
+stroke-associated morbidity was delayed in stroke-prone rats who were
+fed with milk-protein enriched diets \citep{Chiba2012, singh2016diets}.
+More precisely, \citet{Singh2020} found that whey protein and its
+components lactalbumin and lactoferrin improved energy balance and
+glycemic control against the onset of neurological deficits associated
+with stroke. Bioactive peptides from milk proteins were also responsible
+for limitation of thrombosis \citep{tokajuk2019whey} through their
+angiotensin convertase enzyme inhibitory potential, which might partly
+explain why the effect was found mainly for mortality from cerebral
+infarction in the current study.
+
+Some limitations here are worth mentioning. First, although our object
+was not to answer which type of milk is protective, but if such
+information were somehow available in the JACC study database, more
+detailed comparison or stratification would have been possible. Second,
+despite reasonable validity of FFQ in the JACC study cohort was assessed
+and confirmed, measurement errors are inevitable. Therefore, we did not
+try to compute the amount of consumption by multiplying an average
+volume per occasion with the frequency of intake since the random error
+might be exaggerated and the observed associations may have attenuated.
+Strengths of our analyses included that we have transformed the research
+questions to more transparent ones that is easier for interpretation.
+Direct probabilities that daily milk intake is associated with lower
+hazard or delayed stroke mortality event were provided here after
+thorough computer simulation.
+
+In conclusion, the JACC study database has provided evidence that
+Japanese men who consumed milk daily had lower hazard of dying from
+stroke especially cerebral infarction compared with their counterparts
+who never consumed milk. Time before an event of stroke mortality
+occurred were slowed down and delayed among men who drank milk
+regularly.
+
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{``C.W. and H.Y. conceive and designed the study;
+\authorcontributions{``C.W. and H.Y. conceived and designed the study;
 C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T.

### 2020-07-16 Paperfolder/latexdiff.R
updated latexdiff workflow

@@ -1,0 +1,16 @@
+##%######################################################%##
+#                                                          #
+####                  make traced pdf                   ####
+#                                                          #
+##%######################################################%##
+# library(latexdiffr)
+# setwd("/Paperfolder")
+# latexdiff("Paperfolder_v0_0_0.Rmd", "Paperfolder.Rmd", 
+#           output = "diff_v0_0_1", clean = FALSE)
+system("latexdiff Paperfolder_v0_0_0.tex Paperfolder.tex > diff_v_0_0_1.tex")
+
+# abstract diff: Paperfolder_v0_0_0.tex Paperfolder.tex 20200716
+# \DIFaddbegin \DIFadd{In conclusion, %DIF >
+#     data from the JACC study has provided strong evidence that daily milk %DIF >
+#     intake among Japanese men was associated with delayed and lower hazard %DIF >
+#     of mortality from stroke especially cerebral infarction. }\DIFaddend

### 2020-07-16 Paperfolder/Paperfolder.Rmd
Updated according to hy comments v0_0_1

@@
       Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
-#    email: yatsuya@gmail.com
-# firstnote to eighthnote
-# firstnote: |
-#   Current address: Updated affiliation
-# secondnote: |
-#   These authors contributed equally to this work.
 correspondence: |
@@
 type: article
-status: To be submitted
+status: submitted
 bibliography: milk.bib
@@
   The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population.
-We used data from the Japan Collaborative Cohort Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline.
+We used data from the Japan Collaborative Cohort (JACC) Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline.
 These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process.
@@
 Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.
+In conclusion, data from the JACC study has provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.
 keywords: |
@@
 
-Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
-More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all.
-For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling].
-Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably.
-However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings.
-For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.
-Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met.
-Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly showing how faster/slower one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
+Eastern Asian populations were reported to have higher burden from either mortality or morbidity from stroke than populations in European or American regions [@Kim2014].
+Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
+Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in the Western countries [@Saito2019].
+Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would be questionable.
+Even if there is any benefit, not every individual with habitual milk intake can avoid dying from stroke.
+A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay a stroke event or lower the hazard of dying from stroke.
+Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in an exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
 
-Our aim was to overcome these potential pitfalls, avoid misunderstanding, and provide a more straightforward answer to the main research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk.
+Our aim was to provide a more straightforward answer to the primary research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk.
 If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process.
-A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a mortality from stroke event from happening after controlling for the other potential confounders.
+A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.
 
@@
 We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
-Overall difference across the milk intake groups were tested by either analysis of variance for continuous variables or $\chi^2$ test for categorical variables.
+Age-adjusted stroke mortality rate were expressed as per 1000 person-year through the poisson regression model.
 
@@
 Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
+Age-adjusted stroke mortality rate for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.
 
@@
 Some limitations here are worth mentioning.
-First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible.
+First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported.
+Apparently habits in life are possible to alter over the time and these would resulted in misclassfication and residual confoudings.
 Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.

### 2020-07-16 Paperfolder/Paperfolder.tex
Updated according to hy comments v0_0_1

@@
 %=================================================================
-\documentclass[nutrients,article,To be
-submitted,moreauthors,pdftex]{mdpi}
+\documentclass[nutrients,article,submitted,moreauthors,pdftex]{mdpi}
 
@@
 intake and stroke mortality among the Japanese population. We used data
-from the Japan Collaborative Cohort Study to estimate the posterior
-acceleration factors (AF) as well as the hazard ratios (HR) comparing
-individuals with different milk intake frequencies against those who
-never consumed milk at the study baseline. These estimations were
-computed through a series of Bayesian survival models that employed a
-Markov Chain Monte Carlo simulation process. 100000 posterior samples
+from the Japan Collaborative Cohort (JACC) Study to estimate the
+posterior acceleration factors (AF) as well as the hazard ratios (HR)
+comparing individuals with different milk intake frequencies against
+those who never consumed milk at the study baseline. These estimations
+were computed through a series of Bayesian survival models that employed
+a Markov Chain Monte Carlo simulation process. 100000 posterior samples
 for each individual were generated separately through four independent
@@
 0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
-0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women.}
+0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women. In conclusion,
+data from the JACC study has provided strong evidence that daily milk
+intake among Japanese men was associated with delayed and lower hazard
+of mortality from stroke especially cerebral infarction.}
 
@@
 
-Dairy food, especially milk has been recommended to reduce stroke risk
-by nearly 7\% for each 200 g increment of daily consumption
-\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
-would be possible if we were able to compute the exact probability for
-people who had milk intake may had lower hazard of dying from stroke
-compared with those who never drank milk at all. For general
-public/media reporting, concept of hazard in epidemiological studies
-could still sometimes be challenging to be understood or misinterpreted
-since hazard is formally defined as the probability of the occurrence of
-an event at a given time point \citep{collett2015modelling}. Usually,
-authors of epidemiological papers would tend to use ``risk'' instead of
-``hazard'' or interchangeably. However, it would still possibly be mixed
-up with ``risk'' that only contain pure meaning of ``probability of an
-event'' without redefining a point or a period of time in
-cross-sectional settings. For better understanding and interpretation of
-the findings from data that researchers endeavored to collect,
-statistical literature have provided plenty of choices that could help
-us better communicate with each other. Another approach of comparing the
-time-to-event survival probabilities between different groups would be
-to model the time before observing an event rather than the hazard which
-always required the assumption of a proportional hazard to be met.
-Accelerated failure time models are among these convenient tools that
-would avoid worrying about the assumption of proportional hazard and
-directly showing how faster/slower one individual in an exposure group
+Eastern Asian populations were reported to have higher burden from
+either mortality or morbidity from stroke than populations in European
+or American regions \citep{Kim2014}. Dairy food, especially milk has
+been suggested to reduce stroke risk by nearly 7\% for each 200 g
+increment of daily consumption \citep{DeGoede2016}. Although 2 daily
+servings of milk or dairy products is recommended in Japan
+\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
+g/day) of these food groups is much lower and less frequent than that in
+the Western countries \citep{Saito2019}. Given that previous reports
+have also indicated no significant
+\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
+associations \citep{Larsson2009}, whether people with such a low level
+intake of milk can still benefit against stroke would be questionable.
+Even if there is any benefit, not every individual with habitual milk
+intake can avoid dying from stroke. A more intuitive interpretation
+would be available if we were able to show the probabilities and how
+certain the existing data can provide evidence about whether drinking
+milk can delay a stroke event or lower the hazard of dying from stroke.
+Accelerated failure time models under Bayesian framework are convenient
+tools that would help avoid worrying about the assumption of
+proportional hazard normally required in a Cox proportional hazard model
+and can directly show how faster/slower individuals in an exposure group
 might have an event compared to others among different exposure groups
-\citep{Wei1992}.
+\citep{Wei1992, ibrahim2014b}.
 
-Our aim was to overcome these potential pitfalls, avoid
-misunderstanding, and provide a more straightforward answer to the main
+Our aim was to provide a more straightforward answer to the primary
 research question that whether someone answered he/she drank milk at the
@@
 method was applied on an existing database and through which, we also
-provided estimates about whether drinking milk could delay or slow down
-the speed towards a mortality from stroke event from happening after
-controlling for the other potential confounders.
+provided estimates about whether drinking milk could delay a stroke
+mortality event from happening after controlling for the other potential
+confounders.
 
@@
 of selected baseline characteristics according to the frequency of milk
-intake. Overall difference across the milk intake groups were tested by
-either analysis of variance for continuous variables or \(\chi^2\) test
-for categorical variables.
+intake. Age-adjusted stroke mortality rate were expressed as per 1000
+person-year through the poisson regression model.
 
@@
 men and 520 women), and 957 were cerebral infarction (520 men and 437
-women).
+women). Age-adjusted stroke mortality rate for each category of milk
+intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
+person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for
+women.
 
@@
 
-Some limitations here are worth mentioning. First, although our object
-was not to answer which type of milk is protective, but if such
-information were somehow available in the JACC study database, more
-detailed comparison or stratification would have been possible. Second,
-despite reasonable validity of FFQ in the JACC study cohort was assessed
-and confirmed, measurement errors are inevitable. Therefore, we did not
-try to compute the amount of consumption by multiplying an average
-volume per occasion with the frequency of intake since the random error
-might be exaggerated and the observed associations may have attenuated.
-Strengths of our analyses included that we have transformed the research
-questions to more transparent ones that is easier for interpretation.
-Direct probabilities that daily milk intake is associated with lower
-hazard or delayed stroke mortality event were provided here after
-thorough computer simulation.
+Some limitations here are worth mentioning. First, the milk intake
+frequency as well as other lifestyle information was collected only once
+at the baseline and was self-reported. Apparently habits in life are
+possible to alter over the time and these would resulted in
+misclassfication and residual confoudings. Second, despite reasonable
+validity of FFQ in the JACC study cohort was assessed and confirmed,
+measurement errors are inevitable. Therefore, we did not try to compute
+the amount of consumption by multiplying an average volume per occasion
+with the frequency of intake since the random error might be exaggerated
+and the observed associations may have attenuated. Strengths of our
+analyses included that we have transformed the research questions to
+more transparent ones that is easier for interpretation. Direct
+probabilities that daily milk intake is associated with lower hazard or
+delayed stroke mortality event were provided here after thorough
+computer simulation.
 

### 2020-07-16 Paperfolder/latexdiff.R

@@ -10,7 +10,50 @@
 system("latexdiff Paperfolder_v0_0_0.tex Paperfolder.tex > diff_v_0_0_1.tex")
 
 # abstract diff: Paperfolder_v0_0_0.tex Paperfolder.tex 20200716
-# \DIFaddbegin \DIFadd{In conclusion, %DIF >
-#     data from the JACC study has provided strong evidence that daily milk %DIF >
-#     intake among Japanese men was associated with delayed and lower hazard %DIF >
-#     of mortality from stroke especially cerebral infarction. }\DIFaddend
+\DIFaddbegin \DIFadd{In conclusion, %DIF >
+    data from the JACC study has provided strong evidence that daily milk %DIF >
+    intake among Japanese men was associated with delayed and lower hazard %DIF >
+    of mortality from stroke especially cerebral infarction. }\DIFaddend
+
+# calculate mortality rate using poisson regression
+MData_men$Tot_Stro_bin <- MData_men$Tot_Stroke == "I60_9"
+meanAge <- mean(MData_men$Age)
+medianFY <- mean(MData_men$followpy)
+MData_fem$Tot_Stro_bin <- MData_fem$Tot_Stroke == "I60_9"
+meanAge <- mean(MData_fem$Age)
+medianFY <- mean(MData_fem$followpy)
+
+
+
+
+library(tidyverse)
+ex <- MData_men %>% 
+  select(Tot_Stro_bin, Age, Mlkfre, followpy)
+ex <- MData_fem %>% 
+  select(Tot_Stro_bin, Age, Mlkfre, followpy)
+
+M <- glm(Tot_Stro_bin ~ Age + Mlkfre + offset(log(followpy)), data = ex)
+# M <- glm(Tot_Stro_bin ~ Age + Mlkfre, data = ex)
+summary(M)
+
+newdata <- data.frame(Age = rep(meanAge, 5), 
+                      Mlkfre = c( "Never", "Mon1_2", 
+                                  "Wek1_2", "Wek3_4", "Daily"), 
+                      followpy = medianFY)
+# newdata <- data.frame(Age = rep(meanAge, 5), 
+#                       Mlkfre = c( "Never", "Mon1_2", 
+#                                   "Wek1_2", "Wek3_4", "Daily"))
+Mpred <- predict(M, newdata, type="response",  se.fit = TRUE)
[…]

### 2020-07-17 Paperfolder/Paperfolder.Rmd
Updated paper folder would be sent to coauthors

@@
   The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
+The funding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
 # sampleavailability: |
@@
 Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
-Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in the Western countries [@Saito2019].
-Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would be questionable.
-Even if there is any benefit, not every individual with habitual milk intake can avoid dying from stroke.
-A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay a stroke event or lower the hazard of dying from stroke.
-Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in an exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
+Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019].
+Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would require elucidation.
+A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
+Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
 
@@
 Finally, 94385 (39386 men and 54999 women) are left in the database.
-The study design and informed consent procedure were approved by the Ethics Review Committee of Nagoya University School of Medicine.
+The study design and informed consent procedure were approved by the Ethics Review Committee of Hokkaido University School of Medicine.
 
@@
 We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
-Age-adjusted stroke mortality rate were expressed as per 1000 person-year through the poisson regression model.
+Age-adjusted stroke mortality rate were expressed as per 1000 person-year predicted through poisson regression models.
 
@@
 Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated hazard ratios (HRs) as well as acceleration factors (AFs) were presented for each category of milk intake frequency taking the "never" category as the reference.
-Posterior probabilities that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $P(\text{HR} < 1)$.
+Posterior probabilities that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $Pr(\text{HR} < 1)$.
 
@@
 Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
-Age-adjusted stroke mortality rate for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.
+Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.
 
 As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women.
-Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sex.
+Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sexes.
 
@@
 Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
-Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
+Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
 
@@
 First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported.
-Apparently habits in life are possible to alter over the time and these would resulted in misclassfication and residual confoudings.
+Apparently life habits are possible to alter over time and these would resulted in misclassfication and residual confoundings.
 Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
@@
 Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation.
-Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.
+Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulations.
 
-In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke especially cerebral infarction compared with their counterparts who never consumed milk.
+In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke particularly cerebral infarction compared with their counterparts who never consumed milk.
 Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.

### 2020-07-17 Paperfolder/Paperfolder.tex
Updated paper folder would be sent to coauthors

@@
 g/day) of these food groups is much lower and less frequent than that in
-the Western countries \citep{Saito2019}. Given that previous reports
-have also indicated no significant
+Western countries \citep{Saito2019}. Given that previous reports have
+also indicated no significant
 \citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
 associations \citep{Larsson2009}, whether people with such a low level
-intake of milk can still benefit against stroke would be questionable.
-Even if there is any benefit, not every individual with habitual milk
-intake can avoid dying from stroke. A more intuitive interpretation
-would be available if we were able to show the probabilities and how
-certain the existing data can provide evidence about whether drinking
-milk can delay a stroke event or lower the hazard of dying from stroke.
-Accelerated failure time models under Bayesian framework are convenient
-tools that would help avoid worrying about the assumption of
-proportional hazard normally required in a Cox proportional hazard model
-and can directly show how faster/slower individuals in an exposure group
-might have an event compared to others among different exposure groups
-\citep{Wei1992, ibrahim2014b}.
+intake of milk can still benefit against stroke would require
+elucidation. A more intuitive interpretation would be available if we
+were able to show the probabilities and how certain the existing data
+can provide evidence about whether drinking milk can delay or lower the
+hazard of dying from stroke. Accelerated failure time models under
+Bayesian framework are convenient tools that would help avoid worrying
+about the assumption of proportional hazard normally required in a Cox
+proportional hazard model and can directly show how faster/slower
+individuals in one exposure group might have an event compared to others
+among different exposure groups \citep{Wei1992, ibrahim2014b}.
 
@@
 design and informed consent procedure were approved by the Ethics Review
-Committee of Nagoya University School of Medicine.
+Committee of Hokkaido University School of Medicine.
 
@@
 intake. Age-adjusted stroke mortality rate were expressed as per 1000
-person-year through the poisson regression model.
+person-year predicted through poisson regression models.
 
@@
 those who chose ``never'' to their milk intake frequency were calculated
-as \(P(\text{HR} < 1)\).
+as \(Pr(\text{HR} < 1)\).
 
@@
 men and 520 women), and 957 were cerebral infarction (520 men and 437
-women). Age-adjusted stroke mortality rate for each category of milk
+women). Age-adjusted stroke mortality rates for each category of milk
 intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
@@
 vegetable, fruit as well as coffee, and more likely to join exercise
-more than 1 hour/week among both sex.
+more than 1 hour/week among both sexes.
 
@@
 value (=1). Daily female milk consumers had posterior AFs and HRs that
-was distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10) and
-0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of chance
-that their HRs could be smaller than 1.
+were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10)
+and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
+chance that their HRs could be smaller than 1.
 
@@
 frequency as well as other lifestyle information was collected only once
-at the baseline and was self-reported. Apparently habits in life are
-possible to alter over the time and these would resulted in
-misclassfication and residual confoudings. Second, despite reasonable
-validity of FFQ in the JACC study cohort was assessed and confirmed,
-measurement errors are inevitable. Therefore, we did not try to compute
-the amount of consumption by multiplying an average volume per occasion
-with the frequency of intake since the random error might be exaggerated
-and the observed associations may have attenuated. Strengths of our
-analyses included that we have transformed the research questions to
-more transparent ones that is easier for interpretation. Direct
-probabilities that daily milk intake is associated with lower hazard or
-delayed stroke mortality event were provided here after thorough
-computer simulation.
+at the baseline and was self-reported. Apparently life habits are
+possible to alter over time and these would resulted in misclassfication
+and residual confoundings. Second, despite reasonable validity of FFQ in
+the JACC study cohort was assessed and confirmed, measurement errors are
+inevitable. Therefore, we did not try to compute the amount of
+consumption by multiplying an average volume per occasion with the
+frequency of intake since the random error might be exaggerated and the
+observed associations may have attenuated. Strengths of our analyses
+included that we have transformed the research questions to more
+transparent ones that is easier for interpretation. Direct probabilities
+that daily milk intake is associated with lower hazard or delayed stroke
+mortality event were provided here after thorough computer simulations.
 
@@
 Japanese men who consumed milk daily had lower hazard of dying from
-stroke especially cerebral infarction compared with their counterparts
+stroke particularly cerebral infarction compared with their counterparts
 who never consumed milk. Time before an event of stroke mortality
@@
 \conflictsofinterest{The authors declare no conflict of interest. The
-founding sponsors had no role in the design of the study; in the
+funding sponsors had no role in the design of the study; in the
 collection, analyses, or interpretation of data; in the writing of the

### 2020-07-17 Paperfolder/Paperfolder.tex
updated versions sent to coauthors

@@
 University Graduate School of Medicine, Osaka, Japan; \\
-$^{4}$ \quad Department of Public Health, Faculty of Medicine, Hokkaido
-University, Sapporo, Japan; \\
+$^{4}$ \quad Department of Public Health, Hokkaido University, Graduate
+School of Medicine, Sapporo, Japan; \\
 }

### 2020-07-17 paprfolder_docx/strokeJACC.Rmd
docx updated

@@
 
-Abstract:
+**Abstract**:
 
@@
 Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.
+In conclusion, data from the JACC study has provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.
 
-keywords: 
+**keywords**: 
   milk intake; mortality; stroke; Bayesian survival anlysis; time-to-event data; JACC study
@@
 
-Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
-More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all.
-For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling].
-Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably.
-However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings.
-For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.
-Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met.
-Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly showing how faster/slower one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].
+Eastern Asian populations were reported to have higher burden from either mortality or morbidity from stroke than populations in European or American regions [@Kim2014].
+Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
+Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019].
+Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would require elucidation.
+A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
+Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
 
-Our aim was to overcome these potential pitfalls, avoid misunderstanding, and provide a more straightforward answer to the main research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk.
+Our aim was to provide a more straightforward answer to the primary research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk.
 If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process.
-A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a mortality from stroke event from happening after controlling for the other potential confounders.
+A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.
 
@@
 We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
-Overall difference across the milk intake groups were tested by either analysis of variance for continuous variables or $\chi^2$ test for categorical variables.
+Age-adjusted stroke mortality rate were expressed as per 1000 person-year predicted through poisson regression models.
 
@@
 Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
+Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.
 
@@
 Some limitations here are worth mentioning.
-First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible.
+First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported.
+Apparently life habits are possible to alter over time and these would resulted in misclassfication and residual confoundings.
 Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
@@
 Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation.
-Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.
+Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulations.
 

### 2020-07-31 Paperfolder/Paperfolder.Rmd
updated versions sent to coauthors
updated confirmed and edited (energy, education, sleep)

@@
     address: |
-      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
+      Department of Public Health, Hokkaido University, Graduate School of Medicine, Sapporo, Japan
 correspondence: |
@@
 
-The parametric forms of the models fitted in the Bayesian survival analyses included three models: 1) the crude model, 2) the age-centered adjusted model, 3) and a model further adjusted for potential confounders which includes: age (centered, continuous), smoking habit (never, current, former), alcohol intake (never or past, $<$ 4 times/week, Daily), body mass index ($<$ 18.5, $\geq$ 18.5 and $<$ 25, $\geq$ 25 and $<$ 30, $\geq$ 30 kg/m$^2$), history of hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more than 1 hour/week, yes/no), sleep duration ($<$ 7, $\geq$ 7 and $<$ 8, $\geq$ 8 and $<$ 9, $\geq$ 9, hours), coffee intake (never, $<$ 3-4 times/week, almost daily), education level (attended school till age 18, yes/no)
+The parametric forms of the models fitted in the Bayesian survival analyses included three models: 1) the crude model, 2) the age-centered adjusted model, 3) and a model further adjusted for potential confounders which includes: age (centered, continuous), smoking habit (never, current, former), alcohol intake (never or past, $<$ 4 times/week, Daily), body mass index ($<$ 18.5, $\geq$ 18.5 and $<$ 25, $\geq$ 25 and $<$ 30, $\geq$ 30 kg/m$^2$), history of hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more than 1 hour/week, yes/no), sleep duration ($<$ 7, $\geq$ 7 and $<$ 8, $\geq$ 8 and $<$ 9, $\geq$ 9, hours), quartiles of total energy intake, coffee intake (never, $<$ 3-4 times/week, almost daily), and education level (attended school till age 18, yes/no).
 
@@
 \rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3\\
+\hspace{1em}Energy intake, kcal/day (mean (SD))  & 1611 (505) & 1764 (504) & 1606 (496) & 1679 (495) & 1772 (509) & 1830 (495)\\
 \hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1\\
@@
 \rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9\\
-\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6\\
+\hspace{1em}Educated over 18 years old, \% & 9.9 & 14.1 & 12.4 & 12.8 & 11.1 & 15.9 \\
 \rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 5.0 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7\\
@@
 \rowcolor{gray!6}  \hspace{1em}Sleep duration, 8-9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7\\
+\hspace{1em}Energy intake, kcal/day (mean (SD)) & 1519 (451) & 1690 (449) & 1522 (447) & 1596 (443) & 1661 (432) & 1752 (443)\\
 \hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8\\
@@
 \rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2\\
-\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0\\
+\hspace{1em}Educated over 18 years old, \% & 4.8 & 8.3 & 6.7 & 7.2 & 6.5 & 9.4\\
 \rowcolor{gray!6}  \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4\\

### 2020-08-21 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
Updated comments from Nutrients

---
title: Response to the reviewers
subtitle: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis
author:  Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Tae Sasakabe, Sayo Kawai, Shogo Kikuchi, Hiroyasu Iso, Akiko Tamakoshi
# date:  `r Sys.Date()` updated
output:
  redoc::redoc:
    highlight_outputs: TRUE
    margins: 1 
    line_numbers: FALSE 
---

## Comment from reviewer #1

*Thank you very much to the Editorial for entrusting me with the task of reviewing the article. The manuscript presented for review raises a very important health problem, which is stroke. Stroke continues to be one of the leading causes of death and disability in adults. It is a significant health problem which contributes significantly to reduce the quality of life. The key issue from the medical and social point of view remains effective primary and secondary prevention. The current state of knowledge indicates a significant and constantly growing importance non-pharmacological activities undertaken as part of primary prevention stroke, representing a complementary for drug therapy and just as important area of intervention. The broadly understood "primary prevention” has to be implementing it at an early stage, raising awareness of health care professionals and patients.*

*It is known that what you eat can increase or decrease your risk of stroke. The relationship between milk intake and stroke mortality is very interesting and it  has a practical effect.The authors of the presented manuscript, as well as other researchers, observed that higher milk consumption is also associated with a healthier diet, greater physical activity and not smoking.*

*The summary actually shows the problem at hand.*

*The work structure is correct. Most sections are clearly and accurately described.*

*Tables are legible and correctly described.*

*The writings cited by the authors are up-to-date and appropriate.*

### **Minor revision:**

*I would make a clearer and separate section for "Conclusions" and "Study limitations".*

*Congratulations to the authors of the interestingly described research on a large group of participants.*

## Comments from reviewer #2

*The manuscript by C Wang et al includes a cohort of 94385 men and women from Japan, free from self-reported history of stroke, cancer, myocardial infarction and other types of heart disease at baseline who answered an FFQ regarding milk consumption. Between baseline in 1988-90 and end of follow-up in 2009, 2675 deaths from stroke were recorded on death registers. The authors applied Bayesian survival analysis to calculate hazard ratios and acceleration factors. With a range of milk consumption from “never” to “almost daily”, a higher milk consumption was associated with lower hazard and speed from dying from total stroke among men but not among women.*

*I have the following comments and questions for the authors:*

1. *The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution. The dose-response meta-analysis in reference 2 indicates that the association may be non-linear. It would be good if the authors in more detail compared their results with other studies using fatal stroke as outcome and perhaps also focus on those cohorts with a low milk intake. For example, please elaborate on references 6, 20-23 in the discussion. Some of the references do not investigate milk intake per se. In the discussion, please specify that reference 19 does not investigate stroke mortality but CVD and all-cause mortality.*
2. *I am unfortunately not familiar with the Bayesian models used in this work. I am sure that many readers will be in a similar situation as me. I appreciate that these models can calculate hazard ratios without fulfilling the proportional hazards assumption. The authors should in more detail describe the benefits and limitations of these models in relation to the more commonly used Cox proportional hazards regression. Is a HR estimated from these models directly comparable with that from a Cox model? How is an acceleration factor interpreted? Do the models assume that a higher milk intake is associated with a lower stroke mortality, indicated also by the Pr(HR<1)? If so, how would that influence the validity of the method since you in the introduction write that there are reports of inverse associations, no association, and direct associations? In Table 2, both SD and 95% CrI are given. Is there a reason for specifying the SD?*
2. *Why were analyses performed stratified by sex? Since no pooled analysis is presented, the reason for a stratified analysis should be stated in the aims, unless this was a secondary analysis and then also the results from the total cohort should be presented. The authors should also discuss the observed sex differences in more detail. Do other studies show similar sex differences? What potential biological mechanisms may explain them?*
3. *The aim states to “provide a more straightforward answer to the primary research question” – compared to what? And how is this more straightforward answer achieved. This is not clear, neither in the aim nor in the discussion (lines166-167). Please revise.*
3. *Please describe the context of milk intake in Japan. Is milk consumed as a beverage with food, added to coffee or other consumption patterns? Are other milk products than fresh non-fermented milk consumed and could be included in the “milk” exposure?*
2. *Please specify age at baseline in abstract and methods.*
2. *Outcome ascertainment: Information on cause of death was from death certificates. Is there a possibility of individual linkage of the FFQ responses to a cause of death registry or were each of the participants’ death certificates reviewed? How many died from other causes, how many moved from the study area (and were thus lost to follow-up) and how many were censored at the end of follow-up (alive). Has stroke mortality changed during follow-up? Is there a difference in time trends of stroke subtype mortality? In how many cases was stroke subtype not recorded? The authors should also discuss potential reasons for differences in the results for stroke subtypes.*
2. *I agree with the authors that presenting the results in the FFQ categories is a good option, rather than to calculate the amount of consumption. However, I wonder if there is some indication from the validation study as to how much is on average consumed in the higher categories of intake?*
2. *Why did you adjust for sleep duration, is that a factor that influences both milk intake and stroke mortality risk?*
2. *The manuscript has minor language errors throughout and would benefit from a language review.*

### 2020-08-21 Paperfolder/MDPI_submission/Revision01/MDPI_submission/Paperfolder.tex
Updated comments from Nutrients

--- 2020-07-17 Paperfolder/Paperfolder.tex
@@
 %=================================================================
-\documentclass[nutrients,article,submitted,moreauthors,pdftex]{mdpi}
+\documentclass[nutrients,article,submitted,moreauthors,pdftex]{Definitions/mdpi}
 
@@
 than 1 hour/week, yes/no), sleep duration (\(<\) 7, \(\geq\) 7 and \(<\)
-8, \(\geq\) 8 and \(<\) 9, \(\geq\) 9, hours), coffee intake (never,
-\(<\) 3-4 times/week, almost daily), education level (attended school
-till age 18, yes/no)
+8, \(\geq\) 8 and \(<\) 9, \(\geq\) 9, hours), quartiles of total energy
+intake, coffee intake (never, \(<\) 3-4 times/week, almost daily), and
+education level (attended school till age 18, yes/no).
 

### 2020-08-21 AnalysisScript/traditionalPH.R
updated total sample results

@@ -446,6 +446,9 @@ library(survminer)
 library(cowplot)
 library(ggsci)
 
+# In all
+su_obj <- Surv(MData$followpy, MData$Tot_Stroke == "I60_9")
+
 # in Men
 su_obj_men <- Surv(MData_men$followpy, MData_men$Tot_Stroke == "I60_9")
 # in Women
@@ -518,6 +521,54 @@ ggsurv_Drfreq <- ggpar(
   legend.title = ""
 )
 ggsurv_Drfreq
+
+
+#' # In ALL
+#' ## Model0
+
+SurvM0 <-  coxph(su_obj ~ Mlkfre, 
+                 data = MData)
+
+library("broom")
+tidy(SurvM0, exponentiate = TRUE, conf.int = TRUE) %>% 
+  knitr::kable(.)
+
+epiDisplay::tabpct(MData$Mlkfre, MData$Tot_Stroke, graph = FALSE)
+
+MData %>% 
+  group_by(Mlkfre) %>% 
+  summarise(TotPY = sum(followpy))
+
+#' ## Model1 
+
+SurvM1 <-  coxph(su_obj ~ Mlkfre + Age + strata(Agegrp) + as.factor(tr_sex), 
+                 data = MData)
+
+tidy(SurvM1, exponentiate = TRUE, conf.int = TRUE) %>% 
+  knitr::kable(.)
+
+#' ## Model2 
+
+SurvM2 <-  coxph(su_obj ~ Mlkfre + Age + strata(Agegrp)+ as.factor(tr_sex) + Smoking + Alc_Fre + 
+                   BMIgrp + DM_hist + HT_hist + KID_hist + LIV_hist + Exercise + 
+                   Slepgrp + Spi + Fru + Cofe + Educgrp + Gretea, 
+                 data = MData)
+
+tidy(SurvM2, exponentiate = TRUE, conf.int = TRUE) %>% 
+  knitr::kable(.)
+
+#' ## Model2 sex interaction 
+
+SurvM3 <-  coxph(su_obj ~ Mlkfre*as.factor(tr_sex) + Age + strata(Agegrp) + Smoking + Alc_Fre + 
+                   BMIgrp + DM_hist + HT_hist + KID_hist + LIV_hist + Exercise + 
+                   Slepgrp + Spi + Fru + Cofe + Educgrp + Gretea, 
+                 data = MData)
+
[…]

### 2020-08-21 AnalysisScript/traditionalPH.R
interaction by sex confirmed

@@ -12,8 +12,6 @@
 #' header-includes: 
 #'   - \usepackage{bookmark} 
 #'   - \usepackage{xltxtra} 
-#'   - \usepackage{zxjatype} 
-#'   - \usepackage[ipaex]{zxjafont} 
 #' ---
 #' # Read in the data
 
@@ -567,7 +565,14 @@ SurvM3 <-  coxph(su_obj ~ Mlkfre*as.factor(tr_sex) + Age + strata(Agegrp) + Smok
 tidy(SurvM3, exponentiate = TRUE, conf.int = TRUE) %>% 
   knitr::kable(.)
 
-anova(SurvM2, SurvM3)
+
+SurvM <-  coxph(su_obj ~ Mlkfre + Age + strata(Agegrp) + Smoking + Alc_Fre + 
+                   BMIgrp + DM_hist + HT_hist + KID_hist + LIV_hist + Exercise + 
+                   Slepgrp + Spi + Fru + Cofe + Educgrp + Gretea, 
+                 data = MData)
+
+
+anova(SurvM, SurvM3)
 
 
 #' # In Men

### 2020-08-24 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
updated 20% answers to reviewers

@@
 ---
+
+We appreciate the reviewers for their helpful comments.
+We have incorporated them in the revised manuscript.
+Please find below a detailed point-by-point responses to all comments.
+In the tracked changes manuscript, we provided the LaTeX diff file so that changes made can easily be identified.
+A clean file without tracked changes was also included.
 
@@
 
+[Response:] We really appreciate the reviewer for the positive comments. We have updated the manuscript with separated sections for study limitations and conclusions.
+
 ## Comments from reviewer #2
@@
 In the discussion, please specify that reference 19 does not investigate stroke mortality but CVD and all-cause mortality.*
+
+[Response:] Thanks for pointing these out.
+We have updated the introduction as well as the discussion parts in order to better showing that these participants actually represent those in the lower range of milk intake.
+Discussion comparing our findings with previous studies conducted in East Asian population has been expanded in more details.
+The fact that reference 19 was looking into CVD and all-cause mortality has been clarified.
+
 2.
@@
 Is there a reason for specifying the SD?*
+
 2.
@@
 What potential biological mechanisms may explain them?*
+
+[Response:] It is reasonable to conduct the analysis separated in men and women since we found significant interaction effect by sex on the association between milk intake through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001).
+Our stratified analyses also suggested the AFs and HRs might be in slightly different directions among 2 out of 4 frequencies (Table 2 and Table 3, results in the "total stroke" parts), we therefore believe it is legitimate to conduct analyses stratified by sex.
+
+The interaction effect by sex was found probably due to the fact that women had relatively less mortality rates of fatal stroke and much better life habits (much less smokers and alcohol drinkers).
+The probably existing but tiny beneficial effect by milk intake is probably less apparent in women than in men in the JACC study cohort.
+
 3.

### 2020-08-24 Paperfolder/Paperfolder.Rmd
updated 20% answers to reviewers

@@
     address: |
-      Department of Public Health, Hokkaido University, Graduate School of Medicine, Sapporo, Japan
+      Department of Public Health, Hokkaido University, Faculty of Medicine, Sapporo, Japan
 correspondence: |
@@
 Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019].
-Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would require elucidation.
-A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
-Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
+Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], it would be of interest to provide information on the association within a context that most individuals have much lower range of milk intake compared to most of the previous studies.
+Whether people with such a low level intake of milk can still benefit against stroke would require elucidation.
+
+Moreover, a more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
+Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model.
+AFT model is also helpful in estimating acceleration factors in addition to hazard ratios which can be interpreted as the speed for developing an event of interest.
+This speed parameter shows how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
+AFT models
 
@@
 \multicolumn{6}{l}{\textit{Note: }}\\
-\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
+\multicolumn{6}{l}{Abbreviations: N, number of subjects, SD, standard deviation; CrI, credible interval.}\\
 \multicolumn{6}{l}{ Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
 \multicolumn{6}{l}{Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.}\\
-\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of}\\
-\multicolumn{6}{l}{hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.}\\
+\multicolumn{6}{l}{Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of hypertension, }\\
+\multicolumn{6}{l}{diabetes, kidney/liver diseases, exercise, sleep duration,  quartiles of total energy intake, coffee intake, and }\\
+\multicolumn{6}{l}{education level.}\\
 \end{tabular}}
@@
 
-<!-- - comparison with previous meta-analyses -->
-These findings are in line with our previous report [@wang_milk_2015] as well as other studies conducted in East Asian populations [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@sauvaget2003intake;@Talaei_2016].
+<!-- - comparison with previous meta-analyses/studies in japan -->
+These findings showed similar negative effect estimates reported previously [@wang_milk_2015], in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality.
+Other studies conducted in East Asian populations also suggested comparable results [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@Talaei_2016].
+However the Life Span Study [@sauvaget2003intake] which was conducted about 10 years prior to the JACC Study reported null association between milk intake and fatal stroke among men and women combined who survived from the Hiroshima and Nagasaki atomic bomb.
+The difference could be explained by the different population targeted as well as the fact that
+
 Moreover, we have further updated with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
@@
 <!-- - strength and limitation of current study -->
+## Strength and limitations
+
 Some limitations here are worth mentioning.
@@
 Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulations.
+
+## Conclusion
 

### 2020-08-24 Paperfolder/Paperfolder.tex
updated 20% answers to reviewers

--- 2020-07-17 Paperfolder/Paperfolder.tex
@@
 University Graduate School of Medicine, Osaka, Japan; \\
-$^{4}$ \quad Department of Public Health, Faculty of Medicine, Hokkaido
-University, Sapporo, Japan; \\
+$^{4}$ \quad Department of Public Health, Hokkaido University, Faculty
+of Medicine, Sapporo, Japan; \\
 }
@@
 \citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
-associations \citep{Larsson2009}, whether people with such a low level
-intake of milk can still benefit against stroke would require
-elucidation. A more intuitive interpretation would be available if we
-were able to show the probabilities and how certain the existing data
-can provide evidence about whether drinking milk can delay or lower the
-hazard of dying from stroke. Accelerated failure time models under
+associations \citep{Larsson2009}, it would be of interest to provide
+information on the association within a context that most individuals
+have much lower range of milk intake compared to most of the previous
+studies. Whether people with such a low level intake of milk can still
+benefit against stroke would require elucidation.
+
+Moreover, a more intuitive interpretation would be available if we were
+able to show the probabilities and how certain the existing data can
+provide evidence about whether drinking milk can delay or lower the
+hazard of dying from stroke. Accelerated failure time models (AFT) under
 Bayesian framework are convenient tools that would help avoid worrying
 about the assumption of proportional hazard normally required in a Cox
-proportional hazard model and can directly show how faster/slower
-individuals in one exposure group might have an event compared to others
-among different exposure groups \citep{Wei1992, ibrahim2014b}.
+proportional hazard model. AFT model is also helpful in estimating
+acceleration factors in addition to hazard ratios which can be
+interpreted as the speed for developing an event of interest. This speed
+parameter shows how faster/slower individuals in one exposure group
+might have an event compared to others among different exposure groups
+\citep{Wei1992, ibrahim2014b}. AFT models
 
@@
 
-These findings are in line with our previous report
-\citep{wang_milk_2015} as well as other studies conducted in East Asian
-populations
-\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
+These findings showed similar negative effect estimates reported
+previously \citep{wang_milk_2015}, in which the outcomes of interests
+were focused on cardiovascular diseases and all-cause mortality. Other
+studies conducted in East Asian populations also suggested comparable
+results
+\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, Talaei_2016}.
+However the Life Span Study \citep{sauvaget2003intake} which was
+conducted about 10 years prior to the JACC Study reported null
+association between milk intake and fatal stroke among men and women
+combined who survived from the Hiroshima and Nagasaki atomic bomb. The
+difference could be explained by the different population targeted as
+well as the fact that
+
 Moreover, we have further updated with more comprehensive and
@@
 
+\hypertarget{strength-and-limitations}{%
+\subsection{Strength and limitations}\label{strength-and-limitations}}
+
 Some limitations here are worth mentioning. First, the milk intake
@@
 mortality event were provided here after thorough computer simulations.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 

### 2020-08-24 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
updated about 35% revision and response

@@
 
-[Response:] It is reasonable to conduct the analysis separated in men and women since we found significant interaction effect by sex on the association between milk intake through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001).
+[Response:] It is reasonable to conduct the analysis separated in men and women since we found significant interaction effect by sex on the association between milk intake through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, but not shown in the main text).
 Our stratified analyses also suggested the AFs and HRs might be in slightly different directions among 2 out of 4 frequencies (Table 2 and Table 3, results in the "total stroke" parts), we therefore believe it is legitimate to conduct analyses stratified by sex.
 
-The interaction effect by sex was found probably due to the fact that women had relatively less mortality rates of fatal stroke and much better life habits (much less smokers and alcohol drinkers).
-The probably existing but tiny beneficial effect by milk intake is probably less apparent in women than in men in the JACC study cohort.
+The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better life habits (much less smokers and alcohol drinkers) than men.
+The existing beneficial effect by milk intake is probably less evident in women than that in men in the JACC study cohort.
+
+The updated manuscript have included these information in the aim as well as in the discussion about sex differences on the association.
 

### 2020-08-24 Paperfolder/Paperfolder.Rmd
updated about 35% revision and response

@@
 These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process.
-100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed.
+100000 posterior samples were generated separately through four independent chains after model convergency were confirmed.
 Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively.
@@
 A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.
+Analyses would be conducted stratified by sex or any other factor that might suggest any modification effect on the association.
 
@@
 However, good reproducibility and validity were confirmed previously (Spearman rank correlation coefficient between milk intake frequency and weighed dietary record for 12 days was 0.65) [@Date2005].
+From the validation study [@Date2005] of the FFQ, daily consumers of milk was found to have a median intake of 146 gram per day.
 
@@
 
+Since there is significant effect modification by sex found in the total sample, all of the subsequent analyses were performed in men and women separately.
 We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
@@
 <!-- - comparison with previous meta-analyses/studies in japan -->
-These findings showed similar negative effect estimates reported previously [@wang_milk_2015], in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality.
-Other studies conducted in East Asian populations also suggested comparable results [@umesawa2008dietary;@kondo2013consumption;@ozawa2017dietary;@Talaei_2016].
-However the Life Span Study [@sauvaget2003intake] which was conducted about 10 years prior to the JACC Study reported null association between milk intake and fatal stroke among men and women combined who survived from the Hiroshima and Nagasaki atomic bomb.
-The difference could be explained by the different population targeted as well as the fact that
-
-Moreover, we have further updated with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
-A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
+These findings showed similar negative effect estimates reported previously [@wang_milk_2015] using data from the same cohort, in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality.
+Moreover, we have further updated the results with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
+A recent dose-response meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
 The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined.
 Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association].
+However, the Life Span Study [@sauvaget2003intake], which was conducted about 10 years earlier than the JACC Study, reported null association between milk intake and fatal stroke among men and women combined who survived from the Hiroshima and Nagasaki atomic bomb.
+The difference could be largely explained by the different targeting populations between the two studies.
+@kondo2013consumption also reported null association in either men or women from the NIPPON DATA80 study.
+In fact, the exact number of stroke mortality events was about 85% less and the number of participants in the NIPPON DATA80 was about 90% less than those in the JACC study database, their null association might likely due to its limited statistical power.
+@umesawa2008dietary reported that dairy calcium intake was inversely associated with ischemic stroke mortality risk which could be considered as one of the potential evidence that supported our findings.
+Furthermore, stronger inverse association between milk consumption and stroke mortality in men rather than in women was found in the Singapore Chinese Health Study [@Talaei_2016] as well.
+The reasons for this gender differences is currently unknown.
+It might be contributed by generally better/healthier lifestyles (much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available/considered by our models such as intake of calcium supplements.
+The probably existing beneficial effect by milk intake is probably less evident in women than that in men.
+Further investigation is needed.
+
 <!-- - potential biological reasons -->

### 2020-08-24 Paperfolder/Paperfolder.tex
updated about 35% revision and response

@@
 a Markov Chain Monte Carlo simulation process. 100000 posterior samples
-for each individual were generated separately through four independent
-chains after model convergency were confirmed. Posterior probabilites
-that daily milk consumers had lower hazard or delayed mortality from
-strokes compared to non-consumers was 99.0\% and 78.0\% for men and
-women, respectively. Accordingly, the estimated posterior means of AF
-and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
-0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
-0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women. In conclusion,
-data from the JACC study has provided strong evidence that daily milk
-intake among Japanese men was associated with delayed and lower hazard
-of mortality from stroke especially cerebral infarction.}
+were generated separately through four independent chains after model
+convergency were confirmed. Posterior probabilites that daily milk
+consumers had lower hazard or delayed mortality from strokes compared to
+non-consumers was 99.0\% and 78.0\% for men and women, respectively.
+Accordingly, the estimated posterior means of AF and HR for daily milk
+consumers were 0.88 (95\% Credible Interval, CrI: 0.81, 0.96) and 0.80
+(95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI: 0.88, 1.10) and 0.95
+(95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
+study has provided strong evidence that daily milk intake among Japanese
+men was associated with delayed and lower hazard of mortality from
+stroke especially cerebral infarction.}
 
@@
 mortality event from happening after controlling for the other potential
-confounders.
+confounders. Analyses would be conducted stratified by sex or any other
+factor that might suggest any modification effect on the association.
 
@@
 coefficient between milk intake frequency and weighed dietary record for
-12 days was 0.65) \citep{Date2005}.
+12 days was 0.65) \citep{Date2005}. From the validation study
+\citep{Date2005} of the FFQ, daily consumers of milk was found to have a
+median intake of 146 gram per day.
 
@@
 
-We calculated sex-specific means (standard deviation, sd) and proportion
-of selected baseline characteristics according to the frequency of milk
-intake. Age-adjusted stroke mortality rate were expressed as per 1000
-person-year predicted through poisson regression models.
+Since there is significant effect modification by sex found in the total
+sample, all of the subsequent analyses were performed in men and women
+separately. We calculated sex-specific means (standard deviation, sd)
+and proportion of selected baseline characteristics according to the
+frequency of milk intake. Age-adjusted stroke mortality rate were
+expressed as per 1000 person-year predicted through poisson regression
+models.
 
@@
 These findings showed similar negative effect estimates reported
-previously \citep{wang_milk_2015}, in which the outcomes of interests
-were focused on cardiovascular diseases and all-cause mortality. Other
-studies conducted in East Asian populations also suggested comparable
-results
-\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, Talaei_2016}.
-However the Life Span Study \citep{sauvaget2003intake} which was
-conducted about 10 years prior to the JACC Study reported null
-association between milk intake and fatal stroke among men and women
-combined who survived from the Hiroshima and Nagasaki atomic bomb. The
-difference could be explained by the different population targeted as
-well as the fact that
-
-Moreover, we have further updated with more comprehensive and
-straightforward evidence about whether and how certain the data had
-shown about daily consumption of milk is contributing to a postponed
-stroke (mostly cerebral infarction) mortality event among Japanese men.
-A recent dose-response meta-analysis of 18 prospective cohort studies
-had also shown a similar negative association \citep{DeGoede2016}
-between milk consumption and risk of stroke. The same meta-analysis also
-reported a greater reduction of risk of stroke (18\%) for East Asian
-population in contrast with the 7\% less risk in the pooled overall
-finding for all populations combined. Benefits of increased milk intake
-might be particularly noticeable in East Asian countries where strokes
-are relatively more common, and milk consumption is much lower than
-those studies conducted among European or American populations
-\citep{dehghan2018association}.
+previously \citep{wang_milk_2015} using data from the same cohort, in
+which the outcomes of interests were focused on cardiovascular diseases
+and all-cause mortality. Moreover, we have further updated the results
+with more comprehensive and straightforward evidence about whether and
+how certain the data had shown about daily consumption of milk is
+contributing to a postponed stroke (mostly cerebral infarction)
+mortality event among Japanese men. A recent dose-response meta-analysis
+of 18 prospective cohort studies had shown a similar negative
+association \citep{DeGoede2016} between milk consumption and risk of
+stroke. The same meta-analysis also reported a greater reduction of risk
+of stroke (18\%) for East Asian population in contrast with the 7\% less
+risk in the pooled overall finding for all populations combined.
+Benefits of increased milk intake might be particularly noticeable in
+East Asian countries where strokes are relatively more common, and milk
+consumption is much lower than those studies conducted among European or
+American populations \citep{dehghan2018association}. However, the Life
+Span Study \citep{sauvaget2003intake}, which was conducted about 10
+years earlier than the JACC Study, reported null association between
+milk intake and fatal stroke among men and women combined who survived
+from the Hiroshima and Nagasaki atomic bomb. The difference could be
+largely explained by the different targeting populations between the two
+studies. \citet{kondo2013consumption} also reported null association in
+either men or women from the NIPPON DATA80 study. In fact, the exact
+number of stroke mortality events was about 85\% less and the number of
+participants in the NIPPON DATA80 was about 90\% less than those in the
+JACC study database, their null association might likely due to its
+limited statistical power. \citet{umesawa2008dietary} reported that
+dairy calcium intake was inversely associated with ischemic stroke
+mortality risk which could be considered as one of the potential
+evidence that supported our findings. Furthermore, stronger inverse
+association between milk consumption and stroke mortality in men rather
+than in women was found in the Singapore Chinese Health Study
+\citep{Talaei_2016} as well. The reasons for this gender differences is
+currently unknown. It might be contributed by generally better/healthier
+lifestyles (much less smokers and alcohol drinkers) in women regardless
+of milk intake frequency, or maybe due to other factors that was not
+available/considered by our models such as intake of calcium
+supplements. The probably existing beneficial effect by milk intake is
+probably less evident in women than that in men. Further investigation
+is needed.
 

### 2020-08-24 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
Updated gender diff

@@
 
-[Response:] It is reasonable to conduct the analysis separated in men and women since we found significant interaction effect by sex on the association between milk intake through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, but not shown in the main text).
+[Response:] It is reasonable to conduct the analysis separated in men and women since we expected there is a sex difference in the association based on our prior information from the same cohort as well as the Singapore Chinese Health Study.
+Our expectation was further confirmed through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, but not shown in the main text).
 Our stratified analyses also suggested the AFs and HRs might be in slightly different directions among 2 out of 4 frequencies (Table 2 and Table 3, results in the "total stroke" parts), we therefore believe it is legitimate to conduct analyses stratified by sex.
 
-The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better life habits (much less smokers and alcohol drinkers) than men.
+The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better lifestyles (much less smokers and alcohol drinkers) than men, or maybe due to other factors that was not available in/considered by our models such as intake of calcium supplements.
 The existing beneficial effect by milk intake is probably less evident in women than that in men in the JACC study cohort.
 
-The updated manuscript have included these information in the aim as well as in the discussion about sex differences on the association.
+The updated manuscript have included these information in the methods section as well as in the discussion about sex differences on the association.
 

### 2020-08-24 Paperfolder/Paperfolder.Rmd
Updated gender diff

@@
 A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.
-Analyses would be conducted stratified by sex or any other factor that might suggest any modification effect on the association.
 
@@
 
-Since there is significant effect modification by sex found in the total sample, all of the subsequent analyses were performed in men and women separately.
+Analyses were stratified by sex as difference in milk consumption levels and mortality rate was suggested previously [@wang_milk_2015;@Talaei_2016].
 We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
@@
 The reasons for this gender differences is currently unknown.
-It might be contributed by generally better/healthier lifestyles (much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available/considered by our models such as intake of calcium supplements.
+It might be contributed by generally better/healthier lifestyles (much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available in/considered by our models such as intake of calcium supplements.
 The probably existing beneficial effect by milk intake is probably less evident in women than that in men.

### 2020-08-24 Paperfolder/Paperfolder.tex
Updated gender diff

@@
 mortality event from happening after controlling for the other potential
-confounders. Analyses would be conducted stratified by sex or any other
-factor that might suggest any modification effect on the association.
+confounders.
 
@@
 
-Since there is significant effect modification by sex found in the total
-sample, all of the subsequent analyses were performed in men and women
-separately. We calculated sex-specific means (standard deviation, sd)
-and proportion of selected baseline characteristics according to the
-frequency of milk intake. Age-adjusted stroke mortality rate were
-expressed as per 1000 person-year predicted through poisson regression
-models.
+Analyses were stratified by sex as difference in milk consumption levels
+and mortality rate was suggested previously
+\citep{wang_milk_2015, Talaei_2016}. We calculated sex-specific means
+(standard deviation, sd) and proportion of selected baseline
+characteristics according to the frequency of milk intake. Age-adjusted
+stroke mortality rate were expressed as per 1000 person-year predicted
+through poisson regression models.
 
@@
 of milk intake frequency, or maybe due to other factors that was not
-available/considered by our models such as intake of calcium
+available in/considered by our models such as intake of calcium
 supplements. The probably existing beneficial effect by milk intake is

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
40% answer

@@
 
+[Response:] Thanks for your suggestions and comments on this.
+Acceleration factor (AF) can be interpreted as the speed/velocity just like all individuals are driving their cars from the same start point (entry into the study setting) to their goals (stroke mortality) but different people can drive their own cars with different speeds.
+If the AF is smaller than 1 (reference group - never drinker), then it is considered that individual will end up at the goal with slower speed (or takes longer time).
+Actually these AF maybe easier to be interpreted if compared with hazard ratio for readers without any training in epidemiology.
+Because the idea of HR includes hazard that is defined as a risk at a point in time.
+
+We understand that some readers may not be familiar with the alternative and relatively computationally expensive approach.
+The biggest features in the traditional Cox proportional hazard model or any other classical statistical methods are that they assumes 1) there is only one true but unknown value of the parameter (in this context, the hazard ratio or the acceleration factor) from the data at hand to estimate; 2) the experiment/study can be repeated, therefore the confidence intervals in that framework uses standard error to provide precision for the estimates and can be interpreted as "if we repeat the same experiment for many times, 95% of these confidence intervals will contain the true but unknown value of interest"; 3) continue on the repeatable assumption, so that the P-values are actually saying that "if we can repeat the same experiment for many times, the same or more extreme results can happen with this probability, if this probability is lower than 0.05 (commonly used as the cut-off value but without actual solid scientific support) it is considered as rarely happens or 'statistically significant'."
+
+Bayesian ways of statistical analyses would disagree with all of the above assumptions because literally no one experiment/study can be repeated even with the same study design, and Bayesian statistics will provide a posterior distribution of the parameter that we want to estimates which means that the HR or AF is not fixed and unknown but with a distribution that has a mean and a standard deviation to describe its features, and the 95% credible intervals is directly showing us that we are 95% sure that the parameter of interest is distributed in this range.
+Furthermore, because of the large amount of simulations that we have conducted, the Pr(HR < 1) is showing the percentages that these HRs are smaller than 1.
+So a percentage of Pr(HR < 1) = 99% can be directly interpreted as "we are 99% sure that drinking milk at this frequency has lower hazard than those who never consume milk." The models in both classical and the Bayesian frameworks are the same, so the HRs from both frameworks can be interpreted in the same way.
+However, the estimating processes are different: one is based on the maximum likelihood estimation but the others is based on extensive Markov Chain Monte Carlo (MCMC) simulation.
+Therefore we would say that the only limitation for the Bayesian approach would be the computational cost but with the development of the modern computers we expect the Bayesian approaches would become the future default.
+The above discussion would be out of the scope of the current paper but we understand the confusions could be still exist even if we add them into the manuscript.
+As requested, we added some of the discussion in the revised manuscript in the "strength and limitation" section.
+
 2.
@@
 Please revise.*
+
+[Response:] Thanks for your suggestion.
+The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs calculated through the large amount of simulations.
+The detailed interpretation is described above in answering your second comment.
+These probabilities shows directly how certain it is for individuals with that milk intake frequency could have lower hazard compared with those who never consume milk.
+We have added clearer descriptions about these
+
 3.

### 2020-08-25 Paperfolder/Paperfolder.Rmd
40% answer

@@
 First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported.
-Apparently life habits are possible to alter over time and these would resulted in misclassfication and residual confoundings.
+Apparently life habits are possible to alter over time and these would result in misclassfication and residual confoundings.
 Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
 Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated.
+Third, the Bayesian way of conducting the survival analysis using a large sample size is computationally expensive.
+However, the classic maximum likelihood estimations are based on unrealistic assumptions such as repeatability of the study and fixed but unknown values of parameters which are unfulfilled in a large cohort study in the current setting.
 Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation.

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
Updated 60% answers

@@
 [Response:] Thanks for your suggestion.
-The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs calculated through the large amount of simulations.
+The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs < 1 calculated through the large amount of simulations.
 The detailed interpretation is described above in answering your second comment.
 These probabilities shows directly how certain it is for individuals with that milk intake frequency could have lower hazard compared with those who never consume milk.
-We have added clearer descriptions about these
+In traditional way the answer was not clear since only estimates of HRs, 95% confidence intervals, and/or P-values were shown.
+None of these actually directly answer the question "how sure it is to have lower hazard?" We have added clearer descriptions about these research questions and interpretations.
 
@@
 Are other milk products than fresh non-fermented milk consumed and could be included in the “milk” exposure?*
+
+[Response:]
+
 2. *Please specify age at baseline in abstract and methods.*

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
updated with 3 q left

--- 2020-08-24 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
@@
 
-1.
-*The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution.
+- *The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution.
 The dose-response meta-analysis in reference 2 indicates that the association may be non-linear.
@@
 
-2.
-*I am unfortunately not familiar with the Bayesian models used in this work.
+- *I am unfortunately not familiar with the Bayesian models used in this work.
 I am sure that many readers will be in a similar situation as me.
@@
 
-2.
-*Why were analyses performed stratified by sex?
+[Response:] Thanks for your suggestions and comments on this.
+Acceleration factor (AF) can be interpreted as the speed/velocity just like all individuals are driving their cars from the same start point (entry into the study setting) to their goals (stroke mortality) but different people can drive their own cars with different speeds.
+If the AF is smaller than 1 (reference group - never drinker), then it is considered that individual will end up at the goal with slower speed (or takes longer time).
+Actually these AF maybe easier to be interpreted compared with hazard ratios (HR) for readers without any training in epidemiology.
+Because the idea of HR includes hazard that is defined as a risk at a given point in time which is more confusing for many readers.
+
+We understand that some readers may not be familiar with the alternative and relatively computationally expensive approach.
+The biggest features in the traditional Cox proportional hazard model or any other classical statistical methods are that they assume 1) there is only one true but unknown value of the parameter (in this context, the HR and AF) from the data at hand to estimate; 2) the experiment/study can be repeated, therefore the confidence intervals in that framework uses standard error to provide precision for the estimates that can be interpreted as "if we repeat the same experiment for many times, 95% of these confidence intervals will contain the true but unknown value of interest"; 3) continue on the repeatable assumption, so that the P-values are actually saying that "if we can repeat the same experiment for many times, the same or more extreme results can happen with this probability, if this probability is lower than 0.05 (commonly used as the cut-off value but without actual solid scientific support) it is considered as rarely happens or 'statistically significant'."
+
+Bayesian ways of statistical analyses would disagree with all of the above assumptions because literally no one experiment/study can be repeated especially large scale cohort studies that take years and many participants/investigators to carry out.
+Bayesian statistics would provide a posterior distribution of the parameter that we want to estimates which means that the HR or AF is not fixed and unknown but with a distribution that has a mean and a standard deviation to describe its features, and the 95% credible intervals is directly showing us that we are 95% sure that the parameter of interest is distributed in this range.
+Furthermore, because of the large amount of simulations that we have conducted, the Pr(HR < 1) is showing the percentages that these HRs are smaller than 1.
+So a percentage of Pr(HR < 1) = 99% can be directly interpreted as "we are 99% sure that drinking milk at this frequency has lower hazard than those who never consume milk." The models in both classical and the Bayesian frameworks are the same, so the HRs from both frameworks can be interpreted in the same way.
+However, the estimating processes are different: one is based on the maximum likelihood estimation but the other is based on extensive Markov Chain Monte Carlo (MCMC) simulation.
+Therefore we would say that the only limitation for the Bayesian approach would be the computational cost but with the development of the modern computers we expect the Bayesian approaches would become the future default.
+The above discussion would be out of the scope of the current paper but we understand the confusions could still exist even if we add them into the manuscript.
+As requested, we added some of the discussion in the revised manuscript in the "strength and limitation" section.
+
+- *Why were analyses performed stratified by sex?
 Since no pooled analysis is presented, the reason for a stratified analysis should be stated in the aims, unless this was a secondary analysis and then also the results from the total cohort should be presented.
@@
 
-[Response:] It is reasonable to conduct the analysis separated in men and women since we expected there is a sex difference in the association based on our prior information from the same cohort as well as the Singapore Chinese Health Study.
-Our expectation was further confirmed through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, but not shown in the main text).
+[Response:] It is reasonable to conduct the analysis separated in men and women since we expected there is a sex difference in the association based on our prior knowledge from the same cohort as well as the Singapore Chinese Health Study.
+Our expectation was further confirmed through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, not shown in the main text).
 Our stratified analyses also suggested the AFs and HRs might be in slightly different directions among 2 out of 4 frequencies (Table 2 and Table 3, results in the "total stroke" parts), we therefore believe it is legitimate to conduct analyses stratified by sex.
 
-The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better lifestyles (much less smokers and alcohol drinkers) than men, or maybe due to other factors that was not available in/considered by our models such as intake of calcium supplements.
+The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better lifestyles (much less smokers and alcohol drinkers) than men regardless of milk intake frequency, or maybe due to other factors that was not available in/considered by our models such as intake of calcium or other supplements.
 The existing beneficial effect by milk intake is probably less evident in women than that in men in the JACC study cohort.
@@
 
-3.
-*The aim states to “provide a more straightforward answer to the primary research question” – compared to what?
+- *The aim states to “provide a more straightforward answer to the primary research question” – compared to what?
 And how is this more straightforward answer achieved.
@@
 Please revise.*
-3.
-*Please describe the context of milk intake in Japan.
+
+[Response:] Thanks for your suggestion.
+The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs < 1 calculated through the large amount of simulations.
+The detailed interpretation is described above in answering your second comment.
+These probabilities show directly how certain it is for individuals with that milk intake frequency could have lower hazard compared with those who never consume milk.
+In the traditional way the answer was not clear since only estimates of HRs, 95% confidence intervals, and/or P-values were shown.
+None of these actually can directly answer the question "how sure it is to have lower hazard in one group compared with another?" We have added clearer descriptions about these research questions and interpretations.
+
+- *Please describe the context of milk intake in Japan.
 Is milk consumed as a beverage with food, added to coffee or other consumption patterns?
 Are other milk products than fresh non-fermented milk consumed and could be included in the “milk” exposure?*
-2. *Please specify age at baseline in abstract and methods.*
-2.
-*Outcome ascertainment: Information on cause of death was from death certificates.
+
+[Response:] Thanks for your suggestions.
+In the baseline year of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk.
+We have added the context of milk intake in Japan for participants who were invited into the JACC study.
+
+- *Please specify age at baseline in abstract and methods.*
+
+[Response:] Age range are now added in the abstract and methods accordingly.
+
+- *Outcome ascertainment: Information on cause of death was from death certificates.
 Is there a possibility of individual linkage of the FFQ responses to a cause of death registry or were each of the participants’ death certificates reviewed?
@@
 The authors should also discuss potential reasons for differences in the results for stroke subtypes.*
-2.
-*I agree with the authors that presenting the results in the FFQ categories is a good option, rather than to calculate the amount of consumption.
+
+[Response:] We have added these details of information at the beginning of the results section.
+In the study area, investigators conducted systematic review of death certificates till the end of 2009.
+Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office.
+
+- *I agree with the authors that presenting the results in the FFQ categories is a good option, rather than to calculate the amount of consumption.
 However, I wonder if there is some indication from the validation study as to how much is on average consumed in the higher categories of intake?*
-2. *Why did you adjust for sleep duration, is that a factor that influences both milk intake and stroke mortality risk?*
-2. *The manuscript has minor language errors throughout and would benefit from a language review.*
+- *Why did you adjust for sleep duration, is that a factor that influences both milk intake and stroke mortality risk?*
+- *The manuscript has minor language errors throughout and would benefit from a language review.*

### 2020-08-25 Paperfolder/Paperfolder.Rmd
updated with 3 q left

@@
   The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population.
-We used data from the Japan Collaborative Cohort (JACC) Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline.
+We used data from the Japan Collaborative Cohort (JACC) Study (total number of participants = 110585, age range: 40-79) to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline.
 These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process.
@@
 Moreover, a more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
-Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model.
-AFT model is also helpful in estimating acceleration factors in addition to hazard ratios which can be interpreted as the speed for developing an event of interest.
+This would require transformation of the research questions into "Do individuals with milk intake habit have lower hazard of dying from a stroke event compared with people who never consume milk?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is indeed directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event.
+Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumptions of repeatability of a large scale prospective study, and can calculate the exact proportion of posterior estimates (a hazard ratio) that is lower than 1.
+AFT model is helpful in estimating acceleration factors which can be interpreted as the speed for developing an event of interest.
 This speed parameter shows how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
-AFT models
 
@@
 If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process.
-A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.
+A Bayesian survival analysis method was applied on an existing database and through which, we provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.
 
@@
 Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer.
-In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) were successfully retained for the current analysis.
+In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) who aged between 40-79 at the baseline year were successfully retained for the current analysis.
 We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women).
@@
 However, good reproducibility and validity were confirmed previously (Spearman rank correlation coefficient between milk intake frequency and weighed dietary record for 12 days was 0.65) [@Date2005].
-From the validation study [@Date2005] of the FFQ, daily consumers of milk was found to have a median intake of 146 gram per day.
+From the same validation study [@Date2005] on the FFQ, daily consumers of milk was found to have a median intake of 146 gram per day.
+In the baseline year of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk [@eigyogenjyo].
 

### 2020-08-25 Paperfolder/Paperfolder.tex
updated with 3 q left

@@
 provide evidence about whether drinking milk can delay or lower the
-hazard of dying from stroke. Accelerated failure time models (AFT) under
-Bayesian framework are convenient tools that would help avoid worrying
-about the assumption of proportional hazard normally required in a Cox
-proportional hazard model. AFT model is also helpful in estimating
-acceleration factors in addition to hazard ratios which can be
-interpreted as the speed for developing an event of interest. This speed
-parameter shows how faster/slower individuals in one exposure group
-might have an event compared to others among different exposure groups
-\citep{Wei1992, ibrahim2014b}. AFT models
+hazard of dying from stroke. This would require transformation of the
+research questions into ``Do individuals with milk intake habit have
+lower hazard of dying from a stroke event compared with people who never
+consume milk?'' Another way of asking the same research question would
+be ``Can a event of dying from stroke be postponed by having a milk
+intake habit?'' The later question is indeed directly comparing the
+length of times before events or the speed from the same departure point
+(entry of the study) to a fatal stroke event. Accelerated failure time
+models (AFT) under Bayesian framework are convenient tools that would
+help avoid worrying about the assumptions of repeatability of a large
+scale prospective study, and can calculate the exact proportion of
+posterior estimates (a hazard ratio) that is lower than 1. AFT model is
+helpful in estimating acceleration factors which can be interpreted as
+the speed for developing an event of interest. This speed parameter
+shows how faster/slower individuals in one exposure group might have an
+event compared to others among different exposure groups
+\citep{Wei1992, ibrahim2014b}.
 
@@
 Monte Carlo (MCMC) simulation process. A Bayesian survival analysis
-method was applied on an existing database and through which, we also
+method was applied on an existing database and through which, we
 provided estimates about whether drinking milk could delay a stroke
@@
 coefficient between milk intake frequency and weighed dietary record for
-12 days was 0.65) \citep{Date2005}. From the validation study
-\citep{Date2005} of the FFQ, daily consumers of milk was found to have a
-median intake of 146 gram per day.
+12 days was 0.65) \citep{Date2005}. From the same validation study
+\citep{Date2005} on the FFQ, daily consumers of milk was found to have a
+median intake of 146 gram per day. In the baseline year of the JACC
+study (between 1988 and 1990), most ``milk and dairy product''
+consumption (92.1\%) was in the form of whole milk \citep{eigyogenjyo}.
 
@@
 at the baseline and was self-reported. Apparently life habits are
-possible to alter over time and these would resulted in misclassfication
+possible to alter over time and these would result in misclassfication
 and residual confoundings. Second, despite reasonable validity of FFQ in
@@
 frequency of intake since the random error might be exaggerated and the
-observed associations may have attenuated. Strengths of our analyses
-included that we have transformed the research questions to more
-transparent ones that is easier for interpretation. Direct probabilities
-that daily milk intake is associated with lower hazard or delayed stroke
-mortality event were provided here after thorough computer simulations.
+observed associations may have attenuated. Third, the Bayesian way of
+conducting the survival analysis using a large sample size is
+computationally expensive. However, the classic maximum likelihood
+estimations are based on unrealistic assumptions such as repeatability
+of the study and fixed but unknown values of parameters which are
+unfulfilled in a large cohort study in the current setting. Strengths of
+our analyses included that we have transformed the research questions to
+more transparent ones that is easier for interpretation. Direct
+probabilities that daily milk intake is associated with lower hazard or
+delayed stroke mortality event were provided here after thorough
+computer simulations.
 

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/MDPI_submission/Paperfolder.tex
updated respnses and revision and diff files

@@
 %=================================================================
-\documentclass[nutrients,article,submitted,moreauthors,pdftex]{Definitions/mdpi}
+\documentclass[nutrients,article,submitted,moreauthors,pdftex]{mdpi}
 
@@
 University Graduate School of Medicine, Osaka, Japan; \\
-$^{4}$ \quad Department of Public Health, Hokkaido University, Graduate
-School of Medicine, Sapporo, Japan; \\
+$^{4}$ \quad Department of Public Health, Hokkaido University, Faculty
+of Medicine, Sapporo, Japan; \\
 }
@@
 intake and stroke mortality among the Japanese population. We used data
-from the Japan Collaborative Cohort (JACC) Study to estimate the
-posterior acceleration factors (AF) as well as the hazard ratios (HR)
-comparing individuals with different milk intake frequencies against
-those who never consumed milk at the study baseline. These estimations
-were computed through a series of Bayesian survival models that employed
-a Markov Chain Monte Carlo simulation process. 100000 posterior samples
-for each individual were generated separately through four independent
-chains after model convergency were confirmed. Posterior probabilites
-that daily milk consumers had lower hazard or delayed mortality from
-strokes compared to non-consumers was 99.0\% and 78.0\% for men and
-women, respectively. Accordingly, the estimated posterior means of AF
-and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
-0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
-0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women. In conclusion,
-data from the JACC study has provided strong evidence that daily milk
-intake among Japanese men was associated with delayed and lower hazard
-of mortality from stroke especially cerebral infarction.}
+from the Japan Collaborative Cohort (JACC) Study (total number of
+participants = 110585, age range: 40-79) to estimate the posterior
+acceleration factors (AF) as well as the hazard ratios (HR) comparing
+individuals with different milk intake frequencies against those who
+never consumed milk at the study baseline. These estimations were
+computed through a series of Bayesian survival models that employed a
+Markov Chain Monte Carlo simulation process. 100000 posterior samples
+were generated separately through four independent chains after model
+convergency were confirmed. Posterior probabilites that daily milk
+consumers had lower hazard or delayed mortality from strokes compared to
+non-consumers was 99.0\% and 78.0\% for men and women, respectively.
+Accordingly, the estimated posterior means of AF and HR for daily milk
+consumers were 0.88 (95\% Credible Interval, CrI: 0.81, 0.96) and 0.80
+(95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI: 0.88, 1.10) and 0.95
+(95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
+study has provided strong evidence that daily milk intake among Japanese
+men was associated with delayed and lower hazard of mortality from
+stroke especially cerebral infarction.}
 
@@
 \citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
-associations \citep{Larsson2009}, whether people with such a low level
-intake of milk can still benefit against stroke would require
-elucidation. A more intuitive interpretation would be available if we
-were able to show the probabilities and how certain the existing data
-can provide evidence about whether drinking milk can delay or lower the
-hazard of dying from stroke. Accelerated failure time models under
-Bayesian framework are convenient tools that would help avoid worrying
-about the assumption of proportional hazard normally required in a Cox
-proportional hazard model and can directly show how faster/slower
-individuals in one exposure group might have an event compared to others
-among different exposure groups \citep{Wei1992, ibrahim2014b}.
+associations \citep{Larsson2009}, it would be of interest to provide
+information on the association within a context that most individuals
+have much lower range of milk intake compared to most of the previous
+studies. Whether people with such a low level intake of milk can still
+benefit against stroke would require elucidation.
+
+Moreover, a more intuitive interpretation would be available if we were
+able to show the probabilities and how certain the existing data can
+provide evidence about whether drinking milk can delay or lower the
+hazard of dying from stroke. This would require transformation of the
+research questions into ``Do individuals with milk intake habit have
+lower hazard of dying from a stroke event compared with people who never
+consume milk?'' Another way of asking the same research question would
+be ``Can a event of dying from stroke be postponed by having a milk
+intake habit?'' The later question is indeed directly comparing the
+length of times before events or the speed from the same departure point
+(entry of the study) to a fatal stroke event. Accelerated failure time
+models (AFT) under Bayesian framework are convenient tools that would
+help avoid worrying about the assumptions of repeatability of a large
+scale prospective study, and can calculate the exact proportion of
+posterior estimates (a hazard ratio) that is lower than 1. AFT model is
+helpful in estimating acceleration factors which can be interpreted as
+the speed for developing an event of interest. This speed parameter
+shows how faster/slower individuals in one exposure group might have an
+event compared to others among different exposure groups
+\citep{Wei1992, ibrahim2014b}.
 
@@
 study, data from a total of 110585 individuals (46395 men and 64190
-women) were successfully retained for the current analysis. We further
-excluded samples if they meet one of the following criteria: 1) with any
-disease history of stroke, cancer, myocardial infarction, ischemic heart
-disease, or other types heart disease (n = 6655, 2931 men and 3724
-women); 2) did not answer the question regarding their milk consumption
-in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally,
-94385 (39386 men and 54999 women) are left in the database. The study
-design and informed consent procedure were approved by the Ethics Review
-Committee of Hokkaido University School of Medicine.
+women) who aged between 40-79 at the baseline year were successfully
+retained for the current analysis. We further excluded samples if they
+meet one of the following criteria: 1) with any disease history of
+stroke, cancer, myocardial infarction, ischemic heart disease, or other
+types heart disease (n = 6655, 2931 men and 3724 women); 2) did not
+answer the question regarding their milk consumption in the baseline FFQ
+survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men
+and 54999 women) are left in the database. The study design and informed
+consent procedure were approved by the Ethics Review Committee of
+Hokkaido University School of Medicine.
 
@@
 coefficient between milk intake frequency and weighed dietary record for
-12 days was 0.65) \citep{Date2005}.
+12 days was 0.65) \citep{Date2005}. From the same validation study
+\citep{Date2005} on the FFQ, daily consumers of milk was found to have a
+median intake of 146 gram per day. In the baseline year of the JACC
+study (between 1988 and 1990), most ``milk and dairy product''
+consumption (92.1\%) was in the form of whole milk \citep{eigyogenjyo}.
 
-The causes and date of death were obtained from death certificates and
-were systematically reviewed. The follow-up period was defined as from
-the time of the baseline survey was completed, which was between
-1988-1990, until the end of 2009 (administrative censor), or the date
-when move-out of study area, or the date of death from stroke recorded,
-whichever occurred first. Other causes of death were treated as censored
-and assumed not informative. The causes of death were coded by the 10th
+In the study area, investigators conducted systematic review of death
+certificates till the end of 2009. Date and cause of death were
+confirmed with the permission of the Director-General of the Prime
+Minister's Office. The follow-up period was defined as from the time of
+the baseline survey was completed, which was between 1988-1990, until
+the end of 2009 (administrative censor), or the date when move-out of
+study area, or the date of death from stroke recorded, whichever
+occurred first. Other causes of death were treated as censored and
+assumed not informative. The causes of death were coded by the 10th
 Revision of the International Statistical Classification of Diseases and
@@
 
-We calculated sex-specific means (standard deviation, sd) and proportion
-of selected baseline characteristics according to the frequency of milk
-intake. Age-adjusted stroke mortality rate were expressed as per 1000
-person-year predicted through poisson regression models.
+Analyses were stratified by sex as difference in milk consumption levels
+and mortality rate was suggested previously
+\citep{wang_milk_2015, Talaei_2016}. We calculated sex-specific means
+(standard deviation, sd) and proportion of selected baseline
+characteristics according to the frequency of milk intake. Age-adjusted
+stroke mortality rate were expressed as per 1000 person-year predicted
+through poisson regression models.
 
@@
 The total follow-up was 1555073 person-years (median = 19.3 years),
-during which 2675 death from stroke was confirmed (1352 men and 1323
+during which 2675 deaths from stroke were confirmed (1352 men and 1323
 women). Among these stroke mortality, 952 were hemorrhagic stroke (432
 men and 520 women), and 957 were cerebral infarction (520 men and 437
-women). Age-adjusted stroke mortality rates for each category of milk
-intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
-person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for
-women.
+women). Number of deaths from causes other than stroke were 18868 (10731
+men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the
+follow-up (5.8\%); 67349 (25281 men and 42068 women) were censored at
+the end of follow-up (71.4\%). The median (interquartile range, IQR) of
+follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in
+men and 10.9 (5.9, 15.1) in women; the median (IQR) of follow-up years
+for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9,
+16.4) in men and women. Age-adjusted stroke mortality rates for each
+category of milk intake frequency was estimated to be 1.8, 2.0, 1.7,
+1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per
+1000 person-year for women.
 
@@
 lower hazard and delayed time-to-event was observed to remain after age
-or multivariable adjustment only among daily male milk consumers.
-Specifically, the mean (sd; 95\% CrI) of posterior
-multivariable-adjusted AF and HR for daily male consumers of milk were
-0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
-0.69, 0.93) with a probability of 99.0\% to be smaller than the null
-value (=1). Daily female milk consumers had posterior AFs and HRs that
-were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10)
-and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
-chance that their HRs could be smaller than 1.
-
-Posterior distributions of AFs and HRs for mortality from hemorrhagic
-stroke were found to contain the null value for either men or women
-among all fitted models. In contrast, men who had milk intake frequency
-higher than 1-2 times/week were found to be associated with averagely
-17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
-cerebral infarction compared to men who never drank milk (Model 2 in
-\textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs
-distributed below the null value was greater or equal to 97.5\%. No
-evidence was found about the associations between milk intake and hazard
-of cerebral infarction mortality among women.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In the JACC study cohort, our analyses showed that men in Japan who
-consumed milk almost daily had lower hazard of dying from stroke
-especially from cerebral infarction. Our evidence also suggested that
-stroke mortality events were delayed among Japanese male daily milk
-consumers compared with non-consumers.
+or multivariable adjustment only among daily male
 
@@
 
-These findings are in line with our previous report
-\citep{wang_milk_2015} as well as other studies conducted in East Asian
-populations
-\citep{umesawa2008dietary, kondo2013consumption, ozawa2017dietary, sauvaget2003intake, Talaei_2016}.
-Moreover, we have further updated with more comprehensive and
-straightforward evidence about whether and how certain the data had
-shown about daily consumption of milk is contributing to a postponed
-stroke (mostly cerebral infarction) mortality event among Japanese men.
-A recent dose-response meta-analysis of 18 prospective cohort studies
-had also shown a similar negative association \citep{DeGoede2016}
-between milk consumption and risk of stroke. The same meta-analysis also
-reported a greater reduction of risk of stroke (18\%) for East Asian
-population in contrast with the 7\% less risk in the pooled overall
-finding for all populations combined. Benefits of increased milk intake
-might be particularly noticeable in East Asian countries where strokes
-are relatively more common, and milk consumption is much lower than
-those studies conducted among European or American populations
-\citep{dehghan2018association}.
+\noindent milk consumers. Specifically, the mean (sd; 95\% CrI) of
+posterior multivariable-adjusted AF and HR for daily male consumers of
+milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07;
+95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller than
+the null value (=1). Daily female milk consumers had posterior AFs and
+HRs that were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88,
+1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\%
+of chance that their HRs could be smaller than 1.
+
+Posterior distributions of AFs and HRs for mortality from hemorrhagic
+stroke were found to contain the null value for either men or women
+among all fitted models. In contrast, men who had milk intake frequency
+higher than 1-2 times/week were found to be associated with averagely
+17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
+cerebral infarction compared to men who never drank milk (Model 2 in
+\textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs
+distributed below the null value was greater or equal to 97.5\%. No
+evidence was found about the associations between milk intake and hazard
+of cerebral infarction mortality among women.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+In the JACC study cohort, our analyses showed that men in Japan who
+consumed milk almost daily had lower hazard of dying from stroke
+especially from cerebral infarction. Our evidence also suggested that
+stroke mortality events were delayed among Japanese male daily milk
+consumers compared with non-consumers.
+
+These findings showed similar negative effect estimates reported
+previously \citep{wang_milk_2015} using data from the same cohort, in
+which the outcomes of interests were focused on cardiovascular diseases
+and all-cause mortality. Moreover, we have further updated the results
+with more comprehensive and straightforward evidence about whether and
+how certain the data had shown about daily consumption of milk is
+contributing to a postponed stroke (mostly cerebral infarction)
+mortality event among Japanese men. A recent dose-response meta-analysis
+of 18 prospective cohort studies had shown a similar negative
+association \citep{DeGoede2016} between milk consumption and risk of
+stroke. The same meta-analysis also reported a greater reduction of risk
+of stroke (18\%) for East Asian population in contrast with the 7\% less
+risk in the pooled overall finding for all populations combined.
+Benefits of increased milk intake might be particularly noticeable in
+East Asian countries where strokes are relatively more common, and milk
+consumption is much lower than those studies conducted among European or
+American populations \citep{dehghan2018association}. However, the Life
+Span Study \citep{sauvaget2003intake}, which was conducted about 10
+years earlier than the JACC Study, reported null association between
+milk intake and fatal stroke among men and women combined who survived
+from the Hiroshima and Nagasaki atomic bomb. The difference could be
+largely explained by the different targeting populations between the two
+studies. \citet{kondo2013consumption} also reported null association in
+either men or women from the NIPPON DATA80 study. In fact, the exact
+number of stroke mortality events was about 85\% less and the number of
+participants in the NIPPON DATA80 was about 90\% less than those in the
+JACC study database, their null association might likely due to its
+limited statistical power. \citet{umesawa2008dietary} reported that
+dairy calcium intake was inversely associated with ischemic stroke
+mortality risk which could be considered as one of the potential
+evidence that supported our findings. Furthermore, stronger inverse
+association between milk consumption and stroke mortality in men rather
+than in women was found in the Singapore Chinese Health Study
+\citep{Talaei_2016} as well. The reasons for this gender differences is
+currently unknown. It might be contributed by generally better/healthier
+lifestyles (much less smokers and alcohol drinkers) in women regardless
+of milk intake frequency, or maybe due to other factors that was not
+available in/considered by our models such as intake of calcium
+supplements. The probably existing beneficial effect by milk intake is
+probably less evident in women than that in men. Further investigation
+is needed.
 
@@
 frequency of intake since the random error might be exaggerated and the
-observed associations may have attenuated. Strengths of our analyses
-included that we have transformed the research questions to more
-transparent ones that is easier for interpretation. Direct probabilities
-that daily milk intake is associated with lower hazard or delayed stroke
-mortality event were provided here after thorough computer simulations.
+observed associations may have attenuated. Third, the Bayesian way of
+conducting the survival analysis using a large sample size is
+computationally expensive. However, the classic maximum likelihood
+estimations are based on unrealistic assumptions such as repeatability
+of the study and fixed but unknown values of parameters which are
+unfulfilled in a large cohort study in the current setting. Strengths of
+our analyses included that we have transformed the research questions to
+more transparent ones that is easier for interpretation. Direct
+probabilities that daily milk intake is associated with lower hazard or
+delayed stroke mortality event were provided here after thorough
+computer simulations.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
updated responses, files for latexdiff, manuscripts

@@
 author:  Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Tae Sasakabe, Sayo Kawai, Shogo Kikuchi, Hiroyasu Iso, Akiko Tamakoshi
-# date:  `r Sys.Date()` updated
+# date:  " updated `r Sys.Date()`"
 output:
@@
 Discussion comparing our findings with previous studies conducted in East Asian population has been expanded in more details.
-The fact that reference 19 was looking into CVD and all-cause mortality has been clarified.
+The fact that reference 19 (currently reference 16) was looking into CVD and all-cause mortality has been clarified.
 
@@
 
-[Response:] We have added these details of information at the beginning of the results section.
+[Response:] We have added these detailed information at the beginning of the results section.
 In the study area, investigators conducted systematic review of death certificates till the end of 2009.
 Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office.
+Number of deaths from causes other than stroke were 18868 (10731 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the follow-up (5.8%); 67349 (25281 men and 42068 women) were censored at the end of follow-up (71.4%).
+Among the 2675 stroke mortality confirmed in the JACC study, 766 were unfortunately not recorded with subtypes.
+The median (IQR) of follow-up years for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9, 16.4) in men and women; the median (IQR) of follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) and 10.9 (5.9, 15.1) in men and women.
+Potential reasons for differences in the results for stroke subtypes are described in discussion.
 
@@
 However, I wonder if there is some indication from the validation study as to how much is on average consumed in the higher categories of intake?*
+
+[Response:] Thanks for your positive comments.
+The validation study of the FFQ used in the JACC study found that the median intake for a daily milk consumer was about 146 grams per day.
+This has been added in the first paragraph of "2.2 Exposure and the outcome of interest" section.
+
 - *Why did you adjust for sleep duration, is that a factor that influences both milk intake and stroke mortality risk?*
+
+[Response:] Thanks for pointing this out.
+Previous report (cited as below) using the same data showed that healthy lifestyle behaviors (including milk intake daily and proper sleep duration) were associated with CVD mortality and therefore, we also included sleep duration as one of the potential confounders.
+
+Eri Eguchi, Hiroyasu Iso, Naohito Tanabe, Yasuhiko Wada, Hiroshi Yatsuya, Shogo Kikuchi, Yutaka Inaba, Akiko Tamakoshi, on behalf of the Japan Collaborative Cohort Study Group, Healthy lifestyle behaviours and cardiovascular mortality among Japanese men and women: the Japan collaborative cohort study, European Heart Journal, Volume 33, Issue 4, February 2012, Pages 467–477.
+
 - *The manuscript has minor language errors throughout and would benefit from a language review.*
+
+[Response:] Many thanks for your detailed comments that helped us in improving the quality and readability of our manuscript.
+We tried our best to check and fixed the language errors throughout the revised version of the paper.

### 2020-08-25 ForReport20200114/HandOutEng.Rmd
updated handouteng
updated responses, files for latexdiff, manuscripts

@@
 MILK_0 <- MILK_0 %>% 
+  mutate(Death = if_else(T_DX > 1, "dropped", "deaths")) %>% 
   mutate(Tot_Stroke = if_else(grepl("I6[0-9][0-9]|I6[0-9]",  
@@
            OtheHeart != "TRUE" & Can_hist != "TRUE" & MI_hist != "TRUE" & !is.na(Mlkfre)) %>% 
-  select(Area, Age, Agegrp, tr_sex, ICD10, T_DX, Tot_Stroke, HemoStroke, IscheStroke, CHD, HeartF, MlkLogi, 
+  select(Area, Age, Agegrp, tr_sex, ICD10, T_DX, Tot_Stroke, HemoStroke, IscheStroke, CHD, HeartF, MlkLogi, Death, 
          Mlkfre, followpy, Smoking, Alc_Fre, BMI, BMIgrp, DM_hist, HT_hist, KID_hist, 
@@
 \newpage
+- Numbers of individuals dropped out from follow-up
 - Subtypes of stroke and CHD, heart failure: 
@@
   group_by(tr_sex, Tot_Stroke) %>% 
-  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), MaxFolYear = max(followpy))
+  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), minFolYear = min(followpy), MaxFolYear = max(followpy))
+
+MData %>% 
+  group_by(tr_sex, IscheStroke) %>% 
+  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), minFolYear = min(followpy), MaxFolYear = max(followpy), qs = quantile(followpy, c(0.25, 0.75)), prob = c(0.25, 0.75))
+
+MData %>% 
+  group_by(tr_sex, HemoStroke) %>% 
+  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), minFolYear = min(followpy), MaxFolYear = max(followpy), qs = quantile(followpy, c(0.25, 0.75)), prob = c(0.25, 0.75))
+
 ```

### 2020-08-25 Paperfolder/Paperfolder.Rmd
updated responses, files for latexdiff, manuscripts

@@
 
-The causes and date of death were obtained from death certificates and were systematically reviewed.
+In the study area, investigators conducted systematic review of death certificates till the end of 2009.
+Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office.
 The follow-up period was defined as from the time of the baseline survey was completed, which was between 1988-1990, until the end of 2009 (administrative censor), or the date when move-out of study area, or the date of death from stroke recorded, whichever occurred first.
@@
 
-The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women).
+The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 deaths from stroke were confirmed (1352 men and 1323 women).
 Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
+Number of deaths from causes other than stroke were 18868 (10731 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the follow-up (5.8%); 67349 (25281 men and 42068 women) were censored at the end of follow-up (71.4%).
+The median (interquartile range, IQR) of follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in men and 10.9 (5.9, 15.1) in women; the median (IQR) of follow-up years for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9, 16.4) in men and women.
 Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.
@@
 Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women.
-However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers.
-Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
-Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
-
-Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
-In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared to men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
-Probability that the posterior HRs distributed below the null value was greater or equal to 97.5%.
-No evidence was found about the associations between milk intake and hazard of cerebral infarction mortality among women.
-
-# Discussion
-
-<!-- - summary of the finding -->
-
-In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
-Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
+However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male
 
@@
 
+\noindent
+milk consumers.
+Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
+Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
+
+Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
+In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared to men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
+Probability that the posterior HRs distributed below the null value was greater or equal to 97.5%.
+No evidence was found about the associations between milk intake and hazard of cerebral infarction mortality among women.
+
+# Discussion
+
+<!-- - summary of the finding -->
+
+In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
+Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
+
 <!-- - comparison with previous meta-analyses/studies in japan -->

### 2020-08-26 Paperfolder/MDPI_submission/Revision01/MDPI_submission/Paperfolder.tex
updated ready to send to Yatsuya

@@
 were generated separately through four independent chains after model
-convergency were confirmed. Posterior probabilites that daily milk
+convergency was confirmed. Posterior probabilites that daily milk
 consumers had lower hazard or delayed mortality from strokes compared to
@@
 
-Eastern Asian populations were reported to have higher burden from
-either mortality or morbidity from stroke than populations in European
-or American regions \citep{Kim2014}. Dairy food, especially milk has
-been suggested to reduce stroke risk by nearly 7\% for each 200 g
-increment of daily consumption \citep{DeGoede2016}. Although 2 daily
-servings of milk or dairy products is recommended in Japan
+Eastern Asian populations were reported to have higher burden from both
+mortality and morbidity from stroke than populations in European or
+American regions \citep{Kim2014}. Dairy foods, especially milk has been
+suggested to related with decreased stroke risk by nearly 7\% for each
+200 g increment of daily consumption \citep{DeGoede2016}. Although 2
+daily servings of milk or dairy products is recommended in Japan
 \citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
@@
 
-Moreover, a more intuitive interpretation would be available if we were
-able to show the probabilities and how certain the existing data can
-provide evidence about whether drinking milk can delay or lower the
-hazard of dying from stroke. This would require transformation of the
-research questions into ``Do individuals with milk intake habit have
-lower hazard of dying from a stroke event compared with people who never
-consume milk?'' Another way of asking the same research question would
-be ``Can a event of dying from stroke be postponed by having a milk
-intake habit?'' The later question is indeed directly comparing the
-length of times before events or the speed from the same departure point
-(entry of the study) to a fatal stroke event. Accelerated failure time
-models (AFT) under Bayesian framework are convenient tools that would
-help avoid worrying about the assumptions of repeatability of a large
-scale prospective study, and can calculate the exact proportion of
-posterior estimates (a hazard ratio) that is lower than 1. AFT model is
-helpful in estimating acceleration factors which can be interpreted as
-the speed for developing an event of interest. This speed parameter
-shows how faster/slower individuals in one exposure group might have an
-event compared to others among different exposure groups
+Moreover, a more intuitive or straightforward interpretation would be
+available if we were able to show the probabilities and the certainty
+that the existing data can provide evidence about whether drinking milk
+can delay or lower the hazard of dying from stroke. This would require
+transformation of the research question into ``Do individuals with milk
+intake habit have lower hazard of dying from a stroke event?'' Another
+way of asking the same research question would be ``Can a event of dying
+from stroke be postponed by having a milk intake habit?'' The later
+question is indeed directly comparing the length of times before events
+or the speed from the same departure point (entry of the study) to a
+fatal stroke event. Accelerated failure time models (AFT) under Bayesian
+framework are convenient tools that would help avoid worrying about the
+assumptions of repeatability of a large scale prospective study, and can
+calculate the exact proportion of posterior estimates (hazard ratios,
+HR) that is lower than 1. AFT model is helpful in estimating
+acceleration factors (AF) which can be interpreted as the velocity for
+developing an event of interest. This velocity parameter shows how
+faster/slower individuals in one exposure group might have an event
+compared to others in different exposure groups
 \citep{Wei1992, ibrahim2014b}.
@@
 Frequency of milk intake during the preceding year of the baseline was
-assessed by FFQ from ``never'', ``1-2 times/month'', ``1-2 times/week'',
+assessed by FFQ as ``never'', ``1-2 times/month'', ``1-2 times/week'',
 ``3-4 times/week'', and ``Almost daily''. The exact amount of milk
@@
 \citep{Date2005} on the FFQ, daily consumers of milk was found to have a
-median intake of 146 gram per day. In the baseline year of the JACC
-study (between 1988 and 1990), most ``milk and dairy product''
-consumption (92.1\%) was in the form of whole milk \citep{eigyogenjyo}.
+median intake of 146 gram per day. At the baseline of the JACC study
+(between 1988 and 1990), most ``milk and dairy product'' consumption
+(92.1\%) was in the form of whole milk \citep{eigyogenjyo}.
 
@@
 \citep{wang_milk_2015, Talaei_2016}. We calculated sex-specific means
-(standard deviation, sd) and proportion of selected baseline
+(standard deviation, SD) and proportion of selected baseline
 characteristics according to the frequency of milk intake. Age-adjusted
@@
 size of 100000 from four separated chains with a ``burn-in'' of 2500
-iterations. Posterior means (sd) and 95\% Credible Intervals (CrI) of
+iterations. Posterior means (SD) and 95\% Credible Intervals (CrI) of
 the estimated hazard ratios (HRs) as well as acceleration factors (AFs)
@@
 \bottomrule
+\multicolumn{6}{l}{\textit{Note: }}\\
+\multicolumn{6}{l}{Abbreviations: JACC: Japan Collaborative Cohort; SD: standard deviation; BMI: body mass index.   }\\
 \end{tabular}}
@@
 men and 520 women), and 957 were cerebral infarction (520 men and 437
-women). Number of deaths from causes other than stroke were 18868 (10731
+women). Number of deaths from causes other than stroke was 18868 (10731
 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the
@@
 follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in
-men and 10.9 (5.9, 15.1) in women; the median (IQR) of follow-up years
+men and 10.9 (5.9, 15.1) in women; the medians (IQR) of follow-up years
 for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9,
-16.4) in men and women. Age-adjusted stroke mortality rates for each
-category of milk intake frequency was estimated to be 1.8, 2.0, 1.7,
-1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per
-1000 person-year for women.
+16.4) in men and women, respectively. Age-adjusted stroke mortality
+rates for each category of milk intake frequency was estimated to be
+1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2,
+1.1, 1.2 per 1000 person-year for women.
 
@@
 total stroke in crude models. Velocities that milk consumers dying from
-stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
-0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
+stroke is slower by a crude acceleration factor (AF) between 0.79 (SD =
+0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85, 1.02)
 compared with non-consumers. Chances that the posterior crude HRs were
 estimated to be lower than 1 for those who had at least 1-2 times/month
-was higher than 86.5\% in men and greater than 94.6\% in women. However,
-lower hazard and delayed time-to-event was observed to remain after age
-or multivariable adjustment only among daily male
 
@@
 
-\noindent milk consumers. Specifically, the mean (sd; 95\% CrI) of
-posterior multivariable-adjusted AF and HR for daily male consumers of
-milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07;
-95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller than
-the null value (=1). Daily female milk consumers had posterior AFs and
-HRs that were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88,
-1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\%
-of chance that their HRs could be smaller than 1.
+\noindent was higher than 86.5\% in men and greater than 94.6\% in
+women. However, lower hazard and delayed time-to-event was observed to
+remain after age or multivariable adjustment only among daily male milk
+consumers. Specifically, the mean (SD; 95\% CrI) of posterior
+multivariable-adjusted AF and HR for daily male consumers of milk were
+0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95\% CrI:
+0.69, 0.93) with a probability of 99.0\% to be smaller than the null
+value (=1). Daily female milk consumers had posterior AFs and HRs that
+were distributed with means of 0.97 (SD = 0.09; 95\% CrI: 0.88, 1.10)
+and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
+chance that their HRs could be smaller than 1.
 
@@
 
-These findings showed similar negative effect estimates reported
-previously \citep{wang_milk_2015} using data from the same cohort, in
-which the outcomes of interests were focused on cardiovascular diseases
-and all-cause mortality. Moreover, we have further updated the results
-with more comprehensive and straightforward evidence about whether and
-how certain the data had shown about daily consumption of milk is
-contributing to a postponed stroke (mostly cerebral infarction)
-mortality event among Japanese men. A recent dose-response meta-analysis
-of 18 prospective cohort studies had shown a similar negative
-association \citep{DeGoede2016} between milk consumption and risk of
-stroke. The same meta-analysis also reported a greater reduction of risk
-of stroke (18\%) for East Asian population in contrast with the 7\% less
-risk in the pooled overall finding for all populations combined.
-Benefits of increased milk intake might be particularly noticeable in
-East Asian countries where strokes are relatively more common, and milk
-consumption is much lower than those studies conducted among European or
-American populations \citep{dehghan2018association}. However, the Life
-Span Study \citep{sauvaget2003intake}, which was conducted about 10
-years earlier than the JACC Study, reported null association between
-milk intake and fatal stroke among men and women combined who survived
-from the Hiroshima and Nagasaki atomic bomb. The difference could be
-largely explained by the different targeting populations between the two
+These findings showed similar negative effect estimates that were
+reported previously \citep{wang_milk_2015} using data from the same
+cohort, in which the outcomes of interests were focused on
+cardiovascular diseases and all-cause mortality. Moreover, we have
+further updated the results with more comprehensive and straightforward
+evidence about whether and how certain the data had shown about daily
+consumption of milk is contributing to a postponed stroke (mostly
+cerebral infarction) mortality event among Japanese men. A recent
+dose-response meta-analysis of 18 prospective cohort studies had shown a
+similar negative association \citep{DeGoede2016} between milk
+consumption and risk of stroke. The same meta-analysis also reported a
+greater reduction of risk of stroke (18\%) for East Asian population in
+contrast with the 7\% less risk in the pooled overall finding for all
+populations combined. Benefits of increased milk intake might be
+particularly noticeable in East Asian countries where strokes are
+relatively more common, and milk consumption is much lower than those
+studies conducted among European or American populations
+\citep{dehghan2018association}. However, the Life Span Study
+\citep{sauvaget2003intake}, which was conducted about 10 years earlier
+than the JACC Study, reported null association between milk intake and
+fatal stroke among men and women combined who survived from the
+Hiroshima and Nagasaki atomic bomb. The difference could be largely
+explained by the different targeting populations between the two
 studies. \citet{kondo2013consumption} also reported null association in
@@
 currently unknown. It might be contributed by generally better/healthier
-lifestyles (much less smokers and alcohol drinkers) in women regardless
-of milk intake frequency, or maybe due to other factors that was not
-available in/considered by our models such as intake of calcium
-supplements. The probably existing beneficial effect by milk intake is
-probably less evident in women than that in men. Further investigation
-is needed.
+lifestyles (such as much less smokers and alcohol drinkers) in women
+regardless of milk intake frequency, or maybe due to other factors that
+was not available in/considered by our models such as intake of calcium
+or other supplements. The probably existing beneficial effect by milk
+intake is probably less evident in women than that in men. Further
+investigation is needed.
 
@@
 AF & acceleration factor \\
-sd & standard deviation \\
+SD & standard deviation \\
 CrI & credible interval \\

### 2020-08-26 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
Updated and sent to yatsuya before submission

@@
 
-[Response:] Many thanks for your detailed comments that helped us in improving the quality and readability of our manuscript.
-We tried our best to check and fixed the language errors throughout the revised version of the paper.
+[Response:] Many thanks for your detailed comments that helped us to improve the quality and readability of our manuscript.
+We tried our best to check and fix the language errors throughout the revised version of the paper.

### 2020-08-26 Paperfolder/Paperfolder.Rmd
Updated and sent to yatsuya before submission

--- 2020-08-25 Paperfolder/Paperfolder.Rmd
@@
 These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process.
-100000 posterior samples were generated separately through four independent chains after model convergency were confirmed.
+100000 posterior samples were generated separately through four independent chains after model convergency was confirmed.
 Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively.
@@
     long: acceleration factor
-  - short: sd
+  - short: SD
     long: standard deviation
@@
 
-Eastern Asian populations were reported to have higher burden from either mortality or morbidity from stroke than populations in European or American regions [@Kim2014].
-Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
+Eastern Asian populations were reported to have higher burden from both mortality and morbidity from stroke than populations in European or American regions [@Kim2014].
+Dairy foods, especially milk has been suggested to related with decreased stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
 Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019].
@@
 
-Moreover, a more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
-This would require transformation of the research questions into "Do individuals with milk intake habit have lower hazard of dying from a stroke event compared with people who never consume milk?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is indeed directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event.
-Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumptions of repeatability of a large scale prospective study, and can calculate the exact proportion of posterior estimates (a hazard ratio) that is lower than 1.
-AFT model is helpful in estimating acceleration factors which can be interpreted as the speed for developing an event of interest.
-This speed parameter shows how faster/slower individuals in one exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].
+Moreover, a more intuitive or straightforward interpretation would be available if we were able to show the probabilities and the certainty that the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
+This would require transformation of the research question into "Do individuals with milk intake habit have lower hazard of dying from a stroke event?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is indeed directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event.
+Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumptions of repeatability of a large scale prospective study, and can calculate the exact proportion of posterior estimates (hazard ratios, HR) that is lower than 1.
+AFT model is helpful in estimating acceleration factors (AF) which can be interpreted as the velocity for developing an event of interest.
+This velocity parameter shows how faster/slower individuals in one exposure group might have an event compared to others in different exposure groups [@Wei1992;@ibrahim2014b].
 
@@
 
-Frequency of milk intake during the preceding year of the baseline was assessed by FFQ from "never", "1-2 times/month", "1-2 times/week", "3-4 times/week", and "Almost daily".
+Frequency of milk intake during the preceding year of the baseline was assessed by FFQ as "never", "1-2 times/month", "1-2 times/week", "3-4 times/week", and "Almost daily".
 The exact amount of milk consumption was difficult to assess here.
@@
 From the same validation study [@Date2005] on the FFQ, daily consumers of milk was found to have a median intake of 146 gram per day.
-In the baseline year of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk [@eigyogenjyo].
+At the baseline of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk [@eigyogenjyo].
 
-The causes and date of death were obtained from death certificates and were systematically reviewed.
+In the study area, investigators conducted systematic review of death certificates till the end of 2009.
+Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office.
 The follow-up period was defined as from the time of the baseline survey was completed, which was between 1988-1990, until the end of 2009 (administrative censor), or the date when move-out of study area, or the date of death from stroke recorded, whichever occurred first.
@@
 Analyses were stratified by sex as difference in milk consumption levels and mortality rate was suggested previously [@wang_milk_2015;@Talaei_2016].
-We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake.
+We calculated sex-specific means (standard deviation, SD) and proportion of selected baseline characteristics according to the frequency of milk intake.
 Age-adjusted stroke mortality rate were expressed as per 1000 person-year predicted through poisson regression models.
@@
 All models had a posterior sample size of 100000 from four separated chains with a "burn-in" of 2500 iterations.
-Posterior means (sd) and 95% Credible Intervals (CrI) of the estimated hazard ratios (HRs) as well as acceleration factors (AFs) were presented for each category of milk intake frequency taking the "never" category as the reference.
+Posterior means (SD) and 95% Credible Intervals (CrI) of the estimated hazard ratios (HRs) as well as acceleration factors (AFs) were presented for each category of milk intake frequency taking the "never" category as the reference.
 Posterior probabilities that the estimated hazard of dying from stroke for the milk intake for frequency that higher or equal to "1-2 times/month" is smaller compared with those who chose "never" to their milk intake frequency were calculated as $Pr(\text{HR} < 1)$.
@@
 
-The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women).
+The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 deaths from stroke were confirmed (1352 men and 1323 women).
 Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).
+Number of deaths from causes other than stroke was 18868 (10731 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the follow-up (5.8%); 67349 (25281 men and 42068 women) were censored at the end of follow-up (71.4%).
+The median (interquartile range, IQR) of follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in men and 10.9 (5.9, 15.1) in women; the medians (IQR) of follow-up years for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9, 16.4) in men and women, respectively.
 Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.
@@
 Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models.
-Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers.
-Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women.
-However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers.
-Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
-Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
-
-Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
-In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared to men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
-Probability that the posterior HRs distributed below the null value was greater or equal to 97.5%.
-No evidence was found about the associations between milk intake and hazard of cerebral infarction mortality among women.
-
-# Discussion
-
-<!-- - summary of the finding -->
-
-In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
-Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
+Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (SD = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers.
+Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month
 
@@
 
+\noindent was higher than 86.5% in men and greater than 94.6% in women.
+However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers.
+Specifically, the mean (SD; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (SD = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1).
+Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (SD = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (SD = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
+
+Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models.
+In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared to men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}).
+Probability that the posterior HRs distributed below the null value was greater or equal to 97.5%.
+No evidence was found about the associations between milk intake and hazard of cerebral infarction mortality among women.
+
+# Discussion
+
+<!-- - summary of the finding -->
+
+In the JACC study cohort, our analyses showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction.
+Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.
+
 <!-- - comparison with previous meta-analyses/studies in japan -->
-These findings showed similar negative effect estimates reported previously [@wang_milk_2015] using data from the same cohort, in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality.
+These findings showed similar negative effect estimates that were reported previously [@wang_milk_2015] using data from the same cohort, in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality.
 Moreover, we have further updated the results with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men.
@@
 The reasons for this gender differences is currently unknown.
-It might be contributed by generally better/healthier lifestyles (much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available in/considered by our models such as intake of calcium supplements.
+It might be contributed by generally better/healthier lifestyles (such as much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available in/considered by our models such as intake of calcium or other supplements.
 The probably existing beneficial effect by milk intake is probably less evident in women than that in men.

### 2020-08-26 Paperfolder/Paperfolder.tex
Updated and sent to yatsuya before submission

@@
 intake and stroke mortality among the Japanese population. We used data
-from the Japan Collaborative Cohort (JACC) Study to estimate the
-posterior acceleration factors (AF) as well as the hazard ratios (HR)
-comparing individuals with different milk intake frequencies against
-those who never consumed milk at the study baseline. These estimations
-were computed through a series of Bayesian survival models that employed
-a Markov Chain Monte Carlo simulation process. 100000 posterior samples
+from the Japan Collaborative Cohort (JACC) Study (total number of
+participants = 110585, age range: 40-79) to estimate the posterior
+acceleration factors (AF) as well as the hazard ratios (HR) comparing
+individuals with different milk intake frequencies against those who
+never consumed milk at the study baseline. These estimations were
+computed through a series of Bayesian survival models that employed a
+Markov Chain Monte Carlo simulation process. 100000 posterior samples
 were generated separately through four independent chains after model
-convergency were confirmed. Posterior probabilites that daily milk
+convergency was confirmed. Posterior probabilites that daily milk
 consumers had lower hazard or delayed mortality from strokes compared to
@@
 \citep{Date2005} on the FFQ, daily consumers of milk was found to have a
-median intake of 146 gram per day. In the baseline year of the JACC
-study (between 1988 and 1990), most ``milk and dairy product''
-consumption (92.1\%) was in the form of whole milk \citep{eigyogenjyo}.
+median intake of 146 gram per day. At the baseline of the JACC study
+(between 1988 and 1990), most ``milk and dairy product'' consumption
+(92.1\%) was in the form of whole milk \citep{eigyogenjyo}.
 
-The causes and date of death were obtained from death certificates and
-were systematically reviewed. The follow-up period was defined as from
-the time of the baseline survey was completed, which was between
-1988-1990, until the end of 2009 (administrative censor), or the date
-when move-out of study area, or the date of death from stroke recorded,
-whichever occurred first. Other causes of death were treated as censored
-and assumed not informative. The causes of death were coded by the 10th
+In the study area, investigators conducted systematic review of death
+certificates till the end of 2009. Date and cause of death were
+confirmed with the permission of the Director-General of the Prime
+Minister's Office. The follow-up period was defined as from the time of
+the baseline survey was completed, which was between 1988-1990, until
+the end of 2009 (administrative censor), or the date when move-out of
+study area, or the date of death from stroke recorded, whichever
+occurred first. Other causes of death were treated as censored and
+assumed not informative. The causes of death were coded by the 10th
 Revision of the International Statistical Classification of Diseases and
@@
 The total follow-up was 1555073 person-years (median = 19.3 years),
-during which 2675 death from stroke was confirmed (1352 men and 1323
+during which 2675 deaths from stroke were confirmed (1352 men and 1323
 women). Among these stroke mortality, 952 were hemorrhagic stroke (432
 men and 520 women), and 957 were cerebral infarction (520 men and 437
-women). Age-adjusted stroke mortality rates for each category of milk
-intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000
-person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for
-women.
+women). Number of deaths from causes other than stroke was 18868 (10731
+men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the
+follow-up (5.8\%); 67349 (25281 men and 42068 women) were censored at
+the end of follow-up (71.4\%). The median (interquartile range, IQR) of
+follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in
+men and 10.9 (5.9, 15.1) in women; the medians (IQR) of follow-up years
+for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9,
+16.4) in men and women, respectively. Age-adjusted stroke mortality
+rates for each category of milk intake frequency was estimated to be
+1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2,
+1.1, 1.2 per 1000 person-year for women.
 
@@
 total stroke in crude models. Velocities that milk consumers dying from
-stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
-0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
+stroke is slower by a crude acceleration factor (AF) between 0.79 (SD =
+0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85, 1.02)
 compared with non-consumers. Chances that the posterior crude HRs were
 estimated to be lower than 1 for those who had at least 1-2 times/month
-was higher than 86.5\% in men and greater than 94.6\% in women. However,
-lower hazard and delayed time-to-event was observed to remain after age
-or multivariable adjustment only among daily male milk consumers.
-Specifically, the mean (sd; 95\% CrI) of posterior
-multivariable-adjusted AF and HR for daily male consumers of milk were
-0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
-0.69, 0.93) with a probability of 99.0\% to be smaller than the null
-value (=1). Daily female milk consumers had posterior AFs and HRs that
-were distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10)
-and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
-chance that their HRs could be smaller than 1.
-
-Posterior distributions of AFs and HRs for mortality from hemorrhagic
-stroke were found to contain the null value for either men or women
-among all fitted models. In contrast, men who had milk intake frequency
-higher than 1-2 times/week were found to be associated with averagely
-17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
-cerebral infarction compared to men who never drank milk (Model 2 in
-\textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs
-distributed below the null value was greater or equal to 97.5\%. No
-evidence was found about the associations between milk intake and hazard
-of cerebral infarction mortality among women.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In the JACC study cohort, our analyses showed that men in Japan who
-consumed milk almost daily had lower hazard of dying from stroke
-especially from cerebral infarction. Our evidence also suggested that
-stroke mortality events were delayed among Japanese male daily milk
-consumers compared with non-consumers.
 
@@
 
-These findings showed similar negative effect estimates reported
-previously \citep{wang_milk_2015} using data from the same cohort, in
-which the outcomes of interests were focused on cardiovascular diseases
-and all-cause mortality. Moreover, we have further updated the results
-with more comprehensive and straightforward evidence about whether and
-how certain the data had shown about daily consumption of milk is
-contributing to a postponed stroke (mostly cerebral infarction)
-mortality event among Japanese men. A recent dose-response meta-analysis
-of 18 prospective cohort studies had shown a similar negative
-association \citep{DeGoede2016} between milk consumption and risk of
-stroke. The same meta-analysis also reported a greater reduction of risk
-of stroke (18\%) for East Asian population in contrast with the 7\% less
-risk in the pooled overall finding for all populations combined.
-Benefits of increased milk intake might be particularly noticeable in
-East Asian countries where strokes are relatively more common, and milk
-consumption is much lower than those studies conducted among European or
-American populations \citep{dehghan2018association}. However, the Life
-Span Study \citep{sauvaget2003intake}, which was conducted about 10
-years earlier than the JACC Study, reported null association between
-milk intake and fatal stroke among men and women combined who survived
-from the Hiroshima and Nagasaki atomic bomb. The difference could be
-largely explained by the different targeting populations between the two
+\noindent was higher than 86.5\% in men and greater than 94.6\% in
+women. However, lower hazard and delayed time-to-event was observed to
+remain after age or multivariable adjustment only among daily male milk
+consumers. Specifically, the mean (SD; 95\% CrI) of posterior
+multivariable-adjusted AF and HR for daily male consumers of milk were
+0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95\% CrI:
+0.69, 0.93) with a probability of 99.0\% to be smaller than the null
+value (=1). Daily female milk consumers had posterior AFs and HRs that
+were distributed with means of 0.97 (SD = 0.09; 95\% CrI: 0.88, 1.10)
+and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
+chance that their HRs could be smaller than 1.
+
+Posterior distributions of AFs and HRs for mortality from hemorrhagic
+stroke were found to contain the null value for either men or women
+among all fitted models. In contrast, men who had milk intake frequency
+higher than 1-2 times/week were found to be associated with averagely
+17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
+cerebral infarction compared to men who never drank milk (Model 2 in
+\textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs
+distributed below the null value was greater or equal to 97.5\%. No
+evidence was found about the associations between milk intake and hazard
+of cerebral infarction mortality among women.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+In the JACC study cohort, our analyses showed that men in Japan who
+consumed milk almost daily had lower hazard of dying from stroke
+especially from cerebral infarction. Our evidence also suggested that
+stroke mortality events were delayed among Japanese male daily milk
+consumers compared with non-consumers.
+
+These findings showed similar negative effect estimates that were
+reported previously \citep{wang_milk_2015} using data from the same
+cohort, in which the outcomes of interests were focused on
+cardiovascular diseases and all-cause mortality. Moreover, we have
+further updated the results with more comprehensive and straightforward
+evidence about whether and how certain the data had shown about daily
+consumption of milk is contributing to a postponed stroke (mostly
+cerebral infarction) mortality event among Japanese men. A recent
+dose-response meta-analysis of 18 prospective cohort studies had shown a
+similar negative association \citep{DeGoede2016} between milk
+consumption and risk of stroke. The same meta-analysis also reported a
+greater reduction of risk of stroke (18\%) for East Asian population in
+contrast with the 7\% less risk in the pooled overall finding for all
+populations combined. Benefits of increased milk intake might be
+particularly noticeable in East Asian countries where strokes are
+relatively more common, and milk consumption is much lower than those
+studies conducted among European or American populations
+\citep{dehghan2018association}. However, the Life Span Study
+\citep{sauvaget2003intake}, which was conducted about 10 years earlier
+than the JACC Study, reported null association between milk intake and
+fatal stroke among men and women combined who survived from the
+Hiroshima and Nagasaki atomic bomb. The difference could be largely
+explained by the different targeting populations between the two
 studies. \citet{kondo2013consumption} also reported null association in

### 2020-08-29 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
updated 80% changes by HY

@@
 
-- *The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution.
+- *#1: The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution.
 The dose-response meta-analysis in reference 2 indicates that the association may be non-linear.
@@
 
-[Response:] Thanks for pointing these out.
-We have updated the introduction as well as the discussion parts in order to better showing that these participants actually represent those in the lower range of milk intake.
-Discussion comparing our findings with previous studies conducted in East Asian population has been expanded in more details.
-The fact that reference 19 (currently reference 16) was looking into CVD and all-cause mortality has been clarified.
+[Response:] We greatly appreciate the reviewer's points.
+We have updated the Introduction as well as the Discussion so that we could draw readers' attention to the fact that absolute milk intake of these participants were actually in the lower range of milk intake in the world.
+We have elaborated the issue in Discussion by comparing our findings with previous studies conducted in East Asian population.
+We have also clarified the fact that the reference #19 in the previous manuscript (#16 in the revised manuscript) dealt with milk intake in relation to CVD and all-cause mortality.
 
-- *I am unfortunately not familiar with the Bayesian models used in this work.
+- *#2: I am unfortunately not familiar with the Bayesian models used in this work.
 I am sure that many readers will be in a similar situation as me.
@@
 
-[Response:] Thanks for your suggestions and comments on this.
-Acceleration factor (AF) can be interpreted as the speed/velocity just like all individuals are driving their cars from the same start point (entry into the study setting) to their goals (stroke mortality) but different people can drive their own cars with different speeds.
-If the AF is smaller than 1 (reference group - never drinker), then it is considered that individual will end up at the goal with slower speed (or takes longer time).
-Actually these AF maybe easier to be interpreted compared with hazard ratios (HR) for readers without any training in epidemiology.
-Because the idea of HR includes hazard that is defined as a risk at a given point in time which is more confusing for many readers.
+[Response:] Thanks for the frank comments about the Bayesian models and suggestions.
+We gave more explanations for the methods as well as benifit and background for their use in the revised manuscript.
+For example, acceleration factor (AF) can be interpreted as the speed/velocity just like all individuals are driving their cars from the same start point (entry into the study setting) to their goals (stroke mortality) but different people can drive their own car with different speeds.
+If the AF of a certain group is smaller than 1 (i.e., reference group - never drinker), then it is considered that individuals in that group would reach the goal with slower speed (or take longer time).
+We might be able to argue that the statistic AF would be easier to be interpreted compared with hazard ratios (HR), which often requires several assumptions.
 
-We understand that some readers may not be familiar with the alternative and relatively computationally expensive approach.
-The biggest features in the traditional Cox proportional hazard model or any other classical statistical methods are that they assume 1) there is only one true but unknown value of the parameter (in this context, the HR and AF) from the data at hand to estimate; 2) the experiment/study can be repeated, therefore the confidence intervals in that framework uses standard error to provide precision for the estimates that can be interpreted as "if we repeat the same experiment for many times, 95% of these confidence intervals will contain the true but unknown value of interest"; 3) continue on the repeatable assumption, so that the P-values are actually saying that "if we can repeat the same experiment for many times, the same or more extreme results can happen with this probability, if this probability is lower than 0.05 (commonly used as the cut-off value but without actual solid scientific support) it is considered as rarely happens or 'statistically significant'."
+We also realized that not many readers would be familiar with the method employed in the present study.
+In an attempt to briefly introduce the Bayesian approach to the reviewer, we would like to give our understanding of the traditional Cox proportionla hazard model (or any other classical statistical methods).
+First, it assumes only one true but unknown value of the parameter (in this context, the HR and AF) is going to be obtained from the data at hand.
+Second, it assumes that the experiment/study can be repeated.
+This is fundamental to the calculation of the confidence intervals through the calculation of standard errors so that they can be interpreted as "if we repeat the same experiment for many times, 95% of these confidence intervals will contain the true but unknown value of interest".
+Third and similarly, a P-value is the probability of observing a certain or more extreme results if an experiment/study can be repeated, which would raise a question that relying on P<0.05 criterion may not be valid if the repeatable assumption is not valid.
 
-Bayesian ways of statistical analyses would disagree with all of the above assumptions because literally no one experiment/study can be repeated especially large scale cohort studies that take years and many participants/investigators to carry out.
-Bayesian statistics would provide a posterior distribution of the parameter that we want to estimates which means that the HR or AF is not fixed and unknown but with a distribution that has a mean and a standard deviation to describe its features, and the 95% credible intervals is directly showing us that we are 95% sure that the parameter of interest is distributed in this range.
-Furthermore, because of the large amount of simulations that we have conducted, the Pr(HR < 1) is showing the percentages that these HRs are smaller than 1.
-So a percentage of Pr(HR < 1) = 99% can be directly interpreted as "we are 99% sure that drinking milk at this frequency has lower hazard than those who never consume milk." The models in both classical and the Bayesian frameworks are the same, so the HRs from both frameworks can be interpreted in the same way.
-However, the estimating processes are different: one is based on the maximum likelihood estimation but the other is based on extensive Markov Chain Monte Carlo (MCMC) simulation.
-Therefore we would say that the only limitation for the Bayesian approach would be the computational cost but with the development of the modern computers we expect the Bayesian approaches would become the future default.
-The above discussion would be out of the scope of the current paper but we understand the confusions could still exist even if we add them into the manuscript.
-As requested, we added some of the discussion in the revised manuscript in the "strength and limitation" section.
+Instead of employing the unrealistic repeatable assumption, Bayesian ways of statistical analyses provide a posterior distribution of the parameter of interest.
+In other words, it estimates the a statistic (e.g., HR, AF, etc.) with a distribution that can be described by its mean and standard deviation.
+And through which the 95% credible intervals can be presented and be interpreted as we are 95% sure that the parameter of interest is distributed in this range.
+Although Bayesian approach requires extensive simulations, it provides straightforward results, that is, Pr(HR < 1), the precentages of observed HRs that were smaller than 1.
 
-- *Why were analyses performed stratified by sex?
+We would like to emphasize that the statistical models used in the Bayesian approach is the same as that in the traditional approach.
+Therefore, the meaning of HRs is the same.
+One and the biggest drawback of the Bayesian approach is the extensive computational cost, which was partly resolved by the recent advancement of personal computers.
+Nevertheless, we presented results obtained using the Bayesian approaches in the present study since we believe it is more appropriate statistically.
+We have added these issues in the "strength and limitation" section of the revised manuscript.
+
+- *#3: Why were analyses performed stratified by sex?
 Since no pooled analysis is presented, the reason for a stratified analysis should be stated in the aims, unless this was a secondary analysis and then also the results from the total cohort should be presented.
@@
 
-[Response:] It is reasonable to conduct the analysis separated in men and women since we expected there is a sex difference in the association based on our prior knowledge from the same cohort as well as the Singapore Chinese Health Study.
-Our expectation was further confirmed through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, not shown in the main text).
-Our stratified analyses also suggested the AFs and HRs might be in slightly different directions among 2 out of 4 frequencies (Table 2 and Table 3, results in the "total stroke" parts), we therefore believe it is legitimate to conduct analyses stratified by sex.
+[Response:] Thanks for the pertinent comment.
+Although we conducted the presenty analyses in men and women separately from the beginning based our previous finding from the same cohort as well as on a prior finding from the Singapre Chinese Health Study, the rationale might not have have been clear.
+We have revised the manuscript (Methods) incorporating the point.
+Nevertheless, a test of interaction for milk intake by sex indicated significant interaction (using traditional likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies, P < 0.0001, not shown in the main test).
+Stratified analyses by sex also suggested the directions of AFs and HRs differ in a few frequency categories (Table 2 and 3, results in the "total stroke" parts).
 
-The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better lifestyles (much less smokers and alcohol drinkers) than men regardless of milk intake frequency, or maybe due to other factors that was not available in/considered by our models such as intake of calcium or other supplements.
-The existing beneficial effect by milk intake is probably less evident in women than that in men in the JACC study cohort.
+We have also added possible explanations for the sex-interaction in the Discussion.
 
-The updated manuscript have included these information in the methods section as well as in the discussion about sex differences on the association.
-
-- *The aim states to “provide a more straightforward answer to the primary research question” – compared to what?
+- *#4: The aim states to “provide a more straightforward answer to the primary research question” – compared to what?
 And how is this more straightforward answer achieved.
@@
 
-[Response:] Thanks for your suggestion.
+[Response:] Thanks
+
+Thanks for your suggestion.
 The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs < 1 calculated through the large amount of simulations.

### 2020-08-30 Paperfolder/MDPI_submission/Revision01/MDPI_submission/Paperfolder.tex
revision 01 99% done

@@
 (95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
-study has provided strong evidence that daily milk intake among Japanese
-men was associated with delayed and lower hazard of mortality from
-stroke especially cerebral infarction.}
+study provided strong evidence that daily milk intake among Japanese men
+was associated with delayed and lower hazard of mortality from stroke
+especially cerebral infarction.}
 
@@
 American regions \citep{Kim2014}. Dairy foods, especially milk has been
-suggested to related with decreased stroke risk by nearly 7\% for each
+suggested to relate with decreased stroke risk by nearly 7\% for each
 200 g increment of daily consumption \citep{DeGoede2016}. Although 2
@@
 from stroke be postponed by having a milk intake habit?'' The later
-question is indeed directly comparing the length of times before events
-or the speed from the same departure point (entry of the study) to a
-fatal stroke event. Accelerated failure time models (AFT) under Bayesian
+question is directly comparing the length of times before events or the
+speed from the same departure point (entry of the study) to a fatal
+stroke event. Accelerated failure time models (AFT) under Bayesian
 framework are convenient tools that would help avoid worrying about the
@@
 study, data from a total of 110585 individuals (46395 men and 64190
-women) who aged between 40-79 at the baseline year were successfully
-retained for the current analysis. We further excluded samples if they
-meet one of the following criteria: 1) with any disease history of
-stroke, cancer, myocardial infarction, ischemic heart disease, or other
-types heart disease (n = 6655, 2931 men and 3724 women); 2) did not
-answer the question regarding their milk consumption in the baseline FFQ
-survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men
-and 54999 women) are left in the database. The study design and informed
-consent procedure were approved by the Ethics Review Committee of
-Hokkaido University School of Medicine.
+women) who aged between 40-79 at the baseline were successfully retained
+for the current analysis. We further excluded samples if they meet one
+of the following criteria: 1) with any disease history of stroke,
+cancer, myocardial infarction, ischemic heart disease, or other types
+heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the
+question regarding their milk consumption in the baseline FFQ survey (n
+= 9545, 3593 men and 5952 women). Finally, 94385 (39386 men and 54999
+women) are left in the database. The study design and informed consent
+procedure were approved by the Ethics Review Committee of Hokkaido
+University School of Medicine.
 
@@
 total stroke in crude models. Velocities that milk consumers dying from
-stroke is slower by a crude acceleration factor (AF) between 0.79 (SD =
-0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85, 1.02)
-compared with non-consumers. Chances that the posterior crude HRs were
-estimated to be lower than 1 for those who had at least 1-2 times/month
+stroke was slowed down by a crude acceleration factor (AF) between 0.79
+(SD = 0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85,
+1.02) compared with non-consumers. Chan-
 
@@
 
-\noindent was higher than 86.5\% in men and greater than 94.6\% in
-women. However, lower hazard and delayed time-to-event was observed to
-remain after age or multivariable adjustment only among daily male milk
-consumers. Specifically, the mean (SD; 95\% CrI) of posterior
-multivariable-adjusted AF and HR for daily male consumers of milk were
-0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95\% CrI:
-0.69, 0.93) with a probability of 99.0\% to be smaller than the null
-value (=1). Daily female milk consumers had posterior AFs and HRs that
-were distributed with means of 0.97 (SD = 0.09; 95\% CrI: 0.88, 1.10)
-and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
-chance that their HRs could be smaller than 1.
+\noindent  ces that the posterior crude HRs were estimated to be lower
+than 1 for those who had at least 1-2 times/month was higher than 86.5\%
+in men and greater than 94.6\% in women. However, lower hazard and
+delayed time-to-event was observed to remain after age or multivariable
+adjustment only among daily male milk consumers. Specifically, the mean
+(SD; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
+male consumers of milk were 0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and
+0.80 (SD = 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
+be smaller than the null value (=1). Daily female milk consumers had
+posterior AFs and HRs that were distributed with means of 0.97 (SD =
+0.09; 95\% CrI: 0.88, 1.10) and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17)
+which had about 78.0\% of chance that their HRs could be smaller than 1.
 
@@
 at the baseline and was self-reported. Apparently life habits are
-possible to alter over time and these would result in misclassfication
-and residual confoundings. Second, despite reasonable validity of FFQ in
+possible to alter over time and these would result in misclassification
+and residual confounding. Second, despite reasonable validity of FFQ in
 the JACC study cohort was assessed and confirmed, measurement errors are
@@
 who never consumed milk. Time before an event of stroke mortality
-occurred were slowed down and delayed among men who drank milk
-regularly.
+occurred were slowed down among men who drank milk regularly.
 

### 2020-08-30 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd
updated revision submitted

@@
 
-[Response:] Thanks
-
-Thanks for your suggestion.
-The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs < 1 calculated through the large amount of simulations.
-The detailed interpretation is described above in answering your second comment.
-These probabilities show directly how certain it is for individuals with that milk intake frequency could have lower hazard compared with those who never consume milk.
-In the traditional way the answer was not clear since only estimates of HRs, 95% confidence intervals, and/or P-values were shown.
-None of these actually can directly answer the question "how sure it is to have lower hazard in one group compared with another?" We have added clearer descriptions about these research questions and interpretations.
+[Response:] Thanks for the useful suggestion.
+We meant that the Bayesian approach would provide more straightforward answer compared to traditional statistical approach.
+We have added clearer descriptions about these research questions and interpretations in Introduction and Discussion.
 
@@
 
-[Response:] Thanks for your suggestions.
-In the baseline year of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk.
+[Response:] We appreciate the reviewer's great points.
+During the baseline years of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk.
 We have added the context of milk intake in Japan for participants who were invited into the JACC study.
+For detailed description about more current situation, as we cited in the Introduction (Reference #4, as cited below), the per capta consumption is still much lower than that in the western population:
+
+Saito, A.; Okada, E.; Tarui, I.; Matsumoto, M.; Takimoto, H.
+The Association between Milk and Dairy Products Consumption and Nutrient Intake Adequacy among Japanese Adults: Analysis of the 2016 National Health and Nutrition Survey.
+Nutrients 2019, 11, 2361.
 
@@
 
-[Response:] We have added these detailed information at the beginning of the results section.
+[Response:] We are grateful to the reviewer's suggestion.
+We have added these detailed information at the beginning of the Results section.
 In the study area, investigators conducted systematic review of death certificates till the end of 2009.
@@
 
-[Response:] Thanks for your positive comments.
-The validation study of the FFQ used in the JACC study found that the median intake for a daily milk consumer was about 146 grams per day.
+[Response:] Thanks for the suggestion.
+The validation study of the FFQ used in the JACC study found that the median intake for a milk consumer was about 146 grams per day.
 This has been added in the first paragraph of "2.2 Exposure and the outcome of interest" section.
@@
 [Response:] Thanks for pointing this out.
-Previous report (cited as below) using the same data showed that healthy lifestyle behaviors (including milk intake daily and proper sleep duration) were associated with CVD mortality and therefore, we also included sleep duration as one of the potential confounders.
+A previous report from the JACC Study (cited as below) showed that healthy lifestyle behaviors are closely related with each other and (including milk intake daily and proper sleep duration) were associated with CVD mortality.
+Therefore, we also included sleep duration as one of the potential confounders.
 

### 2020-08-30 Paperfolder/Paperfolder.Rmd
updated revision submitted

@@
 Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.
-In conclusion, data from the JACC study has provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.
+In conclusion, data from the JACC study provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.
 keywords: |
@@
 Eastern Asian populations were reported to have higher burden from both mortality and morbidity from stroke than populations in European or American regions [@Kim2014].
-Dairy foods, especially milk has been suggested to related with decreased stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
+Dairy foods, especially milk has been suggested to relate with decreased stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016].
 Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019].
@@
 Moreover, a more intuitive or straightforward interpretation would be available if we were able to show the probabilities and the certainty that the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke.
-This would require transformation of the research question into "Do individuals with milk intake habit have lower hazard of dying from a stroke event?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is indeed directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event.
+This would require transformation of the research question into "Do individuals with milk intake habit have lower hazard of dying from a stroke event?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event.
 Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumptions of repeatability of a large scale prospective study, and can calculate the exact proportion of posterior estimates (hazard ratios, HR) that is lower than 1.
@@
 Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer.
-In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) who aged between 40-79 at the baseline year were successfully retained for the current analysis.
+In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) who aged between 40-79 at the baseline were successfully retained for the current analysis.
 We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women).
@@
 Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models.
-Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (SD = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers.
-Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month
+Velocities that milk consumers dying from stroke was slowed down by a crude acceleration factor (AF) between 0.79 (SD = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers.
+Chan-
 
@@
 
-\noindent was higher than 86.5% in men and greater than 94.6% in women.
+\noindent  ces that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women.
 However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers.
@@
 First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported.
-Apparently life habits are possible to alter over time and these would result in misclassfication and residual confoundings.
+Apparently life habits are possible to alter over time and these would result in misclassification and residual confounding.
 Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable.
@@
 In conclusion, the JACC study database has provided evidence that Japanese men who consumed milk daily had lower hazard of dying from stroke particularly cerebral infarction compared with their counterparts who never consumed milk.
-Time before an event of stroke mortality occurred were slowed down and delayed among men who drank milk regularly.
+Time before an event of stroke mortality occurred were slowed down among men who drank milk regularly.
 

### 2020-09-04 Paperfolder/MDPI_submission/proofreading/nutrients-903270.tex
updated modification proofreading

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
%\documentclass[nutrients,article,submitted,moreauthors,pdftex]{Definitions/mdpi}
\documentclass[nutrients,article,accept,moreauthors,pdftex]{Definitions/mdpi} 
% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{4pt}}
\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

\usepackage{longtable}

% see https://stackoverflow.com/a/47122900
\usepackage{array} \newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}m{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}m{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}m{#1}}
%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by:
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
\usepackage{hhline}
%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2020}
\copyrightyear{2020}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Milk Intake and Stroke Mortality in the Japan Collaborative
Cohort Study---A Bayesian Survival~Analysis}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{https://orcid.org/0000-0001-5533-1497} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{https://orcid.org/0000-0002-6220-9251} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{https://orcid.org/0000-0003-0214-3649} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorD}{https://orcid.org/0000-0002-7417-5693} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorE}{https://orcid.org/0000-0002-5156-4880} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorF}{https://orcid.org/0000-0001-9499-9668} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorG}{https://orcid.org/0000-0002-9241-7289} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorH}{https://orcid.org/0000-0002-9761-3879} % Add \orcidA{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Chaochen Wang $^{1,}$*\orcidA{}, Hiroshi Yatsuya $^{2}$\orcidB{}, Yingsong Lin $^{1}$\orcidC{}, Tae Sasakabe $^{1}$\orcidD{}, Sayo Kawai $^{1}$\orcidE{}, Shogo Kikuchi $^{1}$\orcidF{}, Hiroyasu Iso $^{3}$\orcidG{} and Akiko Tamakoshi $^{4}$\orcidH{}}
%MDPI: Please carefully check the accuracy of names and affiliations.

% Authors, for metadata in PDF
\AuthorNames{Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Tae
Sasakabe, Sayo Kawai, Shogo Kikuchi, Hiroyasu Iso, Akiko Tamakoshi}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad  Department of Public Health, Aichi Medical University
School of Medicine, 1-1 Yazakokarimata, Nagakute~480-1195,~Aichi,~Japan \\
% $^{2}$ \quad \hl{Department} of Public Health, Aichi Medical University
% School of Medicine, \hl{Nagakute}, Japan; linys@aichi-med-u.ac.jp (Y.L.); tsasa@aichi-med-u.ac.jp (T.S.); ksayo@aichi-med-u.ac.jp (S.K.); kikuchis@aichi-med-u.ac.jp (S.K.)\\
$^{3}$ \quad Departmet of Public Health, Fujita Health University School
of Medicine, Toyoake, Japan; %yatsuya@fujita-hu.ac.jp\\
$^{4}$ \quad Public Health, Department of Social Medicine, Osaka
University Graduate School of Medicine, Osaka, Japan; %iso@pbhel.med.osaka-u.ac.jp\\
$^{5}$ \quad Department of Public Health, Hokkaido University, Faculty
of Medicine, Sapporo, Japan; %tamaa@med.hokudai.ac.jp\\
}
%MDPI: Please check the aff 1 and 2's address. If they are same, please delete one.
%MDPI: Please add the city's post code.
% C.W. the other co-authors did not agree to print all of their email addresses.
% Contact information of the corresponding author
\corres{Correspondence: chaochen@wangcc.me; Tel.: +81-561-62-3311}

% Current address and/or shared authorship

% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim of this study was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort (JACC) Study (total number of
participants = 110,585, age range: 40--79) to estimate the posterior
acceleration factors (AF) as well as the hazard ratios (HR) comparing
individuals with different milk intake frequencies against those who
never consumed milk at the study baseline. These estimations were
computed through a series of Bayesian survival models that employed a
Markov Chain Monte Carlo simulation process. In total, 100,000 posterior samples
were generated separately through four independent chains after model
convergency was confirmed. Posterior probabilites that daily milk
consumers had lower hazard or delayed mortality from strokes compared to
non-consumers was 99.0\% and 78.0\% for men and women, respectively.
Accordingly, the estimated posterior means of AF and HR for daily milk
consumers were 0.88 (95\% Credible Interval, CrI: 0.81, 0.96) and 0.80
(95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI: 0.88, 1.10) and 0.95
(95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
study provided strong evidence that daily milk intake among Japanese men
was associated with delayed and lower risk of mortality from stroke
especially cerebral infarction.}

% Keywords
\keyword{milk intake; mortality; stroke; Bayesian survival anlysis;
time-to-event data; JACC study}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphicx}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Eastern Asian populations were reported to have a higher burden from both
mortality and morbidity from stroke than populations in European or
American regions \citep{Kim2014}. Dairy foods, especially milk, have been
suggested to relate with decreased stroke risk by nearly 7\% for each
200 g increment of daily consumption \citep{DeGoede2016}. Although~two
daily servings of milk or dairy products is recommended in \mbox{Japan
\citep{Yoshiike2007}}, the~actual per capita intake (\(\approx\)63
g/day) of these food groups is much lower and less frequent than that in
Western countries \citep{Saito2019}. Given that previous reports have
also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, it would be of interest to provide
information on the association within a context where most individuals
have much lower range of milk intake compared to most of the previous
studies. Whether people with such a low level intake of milk can still
benefit against stroke would requires~elucidation.

Moreover, a~more intuitive or straightforward interpretation would be
available if we were able to show the probabilities and the certainty
that the existing data can provide evidence about whether drinking milk
can delay or lower the hazard of dying from stroke. This would require
the transformation of the research question into ``Do individuals with milk
intake habit have lower hazard of dying from a stroke event?'' Another
way of asking the same research question would be ``Can an event of dying
from stroke be postponed by forming a milk intake habit?'' The later
question directly compares the length of times before events or the
speed from the same departure point (entry of the study) to a fatal
stroke event. Accelerated failure time (AFT) models under the Bayesian
framework are convenient tools that would help to avoid worrying about the
assumptions of repeatability of a large scale prospective study, and~can
calculate the exact proportion of posterior estimates (hazard ratios,
HR) that are lower than 1. AFT model is helpful in estimating
acceleration factors (AF) which can be interpreted as the velocity for
developing an event of interest. This velocity parameter shows how
faster/slower individuals in one exposure group might have an event
compared to others in different exposure groups
\citep{Wei1992, ibrahim2014b}.

Our aim was to provide a more straightforward answer to the primary
research question that, whether someone answering that he/she drank milk at the
baseline of study, had lower hazard of dying from stroke compared with
his/her counterparts who said they never consumed milk. If~the answer to
the primary objective was yes, then the probabilities that individuals
with different frequencies of milk intake may have lower risk compared
with those who never drank milk were calculated through a Markov Chain
Monte Carlo (MCMC) simulation process. A~Bayesian survival analysis
method was applied on an existing database and through which we
provided estimates about whether drinking milk could delay a stroke
mortality event from happening after controlling for the other \mbox{potential
confounders.}

\hypertarget{materials-and-methods}{%
\section{Materials and~Methods}\label{materials-and-methods}}
\vspace{-5pt}

\hypertarget{the-database}{%
\subsection{The~Database}\label{the-database}}

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and~Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants in the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and~medical histories
of cardiovascular disease or cancer. In~the final follow-up of the JACC
study, data from a total of 110,585 individuals (46,395 men and 64,190
women) who, aged between 40--79 at the baseline, were successfully retained
for the current analysis. We further excluded samples if they met one
of the following criteria: (1) with any disease history of stroke,
cancer, myocardial infarction, ischemic heart disease, or~other types
heart disease (\emph{n} = 6655, 2931 men and 3724 women); (2) did not answer the
question regarding their milk consumption in the baseline FFQ survey (\emph{n}
= 9545, 3593 men and 5952 women). Finally, 94,385 (39,386 men and 54,999
women) were left in the database. The~study design and informed consent
procedure were approved by the Ethics Review Committee of Hokkaido
University School of~Medicine.

\hypertarget{exposure-and-the-outcome-of-interest}{%
\subsection{Exposure and the Outcome of~Interest}\label{exposure-and-the-outcome-of-interest}}

Frequency of milk intake during the preceding year of the baseline was
assessed by FFQ as ``never'', ``1--2 times/month'', ``1--2 times/week'',
``3--4 times/week'', and~``Almost daily''. The~exact amount of milk
consumption was difficult to assess here. However, good reproducibility
and validity were confirmed previously (Spearman rank correlation
coefficient between milk intake frequency and weighed dietary record for
12 days was 0.65) \citep{Date2005}. From~the same validation study
\citep{Date2005} on the FFQ, daily consumers of milk were found to have a
median intake of 146 grams. At~the baseline of the JACC study
(between 1988 and 1990), most ``milk and dairy product'' consumption
(92.1\%) was in the form of whole milk \citep{eigyogenjyo}.

In the study area, investigators conducted a systematic review of death
certificates till the end of 2009. Date and cause of death were
confirmed with the permission of the Director-General of the Prime
Minister's Office. The~follow-up period was defined as from the time
the baseline survey was completed, which was between 1988--1990, until~the end of 2009 (administrative censor), the date when they moved out of
the study area, or~the date of death from stroke was recorded---whichever
occurred first. Other causes of death were treated as censored and
assumed not informative. The~causes of death were coded by the 10th
Revision of the International Statistical Classification of Diseases and
Related Health Problems (ICD-10); therefore, stroke was defined as
I60--I69. We further classified these deaths into hemorrhagic stroke
(I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke
in their death certificates were~available.

\hypertarget{statistical-approach}{%
\subsection{Statistical~Approach}\label{statistical-approach}}

Analyses were stratified by sex as difference in milk consumption levels
and mortality rate were suggested previously
\citep{wang_milk_2015, Talaei_2016}. We calculated sex-specific means
(standard deviation, SD) and proportion of selected baseline
characteristics according to the frequency of milk intake. Age-adjusted
stroke mortality rate were expressed as per 1000 person-year,
 predicted
through poisson regression~models.

Full parametric proportional hazard models under Bayesian framework with
Weibull distribution were fitted using Just Another Gibbs Sampler (JAGS)
program \citep{Plummer2003}, version 4.3.0 in R, version 4.0.1
\citep{RCT2020}. JAGS program is similar to the OpenBUGS
\citep{Lunn2009} project that uses a Gibbs sampling engine for MCMC
simulation. In~the current analysis, we specified non-informative prior
distributions for each of the parameters in our models
(\(\beta_n \sim N(0, 1000)\), and~\(\kappa_{\text{shape}} \sim \Gamma(0.001, 0.001)\)). The~Brooks--Gelman--Rubin diagnostic \citep{Brooks1998} was used to refine the
approximate point of convergence, the~point when the ratio of the chains
is stable around 1 and the within and between chain variability start to
reach stability, was visually checked. The~auto-correlation tool further
identified if convergence has been achieved or if a high degree of
auto-correlation exists in the sample. Then, the~number of iterations
discarded as ``burn-in'' was chosen. All models had a posterior sample
size of 100,000 from four separated chains with a ``burn-in'' of 2500
iterations. Posterior means (SD) and 95\% Credible Intervals (CrI) of
the estimated hazard ratios (HRs), as well as acceleration factors (AFs),
were presented for each category of milk intake frequency taking the
``never'' category as the reference. Posterior probabilities that the
estimated hazard of dying from stroke for the milk intake for frequency
that higher or equal to ``1--2~times/month'' were smaller compared with
those who chose ``never'' for their milk intake frequency, and were calculated
as \(Pr(\text{HR} < 1)\).

The parametric forms of the models fitted in the Bayesian survival
analyses included three models: (1) the crude model, (2) the age-centered
adjusted model, (3) and a model further adjusted for potential
confounders which includes: age (centered, continuous), smoking habit
(never, current, former), alcohol intake (never or past, \(<\)4
times/week, Daily), body mass index (\(<\)18.5, \(\geq\)18.5 and \(<\)25, \(\geq\)25~and \(<\)30, \(\geq\)30 kg/m\(^2\)), history of
hypertension, diabetes, kidney/liver diseases (yes/no), exercise (more
than 1 h/week, yes/no), sleep duration (\(<\)7, \(\geq\)7 and \(<\)8, \(\geq\)8 and \(<\)9, \(\geq\)9, hours), quartiles of total energy
intake, coffee intake (never, \(<\)3--4 times/week, almost daily), and~education level (attended school till age 18, yes/no).

\hypertarget{results}{%
\section{Results}\label{results}}

The total follow-up was 1,555,073 person-year (median = 19.3 years),
during which 2675~deaths from stroke were confirmed (1352 men and 1323
women). Among~these stroke mortalities, 952~were hemorrhagic stroke (432
men and 520 women), and~957 were cerebral infarction (520 men and \mbox{437
women}). The number of deaths from causes other than stroke was 18,868 (10,731
men and 8137~women); 5493 (2022 men and 3471 women) dropped out from the
follow-up (5.8\%); 67,349 (25,281~men and 42,068 women) were censored at
the end of follow-up (71.4\%). The~medians (interquartile range, IQR) of
follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in
men and 10.9 (5.9, 15.1) in women; the medians (IQR) of follow-up years
for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9,
16.4) in men and women, respectively. Age-adjusted stroke mortality
rates for each category of milk intake frequency was estimated to be
1.8, 2.0, 1.7, 1.6, an 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2,
1.1, and 1.2 per 1000 person-year for~women.

As listed in {Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people who consumed milk more
than 1--2 times/month were more likely to be a daily consumers of
vegetables and fruit, as well as coffee, and~were~more likely to perform exercise
more than 1~h/week among both~sexes.

\begin{table}[H]

\caption{\label{tab:tab1f}Sex-specific baseline characteristics according to the frequency of milk intake  (JACC study, 1988--2009).}
\centering
\fontsize{8}{10}\selectfont
\resizebox{\textwidth}{!}{%
\begin{tabular}[t]{lcccccc}
\noalign{\hrule height 1.0pt} 
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{\textbf{Milk Drinkers}} \\
\cmidrule{4-7}
 & \textbf{Never} & \textbf{Drinkers} & \textbf{1--2 Times/} & \textbf{1--2 Times/} & \textbf{3--4 Times/} & \textbf{Almost}  \\
 &       &         & \textbf{Month}     & \textbf{Week}      & \textbf{Week}         & \textbf{Daily}\\
\hline
%    %MDPI: Is the gray background necessary? If not, please delete it in the all tables.
\multicolumn{7}{l}{\textbf{Men (\emph{n} = 39,386)}}\\
\hspace{1em}Number of subjects & 8508 & 30,878 & 3522 & 5928 & 5563 & 15,865\\
\hspace{1em}Age, year (mean (SD)) & 56.8 (9.9) & 56.8 (10.2) & 55.2 (10.1) & 55.4 (10.1) & 55.4 (9.9) & 58.1 (10.1)\\
   \hspace{1em}Current smoker, \% & 58.7 & 49.8 & 57.4 & 55.9 & 51.1 & 45.4\\
\hspace{1em}Daily alcohol drinker, \% & 51.9 & 47.8 & 50.9 & 48.4 & 48.6 & 46.5\\
   \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 22.6 (3.4) & 22.7 (3.4) & 22.8 (2.8) & 22.8 (2.8) & 22.9 (5.4) & 22.6 (2.8)\\
\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5\\
   \hspace{1em}Sleep duration, 8--9 hours, \% & 35.6 & 35.9 & 34.6 & 36.2 & 35.1 & 36.3\\
\hspace{1em}Energy intake, kcal/day (mean (SD))  & 1611 (505) & 1764 (504) & 1606 (496) & 1679 (495) & 1772 (509) & 1830 (495)\\
\hspace{1em}Vegetable intake, daily, \% & 21.3 & 25.4 & 20.1 & 20.4 & 20.8 & 30.1\\
   \hspace{1em}Fruit intake, daily, \% & 14.8 & 22.4 & 15.4 & 16.3 & 17.3 & 28.1\\
\hspace{1em}Green tea intake, daily, \% & 76.5 & 79.2 & 79.9 & 78.3 & 77.9 & 79.8\\
   \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9\\
\hspace{1em}Educated over 18 years old, \% & 9.9 & 14.1 & 12.4 & 12.8 & 11.1 & 15.9 \\
   \hspace{1em}History of diabetes, \% & 5.0 & 6.3 & 4.5 & 4.2 & 5.5 & 7.7\\
\hspace{1em}History of hypertension, \% & 18.4 & 17.9 & 17.5 & 17.1 & 16.8 & 18.7\\
   \hspace{1em}History of kidney diseases, \% & 3.0 & 3.4 & 3.8 & 3.0 & 3.0 & 3.5\\
\hspace{1em}History of liver diseases, \% & 5.8 & 6.5 & 6.3 & 6.0 & 5.4 & 7.2\\
   \addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{Women (\emph{n} = 54,999)}}\\
\hspace{1em}number of subjects & 10,407 & 44,592 & 3640 & 7590 & 8108 & 25,254\\
\hspace{1em}Age, year (mean (SD)) & 58.0 (10.2) & 56.9 (9.9) & 56.5 (10.2) & 55.6 (10.1) & 55.6 (9.9) & 57.9 (9.9)\\
   \hspace{1em}Current smoker, \% & 6.9 & 4.2 & 6.1 & 5.5 & 4.3 & 3.5\\
\hspace{1em}Daily alcohol drinker, \% & 4.3 & 4.5 & 5.5 & 4.3 & 4.2 & 4.6\\
   \hspace{1em}BMI, kg/m$^2$ (mean (SD)) & 23.0 (3.4) & 22.9 (3.7) & 23.0 (3.8) & 23.1 (4.4) & 23.1 (3.1) & 22.8 (3.6)\\
\hspace{1em}Exercise (> 1h/week), \% & 13.6 & 20.8 & 17.1 & 18.5 & 18.8 & 22.6\\
   \hspace{1em}Sleep duration, 8--9 hours, \% & 27.7 & 25.6 & 25.1 & 25.9 & 25.4 & 25.7\\
\hspace{1em}Energy intake, kcal/day (mean (SD)) & 1519 (451) & 1690 (449) & 1522 (447) & 1596 (443) & 1661 (432) & 1752 (443)\\
\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8\\
   \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1\\
\hspace{1em}Green tea intake, daily, \% & 73.8 & 76.8 & 77.0 & 76.4 & 75.8 & 77.3\\
   \hspace{1em}Coffee intake, daily, \% & 39.6 & 48.2 & 46.2 & 46.4 & 44.4 & 50.2\\
\hspace{1em}Educated over 18 years old, \% & 4.8 & 8.3 & 6.7 & 7.2 & 6.5 & 9.4\\
   \hspace{1em}History of diabetes, \% & 2.6 & 3.7 & 3.2 & 2.7 & 2.7 & 4.4\\
\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0\\
   \hspace{1em}History of kidney diseases, \% & 3.6 & 4.1 & 3.9 & 3.7 & 3.7 & 4.4\\
\hspace{1em}History of liver diseases, \% & 3.5 & 4.6 & 4.9 & 3.9 & 3.9 & 5.0\\
\noalign{\hrule height 1.0pt}

\end{tabular}}

\begin{tabular}{ccc}
\multicolumn{1}{c}{\footnotesize Note: Abbreviations: JACC: Japan Collaborative Cohort; SD: standard deviation; BMI: body mass index.}
\end{tabular}

\end{table}

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable- adjusted) according to the frequency of milk intake
separated by sex are listed in {Table \ref{tab:tab2}} (men) and
{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke were slowed down by a crude acceleration factor (AF) between 0.79
(SD = 0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85,
1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1--2~times/month was higher than 86.5\%
in men and greater than 94.6\% in women. However, lower hazard and
delayed time-to-event was observed to remain after age or multivariable
adjustment only among daily male milk consumers. Specifically, the~means
(SD; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
male consumers of milk were 0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and
0.80 (\mbox{SD = 0.07;} 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
be smaller than the null value (=1). Daily female milk consumers had
posterior AFs and HRs that were distributed with means of 0.97 (SD =
0.09; 95\% CrI: 0.88, 1.10) and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17)
which had about a 78.0\% chance that their HRs could be smaller than~1.

\begin{table}[H]

\caption{\label{tab:tab2}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke types according to the frequency of milk intake in men (JACC study, 1988--2009).}
\centering

%\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
\scalebox{.95}[0.95]{\begin{tabular}{L{32mm}C{8mm}C{26mm}C{25mm}C{25mm}C{20mm}}
\noalign{\hrule height 1.0pt} 
\textbf{ } & \textbf{Never} & \textbf{1--2 Times/Month} & \textbf{1--2 Times/Week} & \textbf{3--4 Times/Week} & \textbf{Almost Daily}\\
\hline
   Person-year & 135,704 & 56,551 & 97,098 & 92,153 & 252,364\\
N & 8508 & 3522 & 5928 & 5563 & 15,865\\
   Total Stroke & 326 & 122 & 181 & 177 & 546\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.07) & 0.83 (0.05) & 0.85 (0.05) & 0.93 (0.04)\\
   \hspace{1em}95\% CrI & - & (0.81, 1.06) & (0.73, 0.94) & (0.74, 0.96) & (0.85, 1.02)\\
\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
   \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
\hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 1}}\\
   \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.06) & 0.90 (0.05) & 0.91 (0.05) & 0.85 (0.04)\\
\hspace{1em}95\% CrI & - & (0.87, 1.11) & (0.81, 1.00) & (0.82, 1.01) & (0.78, 0.92)\\
   \hspace{1em}Mean HR (SD) & 1 & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
\hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
   \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}Mean AF (SD) & 1 & 1.00 (0.07) & 0.92 (0.06) & 0.94 (0.06) & 0.88 (0.05)\\
   \hspace{1em}95\% CrI & - & (0.88, 1.14) & (0.82, 1.03) & (0.84, 1.05) & (0.81, 0.96)\\
\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
   \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
\hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\
\hline
   Hemorrhagic stroke & 100 & 42 & 58 & 56 & 176\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}Mean AF (SD) & 1 & 1.03 (0.17) & 0.85 (0.12) & 0.87 (0.13) & 0.98 (0.11)\\
   \hspace{1em}95\% CrI & - & (0.74, 1.38) & (0.63, 1.12) & (0.65, 1.14) & (0.78, 1.22)\\
\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
   \hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 1}}\\
   \hspace{1em}Mean AF (SD) & 1 & 1.08 (0.17) & 0.91 (0.13) & 0.92 (0.13) & 0.90 (0.10)\\
\hspace{1em}95\% CrI & - & (0.80, 1.45) & (0.70, 1.20) & (0.71, 1.19) & (0.74, 1.11)\\
   \hspace{1em}Mean HR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
\hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
   \hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}Mean AF (SD) & 1 & 1.11 (0.18) & 0.93 (0.15) & 0.96 (0.16) & 0.96 (0.13)\\
   \hspace{1em}95\% CrI & - & (0.79, 1.58) & (0.70, 1.25) & (0.71, 1.34) & (0.76, 1.25)\\
\hspace{1em}Mean HR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
   \hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\
\hline
   Cerebral infarction & 151 & 41 & 64 & 66 & 198\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}Mean AF (SD) & 1 & 0.76 (0.09) & 0.71 (0.07) & 0.74 (0.08) & 0.79 (0.06)\\
   \hspace{1em}95\% CrI & - & (0.59, 0.94) & (0.58, 0.86) & (0.61, 0.89) & (0.68, 0.93)\\
\hspace{1em}Mean HR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
   \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
\noalign{\hrule height 1.0pt}

\end{tabular}}

\end{table}
\unskip

\begin{table}[H]\ContinuedFloat

\caption{\textit{Cont}.}
\label{tab:tab2}
\centering
\fontsize{6}{8}\selectfont
%\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
\scalebox{.95}[0.95]{\begin{tabular}{L{32mm}C{8mm}C{26mm}C{25mm}C{25mm}C{20mm}}
\noalign{\hrule height 1.0pt} 
\textbf{ } & \textbf{Never} & \textbf{1--2 Times/Month} & \textbf{1--2 Times/Week} & \textbf{3--4 Times/Week} & \textbf{Almost Daily}\\
\hline

\hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 1}}\\
   \hspace{1em}Mean AF (SD) & 1 & 0.83 (0.08) & 0.79 (0.07) & 0.82 (0.07) & 0.74 (0.05)\\
\hspace{1em}95\% CrI & - & (0.68, 1.01) & (0.67, 0.93) & (0.69, 0.96) & (0.66, 0.84)\\
   \hspace{1em}Mean HR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
\hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
   \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}Mean AF (SD) & 1 & 0.84 (0.09) & 0.80 (0.08) & 0.83 (0.08) & 0.75 (0.06)\\
   \hspace{1em}95\% CrI & - & (0.67, 1.02) & (0.67, 0.95) & (0.69, 0.99) & (0.66, 0.85)\\
\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
   \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
\hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\
\noalign{\hrule height 1.0pt}

\end{tabular}}\\

\begin{tabular}{@{}c@{}} 
\multicolumn{1}{p{\textwidth -.88in}}{\footnotesize Note: Abbreviations: N, number of subjects,; SD, standard deviation; CrI, credible interval. Pr(HR < 1) indicates the probability for posterior HR to be smaller than 1. Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model. Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of hypertension, diabetes, kidney/liver diseases, exercise, sleep duration,  quartiles of total energy intake, coffee intake, and~education level.}
\end{tabular}

%\begin{tabular}{ccc}
%\multicolumn{1}{c}{\footnotesize Note: Abbreviations: N, number of subjects, SD, standard deviation; CrI, credible interval. Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1. Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model. Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of hypertension, diabetes, kidney/liver diseases, exercise, sleep duration,  quartiles of total energy intake, coffee intake, and~education level.}
%\end{tabular}

\end{table}
\unskip

\begin{table}[H]

\caption{Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke and stroke types according to the frequency of milk intake in women (JACC study, 1988--2009).}
\label{tab:tab3}
\centering
\fontsize{7}{9}\selectfont
%\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
\scalebox{.95}[0.95]{\begin{tabular}{L{32mm}C{8mm}C{26mm}C{25mm}C{25mm}C{20mm}}
\noalign{\hrule height 1.0pt} 
\textbf{ } & \textbf{Never} & \textbf{1--2 Times/Month} & \textbf{1--2 Times/Week} & \textbf{3--4 Times/Week} & \textbf{Almost Daily}\\
\hline
   Person-year & 173,222 & 59,904 & 129,233 & 139,919 & 418,925\\
N & 10,407 & 3640 & 7590 & 8108 & 25,254\\
   Total Stroke & 300 & 84 & 182 & 172 & 585\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}Mean AF (SD) & 1 & 0.88 (0.07) & 0.87 (0.05) & 0.79 (0.05) & 0.88 (0.04)\\
   \hspace{1em}95\% CrI & - & (0.75, 1.03) & (0.78, 0.98) & (0.71, 0.90) & (0.80, 0.96)\\
\hspace{1em}Mean HR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
   \hspace{1em}95\% CrI & - & (0.64, 1.05) & (0.68, 0.97) & (0.58, 0.85) & (0.71, 0.93)\\
\hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 1}}\\
   \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.09) & 1.11 (0.08) & 1.02 (0.08) & 0.95 (0.06)\\
\hspace{1em}95\% CrI & - & (0.85, 1.17) & (0.97, 1.26) & (0.89, 1.16) & (0.86, 1.06)\\
   \hspace{1em}Mean HR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
\hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
   \hspace{1em}Pr(HR < 1) & - & 52.3\% & 6.3\% & 42.0\% & 86.8\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.12) & 1.11 (0.14) & 1.02 (0.12) & 0.97 (0.09)\\
   \hspace{1em}95\% CrI & - & (0.85, 1.20) & (0.97, 1.30) & (0.89, 1.19) & (0.88, 1.10)\\
\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
   \hspace{1em}95\% CrI & - & (0.75, 1.36) & (0.96, 1.52) & (0.81, 1.31) & (0.80, 1.17)\\
\hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
\hline
   Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}Mean AF (SD) & 1 & 0.78 (0.13) & 0.98 (0.12) & 0.90 (0.11) & 0.92 (0.09)\\
   \hspace{1em}95\% CrI & - & (0.55, 1.06) & (0.76, 1.25) & (0.70, 1.13) & (0.76, 1.12)\\
\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
   \hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
\hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\
\multicolumn{6}{l}{\textbf{Model 1}}\\
   \hspace{1em}Mean AF (SD) & 1 & 0.88 (0.13) & 1.12 (0.13) & 1.04 (0.13) & 0.95 (0.09)\\
\hspace{1em}95\% CrI & - & (0.63, 1.17) & (0.90, 1.41) & (0.82, 1.32) & (0.80, 1.14)\\
   \hspace{1em}Mean HR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
\hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
   \hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
\addlinespace[0.3em]

\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.24) & 1.23 (0.38) & 1.14 (0.33) & 1.04 (0.25)\\
\noalign{\hrule height 1.0pt}

\end{tabular}}

\end{table}

\begin{table}[H]\ContinuedFloat

\caption{\textit{Cont}.}
\label{tab:tab3}
\centering
\fontsize{7}{9}\selectfont
%\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
\scalebox{.95}[0.95]{\begin{tabular}{L{32mm}C{8mm}C{26mm}C{25mm}C{25mm}C{20mm}}
\noalign{\hrule height 1.0pt} 
\textbf{ } & \textbf{Never} & \textbf{1--2 Times/Month} & \textbf{1-2 Times/Week} & \textbf{3--4 Times/Week} & \textbf{Almost Daily}\\
\hline

   \hspace{1em}95\% CrI & - & (0.64, 1.33) & (0.93, 1.98) & (0.87, 1.83) & (0.83, 1.55)\\
\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.22) & 1.26 (0.26) & 1.15 (0.23) & 1.02 (0.19)\\
   \hspace{1em}95\% CrI & - & (0.55, 1.39) & (0.90, 1.90) & (0.83, 1.74) & (0.78, 1.51)\\
\hspace{1em}Pr(HR < 1) & - & 73.2\% & 9.5\% & 24.8\% & 53.3\%\\
\hline
   Cerebral infarction & 102 & 35 & 63 & 50 & 187\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.13) & 0.90 (0.09) & 0.75 (0.08) & 0.86 (0.06)\\
   \hspace{1em}95\% CrI & - & (0.79, 1.27) & (0.75, 1.10) & (0.60, 0.91) & (0.75, 0.99)\\
\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.20) & 0.85 (0.14) & 0.61 (0.11) & 0.78 (0.10)\\
   \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
\hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 1}}\\
   \hspace{1em}Mean AF (SD) & 1 & 1.21 (0.32) & 1.16 (0.30) & 0.98 (0.19) & 0.97 (0.14)\\
\hspace{1em}95\% CrI & - & (0.95, 2.08) & (0.93, 1.95) & (0.79, 1.48) & (0.84, 1.43)\\
   \hspace{1em}Mean HR (SD) & 1 & 1.37 (0.33) & 1.25 (0.28) & 0.94 (0.22) & 0.92 (0.17)\\
\hspace{1em}95\% CrI & - & (0.89, 2.18) & (0.87, 1.95) & (0.63, 1.52) & (0.69, 1.40)\\
   \hspace{1em}Pr(HR < 1) & - & 8.5\% & 14.2\% & 70.1\% & 79.4\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}Mean AF (SD) & 1 & 1.19 (0.19) & 1.12 (0.15) & 0.96 (0.12) & 0.97 (0.09)\\
   \hspace{1em}95\% CrI & - & (0.94, 1.62) & (0.92, 1.49) & (0.78, 1.21) & (0.83, 1.18)\\
\hspace{1em}Mean HR (SD) & 1 & 1.38 (0.29) & 1.21 (0.22) & 0.91 (0.18) & 0.94 (0.14)\\
   \hspace{1em}95\% CrI & - & (0.89, 2.02) & (0.85, 1.70) & (0.62, 1.34) & (0.69, 1.25)\\
\hspace{1em}Pr(HR < 1) & - & 7.3\% & 15.6\% & 72.8\% & 70.0\%\\
\noalign{\hrule height 1.0pt}

\end{tabular}}

\begin{tabular}{@{}c@{}} 
\multicolumn{1}{p{\textwidth -.88in}}{\footnotesize Note: Abbreviations: N, number of subjects; SD, standard deviation; CrI, credible interval. Pr(HR < 1) indicates the probability for posterior HR to be smaller than 1. Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model. Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of hypertension, diabetes, kidney/liver diseases, exercise, sleep duration,  quartiles of total energy intake, coffee intake, and~education level.}
\end{tabular}
\end{table}
\vspace{-5pt}

Posterior distributions of AFs and HRs for mortality from hemorrhagic
stroke were found to contain the null value for either men or women
among all fitted models. In~contrast, men who a had milk intake frequency
higher than 1--2 times/week were found to be associated with an average of
17--20\% slower velocity or 28--39\% lower risk of dying from
cerebral infarction compared to men who never drank milk (Model 2 in
{Table \ref{tab:tab2}}). Probability that the posterior HRs
distributed below the null value was greater or equal to 97.5\%. No
evidence was found about the associations between milk intake and risk
of cerebral infarction mortality among~women.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

In the JACC study cohort, our analyses showed that men in Japan who
consumed milk almost daily had lower hazard of dying from stroke
especially from cerebral infarction. Our evidence also suggested that
stroke mortality events were delayed among Japanese male daily milk
consumers compared with~non-consumers.

These findings showed similar negative effect estimates that were
reported previously \citep{wang_milk_2015} using data from the same
cohort, in~which the outcomes of interest were focused on
cardiovascular diseases and all-cause mortality. Moreover, we have
further updated the results with more comprehensive and straightforward
evidence about whether and how certain the data shown about the daily
consumption of milk were contributing to a postponed stroke (mostly
cerebral infarction) mortality event among Japanese men. A~recent
dose-response meta-analysis of 18 prospective cohort studies showed a
similar negative association \citep{DeGoede2016} between milk
consumption and risk of stroke. The~same meta-analysis also reported a
greater reduction in risk of stroke (18\%) for East Asian populations in
contrast with the 7\% less risk in the pooled overall finding for all
populations combined. Benefits of increased milk intake might be
particularly noticeable in East Asian countries where strokes are
relatively more common, and~milk consumption is much lower than those
studies conducted among European or American populations
\citep{dehghan2018association}. However, the~Life Span Study
\citep{sauvaget2003intake}, which was conducted about 10~years earlier
than the JACC Study, reported a null association between milk intake and
fatal stroke among men and women combined who survived the
Hiroshima and Nagasaki atomic bomb. The~difference could be largely
explained by the different targeting populations between the two
\mbox{studies.~\citet{kondo2013consumption}} also reported a null association in
both men or women from the NIPPON DATA80 study. In~fact, the~exact
number of stroke mortality events was about 85\% less and the number of
participants in the NIPPON DATA80 study was about 90\% less than those in the
JACC study database---their null association might likely due to its
limited statistical power. \citet{umesawa2008dietary} reported that
dairy calcium intake was inversely associated with ischemic stroke
mortality risk, which could be considered as one of the potential
pieces of evidence that supported our findings. Furthermore, a stronger inverse
association between milk consumption and stroke mortality in men rather
than in women was found in the Singapore Chinese Health Study
\citep{Talaei_2016} as well. The~reasons for this gender difference is
currently unknown. This~might be due to generally better/healthier
lifestyles (such as much less smokers and alcohol drinkers) in women
regardless of milk intake frequency, or~maybe due to other factors that
were not available in/considered by our models, such as intake of calcium
or other supplements. The~probably existing beneficial effect of milk
intake might be less evident in women than in men. Further
investigation is~needed.

Possible reasons for a protective effect of milk consumption against
stroke could be interpreted, as such an association might be mediated by
its content in calcium, magnesium, potassium, and~other bioactive
compounds, as~recommended by \citet{Iacoviello2018}. Apart from the
inorganic minerals in milk that would be helpful with health effects,
recent studies on animal models also indicated key evidence that
stroke-associated morbidity was delayed in stroke-prone rats who were
fed with milk-protein enriched diets \citep{Chiba2012, singh2016diets}.
More precisely, \citet{Singh2020} found that whey protein and its
components---lactalbumin and lactoferrin---improved energy balance and
glycemic control against the onset of neurological deficits associated
with stroke. Bioactive peptides from milk proteins were also responsible
for the limitation of thrombosis \citep{tokajuk2019whey} through their
angiotensin convertase enzyme inhibitory potential, which might partly
explain why the effect was found mainly for mortality from cerebral
infarction in the current~study.

\hypertarget{strength-and-limitations}{%
\subsection*{Strength and~Limitations}\label{strength-and-limitations}}

Some limitations are worth mentioning here. First, the~milk intake
frequency, as well as other lifestyle information, was collected only once
at the baseline and was self-reported. Apparently, life habits are
possible to alter over time and these would result in misclassification
and residual confounding. Second, despite the fact that the reasonable validity of FFQ in
the JACC study cohort was assessed and confirmed, measurement errors are
inevitable. Therefore, we did not try to compute the amount of
consumption by multiplying an average volume per occasion with the
frequency of intake, since the random error might be exaggerated and the
observed associations may have attenuated. Third, the~Bayesian way of
conducting the survival analysis using a large sample size is
computationally expensive. However, the~classic maximum likelihood
estimations are based on unrealistic assumptions, such as repeatability
of the study, and fixed but unknown values of parameters, which are
unfulfilled in a large cohort study in the current setting. The strengths of
our analyses included that we transformed the research questions to
more transparent ones that are easier for interpretation. Direct
probabilities that daily milk intake is associated with lower hazard or
delayed stroke mortality event were provided here after thorough
computer~simulations.

\hypertarget{conclusion}{%
\section{Conclusions}\label{Conclusion}}

In conclusion, the~JACC study database provided evidence that
Japanese men who consumed milk daily had a lower risk of dying from
stroke, particularly cerebral infarction, compared with their counterparts
who never consumed milk. The time before an event of stroke mortality
occurred was slowed down among men who drank milk~regularly.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% optional
% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
%
% % Only for the journal Methods and Protocols:
% % If you wish to submit a video article, please do so with any other supplementary material.
% % \supplementary{The following are available at www.mdpi.com/link: Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

\vspace{6pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{C.W. and H.Y. conceived and designed the study;
C.W. analyzed the data; C.W. wrote the first draft of the paper. A.T.
provided the database. All authors (C.W., H.Y., Y.L., T.S., Sayo Kawai, Shogo Kikuchi, H.I., A.T.) have read and agreed to the published version of the manuscript.}
%MDPI: Please add the other author contributions. And please add the complete name of Sayo Kawai and Shogo Kikuchi.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{The~funding sponsors had no role in the design of the study; in the
collection, analyses, or~interpretation of data; in the writing of the
manuscript, or~in the decision to publish the~results. This study has been supported by Grants-in-Aid for Scientific Research from the Ministry of Education, Culture, Sports, Science and Technology of Japan (MEXT) (MonbuKagaku-sho); Grants-in-Aid for Scientific Research on Priority Areas of Cancer; Grants-in-Aid for Scientific Research on Priority Areas of Cancer Epidemiology from MEXT (nos. 61010076, 62010074, 63010074, 1010068, 2151065, 3151064, 4151063, 5151069, 6279102, 11181101, 17015022, 18014011, 20014026, 20390156, 26293138); and a JSPS KAKENHI (16H06277). This research was also supported by Grants-in-Aid from the Ministry of Health, Labour and Welfare, Health and Labor sciences research grants, Japan (Comprehensive Research on Cardiovas- cular Disease and Life-Style Related Diseases: H20– Junkankitou [Seishuu]–Ippan–013; H23–Junkankitou [Seishuu]–Ippan–005); an Intramural Research Fund (22-4-5) for Cardiovascular Diseases of the National Cerebral and Cardiovascular Center; Comprehensive Research on Cardiovascular Diseases and Life-Style- Related Diseases (H26-Junkankitou [Seisaku]- Ippan-001) and H29–Junkankitou [Seishuu]–Ippan– 003).}
%MDPI:  We put the this sentence to funding, please confirm this.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{The authors would like to express their sincere
appreciation to Kunio Aoki and Yoshiyuki~Ohno, Professors Emeritus at
Nagoya University School of Medicine and former chairpersons of the JACC
Study. All members of JACC Study Group can be found at
\url{https://publichealth.med.hokudai.ac.jp/jacc/index.html}. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent
\begin{tabular}{@{}ll}
JACC & Japan Collaborative Cohort \\
FFQ & Food Frequency Questionnaire \\
MCMC & Markov Chain Monte Carlo \\
JAGS & Just Another Gibbs Samplers \\
AFT & accelerated failure time \\
HR & hazard ratio \\
AF & acceleration factor \\
SD & standard deviation \\
CrI & credible interval \\
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
\reftitle{References}

\begin{thebibliography}{999}
%\providecommand{\natexlab}[1]{#1}

\bibitem[Kim(2014)]{Kim2014}
Kim, J.S.
\newblock Stroke in Asia: A global disaster.
\newblock {\em Int. J. Stroke} {\bf 2014}, {\em 9},~856--857.

\bibitem[De~Goede {et~al.}(2016)De~Goede, Soedamah-Muthu, Pan, Gijsbers, and
  Geleijnse]{DeGoede2016}
De~Goede, J.; Soedamah-Muthu, S.S.; Pan, A.; Gijsbers, L.; Geleijnse, J.M.
\newblock Dairy consumption and risk of stroke: A systematic review and updated
  dose--response meta-analysis of prospective cohort studies.
\newblock {\em \mbox{J. Am. Heart Assoc}.} {\bf 2016}, {\em
  5},~e002787.

\bibitem[Yoshiike {et~al.}(2007)Yoshiike, Hayashi, Takemi, Mizoguchi, and
  Seino]{Yoshiike2007}
Yoshiike, N.; Hayashi, F.; Takemi, Y.; Mizoguchi, K.; Seino, F.
\newblock A new food guide in Japan: The Japanese food guide Spinning Top.
\newblock {\em Nutr. Rev.} {\bf 2007}, {\em 65},~149--154.

\bibitem[Saito {et~al.}(2019)Saito, Okada, Tarui, Matsumoto, and
  Takimoto]{Saito2019}
Saito, A.; Okada, E.; Tarui, I.; Matsumoto, M.; Takimoto, H.
\newblock The Association between Milk and Dairy Products Consumption and
  Nutrient Intake Adequacy among Japanese Adults: Analysis of the 2016 National
  Health and Nutrition Survey.
\newblock {\em Nutrients} {\bf 2019}, {\em 11},~2361.

\bibitem[Iso {et~al.}(1999)Iso, Stampfer, Manson, Rexrode, Hennekens,
  Colditz, Speizer, and Willett]{Iso1999}
Iso, H.; Stampfer, M.J.; Manson, J.E.; Rexrode, K.; Hennekens, C.H.; Colditz,
  G.A.; Speizer, F.E.; Willett, W.C.
\newblock Prospective study of calcium, potassium, and magnesium intake and
  risk of stroke in women.
\newblock {\em Stroke} {\bf 1999}, {\em 30},~1772--1779.

\bibitem[Sauvaget {et~al.}(2003)Sauvaget, Nagano, Allen, Grant, and
  Beral]{sauvaget2003intake}
Sauvaget, C.; Nagano, J.; Allen, N.; Grant, E.J.; Beral, V.
\newblock Intake of animal products and stroke mortality in the
  Hiroshima/Nagasaki Life Span Study.
\newblock {\em Int. J. Epidemiol.} {\bf 2003}, {\em
  32},~536--543.

\bibitem[Elwood {et~al.}(2004)Elwood, Pickering, Fehily, Hughes, and
  Ness]{Elwood2004}
Elwood, P.C.; Pickering, J.E.; Fehily, A.; Hughes, J.; Ness, A.
\newblock Milk drinking, ischaemic heart disease and ischaemic stroke I.
  Evidence from the Caerphilly cohort.
\newblock {\em Eur. J. Clin. Nutr.} {\bf 2004}, {\em
  58},~711--717.

\bibitem[Larsson {et~al.}(2009)Larsson, M{\"a}nnist{\"o}, Virtanen, Kontto,
  Albanes, and Virtamo]{Larsson2009}
Larsson, S.C.; M{\"a}nnist{\"o}, S.; Virtanen, M.J.; Kontto, J.; Albanes, D.;
  Virtamo, J.
\newblock Dairy foods and risk of stroke.
\newblock {\em Epidemiology} {\bf 2009}, {\em 20},~355.

\bibitem[Wei(1992)]{Wei1992}
Wei, L.J.
\newblock The accelerated failure time model: A useful alternative to the Cox
  regression model in survival analysis.
\newblock {\em Stat. Med.} {\bf 1992}, {\em 11},~1871--1879.

\bibitem[Ibrahim {et~al.}(2014)Ibrahim, Chen, and Sinha]{ibrahim2014b}
Ibrahim, J.G.; Chen, M.H.; Sinha, D.
\newblock Bayesian Survival Analysis.
\newblock In {\em Wiley StatsRef: Statistics Reference Online}; John Wiley \& Sons:  Hoboken, NJ, USA, %newly added information, please confirm
 2014.

\bibitem[Ohno {et~al.}(2001)Ohno, Tamakoshi, Group, et~al.]{Ohno2001}
Ohno, Y.; Tamakoshi, A.; JACC Study Group.
\newblock Japan collaborative cohort study for evaluation of cancer risk
  sponsored by monbusho (JACC study).
\newblock {\em J. Epidemiol.} {\bf 2001}, {\em 11},~144--150.

\bibitem[Tamakoshi {et~al.}(2005)Tamakoshi, Yoshimura, Inaba, Ito, Watanabe,
  Fukuda, and Iso]{Tamakoshi2005}
Tamakoshi, A.; Yoshimura, T.; Inaba, Y.; Ito, Y.; Watanabe, Y.; Fukuda, K.;
  Iso, H.
\newblock Profile of the JACC study.
\newblock {\em J.~Epidemiol.} {\bf 2005}, {\em 15},~S4--S8.

\bibitem[Tamakoshi {et~al.}(2013)Tamakoshi, Ozasa, Fujino, Suzuki, Sakata,
  Mori, Kikuchi, and Iso]{Tamakoshi2013}
Tamakoshi, A.; Ozasa, K.; Fujino, Y.; Suzuki, K.; Sakata, K.; Mori, M.;
  Kikuchi, S.; Iso, H.
\newblock Cohort profile of the Japan Collaborative Cohort Study at final
  follow-up.
\newblock {\em J. Epidemiol.} {\bf 2013}, doi:10.2188/jea.JE20120161.

\bibitem[Date {et~al.}(2005)Date, Fukui, Yamamoto, Wakai, Ozeki, Motohashi,
  Adachi, Okamoto, Kurosawa, Tokudome, et~al.]{Date2005}
Date, C.; Fukui, M.; Yamamoto, A.; Wakai, K.; Ozeki, A.; Motohashi, Y.; Adachi,
  C.; Okamoto, N.; Kurosawa,~M.; Tokudome, Y.; et al.
\newblock Reproducibility and validity of a self-administered food frequency
  questionnaire used in the JACC study.
\newblock {\em J. Epidemiol.} {\bf 2005}, {\em 15},~S9--S23.

\bibitem[{Ministry of Health and Welfare}(1992)]{eigyogenjyo}
{Ministry of Health and Welfare}.
\newblock In {\em Kokumin Eiyo No Genjyo (The National Nutrition Survey in Japan,
  1990)}; Daiichi Shuppan: Tokyo, Japan, 1992.

\bibitem[Wang {et~al.}(2015)Wang, Yatsuya, Tamakoshi, Iso, and
  Tamakoshi]{wang_milk_2015}
Wang, C.; Yatsuya, H.; Tamakoshi, K.; Iso, H.; Tamakoshi, A.
\newblock Milk drinking and mortality: Findings from the {Japan} collaborative
  cohort study.
\newblock {\em J. Epidemiol.} {\bf 2015}, {\em 25},~66--73.

\bibitem[Talaei {et~al.}(2016)Talaei, Koh, Yuan, and Pan]{Talaei_2016}
Talaei, M.; Koh, W.P.; Yuan, J.M.; Pan, A.
\newblock The association between dairy product intake and cardiovascular
  disease mortality in Chinese adults.
\newblock {\em Eur. J. Nutr.} {\bf 2016}, {\em 56},~2343--2352, doi:10.1007/s00394-016-1274-1.

\bibitem[Plummer(2003)]{Plummer2003}
Plummer, M.
\newblock JAGS: A program for analysis of Bayesian graphical models using Gibbs
  sampling. In~Proceedings of the 3rd international workshop on distributed statistical computing, Vienna, Austria, 20--22 March 2003.
%newly added information, please confirm

\bibitem[{R Core Team}(2020)]{RCT2020}
{R Core Team}.
\newblock {\em R: A Language and Environment for Statistical Computing};
\newblock R Foundation for Statistical Computing: Vienna, Austria,  2020.

\bibitem[Lunn {et~al.}(2009)Lunn, Spiegelhalter, Thomas, and Best]{Lunn2009}
Lunn, D.; Spiegelhalter, D.; Thomas, A.; Best, N.
\newblock The BUGS project: Evolution, critique and future directions.
\newblock {\em Stat. Med.} {\bf 2009}, {\em 28},~3049--3067.

\bibitem[Brooks and Gelman(1998)]{Brooks1998}
Brooks, S.P.; Gelman, A.
\newblock General methods for monitoring convergence of iterative simulations.
\newblock {\em J. Comput. Graph. Stat.} {\bf 1998},
  {\em 7},~434--455.

\bibitem[Dehghan {et~al.}(2018)Dehghan, Mente, Rangarajan, Sheridan, Mohan,
  Iqbal, Gupta, Lear, Wentzel-Viljoen, Avezum, et~al.]{dehghan2018association}
Dehghan, M.; Mente, A.; Rangarajan, S.; Sheridan, P.; Mohan, V.; Iqbal, R.;
  Gupta, R.; Lear, S.; Wentzel-Viljoen,~E.; Avezum, A.; et al.
\newblock Association of dairy intake with cardiovascular disease and mortality
  in 21 countries from five continents (PURE): A prospective cohort study.
\newblock {\em  Lancet} {\bf 2018}, {\em 392},~2288--2297.

\bibitem[Kondo {et~al.}(2013)Kondo, Ojima, Nakamura, Hayasaka, Hozawa,
  Saitoh, Ohnishi, Akasaka, Hayakawa, Murakami, et~al.]{kondo2013consumption}
Kondo, I.; Ojima, T.; Nakamura, M.; Hayasaka, S.; Hozawa, A.; Saitoh, S.;
  Ohnishi, H.; Akasaka, H.; Hayakawa, T.; Murakami, Y.; et al.
\newblock Consumption of dairy products and death from cardiovascular disease
  in the Japanese general population: The NIPPON DATA80.
\newblock {\em J. Epidemiol.} {\bf 2013}, {\em 23},~47--54.

\bibitem[Umesawa {et~al.}(2008)Umesawa, Iso, Ishihara, Saito, Kokubo, Inoue,
  and Tsugane]{umesawa2008dietary}
Umesawa, M.; Iso, H.; Ishihara, J.; Saito, I.; Kokubo, Y.; Inoue, M.; Tsugane,
  S.
\newblock Dietary calcium intake and risks of stroke, its subtypes, and
  coronary heart disease in Japanese: The JPHC Study Cohort I.
\newblock {\em Stroke} {\bf 2008}, {\em 39},~2449--2456.

\bibitem[Iacoviello {et~al.}(2018)Iacoviello, Bonaccio, Cairella, Catani,
  Costanzo, D'Elia, Giacco, Rendina, Sabino, Savini, et~al.]{Iacoviello2018}
Iacoviello, L.; Bonaccio, M.; Cairella, G.; Catani, M.V.; Costanzo, S.; D'Elia,
  L.; Giacco, R.; Rendina,~D.; Sabino,~P.; Savini, I.; et al.
\newblock Diet and primary prevention of stroke: Systematic review and dietary
  recommendations by the ad~hoc Working Group of the Italian Society of Human
  Nutrition.
\newblock {\em Nutr. Metab. Cardiovasc. Dis.} {\bf 2018},
  {\em 28},~309--334.

\bibitem[Chiba {et~al.}(2012)Chiba, Itoh, Tabuchi, Ooshima, Satou, and
  Ezaki]{Chiba2012}
Chiba, T.; Itoh, T.; Tabuchi, M.; Ooshima, K.; Satou, T.; Ezaki, O.
\newblock Delay of stroke onset by milk proteins in stroke-prone spontaneously
  hypertensive rats.
\newblock {\em Stroke} {\bf 2012}, {\em 43},~470--477.

\bibitem[Singh {et~al.}(2016)Singh, Pezeshki, Zapata, Yee, Knight, Tuor, and
  Chelikani]{singh2016diets}
Singh, A.; Pezeshki, A.; Zapata, R.C.; Yee, N.J.; Knight, C.G.; Tuor, U.I.;
  Chelikani, P.K.
\newblock Diets enriched in whey or casein improve energy balance and prevent
  morbidity and renal damage in salt-loaded and high-fat-fed spontaneously
  hypertensive stroke-prone rats.
\newblock {\em  J. Nutr. Biochem.} {\bf 2016}, {\em
  37},~47--59.

\bibitem[Singh {et~al.}(2020)Singh, Zapata, Pezeshki, Knight, Tuor, and
  Chelikani]{Singh2020}
Singh, A.; Zapata, R.C.; Pezeshki, A.; Knight, C.G.; Tuor, U.I.; Chelikani,
  P.K.
\newblock Whey Protein and Its Components Lactalbumin and Lactoferrin Affect
  Energy Balance and Protect against Stroke Onset and Renal Damage in
  Salt-Loaded, High-Fat Fed Male Spontaneously Hypertensive Stroke-Prone Rats.
\newblock {\em  J. Nutr.} {\bf 2020}, {\em 150},~763--774.

\bibitem[Tokajuk {et~al.}(2019)Tokajuk, Zakrzeska, Chabielska, and
  Car]{tokajuk2019whey}
Tokajuk, A.; Zakrzeska, A.; Chabielska, E.; Car, H.
\newblock Whey protein concentrate limits venous thrombosis in rats.
\newblock {\em Appl. Physiol. Nutr. Metab.} {\bf 2019}, {\em
  44},~907--910.

\end{thebibliography}

%\begin{thebibliography}{999}
% Reference 1
%\bibitem[Author1(year)]{ref-journal}
%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
%\bibitem[Author2(year)]{ref-book}
%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
%\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
% \reftitle{References}
% \externalbibliography{yes}
% \bibliography{milk.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2020-09-05 Paperfolder/MDPI_submission/proofreading/nutrients-903270.tex
typos in the affiliation

@@
 % School of Medicine, \hl{Nagakute}, Japan; linys@aichi-med-u.ac.jp (Y.L.); tsasa@aichi-med-u.ac.jp (T.S.); ksayo@aichi-med-u.ac.jp (S.K.); kikuchis@aichi-med-u.ac.jp (S.K.)\\
-$^{3}$ \quad Departmet of Public Health, Fujita Health University School
-of Medicine, Toyoake, Japan; %yatsuya@fujita-hu.ac.jp\\
+$^{3}$ \quad Department of Public Health, Fujita Health University School
+of Medicine, Toyoake, Japan; \\%yatsuya@fujita-hu.ac.jp\\
 $^{4}$ \quad Public Health, Department of Social Medicine, Osaka
-University Graduate School of Medicine, Osaka, Japan; %iso@pbhel.med.osaka-u.ac.jp\\
+University Graduate School of Medicine, Osaka, Japan;\\ %iso@pbhel.med.osaka-u.ac.jp\\
 $^{5}$ \quad Department of Public Health, Hokkaido University, Faculty
-of Medicine, Sapporo, Japan; %tamaa@med.hokudai.ac.jp\\
+of Medicine, Sapporo, Japan;\\ %tamaa@med.hokudai.ac.jp\\
 }
